### 2018-07-10 abstract.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\begin{abstract}

The agenda-setting theory is a practical framework in order to understand the role of mass media on a society. The theory treats mass media as a very important actor that is able to make people think about, and in many cases how to think about certain topics.  
When the media successes in this task, we say that the media \textit{set the
agenda.}
In this work we study the agenda of Argentinian newspapers in comparison with public's interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time.We look for characterizing the differences and similarities over time between what what we call the Media Agenda and the Public Agenda.
On the other hand, we aim to detect coverage bias among the newspapers involved in the analysis in the emerging topics. \\

\end{abstract}

### 2018-07-10 appendix/appendix.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\appendix
\label{sec:appendix}

\section{Comparison with other topic model}

\par In this section we apply other topic model, Latent Dirichlet Allocation \cite{blei2003latent} (LDA), to our corpus and compare its results to the shown in this paper. Due to the increasingly use of LDA, we think that a few words about the performance of LDA in our work is necessary.

\par Naturally the topics found with LDA may not coincide with the NMF ones.
However, one expects that the corpus under studying should be in some manner robust to the election of the topic model.
On the other hand, as was discussed in \cite{o2015analysis}, NMF can be a more suitable topic modeling method in certain domains, in the way that it produces more coherent topics, while LDA tends to return higher levels of generality and redundancy. Topic coherence is defined as the semantic interpretability of the terms used to describe a particular topic, although the coherence of a topic may depend on the end user's expectations.

\par We define a simple coherence measure defined in equation \ref{eq:topic_coherence}, where $d_{ij}$ is the number of documents where the term $i$ and term $j$ appear simultaneously, and $d_{x}$ is the number of documents where appears the term $x$. The summation is over the $N$ top terms of the topic.
It's important to note that if two terms have no co-occurrences, the contribution to the summation is zero, and if these ones appear only together the contribution is one.
A topic with higher coherence is a topic where the terms that define it co-occurrence frequently.

\begin{equation}
TC = \sum_{i < j}^N \frac{2d_{ij}}{d_i + d_j}
\label{eq:topic_coherence} 
\end{equation}

\par We perform a decomposition into 10 topics using LDA with the python module \emph{gensim} \cite{rehurek_lrec}, which allow us to modify the number of times the corpus is read, improving the coherence of the topics.
Unlike to what we see with NMF, the LDA's performance depends strongly on the initial condition of the algorithm. After 10 iterations, we chose the one with highest mean topic coherence, and compared this with the NMF results.

\par In figure \ref{fig:temporal_profiles_nmf_lda} we show the temporal profiles of topics \emph{Elections} and \emph{Missing Person} for both NMF and LDA. The association between topic models was simply made by looking at the topics which share common keywords.
As can be seen from the figure and the table \ref{table:correlation_nmf_lda}, those LDA topics which can be linked to NMF ones or to a combination of these, show a temporal profile highly correlated.

\par Nevertheless, LDA returns other topics which can not be directly associated, some of them composed of very general words. 
By keeping only those topics which can be associated with NMF and re-defining the Media Agenda over this topic space with reduced dimension, we observed similar results by both methods.  
The same procedure is proposed in absence of an alternative topic model to which make the comparison: Keep only those topics easily interpretable and define the Agendas over this reduced space.

\begin{figure}
\centering
\includegraphics[scale = 0.4]{images/FigA2.pdf}
\includegraphics[scale = 0.4]{images/FigA1.pdf}
\caption{Temporal profiles of topics \emph{Elections} (left) and \emph{Missing Person} (right) for both LDA and NMF. All the topics found by applying NMF have a highly correlated counterpart in LDA.} 
\label{fig:temporal_profiles_nmf_lda}
\end{figure}

\input{appendix/table_correlation_nmf_lda}

### 2018-07-10 appendix/table_correlation_nmf_lda.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{llc}
\toprule
& Correlation between NMF and LDA \\
\midrule
Elections & \textbf{0.98} \\
Missing person & \textbf{0.99} \\
Former Planning minister + Former Vice-President & \textbf{0.89} \\
Current President & \textbf{0.94} \\
Social leader & \textbf{0.94} \\
Prosecutor's death & \textbf{0.83} \\
\bottomrule
\end{tabular}}
\caption{Correlation between the temporal profiles of the topics found in NMF and associated topics in LDA.}
\label{table:correlation_nmf_lda}
\end{table}

### 2018-07-10 conclusions.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\section{Conclusions}

\par The study of Mass Media, and in particular the agenda setting theory, can be empowered by the used of data mining or machine learning algorithms. 
In this work, through the implementation of a topic detection algorithm we could describe the Agenda of the Media as a distribution which evolves over time and which is defined in a topic's space which emerges from the analysis of the corpus.
This gave us an insight of how we can construct and follow the Public's interests, the Public Agenda, in order to compare with the Media Agenda, i.e. Media interests. 
\par Given the Agendas, we found that the Public one is usually less diverse than the Media, showing that when there is a very attractive topic, the audience focus on this one, when the Media has to cover the other too. 
On the other hand, the measurement of distances between Agendas can be employed to rapidly detect periods when the Public may have an independent behavior respect to the Media. The methodology implemented here also allow us to detect coverage bias in newspapers and gave us a first approximation in the theory of framing. 
\par We hope that some of the elements studied here will give us insights at the time of proposing a mathematical model about Mass Media and Public interaction. Future works may include a more systematic study and its extension to international Media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitave analysis about causation.

### 2018-07-10 context.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\section{Context}
\label{sec:Context}

\subsection{\emph{Elections}}
\par Two legislative elections were celebrated during the period in great part of the Argentina: Primary elections on August 13th and the general elections on October 22th. 
A special focus was put on the elections in the Buenos Aires province, where the former President \emph{Cristina Fernández de Kirchner} participated as a senator candidate representing the alliance \emph{Unidad Ciudadana}, confronting to the alliance \emph{Cambiemos}, which is the alliance of the current President \emph{Mauricio Macri} and the current governor of Buenos Aires province, \emph{Maria Eugenia Vidal}.

\subsection{Current President}
\par \emph{Mauricio Macri} is the current Argentinian President, since December 2015. 
Most articles in political sections are logically devoted to him under different contexts.
However, it is important to point out that during the period analyzed, and specially after the general elections of October 22th, a controversial labour reform promoted by the government was been discussing.

\subsection{\emph{Missing Person}}
\par \emph{Santiago Maldonado} vanished on August 1st after a minor clash between the Gendarmerie (Border Guards) and a group of Mapuches, which recognize as themselves the original population of an area in the Patagonia.
Since that event, the \emph{Mauricio Macri}'s administration was accused by several people as the responsible of a \textbf{forced disappearance}. 
\par A very massive campaign in social media took place on August 26th, under the motto "Where is Santiago Maldonado?", followed by two massive protest marches to the \emph{Plaza de Mayo} took place on September 1st and October 1st, which the first one had a great repercussion due to several incidents that took place during the march.
\par The body of \emph{Santiago Maldonado} was found on 17th October in the \emph{Chubut} river, near the place where he was seen the last time, and the autopsy report told that \emph{Santiago Maldonado} had died from ‘asphyxia after being submerged,’ with no injuries on his body. 
However the responsability of the current administration is still being discussed.

\subsection{\emph{Former Planning minister} and \emph{Former Vice-President}}

\par \emph{Julio de Vido} was the Planning minister during the administration of \emph{Nestor Kirchner} and \emph{Cristina Fernandez de Kirchner} (2003-2015). In 2015, he was elected to integrate the Chamber of Deputies, which finally voted to strip \emph{De Vido} of his congressional immunity over corruption allegations and was inmmediatly jailed on October 27th.

\par \emph{Amado Boudou} was the Vice-President of the \emph{Cristina Kirchner}'s administration.
\emph{Boudou} was arrested on November 3th on charges including money-laundering and hiding undeclared assests.

\subsection{\emph{Social leader} and \emph{Prosecutor's death}}

\par \emph{Milagro Sala} is an indigenous leader’s. 
She has been incarcerated under pre-trial detention ever since she was first detained in January 2016. She faces allegations of embezzlement related to government funding for housing projects managed by Túpac Amaru, her social organization.
Sala accused the government of "violating her human rights", and several people think that she is a political prisoner of the \emph{Mauricio Macri} administration.

\par \emph{Alberto Nisman} was a special prosecutor who were investigating the 1994 terror attack on the Argentine Israeli Mutual Association (AMIA), until his suspicious death on January 2015.
During the period analyzed in this work, a team of experts led by the Gendarmerie (Border Guard) concluded that late prosecutor's death may have been a case of murder, not suicide.

### 2018-07-10 description.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\section{Description of the work}
\label{sec:description}

\par We analyzed a corpus of news' articles that were published between July 31th and November 5th in the section \emph{Politics} of the electronic editions of the Argentinian newspapers \emph{Clarín}, \emph{La Nación}, \emph{Página12}, and the news portal \emph{Infobae}.
The first two lead the sale of printed editions in \emph{Buenos Aires} city, but \emph{Clarín} reaches roughly two times the readers of \emph{La Nación}, and ten times the readers of \emph{Página 12} \footnote{www.ivc.org.ar}. On the other hand, \emph{Infobae} has the website with more visitors, above the websites of \emph{Clarín} and \emph{La Nación} \footnote{https://www.alexa.com/topsites/countries/AR}.

\par The corpus analyzed is constituted by 2908 politics articles of \emph{Clarín}, 3565 of \emph{La Nación}, 3324 of \emph{Página 12}, and 2018 of \emph{Infobae}. Except \emph{Página 12}, all articles were taken from the section \emph{Política} of the respective news portal, while the articles which belong to \emph{Página 12} were taken from the section \emph{El país}.

\par The analysis made basically consist of topic detection over the corpus' articles in order to describe it as a set of topics which evolve over time. Topic detection is a powerful computational technique that allows us to analyze a big amount of texts that can be impossible otherwise \cite{griffiths2004finding}. For a careful description of the methodology implemented please see section \ref{sec:Methodology}. 
This methodology not only gives us the evolution over time of the topics, but also a set of keywords that allow us to interpret and understand what the topics are talking about. 
\par We take advantage of topics' keywords on the one hand by making queries to the \emph{Google Trends} tool and getting the relative size of \emph{Google} searches that people made about the identified topics, and in the other hand by making queries to the advance search tool in the social media \emph{Twitter} in order to get the relative amount of tweets related. 
We take these two tools as a way to measure audience interests in the space of topics defined by the Media.

\par After all this proceedings, which we are going to give more details during the description and discussion of the work, we obtain two objects of study which we call the \textbf{Media Agenda (MA)}, and the \textbf{Public Agenda (PA)}, which at the same time has two faces, one giving by \textbf{Google Trends (Gt)} and the other by \textbf{Twitter (Tw)}. 
In part of the analysis, the Media Agenda will even be described by the agendas of each of the newspapers (or portal news) taken into consideration. 
After normalization, all agendas are described as a time dependent distribution over the topic's space, where the time scale is day by day.
Therefore the agendas give us the relative importance of a given topic respect the other (i.e. it does not give us absolute values such as the number of titles or tweets associated).

### 2018-07-10 discussion/newspapers.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\subsection{Media Agenda: differences between newspapers}

\par In this section we leave aside the Public Agenda and we study how the Media agenda varies when one consider the newspapers separately. 
In figure \ref{fig:news_agenda} we show the bump charts which belongs to each newspaper analogously to figure \ref{fig:all_agenda}.
The topics are the same introduced in the wordclouds of figure \ref{fig:topics_wordclouds}, but at computing the topics' weights the articles are separated by newspaper. 
We also show the radar plots showing the average distribution, as made in figure \ref{fig:topics_wordclouds}. 
\par In figure \ref{fig:news_agenda} we can see in a qualitative way the slightly differences between the newspapers' agendas.
For instance, we can see how \emph{Página 12} gave more importance to the topics \emph{Missing person} and \emph{Social leader}, while it did not pay too much attention to the \emph{Former Planning minister} as the others did.

% Jensen shannon distance of Dynamic way
\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{images/Fig5.pdf}
\caption{\textbf{Bump charts of newspapers' Agenda and radar plot of the average distributions.} The figure shows, in a qualitative way, the differences between the mentioned agendas, for instance, the greater interest of Página 12 (P12) in the \emph{Missing person}’s topic and its slightly lesser interest in the \emph{Former Planning minister} respect to the other newspapers.}
\label{fig:news_agenda}
\end{figure}

\subsubsection{Independent behavior}

\par In other to detect an independent behavior of a newspaper respect the others we again calculate the Jensen-Shannon distance between the newspapers agenda and the Media Agenda.
Note that this is the distance between the distributions of figure \ref{fig:news_agenda} and the top panel of figure \ref{fig:all_agenda}.
\par In figure \ref{fig:jensen_shannon_news} we show the Jensen-Shannon distance is a function of time.
We detect three points as outliers, although we discard the point \textbf{(b)} due to the low information of \emph{Infobae} in that period. 
The other two points belongs to a difference between \emph{Página 12} and the other newspapers. 
We interpret that the coverage of the topic \emph{Missing person} is the principal cause of the outliers.
\emph{Página 12} paid more attention to it than the Media Agenda at point \textbf{(a)} when the first notices of the Santiago Maldonado's disappearance before the primary elections, and in point \textbf{(c)} when a march two months after the disappearance took place, and had not the same coverage as the other march a month before (see section \ref{sec:Context}). Also, in point \textbf{(c)}, it can be seen a greater coverage of \emph{Página 12} in the topic \emph{Social leader} while the others seemed to be more interested in the topic \emph{Former Vice-President}.

% Jensen shannon distance of Dynamic way
\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{images/Fig6.pdf}
\caption{\textbf{Jensen Shannon distance between the newspapers’ agenda and the Media Agenda as a function of time.} \emph{Página 12} (P12) shows the more different behavior, motivated again by its interest in the \emph{Missing person} and \emph{Social leader} topics as can be seen in the radar plots which belongs to points (a) and (c). 
The anomalous behavior of \emph{Infobae} (Inf) at point (b) is due to few articles around that date in our database, therefore we ignore its radar plot.}
\label{fig:jensen_shannon_news}
\end{figure}

\subsubsection{Coverage bias}

\par The greater coverage in the topic \emph{Missing person} by \emph{Página 12} is even more clear if we inspect the temporal profile of the topic and compare the coverage given by each newspaper. A difference in the coverage is what it is called \emph{coverage bias}.
In figure \ref{fig:topics_temporal_profiles} we show the temporal profile of the topic \emph{Missing person} (panel (a)) and the topic \emph{Former Planning minister} in panel (b), as an example where the behavior is the opposite, as can be seen below.

\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{images/Fig7.pdf}
\caption{\textbf{Relative weight of the topics (a) \emph{Missing person}, and (b) \emph{Former Planning Minister}, and wordclouds of frequent newspapers' keywords}. We interpreted the differences shown in certain periods as an indicator of coverage bias. For instance, in figure (a) Página 12 pays a greater attention in the first days. In the wordclouds, we show which of the defining words are more frequently used by the corresponding newspaper. Most of them are less informative, but other seems to represent a first approximation in the study of framing.}
\label{fig:topics_temporal_profiles}
\end{figure}

\par From panel (a) of figure \ref{fig:topics_temporal_profiles}, we can see a more coverage of \emph{Página 12} respect the other newspapers at the first of the period. We can for instance quantify this difference by the median of the signals. If we focus in the period between July 31th and August 27th, the median of the topic relative weight for \emph{Página 12} is roughly 0.14 and this is statistically significant larger ($p < 10^{-7}$) than other medians, which are lower than 0.05.
Analyzing the same period, but in panel (b), we again can show that the median in \emph{Página 12}, which is roughly 0.01, is lower than the others, which oscillate around 0.05 ($p<10^{-3}$)
This quantification is proposed as method of studying coverage bias in the context of the methodology implemented in our work.

\par Finally, in figure \ref{fig:topics_temporal_profiles} we also show wordclouds of topic's keywords but separate those that are most frequent mentioned by each newspaper, filtering the words that are common to all and basically define the factual details of the topic.
Although most words are less informative, some are interesting to inspect, for instance, the word \emph{represión} (repression) when \emph{Pagina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (Fernández de Kirchner) which is employed by all newspapers except \emph{Pagina 12} when talk about the topic \emph{Former Planning minister} (see section \ref{sec:Context}).
We don't go farther but we think that a more deeply study of topics' keywords is a first approximation in the study of framing, which will constitute the core of futures works.

### 2018-07-10 discussion/qualitative.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\par As was mentioned above, the starting point of our analysis is the topic decomposition of the corpus.
We chose to decompose the corpus in 10 topics, which three of them we interpret to be talking about the same macro-topic which we called \emph{Elections}, while other two were intereted as talking about other macro-topic called \emph{Missing person}, as can be seen below. 
The meaning of the topics or macro-topics are more explained in section \ref{sec:Context}. 
So the final description of the agendas is made with only 7 topics.
We opted for choosing this arbitrary number of topics in order to describe the corpus with as least information as possible, but it is not more than an arbitrary decision, validated in some manner by our knowledge of the corpus.
After the proceedings describe in section \ref{sec:Methodology}, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, and all their derivations, as time-dependent distributions.

\subsection{Media and Public agenda: a qualitative approach}

\par In figure \ref{fig:topics_wordclouds} we show the radar plots of the average distributions of the \textbf{MA} and the \textbf{PA} discriminated by \textbf{GT} and \textbf{Tw} together with the introduction of the topics' names.
A radar plot is an alternative of histograms that allows the visual comparison of distributions easier.
In this figure we also show the wordclouds of the keywords that define each topic, where the size of the word belongs to the importance in the topic's definition given by the topic detection algorithm. In green color, we point out the words involved in the Google Trends and Twitter queries in order to construct the Public Agenda. The queries employed are also specified in table \ref{table:gt_all_correlation} together with the linear correlation between the topics' temporal profiles that form the Public Agenda and their counterparts in the Media Agenda.

\par On the other hand, in figure \ref{fig:all_agenda} we show a bump chart of the Agendas, which is the dynamical representation of the Agendas of figure \ref{fig:topics_wordclouds}. 
A bump chart provides us a very useful visualization tool for displaying the relative weight of the topics and at the same time their ranking, putting on the top the most important topic at a particular date.
In figure \ref{fig:all_agenda} we also point out some important events related to the topics.

% Wordclouds
\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{images/Fig1.pdf}
\caption{\textbf{Radar plots of the Media and Public Agenda average distributions and topics' wordclouds.} The Public Agenda is represented either by Google Trends (Gt) and Twitter (Tw). 
Topics’ names are introduced together with the wordclouds containing the most important keywords involved in the definition of each topic.
In green color we show those included in the Google Trends and Twitter queries (see table \ref{table:gt_all_correlation}) and therefore in our construction of the Public Agenda.
}
\label{fig:topics_wordclouds}
\end{figure}

% Global Agenda figure!!!
\begin{figure}[h]
\includegraphics[width = \textwidth]{images/Fig2.pdf}
\caption{\textbf{Bump graph of the Media Agenda (MA) and Public Agenda extracted from Google Trends (Gt) and Twitter (Tw).} Some important events related to the topics are pointed out. The curves’ width and their ordering are related to the topics’ relative weight.}
\label{fig:all_agenda}
\end{figure}

\footnote{Due to different characteristics in the search tool of Twitter, we adapted the queries employed here but preserving the at least at we can the most important keywords. The queries employed by topic were: \\
Elections: elecciones + cambiemos + kirchner + massa + randazzo \\
Missing person: maldonado + otranto + gendarmeria + desaparicion \\
Former Planning minister: vido + desafuero + minnicelli + baratta \\
Current President: macri + cgt + laboral +  triaca \\
Social leader:  sala + cidh + tupac + amaru + pullen + llermanos + morales \\
Prosecutor’s death: nisman + amia + memorandum + timerman +  bonadio \\
Former Vice-President:  boudou + ciccone +  lijo + vandenbroele + carmona
}

% Table with queries and correlations
\input{discussion/table_gt_queries_correlation}

\par The figures introduced above show in a qualitative way the differences between the agendas, and the dynamics of the topics, i.e. the range of dates in which a given topic was an important one, for which topic it was replaced, and so on. 
We can see, for instance in the radar plot of figure \ref{fig:topics_wordclouds}, a more interest of the audience in the topic \emph{Missing person} than the Media, or inversely in the topic \emph{Prosecutor's death}, when we see all the period analyzed as a whole. 
Also we can observe a great similarity between \textbf{Gt} and \textbf{Tw} agendas which form the Public Agenda.
\par On the other hand, the linear correlations of table \ref{table:gt_all_correlation} are in all cases positive and statistically significant, which we interpret as a form of validation of the topics found in the corpus and the keywords that describe it. 
We expected that the Media's and public's interest should generally follow a similar a pattern due to the external events, although the periods where those differ are of particular interest for us. 
A non positive (or a non significant) correlation may imply that we are not properly detecting the keywords or features that describe a particular topic, so the Google Trends' or Twitter's pattern would not be able to reflect a similar behavior that its counterpart in the Media.

### 2018-07-10 discussion/quantitative.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\subsection{A quantitative approach}

\subsubsection{Agenda diversity}

% Agenda diversity

\par In order to quantify the similarities and differences between the Media Agenda and the Public Agenda, we start by asking how is the distribution of each agenda among the topic's space. In particular, we measure how diverse is each agenda. Following \cite{boydstun2014importance}, we calculate the normalized Shannon's entropy ($H$, see eq.\ref{eq:shannon_entropy}) in order to measure the diversity of the \textbf{MA} and \textbf{PA}.
\par In figure \ref{fig:shannon_entropy_agendas} we can see the value of $H$ as a function of time. We can see that there are periods where the diversity is lower than the usual, more notorious in the Public Agenda giving by \textbf{Gt}. 
We are going to pay attention to four dates in the Public Agenda, which three detected as outliers of the typical behavior, two from \textbf{Gt} and one from \textbf{Tw}. 
\par A small value in the diversity is due to the fact that the most important topic attracts practically all the attention of the public or the media.
In the radar plots included also in figure \ref{fig:shannon_entropy_agendas} we can see that two of the points (\textbf{a} and \textbf{d}) belong to the topic \emph{Elections} and coincide with the primary and general legislative elections that took place in August 13th and October 22th. 
In all the agendas these points where detected as outliers except point (d) in Twitter Agenda: By inspecting the radar plot the diversity in this agenda can be the result of the association between the topic \emph{Elections} and the \emph{Current President}.
Discussions in Twitter about elections appear also in point (c), when the other agendas seems to be more diverse. 
On the other hand, we inspect the point (b) despite not being detected as a outlier, which belong to the topic \emph{Missing person} and related to a month after the disappearance of Santiago Maldonado (see section \ref{sec:Context}). 
We emphasize the discussion about this topic because we see interesting facts that appear along the analysis.

\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{images/Fig3.pdf}
\caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda show a less diverse behavior than the Media Agenda as can be seen in the left figure. The horizontal lines are the lower inner fences of each signal in order to identify outliers. The related radar plots shows that those dates when the agenda has a low diversity, the most important topic catches the most public’s attention}
\label{fig:shannon_entropy_agendas}
\end{figure}

\par From the measure of $H$ we can also see that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
Specifically $H_{Gt} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
However from figure \ref{fig:shannon_entropy_agendas} we can see that \textbf{Gt} shows more abrupt falls in the diversity in response to specific events.
We conclude that its an important fact about audience behavior: given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus more in the most important topic than the Media can do, maybe due to editorial decisions.

\subsubsection{Public Agenda's distance}

% Jensen-Shannon distance between PA and MA

\par The measurement of the Shannon's entropy made above is an independent property of each distribution. 
Here we directly compare the Agendas by computing the Jensen-Shannon distance. We again identify outliers and aim to interpret them.
In figure \ref{fig:jensen_shannon_gt} we show the Jensen-Shannon distance as a function of time. We inspect three points that seems to be of particular interest. In all cases, the radar plots shows that a greater distance is associated with a more interest of public in the topic \emph{Missing person}. 
\par Points \textbf{(c)} and \textbf{(d)} shows that both the public and the Media are interest in that topic, but the Media have to cover other topics, so the distance value can be seen as a derivation of the diversity effect discussed in the last section.
However points \textbf{(a)} (we take this point due to be a extreme of the distance in the middle of the period despite not being an outlier) and \textbf{(b)} seem to show an interest of the public in the topic \emph{Missing person} which it is not reflected in the Media. 
In figure \ref{fig:all_agenda} we can see that this topic reached the first place in public's interest in both \textbf{Gt} and \textbf{Tw} before that in the Media. We associate this fact with a campaign made in social media like Facebook and Twitter in August 26th, that paid for the appearance of Santiago Maldonado and had a great repercussion, maybe at first underestimated by the Media (see section \ref{sec:Context}). 
\par It is important to recall that it is our interpretation based on the knowledge of the context, and that we are not studying causality (we will say a few words about it in section \ref{sec:who_sets}), i.e. we can't say, for instance, that in this case the Public Agenda set the Media Agenda. 
However, the Jensen-Shannon distance, in conjunction with the measurement of the agenda diversity given by the Shannon entropy, give an insight of independent behavior of the Public and the Media, and its identification can be a starting point to study the Media reaction to a change in audience's interests.

\begin{figure}[h]
\includegraphics[width = \textwidth]{images/Fig4.pdf}
\caption{\textbf{Jensen Shannon distance between the Media Agenda and the Public Agenda as a function of time} (with upper inner fences pointed out). The larger distances are due to a greater interest of the audience in the topic \emph{Missing person} which leads to lesser interest in the other topics, which the Media has to cover, maybe except in points (a) and (b) where the Media seems not to anticipate the public interest in the mentioned topic.}
\label{fig:jensen_shannon_gt}
\end{figure}

### 2018-07-10 discussion/table_gt_queries_correlation.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{llccc}
\toprule
& Google Trends query & Correlation MA and Gt & MA and Twitter & Gt and Twitter \\ 
\midrule
Elections & elecciones + cambiemos + cristina kirchner + massa + randazzo & \textbf{0.81} & \textbf{0.59} & \textbf{0.75} \\
Missing person & santiago maldonado + juez otranto + patricia bullrich + gendarmería + desaparición forzada & \textbf{0.68} & \textbf{0.76} & \textbf{0.89} \\
Former Planning minister & de vido + desafuero + ministro de planificación + minnicelli + baratta & \textbf{0.92} & \textbf{0.82} & \textbf{0.87} \\
Current President & mauricio macri + cgt + reforma laboral + peña + triaca & \textbf{0.77} & \textbf{0.75} & \textbf{0.63} \\
Social leader & milagro sala + cidh + tupac amaru + pullen llermanos + morales & \textbf{0.49} & \textbf{0.25(*)} & \textbf{0.57} \\
Prosecutor's death & nisman + amia + memorándum con irán + timerman + juez bonadio & \textbf{0.56} & \textbf{0.59} & \textbf{0.75} \\
Former Vice-President & amado boudou + ciccone + ariel lijo + vandenbroele + núñez carmona & \textbf{0.90} & \textbf{0.92} & \textbf{0.97}\\
\bottomrule
\end{tabular}}

\caption{Queries performed in Google Trends in order to made up the Public Agenda. 
We also shown the correlation between the topics' temporal profiles of the Public Agenda and their counterpart in Media Agenda.
All correlation values are statistical significant ($p < 10^{-9}$), except (*) which is significant with $p < 0.05$.}
\label{table:gt_all_correlation}
\end{table}

### 2018-07-10 discussion/whosets.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\subsection{After all: Who sets the Agenda?}
\label{sec:who_sets}

\par The behaviour of the Media Agenda and the Public one, either by looking at Google Trends or Twitter, shows periods when there is a strong similarity, mostly in the presence of an unexpected event, and periods when seem to be unrelated.
These are mere observation that talk about the correlation between the agendas.
However the agenda-setting theory is in its nature a theory about causations:
Is the audience a passive actor who follows what Media say, or there are periods where the Media must paid attention at public's interests?
Paraphrasing the question, who sets the agenda, the Media or the audience?
In a world where social media exists and the feedback between a Media and its audience is common currency, nowadays the idea that the Media sets the agenda and the audience blindly follows it, as it's seemed to be suggested in the original work of McCombs, is a very weak one. 
\par In spite of the fact that we think that to establish a causation, i.e. the direction towards information flows, is a task that must be made with extreme care, we can not totally skip the question about causation. 
Therefore we will discuss at least in a qualitative way the \emph{Missing person} topic. 
This is the more adequate topic to be discussed because it caused a great impact in either the Media and the audience, and on the other hand, its more important related events are fully contained in the period under studying (see section \ref{sec:Context}).
Therefore we can study the way the topic acquired the importance showed along this work.
\par In figure \ref{fig:Maldonado_setagenda} we show the topic relative weight from the Public Agenda and the Media Agenda. 
After the initial news, the agendas seems to differentiate around August 16th, when the topic started to acquire more importance in the Public Agenda than in the Media, but around August 24th the topic abruptly increase in Public's interest while in the Media the reaction is slower, showing a significant peak in the plot of the discrete differences.
This date is very close to August 26th when a campaign in social media took place. After that, the Media increase its coverage about the topic.
\par Is this a case of reverse agenda-setting, i.e, when the audience set the Media Agenda? 
After all the audience get involved about this topic by the Media, so how was the coverage before those events?
By calculating the cumulative sum we can see how the coverage in a cumulative way was during the first events related to the topic. 
This measure can be seen as the numerical integrate of the temporal profiles of figure \ref{fig:topics_temporal_profiles} between the initial date and the current date. 
It is interesting to note that the newspaper which accumulate coverage during the initial stage was the minority one: \emph{Página 12}. 
Our suggestion of how the agenda was set in this particular topic is the following: one of the newspapers gave great coverage to this one, the audience magnified this in social media and also expressed its interest by reiterative Google searches, and then the rest of the Media oughted to pay attention to this behavior. This suggestion is of course a very reductive one but try to catch in a qualitative way how the information flow was.
On the other hand, behind this interpretation there are two important facts that must be mentioned: First, the disappearance of a person is a very sensible theme for the Argentinian society, and second, there are political reasons in why \emph{Página 12} was particularly interested in cover this topic while the other Media did not follow this interest.

\par We took the question about causation only in a qualitative way. 
There are different metrics that would help in this question, such as Granger causality or correlation by sliding windows. We think that this analysis must be performed with extreme care since the acquirement of the data.
With this work we aimed to provide a quantitative characterization of the behaviour of the Media and the Public but not to establish direction of causation, which we hope this to be the core of future ones.

\begin{figure}
\includegraphics[width = \textwidth]{images/Fig8.pdf}
\caption{\textbf{Agenda setting direction in Missing person's topic?}
The temporal profiles of figure (a) show that the Public increased abruptly its interest in the topic around August 24th, which belongs to the peak \textbf{(*)} shown in figure (b), where the discrete differences were computed. 
This date is also pointed out in the rest of the figures with a vertical grey line together with the asterisk. 
With the computing of the cumulative sum of figure \ref{fig:topics_temporal_profiles} and figure (a), represented as a bump chart in figure (c), we suggest that the topic was first set by \emph{Página 12} and then the Public's interest cause the coverage of the other Media.
}
\label{fig:Maldonado_setagenda}
\end{figure}

### 2018-07-10 intro/agenda_setting.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\subsection{Agenda Setting Theory}

% Introducción y descripción de agenda-setting en su nivel más básico.
\par In the famous study performed in Chapel Hill during the US presidential elections in 1968 \cite{mccombs1972agenda}, Maxwell McCombs and Donald Shaw found that those aspects of public affairs that are prominent in the news become prominent among the public.
This study is considered the founding of the agenda-setting theory, which focus in the influence of mass media in public opinion.  
From \cite{mccombs2014agenda}, \textit{``The media agenda is the pattern of news coverage over a period of days, weeks (...) for a set of issues or other topic. In other words, the media agenda is a systematic compilation of the issues or topics presented to the public that identifies the degree of emphasis on these topics.''}

\par Since the Chapel Hill research, several directions of agenda-setting were established \cite{mccombs2005look}.
In its basic stage, the theory is focus on the comparison between the topics coverage by the media and the public agenda, i.e. the topics that the public consider as priority.
It looks for answering the question if the media is able to set the public agenda, which would transform the media as an important actor in the formation of public opinion. The interaction between media and public is rather complex, for instance, \cite{mitchelstein2016brecha} shows that not necessarily the journalists and public preferences coincide.
\par With the emergency of the Internet, the end of agenda-setting were predicted due to the audience fragmentation onto multiple sources, which would virtually lead to a highly individualized agenda.
However, it is based on two assumptions that not necessarily are true: that the public spreads its attention in an homogeneous way across the multiple sources, and that the agendas of that sources are different \cite{mccombs2005look}.

% Agenda setting de segundo nivel: noticias con atributos y contextualización.
\par The basic agenda-setting sometimes is called the ``first level agenda-setting''. 
The very often quoted phrase of Bernard C. Cohen \textit{``The press may not be successful much of the time in telling people what to think, but it is stunningly successful in telling its readers what to think about.''} illustrates its object of study.
On the other hand, the ``second level agenda-setting'', sometimes called \textit{attribute agenda-setting}, studies the \textit{objects} (in a social psychology way, where an \textit{attitude object} designate a thing that an individual has an attitude or opinion about) present in the media agenda. When the media talks about an object some attributes are emphasized, and others not.

\par The ``second level agenda-setting'' is linked with \textit{framing} \cite{guggenheim2015dynamics} \cite{tsur2015frame}. 
To frame is to \textit{select some aspects of a perceived reality and make them more salient in a communicating text, in such a way as to promote a particular problem definition, causal interpretation, moral evaluation and/or treatment recommendation} (Robert Entman) \cite{mccombs2005look}.
This stage of agenda-setting theory can be summary in the phrase \textit{``the media not only can be successful in telling us what to think about, they also can be successful in telling us how to think about it.''}

% Intermedia setting-agenda: compentencia entre medios de comunicación.
\par Other interesting stage of agenda-setting concerns with the sources of media agenda, i.e. if the media set the public agenda, \textit{who sets the agenda media?} 
Within this framework, \textit{intermedia agenda-setting} observes the competition between different media and how they influence each other.
The competition between mass media for the same audience can lead to a homogenization of the agendas \cite{vargo2017networks}, which is in the opposite direction of one of the assumptions that predict the end of agenda-setting, as was mentioned before.

### 2018-07-10 intro/alternative_intro.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

--- 2018-07-10 intro/agenda_setting.tex
@@
+%PRIMERA PARTE TEORIA DE AGENDA SETTING
 \subsection{Agenda Setting Theory}
@@
 The competition between mass media for the same audience can lead to a homogenization of the agendas \cite{vargo2017networks}, which is in the opposite direction of one of the assumptions that predict the end of agenda-setting, as was mentioned before.
+
+% ACA ARRANCA LA REESTRUCTURACION NUEVA
+\subsection{Related works}
+
+\par Typical works in agenda-setting theory in any of its stages mimics the original work of McCombs \cite{mccombs1972agenda}.
+The study of the agenda is usually done in a static way, i.e., by summarizing certain issues present in news media and looking for effects in the audience \cite{brians1996campaign}\cite{gerber2009does}\cite{coleman2007young}.
+For instance, in Argentina, \cite{mitchelstein2016brecha} examines the difference between public and journalists preferences. 
+Several works by E.
+Zunino, like \cite{zunino2010cobertura} and \cite{koziner2013cobertura}, studied the coverage given by the main newspapers of particular events which have happened during the administration of Argentina’s president \emph{Cristina Fernández de Kirchner} (from 2007 to 2015), where the government started to confront with news organizations that were critical to its management as they were an opposition party \cite{mitchelstein2017information}
+
+% Algo sobre bias
+\par Other typical works are concerned with detecting bias in the media, by focusing in detecting its ideology, either by taking into account the number of mentions of a preferred political party \cite{lazaridou2016identifying}\cite{baumgartner2015all} or by identifying the ideology through the position of the media respect to certain issues or actors \cite{elejalde2018nature}\cite{sagarzazu2017hugo}.
+New trends in agenda-setting theory propose to represent ideological aspects or issues emphasized as networks like mind maps, and the basic idea is the comparison between media's knowledge representative network with its counterpart in the audience \cite{guo2012application}\cite{vu2014exploring}.
+
+\par Most work cited above follow usual methods employed in social science research.
+However, a very useful tool in the analysis of large corpus of documents which is not widely used in the agenda setting theory is unsupervised topic modeling.
+It is an alternative to the dictionary-based analysis, which is the most popular automated analysis approach \cite{guo2016big}, and allows to work with a corpus without a prior knowledge, letting the topics emerge from the data.
+Despite the popularity of this methods, we believe that there is still a lack in the employment of these ones through the lens of the agenda setting framework.
+Many works based on news corpus emphasize the performance of the topic model over a labeled corpus, focusing on the proper detection of the topics \cite{dai2010online}\cite{po2016topic}\cite{brun2000experiment}.
+The temporal profile of topics is usually embedded in the context of topic tracking \cite{hu2016news}\cite{li2017joint}, or in the recognition of emerging topics in real-time \cite{cataldi2010emerging} mostly applied to social media.
+\par Typically a dynamical description is not carried out in a set of topics but rather focused on a single issue.
+For instance, in \cite{soroka2017negativity} it is shown that the newspapers and Twitter have an opposite reaction to the changes of the unemployment rates, in \cite{guggenheim2015dynamics} the competition of frames in this case about gun control is explored,
+and in \cite{ali2018measuring} it is shown how twitter activity varies in different regions depending on the location of terrorist attacks.
+A remarkable exception is \cite{russell2014dynamics} where they work with a set of predefined issues.
+In this work the question of \emph{causality} is also faced up.
+Their study shows that sometimes the traditional media set the agenda and sometimes, the social media does.
+They show that social media is always more interested in social issues than the traditional one, and despite the existence of correlation, the social media agenda can not be seen as a \emph{slave} of the traditional media.
+
+% Presentación y descripción de nuestro trabajo
+\par In this work we propose a simple method to the study of Mass Media and audience response through topic detection algorithms.
+Our work intends to contribute another quantitative approach which complements the agenda-setting theory describe above.
+Rather than focus on a single issue or a set of independent topics, we work with the agendas (the media and the public) as an object in their own, studying their evolution over time.
+On the other hand, we aim to take an insight about Media dynamics and Public response in order to create useful tools at the time of constructing mathematical models about the interaction between Media and Public, investigation that we started in \cite{pinto2016setting}.

### 2018-07-10 intro/argentinian_newspapers.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\subsection{Argentinian works}

% Argentinian or newspapers in spanish
\par In Argentina, the role of Mass Media has been particularly discussed during the administration of Argentina’s president \emph{Cristina Fernández de Kirchner} (from 2007 to 2015), where the government started to confront with news organizations that were critical to its management as they were an opposition party \cite{mitchelstein2017information}. Several works by E. Zunino, like \cite{zunino2010cobertura} and \cite{koziner2013cobertura}, studied the coverage given by the main newspapers of particular events which have happened during that period. 
On the other hand, Sagarzazu studied the bias present in the argentinian media respect to \emph{Hugo Chávez Frias} as a reflection of the ideology of the respective newspapers  \cite{sagarzazu2017hugo}.

### 2018-07-10 intro/our_work.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

--- 2018-07-10 intro/agenda_setting.tex
@@
-\subsection{Agenda Setting Theory}
+\subsection{Our contribution}
 
-% Introducción y descripción de agenda-setting en su nivel más básico.
-\par In the famous study performed in Chapel Hill during the US presidential elections in 1968 \cite{mccombs1972agenda}, Maxwell McCombs and Donald Shaw found that those aspects of public affairs that are prominent in the news become prominent among the public.
-This study is considered the founding of the agenda-setting theory, which focus in the influence of mass media in public opinion.  
-From \cite{mccombs2014agenda}, \textit{``The media agenda is the pattern of news coverage over a period of days, weeks (...) for a set of issues or other topic.
-In other words, the media agenda is a systematic compilation of the issues or topics presented to the public that identifies the degree of emphasis on these topics.''}
-
-\par Since the Chapel Hill research, several directions of agenda-setting were established \cite{mccombs2005look}.
-In its basic stage, the theory is focus on the comparison between the topics coverage by the media and the public agenda, i.e. the topics that the public consider as priority.
-It looks for answering the question if the media is able to set the public agenda, which would transform the media as an important actor in the formation of public opinion.
-The interaction between media and public is rather complex, for instance, \cite{mitchelstein2016brecha} shows that not necessarily the journalists and public preferences coincide.
-\par With the emergency of the Internet, the end of agenda-setting were predicted due to the audience fragmentation onto multiple sources, which would virtually lead to a highly individualized agenda.
-However, it is based on two assumptions that not necessarily are true: that the public spreads its attention in an homogeneous way across the multiple sources, and that the agendas of that sources are different \cite{mccombs2005look}.
-
-% Agenda setting de segundo nivel: noticias con atributos y contextualización.
-\par The basic agenda-setting sometimes is called the ``first level agenda-setting''. 
-The very often quoted phrase of Bernard C.
-Cohen \textit{``The press may not be successful much of the time in telling people what to think, but it is stunningly successful in telling its readers what to think about.''} illustrates its object of study.
-On the other hand, the ``second level agenda-setting'', sometimes called \textit{attribute agenda-setting}, studies the \textit{objects} (in a social psychology way, where an \textit{attitude object} designate a thing that an individual has an attitude or opinion about) present in the media agenda.
-When the media talks about an object some attributes are emphasized, and others not.
-
-\par The ``second level agenda-setting'' is linked with \textit{framing} \cite{guggenheim2015dynamics} \cite{tsur2015frame}. 
-To frame is to \textit{select some aspects of a perceived reality and make them more salient in a communicating text, in such a way as to promote a particular problem definition, causal interpretation, moral evaluation and/or treatment recommendation} (Robert Entman) \cite{mccombs2005look}.
-This stage of agenda-setting theory can be summary in the phrase \textit{``the media not only can be successful in telling us what to think about, they also can be successful in telling us how to think about it.''}
-
-% Intermedia setting-agenda: compentencia entre medios de comunicación.
-\par Other interesting stage of agenda-setting concerns with the sources of media agenda, i.e. if the media set the public agenda, \textit{who sets the agenda media?} 
-Within this framework, \textit{intermedia agenda-setting} observes the competition between different media and how they influence each other.
-The competition between mass media for the same audience can lead to a homogenization of the agendas \cite{vargo2017networks}, which is in the opposite direction of one of the assumptions that predict the end of agenda-setting, as was mentioned before.
+% Presentación y descripción de nuestro trabajo
+\par In this work we propose a simple method to the study of Mass Media and audience response through topic detection algorithms.
+Our work intends to contribute another quantitative approach which complements the agenda-setting theory describe above. 
+\par On the other hand, we aim to take an insight about Media dynamics and Public response in order to create useful tools at the time of constructing mathematical models about the interaction between Media and Public, investigation that we started in \cite{pinto2016setting}.

### 2018-07-10 intro/social_media.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\subsection{Social Media}

\par The interaction between media and public is rather complex, and the advance of social media gives new direction in the exploration of this aspect of agenda-setting theory. 
\par In \cite{russell2014dynamics} the question of \emph{causality} is faced up. Their study shows that sometimes the traditional media set the agenda and sometimes, the social media does. They show that social media is always more interested in social issues than the traditional one, and despite the existence of correlation, the social media agenda can not be seen as a \emph{slave} of the traditional media. 
\cite{soroka2017negativity} shows that the newspapers and Twitter have an opposite reaction to the changes of the unemployment rates, and for instance, in Argentina, \cite{mitchelstein2016brecha} shows that not necessarily the journalists and public's preferences coincide, by studying the most viewed articles and the home page articles in online news sites.
\par Other works study various aspects of social media, such as the danger of selective exposure \cite{feezell2017agenda}\cite{messing2014selective}\cite{bakshy2015exposure} and the role of media organization in Twitter discussions \cite{calvo2016time}\cite{malik2016macroscopic}.

### 2018-07-10 intro/topic_detection.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\subsection{Topic detection}

\par Unsupervised topic modeling is a widely used technique in the analysis of a large corpus of documents. 
It is an alternative to the dictionary-based analysis, which is the most popular automated analysis approach in social science research \cite{guo2016big}, and allows to work with a corpus without a prior knowledge, letting the topics emerge from the data. Despite the popularity of this methods, we believe that there is still a lack in the employment of these ones through the lens of the agenda setting framework.
\par As mentioned above, many works based on news corpus emphasize the performance of the topic model over a labeled corpus, focusing on the proper detection of a given topic \cite{dai2010online}\cite{po2016topic}\cite{brun2000experiment} and without taking into account temporal information. 
The temporal profile of topics is usually embedded in the context of topic tracking \cite{hu2016news}\cite{li2017joint}, or in the recognition of emerging topics in real-time \cite{cataldi2010emerging} mostly applied to social media.

### 2018-07-10 methodology.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\section{Methodology} \label{sec:Methodology}

\subsection{Numerical representation of the corpus}

\par In order to perform the analysis of the articles in the corpus, we describe them as numerical vectors through the \textit{term frequency - inverse document frequency (tf-idf)} representation. \textit{Tf-idf} gives greater values to terms that appear in less documents of the corpus (i.e more specific terms) and/or to those which appear more frequent in a document.

\par Given the set of terms made up by all the corpus' words after removing the non-informative ones, such as prepositions and conjunctions, the \textit{tf-idf} algorithm represents the \textit{i}-document as a vector $v_i = [x_{i1}, x_{i2}, ... , x_{it}]$, where the component $x_{ij}$ is computed by the equation \ref{ec:tfidf}, where $\textrm{tf}_{ij}$ is the number of times the \textit{j}-term appears in the \textit{i}-document, $d$ is the number of documents in the corpus, and $n_j$ is the number of documents where the \textit{j}-term appears. Each document's vector is normalized to unit Euclidean length.
Once the documents' vector are constructed, we join them in a document-term matrix (\emph{M}), which has dimensions of number of documents in the corpus ($d$) per number of terms selected ($t$).

% See parameters of sklearn.feature_extraction.text.TfidfVectorizer
\begin{center}
\begin{equation}
\begin{split}
\text{idf}_{j} & = 1 + \textrm{log}(\frac{1 + d}{1 + n_j}) \\
x_{ij} = \textrm{tf}_{ij} \cdot \textrm{idf}_{j}
\end{split}
\label{ec:tfidf}
\end{equation}
\end{center}

\subsection{Topic detection}
\par We perform \emph{non-negative matrix factorization (NMF)} on the document-term matrix (\emph{M}) in order to detect the main topics in the corpus. 
\emph{NMF} is an algorithm which factorize a matrix \emph{M} into two matrices \emph{W} and \emph{H} (eq.\ref{eq:nmf}), with the property that all three matrices have no negative elements. This non-negativity makes the resulting matrices easier to inspect, and very suitable for topic detection.
\begin{equation}
M^{(d \times t)} \sim H^{(d \times k)} \cdot W^{(k \times t)}
\label{eq:nmf}
\end{equation}
\par As can be seen in eq.\ref{eq:nmf}, the resulting matrix \emph{H} has dimensions of number of documents per $k$, and matrix \emph{W} has dimensions of $k$ per number of terms. The number $k$ is interpreted as the number of topics in the documents and it is a parameter that must be set before the factorization.
The matrix \emph{H} is interpreted as the representation of the documents in the topic-space, and the matrix \emph{W} as the topics represented in the original term-space. 
\par This factorization usually can not be made exactly so it is approximated by minimizing the reconstruction error, i.e. the distance between matrix \emph{M} and its approximated form $\tilde{M} = H \cdot W$. We performed \emph{NMF} through the python module \emph{scikit-learn} \cite{scikit-learn}. % See parameters of sklearn.decomposition.NMF

\subsection{Topic interpretation and temporal profiles}
\par The matrix $H$ obtained by \textit{NMF} gives the representation of the documents in the topic-space. In order to improve its interpretation we normalize each document's vector described in that space to unit $l_1$-norm. Therefore the components of these vectors can be viewed as a degree of membership of a given document in the set of topics. The index of the largest component tells us which is the most representative topic of the document.
\par On the other hand, each row of matrix $W$ represent the topic over the term-space. Therefore, the terms associated with the largest components of the \textit{i}-row are the most representative ones and give an insight of what the topic is talking about.
\par We define the temporal profile of the topic $i$, $W_i(day)$ by the eq. \ref{eq:topic_weight} where $l(j)$ is the number of words of the document $j$, and $h_{ji}$ is the degree of membership of document $j$ on topic $i$. This definition allows all documents to contribute to any topic weight, providing by the fact that each document's vector can have non-zero components in more than one topic.
\par As last steps of the data's preprocessing, we filter the topics' weight in order to reduce the noise but keeping the most details as possible, by redefining $W_i(day)$ as the mean value of a 3 days width window, centered on the day, as described in equation \ref{eq:topic_weight_norm}. 
\par Finally we normalize again all the temporal profiles in order to describe each newspaper as dsitribution over the topics' space which evolves over time. This last normalization prevent us against the differences in the number of articles that each newspaper publishes.

\begin{equation}
W_i(day) = \sum_j^d l(j) \cdot h_{ji} \cdot \delta_{d,day}
\label{eq:topic_weight}
\end{equation}

\begin{equation}
\tilde{W}_i(day) = \frac{1}{3} ({W}_i(day) + {W}_i(day - 1) + W_i(day + 1))
\label{eq:topic_weight_norm}
\end{equation}

\subsection{Outliers identification}
\label{sec:outliers_identification}

\par We identify outliers values in a data set of N observations by following the box plot construction. The quantities (called fences) in \ref{eq:fences} are used, where $Q1$ is the lower quartile (range of the distribution where lies the 25th percent of the data), $Q3$ is the upper quartile (where lies the 75th percent of the data) and $IQ = Q3 - Q1$.

\begin{equation}
\begin{split}
\text{lower inner fence (LIF)} & = Q1 - 1.5  \text{IQ} \\
\text{upper inner fence (UIF)} & = Q3 + 1.5  \text{IQ} \\
\text{lower outer fence (LOF)} & = Q1 - 3  \text{IQ} \\
\text{upper outer fence (UOF)} & = Q3 + 3  \text{IQ}
\end{split}
\label{eq:fences}
\end{equation}

\par A point above the upper inner fence considered a mild outlier and a point aove an outer fence is considered an extreme outlier. The same holds for the lower fences. \footnote{http://www.itl.nist.gov/div898/handbook/prc/section1/prc16.htm}

\subsection{Jensen shannon divergence}

\par In probability theory and statistics, the Jensen–Shannon divergence is a method of measuring the similarity between two probability distributions. It is based on the Kullback–Leibler divergence ($D_{KL}$)\ref{eq:jensen_shannon_distance}, but have useful properties such as it is symmetric and it is always a finite value. The square root of the Jensen–Shannon divergence \ref{eq:jensen_shannon_distance} is a metric often referred to as Jensen-Shannon distance. \cite{fuglede2004jensen}

\begin{equation}
\begin{split}
D_{KL}(P||Q) = -\sum{P(i) log(\frac{Q(i)}{P(i)})} \\
\text{JS Divergence}(P||Q) = \frac{1}{2}[D_{KL}(P||M) + D_{KL}(Q||M)] \\
\text{JS Distance (JSD)} = \sqrt(\text{JS Divergence})
\end{split}
\label{eq:jensen_shannon_distance}
\end{equation}

\subsection{Normalized Shannon's H Information Entropy}

\par The normalized Shannon's entropy \ref{eq:shannon_entropy} as a way to measure how spread is a distribution, taking the maximun value where all outcomes are equally probable in the case of a discrete distribution.

\begin{equation}
H[p] = \frac{- \sum_{i = 1}^{N} p(x_i) * ln(p(x_i))}{ln(N)}
\label{eq:shannon_entropy}
\end{equation}

### 2018-07-10 paper.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\documentclass[a4paper, 12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[export]{adjustbox}
\usepackage{amsmath} 
\usepackage{subfigure}
\usepackage{lscape}
\usepackage{authblk}
\usepackage{float}
\usepackage{array}
\usepackage{booktabs}
\usepackage{varwidth}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\bibliographystyle{ieeetr}

\title{Agenda diversity and coverage bias: A quantitative approach to the agenda-seeting theory}

\author[1,2,*]{Sebastián Pinto}
\author[3]{Federico Albanese}
\author[1,2]{Claudio O. Dorso}
\author[1,2]{Pablo Balenzuela}

\affil[1]{Departamento de Física, Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires, Av. Cantilo s/n, Pabellón 1, Ciudad Universitaria, 1428, Buenos Aires, Argentina.}
\affil[2]{Instituto de Física de Buenos Aires (IFIBA), CONICET, Av. Cantilo s/n, Pabellón 1, Ciudad Universitaria, 1428, Buenos Aires, Argentina.}
\affil[3]{Instituto de Cálculo, CONICET, Intendente Güiraldes 2160, Pabellón 2, Ciudad Universitaria, 1428, Buenos Aires, Argentina.}
\affil[*]{Corresponding author: spinto@df.uba.ar}

\renewcommand\Affilfont{\small}

\date{}

\begin{document}

%\twocolumn[
%\begin{@twocolumnfalse}
\maketitle
\input{abstract}
%\end{@twocolumnfalse}
%]

\input{intro/intro}
\input{description}
\input{discussion/discussion}
\input{conclusions}

\newpage
\appendix
\input{methodology}
\newpage
\input{context}
\newpage
\input{appendix/appendix}
\bibliography{bibliography}

\end{document}

### 2018-07-10 paper_balen.tex
Version vista por Balen, con algunas correcciones, hacia la version final para arxiv

\documentclass[a4paper, 12pt]{article}

%\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[export]{adjustbox}
\usepackage{amsmath} 
\usepackage{subfigure}
\usepackage{lscape}
\usepackage{authblk}
\usepackage{float}
\usepackage{array}
\usepackage{booktabs}
\usepackage{varwidth}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\bibliographystyle{ieeetr}

\title{Agenda diversity and coverage bias: A quantitative approach to the agenda-setting theory}

\author[1,2,*]{Sebasti\'an Pinto}
\author[3]{Federico Albanese}
\author[1,2]{Claudio O. Dorso}
\author[1,2]{Pablo Balenzuela}

\affil[1]{Departamento de F\'isica, Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires, Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria, 1428, Buenos Aires, Argentina.}
\affil[2]{Instituto de F\'isica de Buenos Aires (IFIBA), CONICET, Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria, 1428, Buenos Aires, Argentina.}
\affil[3]{Instituto de Investigaci\'on en Ciencias de la Computaci\'on (ICC), CONICET, Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria, 1428, Buenos Aires, Argentina.}
\affil[*]{Corresponding author: spinto@df.uba.ar}

\renewcommand\Affilfont{\small}

\date{}

\begin{document}

%\twocolumn[
%\begin{@twocolumnfalse}
\maketitle
\begin{abstract}

The Agenda Setting theory provides a conceptual framework in order to understand the role played by the Mass Media in a society. Within this framework, the Media are not only capable to make people think about certain issues, but also to make how to think about them. When this is accomplished,  we say that the media set the agenda. 
In this work we study the agenda of Argentinian newspapers in comparison with public's interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time. We measure Agenda's diversity as a function of time using Shannon's entropy and difference between Agendas using Jensen-Shannon's distance. We found that the Public Agenda is less diverse than the Media Agenda, and we are also capable to detect periods of time where coverage of certain issues are biased (coverage bias). \\

\end{abstract}

%\end{@twocolumnfalse}
%]
\section{Introduction}
%PRIMERA PARTE TEORIA DE AGENDA SETTING
\subsection{Agenda Setting Theory}

% Introduccion y descripcion de agenda-setting en su nivel mas basico.

\par Understand the ecosystem of information flow and opinion formation is one of the goals in these days. In this framework, many ingredients can be part of different mechanism of social influence. A major role in this ecosystem is played by the Mass Media outlets, which use tu be the source of information of many of us.  Informed people tends to interact each other, either via personal interactions o through social networks. In this scenario, becomes essential to understand the role of Mass Media Influence in a given social group.
\par  This question has been raised years ago. In the famous study performed in Chapel Hill during the US presidential elections in 1968 \cite{mccombs1972agenda}, Maxwell McCombs and Donald Shaw found that those aspects of public affairs that are prominent in the news become prominent among the public.
This study is considered the founding of the agenda-setting theory, which focus in the influence of mass media in public opinion.  
From \cite{mccombs2014agenda}, \textit{``The media agenda is the pattern of news coverage over a period of days, weeks (...) for a set of issues or other topic. In other words, the media agenda is a systematic compilation of the issues or topics presented to the public that identifies the degree of emphasis on these topics.''}

\par Since the Chapel Hill research, several directions of agenda-setting were established \cite{mccombs2005look}.
In its basic stage, the theory focus on the comparison between the topics coverage by the media and the public agenda, i.e. the topics that the public consider as priority.
It looks for answering the question if the media is able to set the public agenda, which would transform the media as an important actor in the formation of public opinion.

% Agenda setting de segundo nivel: noticias con atributos y contextualización.
\par The basic agenda-setting sometimes is called the ``first level agenda-setting''.  The very often quoted phrase of Bernard C. Cohen \textit{``The press may not be successful much of the time in telling people what to think, but it is stunningly successful in telling its readers what to think about.''} illustrates its object of study. On the other hand, the ``second level agenda-setting'', sometimes called \textit{attribute agenda-setting}, studies the \textit{objects} (in a social psychology way, where an \textit{attitude object} designate a thing that an individual has an attitude or opinion about) present in the media agenda. When the media talks about an object some attributes are emphasized, and others not.

\par The ``second level agenda-setting'' is linked with \textit{framing} \cite{guggenheim2015dynamics} \cite{tsur2015frame}. 
To frame is to \textit{select some aspects of a perceived reality and make them more salient in a communicating text, in such a way as to promote a particular problem definition, causal interpretation, moral evaluation and/or treatment recommendation} (Robert Entman) \cite{mccombs2005look}.
This stage of agenda-setting theory can be summary in the phrase \textit{``the media not only can be successful in telling us what to think about, they also can be successful in telling us how to think about it.''}

\par With the emergency of the Internet, the end of agenda-setting were predicted due to the audience fragmentation onto multiple sources, which would virtually lead to a highly individualized agenda. However, it is based on two assumptions that are not necessarily true: the public spreads its attention in an homogeneous way across the multiple sources, and that the agendas of that sources are different \cite{mccombs2005look}.
%The interaction between media and public is rather complex, for instance, \cite{mitchelstein2016brecha} shows that not necessarily the journalists and public preferences coincide.

\par Other interesting stage of agenda-setting concerns with the sources of media agenda, i.e. if the media set the public agenda, \textit{who sets the agenda media?} Within this framework, \textit{intermedia agenda-setting} observes the competition between different media and how they influence each other. The competition between mass media for the same audience can lead to a homogenization of the agendas \cite{vargo2017networks}, which is in the opposite direction of one of the assumptions that predict the end of agenda-setting, as was mentioned before.

% ACA ARRANCA LA REESTRUCTURACION NUEVA
%\subsection{Related works}

\par Since the irruption of internet in our lives and the access to big data, there were many attempts to analyze from a quantitative point of view the theory of Agenda Setting based on  the original work of McCombs \cite{mccombs1972agenda}. Many of them follows what we called a "static approach", i.e., by summarizing certain issues present in news media and looking for effects in the audience \cite{brians1996campaign, gerber2009does, coleman2007young}.
For instance, in Argentina, \cite{mitchelstein2016brecha} examines the difference between public and journalists preferences. 
Several works by E. Zunino, like \cite{zunino2010cobertura} and \cite{koziner2013cobertura}, studied the coverage given by the main newspapers of particular events which have happened during the former administration of Argentinean president \emph{Cristina Fernandez de Kirchner} (from 2007 to 2015), where the government started to confront with news organizations that were critical to its management as they were an opposition party \cite{mitchelstein2017information}

% Algo sobre bias
\par Other line of research have been focused on detecting bias in the media, either by taking into account the number of mentions related  to a preferred political party \cite{lazaridou2016identifying, baumgartner2015all} or by identifying the ideology through the position of the media regards to certain issues or actors \cite{elejalde2018nature, sagarzazu2017hugo}. New trends in agenda-setting theory propose to represent ideological aspects or issues emphasized as networks like mind maps, and the basic idea is the comparison between media's knowledge representative network with its counterpart in the audience \cite{guo2012application}\cite{vu2014exploring}.

\par Most of the works cited above follow typical methods of social science research. However, a useful tool in the analysis of large corpus of documents, which is not widely used in the agenda setting theory, is unsupervised topic modeling. These methods are an alternative to the dictionary-based analysis, which is the most popular automated analysis approach \cite{guo2016big}, and allows to work with a corpus without a prior knowledge, letting the topics emerge from the data. Despite the popularity of these methods in other fields, they have been under-employed in the agenda setting framework.
Many works based on news corpus emphasize the performance of the topic model over a labeled corpus, focusing on the proper detection of the topics \cite{dai2010online, po2016topic, brun2000experiment}. The temporal profile of topics is usually embedded in the context of topic tracking \cite{hu2016news, li2017joint}, or in the recognition of emerging topics in real-time \cite{cataldi2010emerging} mostly applied to social media.

\par A typical  dynamical analysis of Agenda Setting is focused on a single issue. For instance, in \cite{soroka2017negativity} it is shown that the newspapers and Twitter have an opposite reaction to the changes of the unemployment rates. In \cite{guggenheim2015dynamics} the competition of frames about gun control is explored, and in \cite{ali2018measuring} the authors show how fluctuations of  twitter activity in different regions depend on the location of terrorist attacks.
A remarkable exception is found in  \cite{russell2014dynamics},  (CUAN PARECIDO ES AL NUESTRO?) where they work with a set of predefined issues. In this work the question of \emph{causality} is also faced up. Their study shows that sometimes the traditional media set the agenda and sometimes, the social media does. They show that social media is always more interested in social issues than the traditional one, and despite the existence of correlation, the social media agenda can not be seen as a \emph{slave} of the traditional media.

% Presentacion y descripcion de nuestro trabajo
\par In this work we propose a novel method in order to the study the dynamics of Mass Media Agenda as a set of topic evolving in time and their correspondence with the Public and Social Network Agendas.  Our work intends to contribute another quantitative approach which complements the agenda-setting theory describe above.
Rather than focus on a single issue or a set of independent topics, we work with the agendas (the media and the public) as an object in their own, studying their evolution over time. On the other hand, we aim to take an insight about Media dynamics and Public response in order to create useful tools at the time of constructing mathematical models about the interaction between Media and Public, investigation that we started in \cite{pinto2016setting}.

%\input{description}
\section{Materials and Methods} \label{sec:MatMeth}

\subsection{The Media Agenda}

In this work we analyze a three month period of the Argentinian Media's Agenda composed a corpus of news' articles that were published between July 31th and November 5th in the section \emph{Politics} of the electronic editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\''on}, \emph{P\'agina12}, and the news portal \emph{Infobae}. The first two lead the sale of printed editions in \emph{Buenos Aires} city, but \emph{Clar\'in} reaches roughly two times the readers of \emph{La Naci\'on}, and ten times the readers of \emph{P\'agina 12} \footnote{www.ivc.org.ar}. On the other hand, \emph{Infobae} has the website with more visitors, above the websites of \emph{Clar\'in} and \emph{La Naci\'on} \footnote{https://www.alexa.com/topsites/countries/AR}.

\par The corpus analyzed is constituted by 2908 politics articles of \emph{Clariin}, 3565 of \emph{La Nacion}, 3324 of \emph{Pagina 12}, and 2018 of \emph{Infobae}. Except \emph{Pagina 12}, all articles were taken from the section \emph{Politica}  (Politics) of the respective news portal, while the articles which belong to \emph{Pagina 12} were taken from the section \emph{El pais} (The country).

In order to perform the analysis of the articles in the corpus, we describe them as numerical vectors through the \textit{term frequency - inverse document frequency (tf-idf)} representation [CITA tf-idf]. Given the set of terms contained in the corpus' words after removing the non-informative ones, such as prepositions and conjunctions, the \textit{tf-idf} algorithm represents the \textit{i}-document as a vector $v_i = [x_{i1}, x_{i2}, ... , x_{it}]$, where the component $x_{ij}$ is computed by the equation \ref{ec:tfidf}, where $\textrm{tf}_{ij}$ is the number of times the \textit{j}-term appears in the \textit{i}-document, $d$ is the number of documents in the corpus, and $n_j$ is the number of documents where the \textit{j}-term appears. Each document's vector is normalized to unit Euclidean length. Once the documents' vector are constructed, we put them together in a document-term matrix (\emph{M}), which has dimensions of number of documents in the corpus ($d$) per number of terms selected ($t$).

% See parameters of sklearn.feature_extraction.text.TfidfVectorizer
\begin{center}
\begin{equation}
\begin{split}
\text{idf}_{j} & = 1 + \textrm{log}(\frac{1 + d}{1 + n_j}) \\
x_{ij} = \textrm{tf}_{ij} \cdot \textrm{idf}_{j}
\end{split}
\label{ec:tfidf}
\end{equation}
\end{center}

Then we perform \emph{non-negative matrix factorization (NMF)} on the document-term matrix (\emph{M}) in order to detect the main topics in the corpus. A topic is a group of similar articles which roughly talks about the subject. 
\emph{NMF} is an algorithm which factorize a matrix \emph{M} into two matrices \emph{W} and \emph{H} (eq.\ref{eq:nmf}), with the property that all three matrices have no negative elements. This non-negativity makes the resulting matrices easier to inspect, and very suitable for topic detection.
\begin{equation}
M^{(d \times t)} \sim H^{(d \times k)} \cdot W^{(k \times t)}
\label{eq:nmf}
\end{equation}

\par As can be seen in eq.\ref{eq:nmf}, the resulting matrix \emph{H} has dimensions of number of documents per $k$, and matrix \emph{W} has dimensions of $k$ per number of terms. The number $k$ is interpreted as the number of topics in the documents and it is a parameter that must be set before the factorization.

  \par The matrix \emph{H} is interpreted as the representation of the documents in the topic-space, and the matrix \emph{W} as the topics represented in the original term-space. This factorization usually can not be made exactly so it is approximated by minimizing the reconstruction error, i.e. the distance between matrix \emph{M} and its approximated form $\tilde{M} = H \cdot W$. We performed \emph{NMF} through the python module \emph{scikit-learn} \cite{scikit-learn}.  \footnote{ Even though there are other technics in topic detection, as for instance LDA (Latent Dirichlet Allocation), the NMF decomposition suites perfect for the kind of corpus we  have analyzed in this work (A detailed comparison of both, NMF and LDA methods could be found in Supplementary Material)}.

\par The matrix $H$ obtained by \textit{NMF} gives the representation of the documents in the topic-space. If we normalize each document's vector to unit $l_1$-norm, their components can be viewed as a degree of membership of a given document in the set of topics. In particular, the index of the largest component tells us which is the most representative topic of the document.
\par On the other hand, each row of matrix $W$ represent the topic in the term-space, i.e., the group of words which represent more accurately each topic (the keywords) and those who give an insight of what the topic is talking about.

\par In order to have a time-dependent representation, we define the temporal profile of the topic $i$, $W_i(day)$ by the eq. \ref{eq:topic_weight} where $l(j)$ is the number of words of the document $j$, and $h_{ji}$ is the degree of membership of document $j$ on topic $i$. This definition allows all documents to contribute to any topic weight, providing by the fact that each document's vector can have non-zero components in more than one topic.
\par As last steps of the data's preprocessing, we filter the topics' weight in order to reduce the noise but keeping the most details as possible, by redefining $W_i(day)$ as the mean value of a 3 days width window, centered on the day, as described in equation \ref{eq:topic_weight_norm}. 
\par Finally we normalize again all the temporal profiles in order to describe each newspaper as distribution over the topics' space which evolves over time. This last normalization prevent us against the differences in the number of articles that each newspaper publishes.

\begin{equation}
W_i(day) = \sum_j^d l(j) \cdot h_{ji} \cdot \delta_{d,day}
\label{eq:topic_weight}
\end{equation}

\begin{equation}
\tilde{W}_i(day) = \frac{1}{3} ({W}_i(day) + {W}_i(day - 1) + W_i(day + 1))
\label{eq:topic_weight_norm}
\end{equation}

\subsection{The Public and Twitter Agendas}

\par In order to have a proxy about how the Media Agenda is reaching the public, we look for the same topics in Google Trends and Twitter in the same period of time. We take advantage of topics' keywords on the one hand by making queries to the \emph{Google Trends} tool and getting the relative weight of \emph{Google} searches that people made about the identified topics, and in the other hand, by making queries to the advance search tool in the social media \emph{Twitter} in order to get the relative amount of related tweets .

%\par Following the procedures described above, we obtain two evolving in time discrete distribution in the topic space: The \textbf{Media Agenda (MA)}, and the \textbf{Public Agenda (PA)}, which could be represented by two faces, one given by \textbf{Google Trends (Gt)} and the other by \textbf{Twitter (Tw)}. 
%In the final part of this analysis, the Media Agenda will also be described for each of the newspapers (or portal news) taken into consideration.

%After normalization, all agendas are described as a time dependent distribution over the topic's space, where the time scale is day by day. Therefore the agendas give us the relative importance of a given topic respect the other (i.e. it does not give us absolute values such as the number of titles or tweets associated).

\subsection{Outliers identification}
\label{sec:outliers_identification}

\par We identify outliers values in a data set of N observations by following the box plot construction. The quantities (called fences) in \ref{eq:fences} are used, where $Q1$ is the lower quartile (range of the distribution where lies the 25th percent of the data), $Q3$ is the upper quartile (where lies the 75th percent of the data) and $IQ = Q3 - Q1$.

\begin{equation}
\begin{split}
\text{lower inner fence (LIF)} & = Q1 - 1.5  \text{IQ} \\
\text{upper inner fence (UIF)} & = Q3 + 1.5  \text{IQ} \\
\text{lower outer fence (LOF)} & = Q1 - 3  \text{IQ} \\
\text{upper outer fence (UOF)} & = Q3 + 3  \text{IQ}
\end{split}
\label{eq:fences}
\end{equation}

\par A point above the upper inner fence considered a mild outlier and a point aove an outer fence is considered an extreme outlier. The same holds for the lower fences. \footnote{http://www.itl.nist.gov/div898/handbook/prc/section1/prc16.htm}

\subsection{Jensen-Shannon divergence}

\par In probability theory and statistics, the Jensen-Shannon divergence is a method to measure the similarity between two probability distributions. It is based on the Kulback-Leibler divergence  ($D_{KL}$)\ref{eq:jensen_shannon_distance}, but have also useful properties such as it is symmetric and it is always a finite value. The square root of the Jensen-Shannon divergence \ref{eq:jensen_shannon_distance} is a metric often referred to as Jensen-Shannon distance \cite{fuglede2004jensen}.

\begin{equation}
\begin{split}
D_{KL}(P||Q) = -\sum{P(i) log(\frac{Q(i)}{P(i)})} \\
\text{JS Divergence}(P||Q) = \frac{1}{2}[D_{KL}(P||M) + D_{KL}(Q||M)] \\
\text{JS Distance (JSD)} = \sqrt(\text{JS Divergence})
\end{split}
\label{eq:jensen_shannon_distance}
\end{equation}

\subsection{Normalized Shannon's H Information Entropy}

\par The normalized Shannon's entropy \ref{eq:shannon_entropy} as a way to measure how spread is a distribution, taking the maximum value where all outcomes are equally probable in the case of a discrete distribution.

\begin{equation}
H[p] = \frac{- \sum_{i = 1}^{N} p(x_i) * ln(p(x_i))}{ln(N)}
\label{eq:shannon_entropy}
\end{equation}

%EL PRIMER PASO PARA UNA DESCRIPCION CUANTITATIVA ES TENER UNA REPRESENTACION MATEMATICA DE CADA NOTICIA. PARA ESO USAMOS EL METODO TF-IDF QUE REPRESENTA AL TEXTO COMO UN VECTOR EN EL ESPACIO DE PALABRAS. CADA COMPONENTE (CORRESPONDIENTE A UNA DADA PALABRA) REPRESENTA LA FRECUENCIA DE APARICION DE DICHA PALABRA EN EL TEXTO (TF) PONDERADA POR LA IMPORTANCIA RELATIVA DE DICHA PALABRA EN EL TEXTO, RESPECTO AL CORPUS TOTAL (IDF).

%LUEGO DIVIDIMOS AL CORPUS EN 10 TOPICOS USANDO ALGUNA TECNICA DE AGRUPAMIENTO NO SUPERVISADO. 2 ACLARACIONES:
%1 - PORQUE 10?  PORQUE REPRESENTAN LAS TIPICAS 10 NOTICIAS MAS LEIDAS, UNA CLASIFICACION HABITUAL EN LOS PORTALES DE NOTICIAS. 
%2 - AGRUPAMOS LAS NOTICIAS USANDO LA TECNICA DE NMF, QUE NOS PERMITE NO SOLO DIVIDIR LAS NOTICIAS EN GRUPOS DE NOTICIAS SIMILARES (TOPICOS), SINO REPRESENTAR CADA GRUPO COMO UN SER DE PALABRAS CLAVES, QUE CORRESPONDE A UNA DADA DIRECCION EN EL ESPACIO DE PALABRAS. SI BIEN EXISTEN TECNICAS MAS USADAS COMO LDA, LOS RESULTADOS PARA LOS CORPUS DE NOTICIAS USADOS NOS HAN RESULTADO MEJOR USANDO NMF. UNA COMPARACION EXHAUSTIVA DE AMBAS TECNICAS SE PODRAN HALLAR EN EL APENDICE.

%EL ANALISIS QUE HACEMOS NOS PERMITE, LUEGO DE DIVIDIR AL CORPUS EN 10 TOPICOS, REPRESENTAR CADA NOTICIA EN EL ESPACIO DE TOPICOS. DADA LA NORMALIZACION ELEGIDA, LA COMPONENTE DE CADA NOTICIAS EN EL ESPACIO DE TOPICOS REPRESENTA EL PESO QUE TIENE DICHO TOPICO EN LA NOTICIA. DE ESTA MANERA SE PUEDE SACAR EL PESO DE UN DADO TOPICO POR DIA, MIRANDO LOS PESOS DE LAS NOTICAS EN DICHO TOPICO Y MULTIPLICANDO POR EL LARGO DE LA NOTICIA, COMO MUESTRA LA EQ (XX).

%\par The performed analysis mainly consist  in topic detection over the corpus' articles in order to describe it as a set of topics \cite{griffiths2004finding} which evolve over time.  A "Topic" is a cluster of  new's articles related to the same subject. They refers to the same "topic" and are represented by a set of keywords that allow us to interpret and understand what the topics are talking about.  In this work we take the whole corpus of new's articles and divide them in ten topics. A 
%Topic detection is a powerful computational technique that allows us to analyze a big amount of texts that can be impossible otherwise

%For a careful description of the  implemented methodology please see Appendix.

\section{Results}

\par The starting point of our analysis is the decomposition of the corpus in ten topics. This is an arbitrary decision, validated in some manner by our knowledge of the corpus, which could be revised in future works.  From the initial ten topics, three of them could be interpreted as part of the same macro-topic called \emph{Elections}. The same happen with two others which we classified as part of the macro-topic called \emph{Missing person}, leaving the  final description of the agendas is made with seven topics. The meaning of the topics or macro-topics are contextualized  in section \ref{sec:Context} of Supplementary Material.

After the procedure described in previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, and all their derivations, as time-dependent distributions.

\subsection{The Public and Media agendas}

\par In figure \ref{fig:topics_wordclouds} we show a ten topic decomposition of the whole corpus using radar plots for the Media \textbf{MA} and Public agendas \textbf{PA} discriminated by \textbf{GT} (Google Trends) and \textbf{Tw} (Twitter). A radar plot is an alternative of histograms that allows the visual comparison of distributions easier.
In this figure we also show the wordclouds of the keywords that define each topic, where the size of the word reflects its importance in the topic's definition. In green color, we point out the words involved in the Google Trends and Twitter queries in order to construct the Public Agenda. The queries employed are also specified in table \ref{table:gt_queries}. In table \ref{table:gt_all_correlation} we show the linear correlation between the topics' temporal profiles from the Public Agenda and their counterparts in the Media Agenda.

\par In figure \ref{fig:all_agenda} we show the time evolution of the topics with a bump chart of the Agendas. The bump chart provides  a very useful visualization tool for displaying the relative weight of the topics at the same time that their ranking. In figure \ref{fig:all_agenda} we also highlight some important events related to the dynamics of the topics. \footnote{Due to different characteristics in the search tool of Twitter, we adapted the queries employed here but preserving the at least at we can the most important keywords. The queries employed by topic were: \\
Elections: elecciones + cambiemos + kirchner + massa + randazzo \\
Missing person: maldonado + otranto + gendarmeria + desaparicion \\
Former Planning minister: vido + desafuero + minnicelli + baratta \\
Current President: macri + cgt + laboral +  triaca \\
Social leader:  sala + cidh + tupac + amaru + pullen + llermanos + morales \\
Prosecutor’s death: nisman + amia + memorandum + timerman +  bonadio \\
Former Vice-President:  boudou + ciccone +  lijo + vandenbroele + carmona
}

% Wordclouds
\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{images/Fig1.pdf}
\caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic distribution and their corresponding wordclouds.} The Public Agenda is represented either by Google Trends (GT) and Twitter (Tw). 
Topics names are introduced together with the wordclouds containing the most important keywords involved in the definition of each topic. In green color we show the keywords used to define the topics in the Google Trends and Twitter queries (see table \ref{table:gt_all_correlation}) and therefore in our construction of the Public Agenda.}
\label{fig:topics_wordclouds}
\end{figure}

% Global Agenda figure!!!
\begin{figure}[h]
\includegraphics[width = \textwidth]{images/Fig2.pdf}
\caption{\textbf{Bump graph of the Media Agenda (MA) and Public Agenda extracted from Google Trends (GT) and Twitter (Tw)}. The curves width and their ordering are related to the topics relative weight. Some important events related to the topics are pointed out:
\textbf{A}: First news about Santiago Maldonado's disappearance;
\textbf{B}: Primary elections;
\textbf{C}: March one month after Santiago Maldonado's disappearance;
\textbf{D}: March two months after Santiago Maldonado's disappearance;
\textbf{E}: Appearance of Santiago Maldonado's body;
\textbf{F}: General elections;
\textbf{G}: Julio De Vido's detention;
\textbf{H}: Debates on labor reform;
\textbf{I}: Amado Boudou's detention.
A more detailed explanation is given in section \ref{sec:Context}.}
\label{fig:all_agenda}
\end{figure}

% Table with queries and correlations
%\input{discussion/table_gt_queries_correlation}

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{lp{10cm}}
\toprule
Topic's name & Google Trends query \\ 
\midrule
Elections & elecciones + cambiemos + cristina kirchner + massa + randazzo \\
Missing person & santiago maldonado + juez otranto + patricia bullrich + gendarmería + desaparición forzada \\
Former Planning minister & de vido + desafuero + ministro de planificación + minnicelli + baratta \\
Current President & mauricio macri + cgt + reforma laboral + peña + triaca \\
Social leader & milagro sala + cidh + tupac amaru + pullen llermanos + morales \\
Prosecutor's death & nisman + amia + memorándum con irán + timerman + juez bonadio \\
Former Vice-President & amado boudou + ciccone + ariel lijo + vandenbroele + núñez carmona \\
\bottomrule
\end{tabular}}
\caption{Queries used in Google Trends in order to build the Public Agenda.}
\label{table:gt_queries}
\end{table}

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{lccc}
\toprule
Topic's name & Correlation MA and GT & MA and Twitter & GT and Twitter \\ 
\midrule
Elections & \textbf{0.81} & \textbf{0.59} & \textbf{0.75} \\
Missing person & \textbf{0.68} & \textbf{0.76} & \textbf{0.89} \\
Former Planning minister & \textbf{0.92} & \textbf{0.82} & \textbf{0.87} \\
Current President & \textbf{0.77} & \textbf{0.75} & \textbf{0.63} \\
Social leader & \textbf{0.49} & \textbf{0.25(*)} & \textbf{0.57} \\
Prosecutor's death & \textbf{0.56} & \textbf{0.59} & \textbf{0.75} \\
Former Vice-President & \textbf{0.90} & \textbf{0.92} & \textbf{0.97}\\
\bottomrule
\end{tabular}}
\caption{Correlation between the topics' temporal profiles of the Public Agenda and their counterpart in Media Agenda.
All correlation values are statistical significant ($p < 10^{-9}$), except (*) which is significant with $p < 0.05$.}
\label{table:gt_all_correlation}
\end{table}

\par The figures introduced above show not only the topics and their differences between Agendas, but also the dynamics of the topics.  For instance, we can see in the radar plot of figure \ref{fig:topics_wordclouds}, a greater interest of the audience in the topic \emph{Missing person} than the Media, or inversely in the topic \emph{Prosecutor's death}, at least in the analyzed time-lapse. 
We can also observe a great similarity between \textbf{GT} and \textbf{Tw} agendas which both are different faces of the Public Agenda.

\par On the other hand, figure \ref{fig:all_agenda} allow us to appreciate how the main topic change in time and have a glance of the qualitative differences between agendas.
The linear correlations shown in table \ref{table:gt_all_correlation} are  positive and statistically significant in all the cases, This can be interpreted as a validation of the topics found in the corpus and the keywords that describe it. 
Even though it is expected that the Media's and public's interest should generally follow a similar a pattern due to the external events, we are interested in those periods where they significantly differ. 
A non positive (or a non significant) correlation may imply, besides the obvious conclusion of agenda's disengagement, that we could eventually fail in properly detect the keywords or features that describe a particular topic, so the Google Trends' or Twitter's pattern would not be able to reflect a similar behavior that its counterpart in the Media.

\subsection{A quantitative description of the Agendas}

\subsubsection{Agenda diversity}

% Agenda diversity

\par In order to quantify the diversity of the Agendas, we start by representing them as distributions in the topic's space. 
Following \cite{boydstun2014importance}, we calculate the normalized Shannon's entropy ($H$, see eq.\ref{eq:shannon_entropy}) in order to measure the diversity of the \textbf{MA} and \textbf{PA}.
\par In figure \ref{fig:shannon_entropy_agendas} we can see the value of $H$ as a function of time, where it can be focused in those periods of time where the diversity is lower than usual. This effect is notoriously more pronounced in the Public Agenda giving by \textbf{GT}, and in particular in four specific days  where can be detected four local minima of Shannon's entropies. Three of them are outliers as defined in section \ref{sec:MatMeth}, two of them from \textbf{GT} and one from \textbf{Tw}.

\par A lower value in the agenda's diversity is due to the fact that the most important topic attracts practically all the attention of the public and the media.
In the radar plots included in figure \ref{fig:shannon_entropy_agendas} we can see that two of these outliers (\textbf{a} and \textbf{d}) belong to the topic \emph{Elections} and coincide with the primary and general legislative elections that took place in August 13th and October 22th. 
In all the agendas these points where detected as outliers except point (d) in Twitter Agenda. Why is that? The radar plot of the Twitter agenda for this day displays an association between the topic \emph{Elections} and the \emph{Current President} which could be decreasing the important this topic.
Discussions in Twitter about elections appear also in point (c), when the other agendas seems to be more diverse. 
On the other hand, we focused in point (b), despite not being detected as a outlier, because it belong to the topic \emph{Missing person} and this date correspond to the rally that took place one month after the disappearance of Santiago Maldonado (see section \ref{sec:Context}). It is important to notice that, the Shannon's Entropy of GT Agenda displays a minimum (collapsing agenda) not shown neither in the Media nor in the Twitter Agendas.
We emphasize the discussion about this topic because we can appreciate  interesting facts that appear along the analysis.

\begin{figure}[h]
\centering
\includegraphics[height=0.75\textheight]{images/Fig3.pdf}
\caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda show a less diverse behavior than the Media Agenda as can be seen in the left figure. The horizontal lines are the lower inner fences of each signal in order to identify outliers. The related radar plots shows that those dates when the agenda has a low diversity, the most important topic catches the most public’s attention. \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
\label{fig:shannon_entropy_agendas}
\end{figure}

\par From the measure of $H$ we can also see that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
Specifically $H_{Gt} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
However from figure \ref{fig:shannon_entropy_agendas} we can see that \textbf{GT} shows more abrupt dropouts in the diversity in response to specific events.
We conclude that its an important fact about audience behavior: given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus more in the most important topic than the Media can do, maybe due to editorial decisions.

\subsubsection{Distance between Media and Public Agenda's }

% Jensen-Shannon distance between PA and MA

\par Given our interpretation of  the Agendas and time-evolving distributions, we can  compare them by computing the Jensen-Shannon distance. In this context, outliers in selected dates will correspond to divergences between Public and Media Agenda, i.e., specific events where the public interest do not match with media offer.
In figure \ref{fig:jensen_shannon_gt} we show the Jensen-Shannon distance between Media and Publics Agendas as a function of time. We focus in three points that seems to be relevant enough. In all cases, the topic distributions at that particular dates displayed by  the radar plots shows that a greater distance is associated with a more interest of public in the topic \emph{Missing person}. 
\par Points \textbf{(c)} and \textbf{(d)} shows that both the Public and the Media highlight this topic, but the Media do not disregard other topics, so the corresponding distance between them can be interpreted  of another way of see  the diversity effect discussed in the last section.

\par On the other hand,  points \textbf{(a)} (we take this point due to be a local maximum despite not being an outlier) and \textbf{(b)} seem to show an interest of the public in the topic \emph{Missing person} which it is not reflected in the Media.  In figure \ref{fig:all_agenda} we can see that this topic becomes the most important in public's interest (both \textbf{GT} and \textbf{Tw}) days before that  it happen in the Media Agenda. It can be associates  with a social networks (like Facebook and Twitter) campaign  in favor  of the appearance of Santiago Maldonado ("The missing person") that took place on  August 26th. It was very important and and was initially underestimated by the main Media outlets in Argentina (see section \ref{sec:Context}).

\par It is important to notice that it is our interpretation of the data based on the knowledge of the context, and  we are not measuring causality between Agendas (we will say a few words about it in section \ref{sec:who_sets}), i.e. we can't say, for instance, that in this case the Public Agenda set the Media Agenda. 
However, the Jensen-Shannon distance, in conjunction with the measurement of the agenda diversity given by the Shannon entropy, give an insight of independent behavior of the Public and the Media, and its identification can be a starting point to study the Media reaction to a change in audience's interests.

\begin{figure}[h]
\centering
\includegraphics[height = 0.75\textheight]{images/Fig4.pdf}
\caption{\textbf{Jensen Shannon distance between the Media Agenda and the Public Agenda as a function of time} (with upper inner fences pointed out). The larger distances are due to a greater interest of the audience in the topic \emph{Missing person} which leads to lesser interest in the other topics, which the Media has to cover, maybe except in points (a) and (b) where the Media seems not to anticipate the public interest in the mentioned topic. \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
\label{fig:jensen_shannon_gt}
\end{figure}

\subsection{Agenda bias in different Media outlets}

\par In this section we leave aside the Public Agenda as a whole and we study how the Media agenda of each media outlet. 
In figure \ref{fig:news_agenda} we show the bump charts corresponding to each newspaper analogously to figure \ref{fig:all_agenda}.
The topics are the same introduced in the wordclouds of figure \ref{fig:topics_wordclouds}, but when computing the topics' weights,  the articles are discriminated by newspaper. 
We also show the radar plots showing the average distribution, as made in figure \ref{fig:topics_wordclouds}. 
\par In figure \ref{fig:news_agenda} we can see in a qualitative way the slightly differences between the newspapers' agendas.
For instance, we can see how newspaper called \emph{Pagina 12} gave more importance to the topics \emph{Missing person} and \emph{Social leader}, while it reduces to minimum the coverage of the topic  \emph{Former Planning minister} as the others did.

% Jensen shannon distance of Dynamic way
\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{images/Fig5.pdf}
\caption{\textbf{Bump charts of newspapers' Agenda and radar plot of the average distributions.} The figure shows, in a qualitative way, the bias in the different newspaper's agendas. For instance, the greater interest of \emph{Pagina 12 (P12)} in the \emph{Missing person} topic and its slightly lower coverage in the \emph{Former Planning minister} respect to the other newspapers.}
\label{fig:news_agenda}
\end{figure}

%\subsubsection{Independent behavior}

\par In other to detect outliers behavior of a given newspaper respect to the others, we again calculate the Jensen-Shannon distance between the newspapers agenda and the Media Agenda.
Note that this is the distance between the distributions of figure \ref{fig:news_agenda} and the top panel of figure \ref{fig:all_agenda}.
\par In figure \ref{fig:jensen_shannon_news} we show the Jensen-Shannon distance as a function of time.
We detect three points as outliers, although we discard the point \textbf{(b)} due to the low information of \emph{Infobae} in that period. 
The other two points corresponds to differences between \emph{Pagina 12} and the other newspapers and correspond to differences in the coverage of the topic \emph{Missing person}.

\par The point \textbf{(a)} corresponds  to the first news of the Santiago Maldonado's disappearance  reported by \emph{Pagina 12} before the primary elections, and in point \textbf{(c)} to  the two months rally after the disappearance took place (see section \ref{sec:Context}). Another difference in point \textbf{(c)} corresponds to a greater coverage of \emph{Pagina 12} in the topic \emph{Social leader} where the others media outlets seem to be more interested in the topic \emph{Former Vice-President}.

% Jensen shannon distance of Dynamic way
\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{images/Fig6.pdf}
\caption{\textbf{Jensen-Shannon distance between the newspapers agenda and the Media Agenda as a function of time}. \emph{Pagina 12} shows the more different behavior, motivated again by its interest in the \emph{Missing person} and \emph{Social leader} topics as can be seen in the radar plots which belongs to points (a) and (c). The anomalous behavior of \emph{Infobae} at pint (b) is due to few articles around that date in our database, therefore we ignore its radar plot. \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
\label{fig:jensen_shannon_news}
\end{figure}

%\subsubsection{Coverage bias}

\par The greater coverage in the topic \emph{Missing person} by \emph{Pagina 12} is even more clear if we inspect the temporal profile of the topic and compare the coverage given by each newspaper. A difference in the coverage is what it is called \emph{coverage bias} [CITA ACA SEBAS].  In figure \ref{fig:topics_temporal_profiles} we show the temporal profile of the topic \emph{Missing person} (panel (a)) and the topic \emph{Former Planning minister} in panel (b), as an example where the behavior is the opposite, as can be seen below.

\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{images/Fig7.pdf}
\caption{\textbf{Relative weight of the topics (a) \emph{Missing person}, and (b) \emph{Former Planning Minister}, and their corresponding word-clouds of frequent newspapers' keywords}. We interpreted the differences shown in given periods as an indicator of coverage bias. For instance, in figure (a) Pagina 12 pays a greater attention in the first days. In the word-clouds, we show which of the defining words are more frequently used by the corresponding newspaper. Most of them are less informative, but other seems to represent a first approximation in the study of framing.}
\label{fig:topics_temporal_profiles}
\end{figure}

\par From panel (a) of figure \ref{fig:topics_temporal_profiles}, we can see the larger coverage of \emph{Pagina 12} respect the other newspapers at the beginning of the period. We can, for instance, quantify this difference calculating  the median of the signals. If we focus in the period between July 31th and August 27th, the median of the topic's relative weight for \emph{Pagina 12} is roughly 0.14 and this is statistically significant larger ($p < 10^{-7}$) than other medians, which are lower than 0.05.
Analyzing the same period, but in panel (b), we again can show that the median in \emph{Pagina 12}, which is roughly 0.01, is lower than the others, which oscillate around 0.05 ($p<10^{-3}$)
This quantification is proposed as method of studying coverage bias in the context of the methodology implemented in our work.

\par Finally, in figure \ref{fig:topics_temporal_profiles} we also show word-clouds of topic's keywords but separating those who are more frequently mentioned by each newspaper, and filtering the words that are common to all and basically define the factual details of the topic.
Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represion} (repression) when \emph{Pagina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (Fernandez de Kirchner, former president) which is employed by all newspapers except \emph{Pagina 12} when they  talk about the topic \emph{Former Planning minister} (see section \ref{sec:Context}).

We think that a more deeply study of topics' keywords could be a first approximation in the study of framing, which will constitute the core of futures works.

\subsection{After all: Who sets the Agenda?}
\label{sec:who_sets}

\par The behavior of the Media Agenda and the Public one, either by looking at Google Trends or Twitter, shows periods when there is a strong similarity among them (mostly in the presence of an unexpected event) and periods when they seem to be unrelated. These are mere observation that talk about the correlation between the agendas.
However the agenda-setting theory is in its nature a theory about causality:vIs the audience a passive actor who follows what the Media says, or there are periods where the Media must paid attention at public's interests?
Paraphrasing the question, who sets the agenda, the Media or the audience?
In a world where social media exists and the feedback between a Media and its audience is common currency, nowadays the idea that the Media sets the agenda and the audience blindly follows it (as it's seemed to be suggested in the original work of McCombs) is too naive.

\par In spite of the fact that we think that to establish a causation, i.e. the direction towards information flows, is a task that must be made with extreme care, we have something to say in this work about causality. 
We think that the \emph{Missing person} topic is the most adequate topic to be discussed because:
\begin{itemize} 
\item It caused a great impact in either the Media and the audience
\item  its coverage fully deploys along the time lapse analyzed in this manuscript (see section \ref{sec:Context}).
\end{itemize}

\par In figure \ref{fig:Maldonado_setagenda} we show the topic's relative weight from the Public and Media Agendas.  After the initial coverage, the agendas seem to differentiate around August 16th, when topic started to became more important in the Public Agenda than in the Media one. Around August 24th, the topic abruptly increase in public's interest while the reaction in the Media is slower, showing a significant peak in the plot of the discrete difference (panel (b)) (SEBAS, PODES SENALAR ESTAS FECHAS CON LINEAS PUNTEADAS EN EL GRAFICO?). This date is very close to August 26th, when a campaign in social media took place. After that, the Media increase its coverage about the topic.

\par Is this a case of reverse agenda-setting, i.e, when the audience set the Media Agenda? 
After all,  the audience get involved about this topic by the Media, so how was the coverage before those events?
By calculating the cumulative sum we can see  the cumulative coverage during the first events related to the topic. 
This measure can be seen as the numerical integrate of the temporal profiles of figure \ref{fig:topics_temporal_profiles} between the initial date and the current date. 
It is interesting to note that the newspaper responsible to accumulate coverage during the initial stage was the minority one: \emph{Pagina 12}.

Our interpretation about the setting agenda dynamics of this particular topic is the following: A small newspaper (\emph{Pagina 12}) gives great coverage to this topic; it is amplified  by public in the social networks and also expressed  by reiterative Google searches. Then the rest of the Media  pay attention to this subject and it becomes an important topic in the Media Agenda. 
This interpretation try to catch in a qualitative way how the information flow was in this specific topic.
On the other hand, behind this interpretation there are two important facts that must be mentioned: First, the disappearance of a person is a very sensible theme for the Argentinian society, and second, there are political reasons in why \emph{Pagina 12} was particularly interested in cover this topic while the other Media did not follow this interest.

\par We took the question about causality only in a qualitative way. 
There are different metrics that would help in this question, such as Granger causality or correlation by sliding windows. We think that this analysis must be performed with extreme care since the acquirement of the data.
With this work we aimed to provide a quantitative characterization of the behavior of the Media and the Public but not to establish direction of causation, which we hope this to be the core of future ones.

\begin{figure}
\includegraphics[width = \textwidth]{images/Fig8.pdf}
\caption{\textbf{Agenda setting direction in Missing person's topic?}
The temporal profiles of figure (a) show that the Public increased abruptly its interest in the topic around August 24th, which belongs to the peak \textbf{(*)} shown in figure (b), where the discrete differences were computed. 
This date is also pointed out in the rest of the figures with a vertical grey line together with the asterisk. 
With the computing of the cumulative sum of figure \ref{fig:topics_temporal_profiles} and figure (a), represented as a bump chart in figure (c), we suggest that the topic was first set by \emph{Pagina 12} and then the Public's interest cause the coverage of the other Media.
}
\label{fig:Maldonado_setagenda}
\end{figure}

%\input{conclusions}
\section{Conclusions}

\par The study of Mass Media, and in particular the agenda setting theory, can be empowered by the used of data mining or machine learning algorithms. 
In this work, through the implementation of a topic detection algorithm we could describe the Agenda of the Media as a distribution which evolves over time and which is defined in a topic's space which emerges from the analysis of the corpus.
This gave us an insight of how we can construct and follow the Public's interests, the Public Agenda, in order to compare with the Media Agenda, i.e. Media interests. 
\par Given the Agendas, we found that the Public one is usually less diverse than the Media, showing that when there is a very attractive topic, the audience focus on this one, when the Media has to cover the other too. 
On the other hand, the measurement of distances between Agendas can be employed to rapidly detect periods when the Public may have an independent behavior respect to the Media. The methodology implemented here also allow us to detect coverage bias in newspapers and gave us a first approximation in the theory of framing. 
\par We hope that some of the elements studied here will give us insights at the time of proposing a mathematical model about Mass Media and Public interaction. Future works may include a more systematic study and its extension to international Media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitative analysis about causality.

%\input{discussion/discussion}

\newpage
\section{Supplementary Material}
\subsection{Context}
\label{sec:Context}

\subsubsection{\emph{Elections}}
\par Two legislative elections were celebrated during the period in great part of the Argentina: Primary elections on August 13th and the general elections on October 22th. 
A special focus was put on the elections in the Buenos Aires province, where the former President \emph{Cristina Fernández de Kirchner} participated as a senator candidate representing the alliance \emph{Unidad Ciudadana}, confronting to the alliance \emph{Cambiemos}, which is the alliance of the current President \emph{Mauricio Macri} and the current governor of Buenos Aires province, \emph{Maria Eugenia Vidal}.

\subsubsection{Current President}
\par \emph{Mauricio Macri} is the current Argentinian President, since December 2015. 
Most articles in political sections are logically devoted to him under different contexts.
However, it is important to point out that during the period analyzed, and specially after the general elections of October 22th, a controversial labour reform promoted by the government was been discussing.

\subsubsection{\emph{Missing Person}}
\par \emph{Santiago Maldonado} vanished on August 1st after a minor clash between the Gendarmerie (Border Guards) and a group of Mapuches, which recognize as themselves the original population of an area in the Patagonia.
Since that event, the \emph{Mauricio Macri}'s administration was accused by several people as the responsible of a \textbf{forced disappearance}. 
\par A very massive campaign in social media took place on August 26th, under the motto "Where is Santiago Maldonado?", followed by two massive protest marches to the \emph{Plaza de Mayo} took place on September 1st and October 1st, which the first one had a great repercussion due to several incidents that took place during the march.
\par The body of \emph{Santiago Maldonado} was found on 17th October in the \emph{Chubut} river, near the place where he was seen the last time, and the autopsy report told that \emph{Santiago Maldonado} had died from ‘asphyxia after being submerged,’ with no injuries on his body. 
However the responsability of the current administration is still being discussed.

\subsubsection{\emph{Former Planning minister} and \emph{Former Vice-President}}

\par \emph{Julio de Vido} was the Planning minister during the administration of \emph{Nestor Kirchner} and \emph{Cristina Fernandez de Kirchner} (2003-2015). In 2015, he was elected to integrate the Chamber of Deputies, which finally voted to strip \emph{De Vido} of his congressional immunity over corruption allegations and was inmmediatly jailed on October 27th.

\par \emph{Amado Boudou} was the Vice-President of the \emph{Cristina Kirchner}'s administration.
\emph{Boudou} was arrested on November 3th on charges including money-laundering and hiding undeclared assests.

\subsubsection{\emph{Social leader} and \emph{Prosecutor's death}}

\par \emph{Milagro Sala} is an indigenous leader’s. 
She has been incarcerated under pre-trial detention ever since she was first detained in January 2016. She faces allegations of embezzlement related to government funding for housing projects managed by Túpac Amaru, her social organization.
Sala accused the government of "violating her human rights", and several people think that she is a political prisoner of the \emph{Mauricio Macri} administration.

\par \emph{Alberto Nisman} was a special prosecutor who were investigating the 1994 terror attack on the Argentine Israeli Mutual Association (AMIA), until his suspicious death on January 2015.
During the period analyzed in this work, a team of experts led by the Gendarmerie (Border Guard) concluded that late prosecutor's death may have been a case of murder, not suicide.

\subsection{Comparison between NMF and LDA}

\par In this section we apply other topic model, Latent Dirichlet Allocation \cite{blei2003latent} (LDA), to our corpus and compare its results to the shown in this paper. Due to the increasingly use of LDA, we think that a few words about the performance of LDA in our work is necessary.

\par Naturally the topics found with LDA may not coincide with the NMF ones.
However, one expects that the corpus under studying should be in some manner robust to the election of the topic model.
On the other hand, as was discussed in \cite{o2015analysis}, NMF can be a more suitable topic modeling method in certain domains, in the way that it produces more coherent topics, while LDA tends to return higher levels of generality and redundancy. Topic coherence is defined as the semantic interpretability of the terms used to describe a particular topic, although the coherence of a topic may depend on the end user's expectations.

\par We define a simple coherence measure defined in equation \ref{eq:topic_coherence}, where $d_{ij}$ is the number of documents where the term $i$ and term $j$ appear simultaneously, and $d_{x}$ is the number of documents where appears the term $x$. The summation is over the $N$ top terms of the topic.
It's important to note that if two terms have no co-occurrences, the contribution to the summation is zero, and if these ones appear only together the contribution is one.
A topic with higher coherence is a topic where the terms that define it co-occurrence frequently.

\begin{equation}
TC = \sum_{i < j}^N \frac{2d_{ij}}{d_i + d_j}
\label{eq:topic_coherence} 
\end{equation}

\par We perform a decomposition into 10 topics using LDA with the python module \emph{gensim} \cite{rehurek_lrec}, which allow us to modify the number of times the corpus is read, improving the coherence of the topics.
Unlike to what we see with NMF, the LDA's performance depends strongly on the initial condition of the algorithm. After 10 iterations, we chose the one with highest mean topic coherence, and compared this with the NMF results.

\par In figure \ref{fig:temporal_profiles_nmf_lda} we show the temporal profiles of topics \emph{Elections} and \emph{Missing Person} for both NMF and LDA. The association between topic models was simply made by looking at the topics which share common keywords.
As can be seen from the figure and the table \ref{table:correlation_nmf_lda}, those LDA topics which can be linked to NMF ones or to a combination of these, show a temporal profile highly correlated.

\par Nevertheless, LDA returns other topics which can not be directly associated, some of them composed of very general words. 
By keeping only those topics which can be associated with NMF and re-defining the Media Agenda over this topic space with reduced dimension, we observed similar results by both methods.  
The same procedure is proposed in absence of an alternative topic model to which make the comparison: Keep only those topics easily interpretable and define the Agendas over this reduced space.

\begin{figure}
\centering
\includegraphics[scale = 0.4]{images/FigA2.pdf}
\includegraphics[scale = 0.4]{images/FigA1.pdf}
\caption{Temporal profiles of topics \emph{Elections} (left) and \emph{Missing Person} (right) for both LDA and NMF. All the topics found by applying NMF have a highly correlated counterpart in LDA.} 
\label{fig:temporal_profiles_nmf_lda}
\end{figure}

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{llc}
\toprule
& Correlation between NMF and LDA \\
\midrule
Elections & \textbf{0.98} \\
Missing person & \textbf{0.99} \\
Former Planning minister + Former Vice-President & \textbf{0.89} \\
Current President & \textbf{0.94} \\
Social leader & \textbf{0.94} \\
Prosecutor's death & \textbf{0.83} \\
\bottomrule
\end{tabular}}
\caption{Correlation between the temporal profiles of the topics found in NMF and associated topics in LDA.}
\label{table:correlation_nmf_lda}
\end{table}

%\input{methodology}
\newpage
\bibliography{bibliography}

\end{document}

### 2018-07-10 paper_balen.tex
Intro arreglada

@@
 
-\par Understand the ecosystem of information flow and opinion formation is one of the goals in these days.
+\par To understand the ecosystem of information flow and opinion formation is one of the goals in these days.
 In this framework, many ingredients can be part of different mechanism of social influence.
-A major role in this ecosystem is played by the Mass Media outlets, which use tu be the source of information of many of us.
-Informed people tends to interact each other, either via personal interactions o through social networks.
+A major role in this ecosystem is played by the Mass Media outlets, which used to be the source of information of many of us.
+Informed people tends to interact with each other, either via personal interactions or through social networks.
 In this scenario, becomes essential to understand the role of Mass Media Influence in a given social group.
@@
 From \cite{mccombs2014agenda}, \textit{``The media agenda is the pattern of news coverage over a period of days, weeks (...) for a set of issues or other topic.
-In other words, the media agenda is a systematic compilation of the issues or topics presented to the public that identifies the degree of emphasis on these topics.''}
+In other words, the media agenda is a systematic compilation of the issues or topics presented to the public that identifies the degree of emphasis on these topics.''}.
+\par In its basic stage, the theory focus on the comparison between the topics coverage by the media and the public agenda, i.e. the topics that the public consider as priority.
+It looks for answering the question if the media is able to set the public agenda, which would transform the media as an important actor in the formation of public opinion. 
+This stage is sometimes called the ``first level agenda-setting''.
+The very often quoted phrase of Bernard C.
+Cohen \textit{``The press may not be successful much of the time in telling people what to think, but it is stunningly successful in telling its readers what to think about.''} illustrates its object of study.
+With the emergency of the Internet, the end of agenda-setting were predicted due to the audience fragmentation onto multiple sources, which would virtually lead to a highly individualized agenda.
+However, it is based on two assumptions that are not necessarily true: the public spreads its attention in an homogeneous way across the multiple sources, and that the agendas of that sources are different \cite{mccombs2005look}.
 
 \par Since the Chapel Hill research, several directions of agenda-setting were established \cite{mccombs2005look}.
-In its basic stage, the theory focus on the comparison between the topics coverage by the media and the public agenda, i.e. the topics that the public consider as priority.
-It looks for answering the question if the media is able to set the public agenda, which would transform the media as an important actor in the formation of public opinion.
-
-% Agenda setting de segundo nivel: noticias con atributos y contextualización.
-\par The basic agenda-setting sometimes is called the ``first level agenda-setting''.
-The very often quoted phrase of Bernard C.
-Cohen \textit{``The press may not be successful much of the time in telling people what to think, but it is stunningly successful in telling its readers what to think about.''} illustrates its object of study.
-On the other hand, the ``second level agenda-setting'', sometimes called \textit{attribute agenda-setting}, studies the \textit{objects} (in a social psychology way, where an \textit{attitude object} designate a thing that an individual has an attitude or opinion about) present in the media agenda.
+The ``second level agenda-setting'', sometimes called \textit{attribute agenda-setting}, studies the \textit{objects} (in a social psychology way, where an \textit{attitude object} designate a thing that an individual has an attitude or opinion about) present in the media agenda.
 When the media talks about an object some attributes are emphasized, and others not.
-
-\par The ``second level agenda-setting'' is linked with \textit{framing} \cite{guggenheim2015dynamics} \cite{tsur2015frame}. 
+This theory is linked with \textit{framing} \cite{guggenheim2015dynamics, tsur2015frame}. 
 To frame is to \textit{select some aspects of a perceived reality and make them more salient in a communicating text, in such a way as to promote a particular problem definition, causal interpretation, moral evaluation and/or treatment recommendation} (Robert Entman) \cite{mccombs2005look}.
 This stage of agenda-setting theory can be summary in the phrase \textit{``the media not only can be successful in telling us what to think about, they also can be successful in telling us how to think about it.''}
-
-\par With the emergency of the Internet, the end of agenda-setting were predicted due to the audience fragmentation onto multiple sources, which would virtually lead to a highly individualized agenda.
-However, it is based on two assumptions that are not necessarily true: the public spreads its attention in an homogeneous way across the multiple sources, and that the agendas of that sources are different \cite{mccombs2005look}.
-%The interaction between media and public is rather complex, for instance, \cite{mitchelstein2016brecha} shows that not necessarily the journalists and public preferences coincide.
-
-\par Other interesting stage of agenda-setting concerns with the sources of media agenda, i.e.
+Other interesting stage of agenda-setting concerns with the sources of media agenda, i.e.
 if the media set the public agenda, \textit{who sets the agenda media?} Within this framework, \textit{intermedia agenda-setting} observes the competition between different media and how they influence each other.
@@
 \par Other line of research have been focused on detecting bias in the media, either by taking into account the number of mentions related  to a preferred political party \cite{lazaridou2016identifying, baumgartner2015all} or by identifying the ideology through the position of the media regards to certain issues or actors \cite{elejalde2018nature, sagarzazu2017hugo}.
-New trends in agenda-setting theory propose to represent ideological aspects or issues emphasized as networks like mind maps, and the basic idea is the comparison between media's knowledge representative network with its counterpart in the audience \cite{guo2012application}\cite{vu2014exploring}.
+New trends in agenda-setting theory propose to represent ideological aspects or issues emphasized as networks like mind maps, and the basic idea is the comparison between media's knowledge representative network with its counterpart in the audience \cite{guo2012application, vu2014exploring}.
 
@@
 In \cite{guggenheim2015dynamics} the competition of frames about gun control is explored, and in \cite{ali2018measuring} the authors show how fluctuations of  twitter activity in different regions depend on the location of terrorist attacks.
-A remarkable exception is found in  \cite{russell2014dynamics},  (CUAN PARECIDO ES AL NUESTRO?) where they work with a set of predefined issues.
+A remarkable exception is found in  \cite{russell2014dynamics}, where they work with a set of predefined issues.
 In this work the question of \emph{causality} is also faced up.
-Their study shows that sometimes the traditional media set the agenda and sometimes, the social media does.
+Their study shows that sometimes the traditional media set the agenda and sometimes the social media does.
 They show that social media is always more interested in social issues than the traditional one, and despite the existence of correlation, the social media agenda can not be seen as a \emph{slave} of the traditional media.
+However, a drawback of working with predefined issues is that they usually reflects general themes, such as unemployment or crime, and the issues selection must be made by the researcher.
 
 % Presentacion y descripcion de nuestro trabajo
-\par In this work we propose a novel method in order to the study the dynamics of Mass Media Agenda as a set of topic evolving in time and their correspondence with the Public and Social Network Agendas.
+\par In this work we propose a novel method in order to study the dynamics of Mass Media Agenda as a set of topic evolving in time and their correspondence with the Public and Social Network Agendas.
 Our work intends to contribute another quantitative approach which complements the agenda-setting theory describe above.
+It mainly stands within the framework of first-level agenda setting, but issues about the comparison between media agendas and framing are also discussed.
 Rather than focus on a single issue or a set of independent topics, we work with the agendas (the media and the public) as an object in their own, studying their evolution over time. 

### 2018-07-10 paper_balen.tex
Algunas cosas de metodos

@@
 
-\par Since the Chapel Hill research, several directions of agenda-setting were established \cite{mccombs2005look}.
+\par From the Chapel Hill research, several directions of agenda-setting were established \cite{mccombs2005look}.
 The ``second level agenda-setting'', sometimes called \textit{attribute agenda-setting}, studies the \textit{objects} (in a social psychology way, where an \textit{attitude object} designate a thing that an individual has an attitude or opinion about) present in the media agenda.
@@
 
-In this work we analyze a three month period of the Argentinian Media's Agenda composed a corpus of news' articles that were published between July 31th and November 5th in the section \emph{Politics} of the electronic editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\''on}, \emph{P\'agina12}, and the news portal \emph{Infobae}.
-The first two lead the sale of printed editions in \emph{Buenos Aires} city, but \emph{Clar\'in} reaches roughly two times the readers of \emph{La Naci\'on}, and ten times the readers of \emph{P\'agina 12} \footnote{www.ivc.org.ar}.
-On the other hand, \emph{Infobae} has the website with more visitors, above the websites of \emph{Clar\'in} and \emph{La Naci\'on} \footnote{https://www.alexa.com/topsites/countries/AR}.
+In this work we analyze a three month period of the Argentinian Media's Agenda composed a corpus of news' articles that were published between July 31th and November 5th in the section \emph{Politics} of the electronic editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\'on}, \emph{P\'agina12}, and the news portal \emph{Infobae}.
+The first two lead the sale of printed editions in \emph{Buenos Aires} city, but \emph{Clar\'in} reaches roughly two times the readers of \emph{La Naci\'on}, and ten times the readers of \emph{P\'agina 12} \cite{IVC}.
+On the other hand, \emph{Infobae} has the website with more visitors, above the websites of \emph{Clar\'in} and \emph{La Naci\'on} \cite{AlexaAR}.
+The corpus analyzed is constituted by 2908 politics articles of \emph{Clar\'in}, 3565 of \emph{La Naci\'on}, 3324 of \emph{P\'agina 12}, and 2018 of \emph{Infobae}.
+Except \emph{P\'agina 12}, all articles were taken from the section \emph{Pol\'itica}  (Politics) of the respective news portal, while the articles which belong to \emph{P\'agina 12} were taken from the section \emph{El pa\'is} (The country).
 
-\par The corpus analyzed is constituted by 2908 politics articles of \emph{Clariin}, 3565 of \emph{La Nacion}, 3324 of \emph{Pagina 12}, and 2018 of \emph{Infobae}.
-Except \emph{Pagina 12}, all articles were taken from the section \emph{Politica}  (Politics) of the respective news portal, while the articles which belong to \emph{Pagina 12} were taken from the section \emph{El pais} (The country).
-
-In order to perform the analysis of the articles in the corpus, we describe them as numerical vectors through the \textit{term frequency - inverse document frequency (tf-idf)} representation [CITA tf-idf].
-Given the set of terms contained in the corpus' words after removing the non-informative ones, such as prepositions and conjunctions, the \textit{tf-idf} algorithm represents the \textit{i}-document as a vector $v_i = [x_{i1}, x_{i2}, ...
+\par In order to perform the analysis of the articles in the corpus, we describe them as numerical vectors through the \textit{term frequency - inverse document frequency (tf-idf)} representation \cite{xu2003document}.
+Given the set of terms contained in the corpus' words after removing non-informative ones, such as prepositions and conjunctions, the \textit{tf-idf} algorithm represents the \textit{i}-document as a vector $v_i = [x_{i1}, x_{i2}, ...
 , x_{it}]$, where the component $x_{ij}$ is computed by the equation \ref{ec:tfidf}, where $\textrm{tf}_{ij}$ is the number of times the \textit{j}-term appears in the \textit{i}-document, $d$ is the number of documents in the corpus, and $n_j$ is the number of documents where the \textit{j}-term appears.
@@
 % See parameters of sklearn.feature_extraction.text.TfidfVectorizer
-\begin{center}
 \begin{equation}
-\begin{split}
-\text{idf}_{j} & = 1 + \textrm{log}(\frac{1 + d}{1 + n_j}) \\
-x_{ij} = \textrm{tf}_{ij} \cdot \textrm{idf}_{j}
-\end{split}
+x_{ij} = \textrm{tf}_{ij} \cdot \textrm{idf}_{j} = \textrm{tf}_{ij} \cdot [1 + \textrm{log}(\frac{1 + d}{1 + n_j})] 
 \label{ec:tfidf}
 \end{equation}
-\end{center}
 
-Then we perform \emph{non-negative matrix factorization (NMF)} on the document-term matrix (\emph{M}) in order to detect the main topics in the corpus.
-A topic is a group of similar articles which roughly talks about the subject.
-\emph{NMF} is an algorithm which factorize a matrix \emph{M} into two matrices \emph{W} and \emph{H} (eq.\ref{eq:nmf}), with the property that all three matrices have no negative elements.
-This non-negativity makes the resulting matrices easier to inspect, and very suitable for topic detection.
+\par We perform \emph{non-negative matrix factorization (NMF)} \cite{xu2003document, lee1999learning} on the document-term matrix (\emph{M}) in order to detect the main topics in the corpus.
+A topic is a group of similar articles which roughly talks about the same subject.
+\emph{NMF} is an algorithm which factorize the matrix \emph{M} into two matrices \emph{W} and \emph{H} (eq.\ref{eq:nmf}), with the property that all three matrices have no negative elements.
+This non-negativity makes the resulting matrices easier to inspect, and very suitable for topic detection \footnote{ Even though there are other techniques in topic detection, as for instance LDA (Latent Dirichlet Allocation), the NMF decomposition suites perfect for the kind of corpus we  have analyzed in this work (A detailed comparison of both, NMF and LDA methods could be found in Supplementary Material)}.
 \begin{equation}
@@
 \end{equation}
+Such as the resulting matrix \emph{H} has dimensions of number of documents per $k$ and matrix \emph{W} has dimensions of $k$ per number of terms, the number $k$ is therefore interpreted as the number of topics in the documents and it is a parameter that must be set before the factorization.
+\par The matrix \emph{H} is the representation of the documents in the topic-space.
+Each row is normalized to unit $l_1$-norm so that their components can be viewed as a degree of membership of a given document in the set of topics.
+In particular, the index of the largest component tells us which is the most representative topic of the document.
+On the other hand, \emph{W} gives the topics representation in the original term-space.
+The largest components of a row give the group of words which represent more accurately each topic (called keywords) and therefore an insight of what the topic is talking about.
+Since the factorization of eq.\ref{eq:nmf} usually can not be made exactly, it is approximated by minimizing the reconstruction error, i.e.
+the distance between matrix \emph{M} and its approximated form $\tilde{M} = H \cdot W$.
+This was performed \emph{NMF} through the python module \emph{scikit-learn} \cite{scikit-learn}.
 
-\par As can be seen in eq.\ref{eq:nmf}, the resulting matrix \emph{H} has dimensions of number of documents per $k$, and matrix \emph{W} has dimensions of $k$ per number of terms.
-The number $k$ is interpreted as the number of topics in the documents and it is a parameter that must be set before the factorization.
-
-  \par The matrix \emph{H} is interpreted as the representation of the documents in the topic-space, and the matrix \emph{W} as the topics represented in the original term-space.
-This factorization usually can not be made exactly so it is approximated by minimizing the reconstruction error, i.e.
-the distance between matrix \emph{M} and its approximated form $\tilde{M} = H \cdot W$.
-We performed \emph{NMF} through the python module \emph{scikit-learn} \cite{scikit-learn}.
-\footnote{ Even though there are other technics in topic detection, as for instance LDA (Latent Dirichlet Allocation), the NMF decomposition suites perfect for the kind of corpus we  have analyzed in this work (A detailed comparison of both, NMF and LDA methods could be found in Supplementary Material)}.
-
-\par The matrix $H$ obtained by \textit{NMF} gives the representation of the documents in the topic-space.
-If we normalize each document's vector to unit $l_1$-norm, their components can be viewed as a degree of membership of a given document in the set of topics.
-In particular, the index of the largest component tells us which is the most representative topic of the document.
-\par On the other hand, each row of matrix $W$ represent the topic in the term-space, i.e., the group of words which represent more accurately each topic (the keywords) and those who give an insight of what the topic is talking about.
-
-\par In order to have a time-dependent representation, we define the temporal profile of the topic $i$, $W_i(day)$ by the eq.
-\ref{eq:topic_weight} where $l(j)$ is the number of words of the document $j$, and $h_{ji}$ is the degree of membership of document $j$ on topic $i$.
-This definition allows all documents to contribute to any topic weight, providing by the fact that each document's vector can have non-zero components in more than one topic.
-\par As last steps of the data's preprocessing, we filter the topics' weight in order to reduce the noise but keeping the most details as possible, by redefining $W_i(day)$ as the mean value of a 3 days width window, centered on the day, as described in equation \ref{eq:topic_weight_norm}.
-\par Finally we normalize again all the temporal profiles in order to describe each newspaper as distribution over the topics' space which evolves over time.
+\par A time-dependent representation is obtained by defining the temporal profile of the topic $i$, $W_i(day)$, by eq.\ref{eq:topic_weight} where $l(j)$ is the number of words of the document $j$, and $h_{ji}$ is the degree of membership of document $j$ on topic $i$.
+Providing by the fact that each document's vector can have all non-zero components, it is allowed that a document contributes to more than one topics' weight.
+In order to reduce noise, we apply a linear filter with a sliding window of size 3, and finally we normalize the temporal profiles in order to describe each newspaper agenda as a distribution over the topics' space which evolves over time.
 This last normalization prevent us against the differences in the number of articles that each newspaper publishes.
@@
 \label{eq:topic_weight}
-\end{equation}
-
-\begin{equation}
-\tilde{W}_i(day) = \frac{1}{3} ({W}_i(day) + {W}_i(day - 1) + W_i(day + 1))
-\label{eq:topic_weight_norm}
 \end{equation}

### 2018-07-11 paper_balen.tex
Varias correcciones hechas

@@
 
-\par A time-dependent representation is obtained by defining the temporal profile of the topic $i$, $W_i(day)$, by eq.\ref{eq:topic_weight} where $l(j)$ is the number of words of the document $j$, and $h_{ji}$ is the degree of membership of document $j$ on topic $i$.
+\par A time-dependent representation is obtained by defining the temporal profile of the topic $i$, $W_i(day)$, by eq.\ref{eq:topic_weight} where $l(j)$ is the number of words of the document $j$, $h_{ji}$ is the degree of membership of document $j$ on topic $i$ and $\delta$ is the Kronecker delta.
 Providing by the fact that each document's vector can have all non-zero components, it is allowed that a document contributes to more than one topics' weight.
@@
 
-\par A point above the upper inner fence considered a mild outlier and a point aove an outer fence is considered an extreme outlier.
-The same holds for the lower fences.
-\footnote{http://www.itl.nist.gov/div898/handbook/prc/section1/prc16.htm}
+\par A point above the upper inner fence considered a mild outlier and a point above an outer fence is considered an extreme outlier. The same holds for the lower fences \cite{natrella2010nist}.
 
-\subsection{Jensen-Shannon divergence}
+\subsection{Jensen-Shannon distance}
 
-\par In probability theory and statistics, the Jensen-Shannon divergence is a method to measure the similarity between two probability distributions.
-It is based on the Kulback-Leibler divergence  ($D_{KL}$)\ref{eq:jensen_shannon_distance}, but have also useful properties such as it is symmetric and it is always a finite value.
-The square root of the Jensen-Shannon divergence \ref{eq:jensen_shannon_distance} is a metric often referred to as Jensen-Shannon distance \cite{fuglede2004jensen}.
+\par In probability theory and statistics, the Jensen-Shannon divergence ($JS_{Div}$) is a method to measure the similarity between two probability distributions.
+It is based on the Kullback-Leibler divergence ($D_{KL}$), but have also useful properties such as it is symmetric and it is always a finite value.
+The square root of the Jensen-Shannon divergence (see eq.\ref{eq:jensen_shannon_distance}, where $M = \frac{P + Q}{2}$) is a metric \cite{fuglede2004jensen} often referred as Jensen-Shannon distance ($JSD$).
 
@@
 D_{KL}(P||Q) = -\sum{P(i) log(\frac{Q(i)}{P(i)})} \\
-\text{JS Divergence}(P||Q) = \frac{1}{2}[D_{KL}(P||M) + D_{KL}(Q||M)] \\
-\text{JS Distance (JSD)} = \sqrt(\text{JS Divergence})
+JSD(P,Q) = \sqrt{JS_{Div}(P,Q)} = \sqrt{\frac{1}{2}[D_{KL}(P||M) + D_{KL}(Q||M)] } \\
 \end{split}
@@
 
-\par The normalized Shannon's entropy \ref{eq:shannon_entropy} as a way to measure how spread is a distribution, taking the maximum value where all outcomes are equally probable in the case of a discrete distribution.
+\par The normalized Shannon's entropy (eq.\ref{eq:shannon_entropy}) is a way to measure how spread is a distribution, taking the maximum value where all outcomes are equally probable in the case of a discrete distribution.
 
@@
 From the initial ten topics, three of them could be interpreted as part of the same macro-topic called \emph{Elections}.
-The same happen with two others which we classified as part of the macro-topic called \emph{Missing person}, leaving the  final description of the agendas is made with seven topics.
-The meaning of the topics or macro-topics are contextualized  in section \ref{sec:Context} of Supplementary Material.
+The same happen with two others which we classified as part of the macro-topic called \emph{Missing person}, leaving the  final description of the agendas as made with seven topics.
+The meaning of the topics or macro-topics is contextualized in section \ref{sec:Context} of Supplementary Material.
 
-After the procedure described in previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, and all their derivations, as time-dependent distributions.
+\par After the procedure described in the previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, and all their derivations, as time-dependent distributions.
 
@@
 In figure \ref{fig:all_agenda} we also highlight some important events related to the dynamics of the topics.
-\footnote{Due to different characteristics in the search tool of Twitter, we adapted the queries employed here but preserving the at least at we can the most important keywords.
+\footnote{Due to different characteristics in the search tool of Twitter, we adapted the queries employed here but preserving at least at we can the most important keywords.
 The queries employed by topic were: \\
@@
 % Wordclouds
-\begin{figure}[h]
+\begin{figure}[H]
 \centering
@@
 Topics names are introduced together with the wordclouds containing the most important keywords involved in the definition of each topic.
-In green color we show the keywords used to define the topics in the Google Trends and Twitter queries (see table \ref{table:gt_all_correlation}) and therefore in our construction of the Public Agenda.}
+In green color we show the keywords used to define the topics in the Google Trends and Twitter queries (see table \ref{table:gt_queries}) and therefore in our construction of the Public Agenda.}
 \label{fig:topics_wordclouds}
@@
 % Global Agenda figure!!!
-\begin{figure}[h]
+\begin{figure}[H]
 \includegraphics[width = \textwidth]{images/Fig2.pdf}
@@
 
-\begin{table}[h]
+\begin{table}[H]
 \centering
@@
 Elections & elecciones + cambiemos + cristina kirchner + massa + randazzo \\
-Missing person & santiago maldonado + juez otranto + patricia bullrich + gendarmería + desaparición forzada \\
-Former Planning minister & de vido + desafuero + ministro de planificación + minnicelli + baratta \\
+Missing person & santiago maldonado + juez otranto + patricia bullrich + gendarmería + desaparici\'on forzada \\
+Former Planning minister & de vido + desafuero + ministro de planificaci\'on + minnicelli + baratta \\
 Current President & mauricio macri + cgt + reforma laboral + peña + triaca \\
 Social leader & milagro sala + cidh + tupac amaru + pullen llermanos + morales \\
-Prosecutor's death & nisman + amia + memorándum con irán + timerman + juez bonadio \\
+Prosecutor's death & nisman + amia + memor\'andum con ir\'an + timerman + juez bonadio \\
 Former Vice-President & amado boudou + ciccone + ariel lijo + vandenbroele + núñez carmona \\
@@
 
-\par The figures introduced above show not only the topics and their differences between Agendas, but also the dynamics of the topics.
+\par The figures introduced above show not only the topics and their differences between the Agendas, but also the dynamics of the topics.
 For instance, we can see in the radar plot of figure \ref{fig:topics_wordclouds}, a greater interest of the audience in the topic \emph{Missing person} than the Media, or inversely in the topic \emph{Prosecutor's death}, at least in the analyzed time-lapse.
@@
 \par A lower value in the agenda's diversity is due to the fact that the most important topic attracts practically all the attention of the public and the media.
-In the radar plots included in figure \ref{fig:shannon_entropy_agendas} we can see that two of these outliers (\textbf{a} and \textbf{d}) belong to the topic \emph{Elections} and coincide with the primary and general legislative elections that took place in August 13th and October 22th.
+In the radar plots included in figure \ref{fig:shannon_entropy_agendas} we can see that two of these outliers (\textbf{a} and \textbf{d}) belong to the topic \emph{Elections} and are related with the primary and general legislative elections that took place in August 13th and October 22th.
 In all the agendas these points where detected as outliers except point (d) in Twitter Agenda.
 Why is that?
-The radar plot of the Twitter agenda for this day displays an association between the topic \emph{Elections} and the \emph{Current President} which could be decreasing the important this topic.
+The radar plot of the Twitter agenda for this day displays an association between the topic \emph{Elections} and the \emph{Current President} which could be decreasing the important of this topic.
 Discussions in Twitter about elections appear also in point (c), when the other agendas seems to be more diverse. 
 On the other hand, we focused in point (b), despite not being detected as a outlier, because it belong to the topic \emph{Missing person} and this date correspond to the rally that took place one month after the disappearance of Santiago Maldonado (see section \ref{sec:Context}).
-It is important to notice that, the Shannon's Entropy of GT Agenda displays a minimum (collapsing agenda) not shown neither in the Media nor in the Twitter Agendas.
+It is important to notice that the Shannon's Entropy of GT Agenda displays a minimum (collapsing agenda) not shown neither in the Media nor in the Twitter Agendas.
 We emphasize the discussion about this topic because we can appreciate  interesting facts that appear along the analysis.
 
-\begin{figure}[h]
+\begin{figure}[H]
 \centering
@@
 \par From the measure of $H$ we can also see that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
-Specifically $H_{Gt} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
+Specifically $H_{GT} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
 However from figure \ref{fig:shannon_entropy_agendas} we can see that \textbf{GT} shows more abrupt dropouts in the diversity in response to specific events.
@@
 
-\par Given our interpretation of  the Agendas and time-evolving distributions, we can  compare them by computing the Jensen-Shannon distance.
+\par Given our interpretation of the Agendas as time-evolving distributions, we can  compare them by computing the Jensen-Shannon distance.
 In this context, outliers in selected dates will correspond to divergences between Public and Media Agenda, i.e., specific events where the public interest do not match with media offer.
@@
 In all cases, the topic distributions at that particular dates displayed by  the radar plots shows that a greater distance is associated with a more interest of public in the topic \emph{Missing person}.
-\par Points \textbf{(c)} and \textbf{(d)} shows that both the Public and the Media highlight this topic, but the Media do not disregard other topics, so the corresponding distance between them can be interpreted  of another way of see  the diversity effect discussed in the last section.
+\par Points \textbf{(c)} and \textbf{(d)} shows that both the Public and the Media highlight this topic, but the Media do not disregard other topics, so the corresponding distance between them can be interpreted  of another way of seeing the diversity effect discussed in the last section.
 
@@
 It can be associates  with a social networks (like Facebook and Twitter) campaign  in favor  of the appearance of Santiago Maldonado ("The missing person") that took place on  August 26th.
-It was very important and and was initially underestimated by the main Media outlets in Argentina (see section \ref{sec:Context}).
+It was very important and was initially underestimated by the main Media outlets in Argentina (see section \ref{sec:Context}).
 
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
 \centering
@@
 \par In figure \ref{fig:news_agenda} we can see in a qualitative way the slightly differences between the newspapers' agendas.
-For instance, we can see how newspaper called \emph{Pagina 12} gave more importance to the topics \emph{Missing person} and \emph{Social leader}, while it reduces to minimum the coverage of the topic  \emph{Former Planning minister} as the others did.
+For instance, we can see how newspaper called \emph{P\'agina 12} gave more importance to the topics \emph{Missing person} and \emph{Social leader}, while it reduces to minimum the coverage of the topic  \emph{Former Planning minister} as the others did.
 
 % Jensen shannon distance of Dynamic way
-\begin{figure}[h]
+\begin{figure}[H]
 \centering
@@
 \caption{\textbf{Bump charts of newspapers' Agenda and radar plot of the average distributions.} The figure shows, in a qualitative way, the bias in the different newspaper's agendas.
-For instance, the greater interest of \emph{Pagina 12 (P12)} in the \emph{Missing person} topic and its slightly lower coverage in the \emph{Former Planning minister} respect to the other newspapers.}
+For instance, the greater interest of \emph{P\'agina 12 (P12)} in the \emph{Missing person} topic and its slightly lower coverage in the \emph{Former Planning minister} respect to the other newspapers.}
 \label{fig:news_agenda}
@@
 We detect three points as outliers, although we discard the point \textbf{(b)} due to the low information of \emph{Infobae} in that period. 
-The other two points corresponds to differences between \emph{Pagina 12} and the other newspapers and correspond to differences in the coverage of the topic \emph{Missing person}.
+The other two points corresponds to differences between \emph{P\'agina 12} and the other newspapers and correspond to differences in the coverage of the topic \emph{Missing person}.
 
-\par The point \textbf{(a)} corresponds  to the first news of the Santiago Maldonado's disappearance  reported by \emph{Pagina 12} before the primary elections, and in point \textbf{(c)} to  the two months rally after the disappearance took place (see section \ref{sec:Context}).
-Another difference in point \textbf{(c)} corresponds to a greater coverage of \emph{Pagina 12} in the topic \emph{Social leader} where the others media outlets seem to be more interested in the topic \emph{Former Vice-President}.
+\par The point \textbf{(a)} corresponds  to the first news of the Santiago Maldonado's disappearance  reported by \emph{P\'agina 12} before the primary elections, and in point \textbf{(c)} to  the two months rally after the disappearance took place (see section \ref{sec:Context}).
+Another difference in point \textbf{(c)} corresponds to a greater coverage of \emph{P\'agina 12} in the topic \emph{Social leader} where the others media outlets seem to be more interested in the topic \emph{Former Vice-President}.
 
 % Jensen shannon distance of Dynamic way
-\begin{figure}[h]
+\begin{figure}[H]
 \centering
@@
 \caption{\textbf{Jensen-Shannon distance between the newspapers agenda and the Media Agenda as a function of time}.
-\emph{Pagina 12} shows the more different behavior, motivated again by its interest in the \emph{Missing person} and \emph{Social leader} topics as can be seen in the radar plots which belongs to points (a) and (c).
+\emph{P\'agina 12} shows the more different behavior, motivated again by its interest in the \emph{Missing person} and \emph{Social leader} topics as can be seen in the radar plots which belongs to points (a) and (c).
 The anomalous behavior of \emph{Infobae} at pint (b) is due to few articles around that date in our database, therefore we ignore its radar plot.
@@
 
-\par The greater coverage in the topic \emph{Missing person} by \emph{Pagina 12} is even more clear if we inspect the temporal profile of the topic and compare the coverage given by each newspaper.
-A difference in the coverage is what it is called \emph{coverage bias} [CITA ACA SEBAS].
+\par The greater coverage in the topic \emph{Missing person} by \emph{P\'agina 12} is even more clear if we inspect the temporal profile of the topic and compare the coverage given by each newspaper.
+A difference in the coverage is what it is called \emph{coverage bias} \cite{dallmann2015media}.
 In figure \ref{fig:topics_temporal_profiles} we show the temporal profile of the topic \emph{Missing person} (panel (a)) and the topic \emph{Former Planning minister} in panel (b), as an example where the behavior is the opposite, as can be seen below.
 
-\begin{figure}[h]
+\begin{figure}[H]
 \centering
@@
 We interpreted the differences shown in given periods as an indicator of coverage bias.
-For instance, in figure (a) Pagina 12 pays a greater attention in the first days.
+For instance, in figure (a) \emph{P\'agina 12} pays a greater attention in the first days.
 In the word-clouds, we show which of the defining words are more frequently used by the corresponding newspaper.
@@
 
-\par From panel (a) of figure \ref{fig:topics_temporal_profiles}, we can see the larger coverage of \emph{Pagina 12} respect the other newspapers at the beginning of the period.
+\par From panel (a) of figure \ref{fig:topics_temporal_profiles}, we can see the larger coverage of \emph{P\'agina 12} respect the other newspapers at the beginning of the period.
 We can, for instance, quantify this difference calculating  the median of the signals.
-If we focus in the period between July 31th and August 27th, the median of the topic's relative weight for \emph{Pagina 12} is roughly 0.14 and this is statistically significant larger ($p < 10^{-7}$) than other medians, which are lower than 0.05.
-Analyzing the same period, but in panel (b), we again can show that the median in \emph{Pagina 12}, which is roughly 0.01, is lower than the others, which oscillate around 0.05 ($p<10^{-3}$)
+If we focus in the period between July 31th and August 27th, the median of the topic's relative weight for \emph{P\'agina 12} is roughly 0.14 and this is statistically significant larger ($p < 10^{-7}$) than other medians, which are lower than 0.05.
+Analyzing the same period, but in panel (b), we again can show that the median in \emph{P\'agina 12}, which is roughly 0.01, is lower than the others, which oscillate around 0.05 ($p<10^{-3}$)
 This quantification is proposed as method of studying coverage bias in the context of the methodology implemented in our work.
@@
 \par Finally, in figure \ref{fig:topics_temporal_profiles} we also show word-clouds of topic's keywords but separating those who are more frequently mentioned by each newspaper, and filtering the words that are common to all and basically define the factual details of the topic.
-Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represion} (repression) when \emph{Pagina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (Fernandez de Kirchner, former president) which is employed by all newspapers except \emph{Pagina 12} when they  talk about the topic \emph{Former Planning minister} (see section \ref{sec:Context}).
+Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represi\'on} (repression) when \emph{P\'agina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (Fernandez de Kirchner, former president) which is employed by all newspapers except \emph{P\'agina 12} when they  talk about the topic \emph{Former Planning minister} (see section \ref{sec:Context}).
 
@@
 These are mere observation that talk about the correlation between the agendas.
-However the agenda-setting theory is in its nature a theory about causality:vIs the audience a passive actor who follows what the Media says, or there are periods where the Media must paid attention at public's interests?
+However the agenda-setting theory is in its nature a theory about causality: Is the audience a passive actor who follows what the Media says, or there are periods where the Media must paid attention at public's interests?
 Paraphrasing the question, who sets the agenda, the Media or the audience?
@@
 \par In figure \ref{fig:Maldonado_setagenda} we show the topic's relative weight from the Public and Media Agendas.
-After the initial coverage, the agendas seem to differentiate around August 16th, when topic started to became more important in the Public Agenda than in the Media one.
-Around August 24th, the topic abruptly increase in public's interest while the reaction in the Media is slower, showing a significant peak in the plot of the discrete difference (panel (b)) (SEBAS, PODES SENALAR ESTAS FECHAS CON LINEAS PUNTEADAS EN EL GRAFICO?).
+After the initial coverage, the agendas seem to differentiate around August 15th, when topic started to became more important in the Public Agenda than in the Media one.
+Around August 24th, the topic abruptly increase in public's interest while the reaction in the Media is slower, showing a significant peak in the plot of the discrete difference (panel (b)).
 This date is very close to August 26th, when a campaign in social media took place.
@@
 This measure can be seen as the numerical integrate of the temporal profiles of figure \ref{fig:topics_temporal_profiles} between the initial date and the current date. 
-It is interesting to note that the newspaper responsible to accumulate coverage during the initial stage was the minority one: \emph{Pagina 12}.
+It is interesting to note that the newspaper responsible to accumulate coverage during the initial stage was the minority one: \emph{P\'agina 12}.
 
-Our interpretation about the setting agenda dynamics of this particular topic is the following: A small newspaper (\emph{Pagina 12}) gives great coverage to this topic; it is amplified  by public in the social networks and also expressed  by reiterative Google searches.
+Our interpretation about the setting agenda dynamics of this particular topic is the following: A small newspaper (\emph{P\'agina 12}) gives great coverage to this topic; it is amplified  by public in the social networks and also expressed  by reiterative Google searches.
 Then the rest of the Media  pay attention to this subject and it becomes an important topic in the Media Agenda.
 This interpretation try to catch in a qualitative way how the information flow was in this specific topic.
-On the other hand, behind this interpretation there are two important facts that must be mentioned: First, the disappearance of a person is a very sensible theme for the Argentinian society, and second, there are political reasons in why \emph{Pagina 12} was particularly interested in cover this topic while the other Media did not follow this interest.
+On the other hand, behind this interpretation there are two important facts that must be mentioned: First, the disappearance of a person is a very sensible theme for the Argentinian society, and second, there are political reasons in why \emph{P\'agina 12} was particularly interested in cover this topic while the other Media did not follow this interest (see section \ref{sec:Context}).
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 \includegraphics[width = \textwidth]{images/Fig8.pdf}
 \caption{\textbf{Agenda setting direction in Missing person's topic?}
-The temporal profiles of figure (a) show that the Public increased abruptly its interest in the topic around August 24th, which belongs to the peak \textbf{(*)} shown in figure (b), where the discrete differences were computed.
-This date is also pointed out in the rest of the figures with a vertical grey line together with the asterisk. 
-With the computing of the cumulative sum of figure \ref{fig:topics_temporal_profiles} and figure (a), represented as a bump chart in figure (c), we suggest that the topic was first set by \emph{Pagina 12} and then the Public's interest cause the coverage of the other Media.
+The temporal profiles of figure (a) show that the Public and Media agenda seem to differentiate around August 15th (vertical grey line (1)) and the Public increase abruptly its interest in the topic around August 24th (grey line (2)).
+It can be seen also in figure (b), where the discrete differences were computed.
+With the computing of the cumulative sum of figure \ref{fig:topics_temporal_profiles} and figure (a), represented as a bump chart in figure (c), we suggest that the topic was first set by \emph{P\'agina 12} and then the Public's interest cause the coverage of the other Media.
 }
@@
 \par Two legislative elections were celebrated during the period in great part of the Argentina: Primary elections on August 13th and the general elections on October 22th. 
-A special focus was put on the elections in the Buenos Aires province, where the former President \emph{Cristina Fernández de Kirchner} participated as a senator candidate representing the alliance \emph{Unidad Ciudadana}, confronting to the alliance \emph{Cambiemos}, which is the alliance of the current President \emph{Mauricio Macri} and the current governor of Buenos Aires province, \emph{Maria Eugenia Vidal}.
+A special focus was put on the elections in the Buenos Aires province, where the former President \emph{Cristina Fern\'andez de Kirchner} participated as a senator candidate representing the alliance \emph{Unidad Ciudadana}, confronting \emph{Cambiemos}, which is the alliance of the current President \emph{Mauricio Macri} and the current governor of Buenos Aires province \emph{Maria Eugenia Vidal}.
 
@@
 Since that event, the \emph{Mauricio Macri}'s administration was accused by several people as the responsible of a \textbf{forced disappearance}. 
-\par A very massive campaign in social media took place on August 26th, under the motto "Where is Santiago Maldonado?", followed by two massive protest marches to the \emph{Plaza de Mayo} took place on September 1st and October 1st, which the first one had a great repercussion due to several incidents that took place during the march.
+\par A very massive campaign in social media took place on August 26th, under the motto "Where is Santiago Maldonado?", followed by two massive protest marches to the \emph{Plaza de Mayo} that took place on September 1st and October 1st, which the first one had a great repercussion due to several incidents that took place during the march.
 \par The body of \emph{Santiago Maldonado} was found on 17th October in the \emph{Chubut} river, near the place where he was seen the last time, and the autopsy report told that \emph{Santiago Maldonado} had died from ‘asphyxia after being submerged,’ with no injuries on his body.
-However the responsability of the current administration is still being discussed.
+However the responsibility of the current administration is still being discussed.
 
@@
 \par \emph{Julio de Vido} was the Planning minister during the administration of \emph{Nestor Kirchner} and \emph{Cristina Fernandez de Kirchner} (2003-2015).
-In 2015, he was elected to integrate the Chamber of Deputies, which finally voted to strip \emph{De Vido} of his congressional immunity over corruption allegations and was inmmediatly jailed on October 27th.
+In 2015, he was elected to integrate the Chamber of Deputies, which finally voted to strip \emph{De Vido} of his congressional immunity over corruption allegations and was immediatly jailed on October 27th.
 
@@
 She has been incarcerated under pre-trial detention ever since she was first detained in January 2016.
-She faces allegations of embezzlement related to government funding for housing projects managed by Túpac Amaru, her social organization.
+She faces allegations of embezzlement related to government funding for housing projects managed by T\'upac Amaru, her social organization.
 Sala accused the government of "violating her human rights", and several people think that she is a political prisoner of the \emph{Mauricio Macri} administration.
@@
 
-\begin{figure}
+\begin{figure}[H]
 \centering

### 2018-07-12 paper_balen.tex
Version para mandarsela a Pablo

@@
 Several works by E.
-Zunino, like \cite{zunino2010cobertura} and \cite{koziner2013cobertura}, studied the coverage given by the main newspapers of particular events which have happened during the former administration of Argentinean president \emph{Cristina Fernandez de Kirchner} (from 2007 to 2015), where the government started to confront with news organizations that were critical to its management as they were an opposition party \cite{mitchelstein2017information}
+Zunino, like \cite{zunino2010cobertura} and \cite{koziner2013cobertura}, studied the coverage given by the main newspapers of particular events which have happened during the former administration of Argentinian president \emph{Cristina Fernandez de Kirchner} (from 2007 to 2015), where the government started to confront with news organizations that were critical to its management as they were an opposition party \cite{mitchelstein2017information}
 
@@
 
+\par From the measure of $H$ we can also see that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
+Specifically $H_{GT} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
+However from figure \ref{fig:shannon_entropy_agendas} we can see that \textbf{GT} shows more abrupt dropouts in the diversity in response to specific events.
+We conclude that its an important fact about audience behavior: given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus more in the most important topic than the Media can do, maybe due to editorial decisions.
+
 \begin{figure}[H]
@@
 \end{figure}
-
-\par From the measure of $H$ we can also see that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
-Specifically $H_{GT} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
-However from figure \ref{fig:shannon_entropy_agendas} we can see that \textbf{GT} shows more abrupt dropouts in the diversity in response to specific events.
-We conclude that its an important fact about audience behavior: given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus more in the most important topic than the Media can do, maybe due to editorial decisions.
 
@@
 
-% Jensen shannon distance of Dynamic way
-\begin{figure}[H]
-\centering
-\includegraphics[width = \textwidth]{images/Fig5.pdf}
-\caption{\textbf{Bump charts of newspapers' Agenda and radar plot of the average distributions.} The figure shows, in a qualitative way, the bias in the different newspaper's agendas.
-For instance, the greater interest of \emph{P\'agina 12 (P12)} in the \emph{Missing person} topic and its slightly lower coverage in the \emph{Former Planning minister} respect to the other newspapers.}
-\label{fig:news_agenda}
-\end{figure}
-
 %\subsubsection{Independent behavior}
@@
 Another difference in point \textbf{(c)} corresponds to a greater coverage of \emph{P\'agina 12} in the topic \emph{Social leader} where the others media outlets seem to be more interested in the topic \emph{Former Vice-President}.
+
+% Jensen shannon distance of Dynamic way
+\begin{figure}[H]
+\centering
+\includegraphics[width = \textwidth]{images/Fig5.pdf}
+\caption{\textbf{Bump charts of newspapers' Agenda and radar plot of the average distributions.} The figure shows, in a qualitative way, the bias in the different newspaper's agendas.
+For instance, the greater interest of \emph{P\'agina 12 (P12)} in the \emph{Missing person} topic and its slightly lower coverage in the \emph{Former Planning minister} respect to the other newspapers.}
+\label{fig:news_agenda}
+\end{figure}
 
@@
 
+\par We provide here a more detailed explanation of the topics discussed among this work.
+The ideology of the media in Argentina expresses the highly polarized politic climate observe in Argentinian society.
+During the administration of \emph{Cristina Fern\'andez de Kirchner} (2007-2015), the government maintained a conflict with several news organizations.
+It led media such as \emph{Clar\'in}, \emph{La Naci\'on} and the portal news \emph{Infobae} to be very critics of the \emph{Fern\'andez}'s administration, emphasizing the allegations of corruption related to it as can be seen in the importance given to the topics \emph{Former Planning minister} and \emph{Former Vice-President}.
+On the other hand, \emph{P\'agina 12} has a opposite ideological inclination, supporting the former administration of \emph{Cristina Kirchner} and therefore being very critical with the current \emph{Maurico Macri}'s administration, doing special emphasis on issues related to human rights, as can be again observed in the coverage given to the topics \emph{Social leader} and \emph{Missing person}.
+
 \subsubsection{\emph{Elections}}

### 2018-07-13 paper_balen.tex
Version para subir al arxiv

@@
 
-The Agenda Setting theory provides a conceptual framework in order to understand the role played by the Mass Media in a society.
-Within this framework, the Media are not only capable to make people think about certain issues, but also to make how to think about them.
-When this is accomplished,  we say that the media set the agenda.
-In this work we study the agenda of Argentinian newspapers in comparison with public's interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time.
-We measure Agenda's diversity as a function of time using Shannon's entropy and difference between Agendas using Jensen-Shannon's distance.
-We found that the Public Agenda is less diverse than the Media Agenda, and we are also capable to detect periods of time where coverage of certain issues are biased (coverage bias).
-\\
+The mass media play a fundamental role in the formation of public opinion, either by defining the topics of discussion or by making a degree of emphasis on certain issues.
+Directly or indirectly, people get informed by consuming news from the media.
+But which is the dynamic of the agenda and how the people becomes interested in the different topics of the agenda?
+The Agenda Setting theory provides a conceptual framework in order to understand the role played by the mass media in public opinion formation, but the previous questions can not be answered without proper quantitative measures of agenda's dynamic and public attention.
+In this work we study the agenda of Argentinian newspapers in comparison with public’s interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time.
+We measure Agenda’s diversity as a function of time using Shannon’s entropy and difference between Agendas using Jensen-Shannon’s distance.
+We found that the Public Agenda is less diverse than the Media Agenda, and we are also capable to detect periods of time where coverage of certain issues are biased (coverage bias).\\
 

### 2018-07-13 agenda_diversity.tex
Comentarios borrados en el bib

--- 2018-07-13 paper_balen.tex
@@
 
-%\twocolumn[
-%\begin{@twocolumnfalse}
 \maketitle
@@
 Directly or indirectly, people get informed by consuming news from the media.
-But which is the dynamic of the agenda and how the people becomes interested in the different topics of the agenda?
-The Agenda Setting theory provides a conceptual framework in order to understand the role played by the mass media in public opinion formation, but the previous questions can not be answered without proper quantitative measures of agenda's dynamic and public attention.
+But which is the dynamics of the agenda and how the people becomes interested in the different topics of the agenda?
+The Agenda Setting theory provides a conceptual framework in order to understand the role played by the mass media in public opinion formation, but the previous questions can not be answered without proper quantitative measures of agenda's dynamics and public attention.
 In this work we study the agenda of Argentinian newspapers in comparison with public’s interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time.
@@
 
-%\end{@twocolumnfalse}
-%]
 \section{Introduction}
-%PRIMERA PARTE TEORIA DE AGENDA SETTING
+
 \subsection{Agenda Setting Theory}
-
-% Introduccion y descripcion de agenda-setting en su nivel mas basico.
 
@@
 
-% ACA ARRANCA LA REESTRUCTURACION NUEVA
-%\subsection{Related works}
-
 \par Since the irruption of internet in our lives and the access to big data, there were many attempts to analyze from a quantitative point of view the theory of Agenda Setting based on  the original work of McCombs \cite{mccombs1972agenda}.
@@
 
-% Algo sobre bias
 \par Other line of research have been focused on detecting bias in the media, either by taking into account the number of mentions related  to a preferred political party \cite{lazaridou2016identifying, baumgartner2015all} or by identifying the ideology through the position of the media regards to certain issues or actors \cite{elejalde2018nature, sagarzazu2017hugo}.
@@
 
-% Presentacion y descripcion de nuestro trabajo
 \par In this work we propose a novel method in order to study the dynamics of Mass Media Agenda as a set of topic evolving in time and their correspondence with the Public and Social Network Agendas.
@@
 
-%\input{description}
 \section{Materials and Methods} \label{sec:MatMeth}
@@
 
-% See parameters of sklearn.feature_extraction.text.TfidfVectorizer
 \begin{equation}
@@
 We take advantage of topics' keywords on the one hand by making queries to the \emph{Google Trends} tool and getting the relative weight of \emph{Google} searches that people made about the identified topics, and in the other hand, by making queries to the advance search tool in the social media \emph{Twitter} in order to get the relative amount of related tweets .
-
-%\par Following the procedures described above, we obtain two evolving in time discrete distribution in the topic space: The \textbf{Media Agenda (MA)}, and the \textbf{Public Agenda (PA)}, which could be represented by two faces, one given by \textbf{Google Trends (Gt)} and the other by \textbf{Twitter (Tw)}.
-%In the final part of this analysis, the Media Agenda will also be described for each of the newspapers (or portal news) taken into consideration.
-
-%After normalization, all agendas are described as a time dependent distribution over the topic's space, where the time scale is day by day.
-Therefore the agendas give us the relative importance of a given topic respect the other (i.e.
-it does not give us absolute values such as the number of titles or tweets associated).
 
@@
 
-%EL PRIMER PASO PARA UNA DESCRIPCION CUANTITATIVA ES TENER UNA REPRESENTACION MATEMATICA DE CADA NOTICIA.
-PARA ESO USAMOS EL METODO TF-IDF QUE REPRESENTA AL TEXTO COMO UN VECTOR EN EL ESPACIO DE PALABRAS.
-CADA COMPONENTE (CORRESPONDIENTE A UNA DADA PALABRA) REPRESENTA LA FRECUENCIA DE APARICION DE DICHA PALABRA EN EL TEXTO (TF) PONDERADA POR LA IMPORTANCIA RELATIVA DE DICHA PALABRA EN EL TEXTO, RESPECTO AL CORPUS TOTAL (IDF).
-
-%LUEGO DIVIDIMOS AL CORPUS EN 10 TOPICOS USANDO ALGUNA TECNICA DE AGRUPAMIENTO NO SUPERVISADO. 2 ACLARACIONES:
-%1 - PORQUE 10?  PORQUE REPRESENTAN LAS TIPICAS 10 NOTICIAS MAS LEIDAS, UNA CLASIFICACION HABITUAL EN LOS PORTALES DE NOTICIAS. 
-%2 - AGRUPAMOS LAS NOTICIAS USANDO LA TECNICA DE NMF, QUE NOS PERMITE NO SOLO DIVIDIR LAS NOTICIAS EN GRUPOS DE NOTICIAS SIMILARES (TOPICOS), SINO REPRESENTAR CADA GRUPO COMO UN SER DE PALABRAS CLAVES, QUE CORRESPONDE A UNA DADA DIRECCION EN EL ESPACIO DE PALABRAS.
-SI BIEN EXISTEN TECNICAS MAS USADAS COMO LDA, LOS RESULTADOS PARA LOS CORPUS DE NOTICIAS USADOS NOS HAN RESULTADO MEJOR USANDO NMF.
-UNA COMPARACION EXHAUSTIVA DE AMBAS TECNICAS SE PODRAN HALLAR EN EL APENDICE.
-
-%EL ANALISIS QUE HACEMOS NOS PERMITE, LUEGO DE DIVIDIR AL CORPUS EN 10 TOPICOS, REPRESENTAR CADA NOTICIA EN EL ESPACIO DE TOPICOS.
-DADA LA NORMALIZACION ELEGIDA, LA COMPONENTE DE CADA NOTICIAS EN EL ESPACIO DE TOPICOS REPRESENTA EL PESO QUE TIENE DICHO TOPICO EN LA NOTICIA.
-DE ESTA MANERA SE PUEDE SACAR EL PESO DE UN DADO TOPICO POR DIA, MIRANDO LOS PESOS DE LAS NOTICAS EN DICHO TOPICO Y MULTIPLICANDO POR EL LARGO DE LA NOTICIA, COMO MUESTRA LA EQ (XX).
-
-%\par The performed analysis mainly consist  in topic detection over the corpus' articles in order to describe it as a set of topics \cite{griffiths2004finding} which evolve over time.
-A "Topic" is a cluster of  new's articles related to the same subject.
-They refers to the same "topic" and are represented by a set of keywords that allow us to interpret and understand what the topics are talking about.
-In this work we take the whole corpus of new's articles and divide them in ten topics.
-A
-%Topic detection is a powerful computational technique that allows us to analyze a big amount of texts that can be impossible otherwise
-
-%For a careful description of the  implemented methodology please see Appendix.
-
 \section{Results}
@@
 
-% Wordclouds
 \begin{figure}[H]
@@
 
-% Global Agenda figure!!!
 \begin{figure}[H]
@@
 \end{figure}
-
-% Table with queries and correlations
-%\input{discussion/table_gt_queries_correlation}
 
@@
 
-% Agenda diversity
-
 \par In order to quantify the diversity of the Agendas, we start by representing them as distributions in the topic's space. 
@@
 \subsubsection{Distance between Media and Public Agenda's }
-
-% Jensen-Shannon distance between PA and MA
 
@@
 
-%\subsubsection{Independent behavior}
-
 \par In other to detect outliers behavior of a given newspaper respect to the others, we again calculate the Jensen-Shannon distance between the newspapers agenda and the Media Agenda.
@@
 
-% Jensen shannon distance of Dynamic way
 \begin{figure}[H]
@@
 \end{figure}
-
-%\subsubsection{Coverage bias}
 
@@
 
-%\input{conclusions}
 \section{Conclusions}
@@
 Future works may include a more systematic study and its extension to international Media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitative analysis about causality.
-
-%\input{discussion/discussion}
 
@@
 
-%\input{methodology}
 \newpage

### 2018-07-13 agenda_diversity.tex
Version bien compilada por arxiv
Version subida

@@
 %\usepackage[utf8]{inputenc}
+\pdfoutput=1
 \usepackage{graphicx}
@@
 Directly or indirectly, people get informed by consuming news from the media.
-But which is the dynamics of the agenda and how the people becomes interested in the different topics of the agenda?
+But which is the dynamics of the agenda and how the people become interested in the different topics of the agenda?
 The Agenda Setting theory provides a conceptual framework in order to understand the role played by the mass media in public opinion formation, but the previous questions can not be answered without proper quantitative measures of agenda's dynamics and public attention.
-In this work we study the agenda of Argentinian newspapers in comparison with public’s interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time.
-We measure Agenda’s diversity as a function of time using Shannon’s entropy and difference between Agendas using Jensen-Shannon’s distance.
+In this work we study the agenda of Argentinian newspapers in comparison with public's interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time.
+We measure Agenda's diversity as a function of time using Shannon's entropy and difference between Agendas using Jensen-Shannon's distance.
 We found that the Public Agenda is less diverse than the Media Agenda, and we are also capable to detect periods of time where coverage of certain issues are biased (coverage bias).\\
@@
 \centering
-\includegraphics[width = \textwidth]{images/Fig1.pdf}
+\includegraphics[width = \textwidth]{Fig1.pdf}
 \caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic distribution and their corresponding wordclouds.} The Public Agenda is represented either by Google Trends (GT) and Twitter (Tw).
@@
 \begin{figure}[H]
-\includegraphics[width = \textwidth]{images/Fig2.pdf}
+\includegraphics[width = \textwidth]{Fig2.pdf}
 \caption{\textbf{Bump graph of the Media Agenda (MA) and Public Agenda extracted from Google Trends (GT) and Twitter (Tw)}.
@@
 
-\par From the measure of $H$ we can also see that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
-Specifically $H_{GT} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
-However from figure \ref{fig:shannon_entropy_agendas} we can see that \textbf{GT} shows more abrupt dropouts in the diversity in response to specific events.
-We conclude that its an important fact about audience behavior: given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus more in the most important topic than the Media can do, maybe due to editorial decisions.
-
 \begin{figure}[H]
 \centering
-\includegraphics[height=0.75\textheight]{images/Fig3.pdf}
+\includegraphics[height=0.7\textheight]{Fig3.pdf}
 \caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda show a less diverse behavior than the Media Agenda as can be seen in the left figure.
@@
 \end{figure}
+
+\par From the measure of $H$ we can also see that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
+Specifically $H_{GT} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
+However from figure \ref{fig:shannon_entropy_agendas} we can see that \textbf{GT} shows more abrupt dropouts in the diversity in response to specific events.
+We conclude that its an important fact about audience behavior: given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus more in the most important topic than the Media can do, maybe due to editorial decisions.
 
@@
 \centering
-\includegraphics[height = 0.75\textheight]{images/Fig4.pdf}
+\includegraphics[height = 0.7\textheight]{Fig4.pdf}
 \caption{\textbf{Jensen Shannon distance between the Media Agenda and the Public Agenda as a function of time} (with upper inner fences pointed out).
@@
 \centering
-\includegraphics[width = \textwidth]{images/Fig5.pdf}
+\includegraphics[width = \textwidth]{Fig5.pdf}
 \caption{\textbf{Bump charts of newspapers' Agenda and radar plot of the average distributions.} The figure shows, in a qualitative way, the bias in the different newspaper's agendas.
@@
 \centering
-\includegraphics[width = \textwidth]{images/Fig6.pdf}
+\includegraphics[width = \textwidth]{Fig6.pdf}
 \caption{\textbf{Jensen-Shannon distance between the newspapers agenda and the Media Agenda as a function of time}.
@@
 \centering
-\includegraphics[width = \textwidth]{images/Fig7.pdf}
+\includegraphics[width = \textwidth]{Fig7.pdf}
 \caption{\textbf{Relative weight of the topics (a) \emph{Missing person}, and (b) \emph{Former Planning Minister}, and their corresponding word-clouds of frequent newspapers' keywords}.
@@
 \begin{figure}[H]
-\includegraphics[width = \textwidth]{images/Fig8.pdf}
+\includegraphics[width = \textwidth]{Fig8.pdf}
 \caption{\textbf{Agenda setting direction in Missing person's topic?}
@@
 \centering
-\includegraphics[scale = 0.4]{images/FigA2.pdf}
-\includegraphics[scale = 0.4]{images/FigA1.pdf}
+\includegraphics[scale = 0.4]{FigA2.pdf}
+\includegraphics[scale = 0.4]{FigA1.pdf}
 \caption{Temporal profiles of topics \emph{Elections} (left) and \emph{Missing Person} (right) for both LDA and NMF. All the topics found by applying NMF have a highly correlated counterpart in LDA.} 
@@
 \newpage
-\bibliography{bibliography}
+\bibliography{agenda_diversity}
 

### 2018-07-13 agenda_diversity.tex
Version_con_minimas_correcciones_submiteada

@@
 From \cite{mccombs2014agenda}, \textit{``The media agenda is the pattern of news coverage over a period of days, weeks (...) for a set of issues or other topic.
-In other words, the media agenda is a systematic compilation of the issues or topics presented to the public that identifies the degree of emphasis on these topics.''}.
+In other words, the media agenda is a systematic compilation of the issues or topics presented to the public that identifies the degree of emphasis on these topics''}.
 \par In its basic stage, the theory focus on the comparison between the topics coverage by the media and the public agenda, i.e. the topics that the public consider as priority.
@@
 \par Since the irruption of internet in our lives and the access to big data, there were many attempts to analyze from a quantitative point of view the theory of Agenda Setting based on  the original work of McCombs \cite{mccombs1972agenda}.
-Many of them follows what we called a "static approach", i.e., by summarizing certain issues present in news media and looking for effects in the audience \cite{brians1996campaign, gerber2009does, coleman2007young}.
+Many of them follows what we called a ``static approach", i.e.
+by summarizing certain issues present in news media and looking for effects in the audience \cite{brians1996campaign, gerber2009does, coleman2007young}.
 For instance, in Argentina, \cite{mitchelstein2016brecha} examines the difference between public and journalists preferences. 
 Several works by E.
-Zunino, like \cite{zunino2010cobertura} and \cite{koziner2013cobertura}, studied the coverage given by the main newspapers of particular events which have happened during the former administration of Argentinian president \emph{Cristina Fernandez de Kirchner} (from 2007 to 2015), where the government started to confront with news organizations that were critical to its management as they were an opposition party \cite{mitchelstein2017information}
+Zunino, like \cite{zunino2010cobertura} and \cite{koziner2013cobertura}, studied the coverage given by the main newspapers of particular events which have happened during the former administration of Argentinian president \emph{Cristina Fern\'andez de Kirchner} (from 2007 to 2015), where the government started to confront with news organizations that were critical to its management as they were an opposition party \cite{mitchelstein2017information}.
 
@@
 
-\subsection{The Public and Twitter Agendas}
+\subsection{The Google and Twitter Agendas}
 
-\par In order to have a proxy about how the Media Agenda is reaching the public, we look for the same topics in Google Trends and Twitter in the same period of time.
-We take advantage of topics' keywords on the one hand by making queries to the \emph{Google Trends} tool and getting the relative weight of \emph{Google} searches that people made about the identified topics, and in the other hand, by making queries to the advance search tool in the social media \emph{Twitter} in order to get the relative amount of related tweets .
+\par In order to have a proxy about how the Media Agenda is reaching the public, we look for the same topics in \emph{Google} and \emph{Twitter} in the same period of time.
+We take advantage of topics' keywords on the one hand by making queries to the \emph{Google Trends} tool and getting the relative weight of Google searches that people made about the identified topics, and in the other hand, by making queries to the advance search tool in the social media Twitter in order to get the relative amount of related tweets.
 
@@
 Elections: elecciones + cambiemos + kirchner + massa + randazzo \\
-Missing person: maldonado + otranto + gendarmeria + desaparicion \\
+Missing person: maldonado + otranto + gendarmer\'ia + desaparici\'on \\
 Former Planning minister: vido + desafuero + minnicelli + baratta \\
@@
 Discussions in Twitter about elections appear also in point (c), when the other agendas seems to be more diverse. 
-On the other hand, we focused in point (b), despite not being detected as a outlier, because it belong to the topic \emph{Missing person} and this date correspond to the rally that took place one month after the disappearance of Santiago Maldonado (see section \ref{sec:Context}).
+On the other hand, we focused in point (b), despite not being detected as a outlier, because it belong to the topic \emph{Missing person} and this date correspond to the rally that took place one month after the disappearance of \emph{Santiago Maldonado} (see section \ref{sec:Context}).
 It is important to notice that the Shannon's Entropy of GT Agenda displays a minimum (collapsing agenda) not shown neither in the Media nor in the Twitter Agendas.
@@
 In figure \ref{fig:all_agenda} we can see that this topic becomes the most important in public's interest (both \textbf{GT} and \textbf{Tw}) days before that  it happen in the Media Agenda.
-It can be associates  with a social networks (like Facebook and Twitter) campaign  in favor  of the appearance of Santiago Maldonado ("The missing person") that took place on  August 26th.
+It can be associates  with a social networks (like Facebook and Twitter) campaign  in favor  of the appearance of \emph{Santiago Maldonado} (``The missing person") that took place on  August 26th.
 It was very important and was initially underestimated by the main Media outlets in Argentina (see section \ref{sec:Context}).
@@
 \par Finally, in figure \ref{fig:topics_temporal_profiles} we also show word-clouds of topic's keywords but separating those who are more frequently mentioned by each newspaper, and filtering the words that are common to all and basically define the factual details of the topic.
-Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represi\'on} (repression) when \emph{P\'agina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (Fernandez de Kirchner, former president) which is employed by all newspapers except \emph{P\'agina 12} when they  talk about the topic \emph{Former Planning minister} (see section \ref{sec:Context}).
+Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represi\'on} (repression) when \emph{P\'agina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (Fern\'andez de Kirchner, former president) which is employed by all newspapers except \emph{P\'agina 12} when they  talk about the topic \emph{Former Planning minister} (see section \ref{sec:Context}).
 
@@
 Since that event, the \emph{Mauricio Macri}'s administration was accused by several people as the responsible of a \textbf{forced disappearance}. 
-\par A very massive campaign in social media took place on August 26th, under the motto "Where is Santiago Maldonado?", followed by two massive protest marches to the \emph{Plaza de Mayo} that took place on September 1st and October 1st, which the first one had a great repercussion due to several incidents that took place during the march.
-\par The body of \emph{Santiago Maldonado} was found on 17th October in the \emph{Chubut} river, near the place where he was seen the last time, and the autopsy report told that \emph{Santiago Maldonado} had died from ‘asphyxia after being submerged,’ with no injuries on his body.
+\par A very massive campaign in social media took place on August 26th, under the motto ``Where is Santiago Maldonado?", followed by two massive protest marches to the \emph{Plaza de Mayo} that took place on September 1st and October 1st, which the first one had a great repercussion due to several incidents that took place during the march.
+\par The body of \emph{Santiago Maldonado} was found on 17th October in the \emph{Chubut} river, near the place where he was seen the last time, and the autopsy report told that \emph{Santiago Maldonado} had died from ``asphyxia after being submerged", with no injuries on his body.
 However the responsibility of the current administration is still being discussed.
@@
 
-\par \emph{Julio de Vido} was the Planning minister during the administration of \emph{Nestor Kirchner} and \emph{Cristina Fernandez de Kirchner} (2003-2015).
+\par \emph{Julio de Vido} was the Planning minister during the administration of \emph{N\'estor Kirchner} and \emph{Cristina Fern\'andez de Kirchner} (2003-2015).
 In 2015, he was elected to integrate the Chamber of Deputies, which finally voted to strip \emph{De Vido} of his congressional immunity over corruption allegations and was immediatly jailed on October 27th.
@@
 
-\par \emph{Milagro Sala} is an indigenous leader’s. 
+\par \emph{Milagro Sala} is an indigenous leader. 
 She has been incarcerated under pre-trial detention ever since she was first detained in January 2016.
 She faces allegations of embezzlement related to government funding for housing projects managed by T\'upac Amaru, her social organization.
-Sala accused the government of "violating her human rights", and several people think that she is a political prisoner of the \emph{Mauricio Macri} administration.
+Sala accused the government of ``violating her human rights", and several people think that she is a political prisoner of the \emph{Mauricio Macri} administration.
 

### 2018-07-28 bmc_article.tex
Version pasada al formato de epjdata

--- 2018-07-13 agenda_diversity.tex
@@
-\documentclass[a4paper, 12pt]{article}
+%% BioMed_Central_Tex_Template_v1.06
+%%                                      %
+%  bmc_article.tex            ver: 1.06 %
+%                                       %
 
-%\usepackage[utf8]{inputenc}
-\pdfoutput=1
-\usepackage{graphicx}
-\usepackage[export]{adjustbox}
-\usepackage{amsmath} 
-\usepackage{subfigure}
-\usepackage{lscape}
-\usepackage{authblk}
-\usepackage{float}
-\usepackage{array}
-\usepackage{booktabs}
-\usepackage{varwidth}
-\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+%%IMPORTANT: do not delete the first line of this template
+%%It must be present to enable the BMC Submission system to
+%%recognise this template!!
 
-\bibliographystyle{ieeetr}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                     %%
+%%  LaTeX template for BioMed Central  %%
+%%     journal article submissions     %%
+%%                                     %%
+%%          <8 June 2012>              %%
+%%                                     %%
+%%                                     %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                                 %%
+%% For instructions on how to fill out this Tex template           %%
+%% document please refer to Readme.html and the instructions for   %%
+%% authors page on the biomed central website                      %%
+%% http://www.biomedcentral.com/info/authors/                      %%
+%%                                                                 %%
+%% Please do not use \input{...} to include other tex files.       %%
+%% Submit your LaTeX manuscript as one .tex document.              %%
+%%                                                                 %%
+%% All additional figures and files should be attached             %%
+%% separately and not embedded in the \TeX\ document itself.       %%
+%%                                                                 %%
+%% BioMed Central currently use the MikTex distribution of         %%
+%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
+%% http://www.miktex.org                                           %%
+%%                                                                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% additional documentclass options:
+%  [doublespacing]
+%  [linenumbers]   - put the line numbers on margins
+
+%%% loading packages, author definitions
+
+%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
+\documentclass{bmcart}
+
+%%% Load packages
+%\usepackage{amsthm,amsmath}
+%\RequirePackage{natbib}
+%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
+%\RequirePackage{hyperref}
+\usepackage[utf8]{inputenc} %unicode support
+%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
+%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                             %%
+%%  If you wish to display your graphics for   %%
+%%  your own use using includegraphic or       %%
+%%  includegraphics, then comment out the      %%
+%%  following two lines of code.               %%
+%%  NB: These line *must* be included when     %%
+%%  submitting to BMC.                         %%
+%%  All figure files must be submitted as      %%
+%%  separate graphics through the BMC          %%
+%%  submission process, not included in the    %%
+%%  submitted article.                         %%
+%%                                             %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\def\includegraphic{}
+\def\includegraphics{}
+
+%%% Put your definitions there:
+\startlocaldefs
+\endlocaldefs
+
+%%% Begin ...
+\begin{document}
+
+%%% Start of article front matter
+\begin{frontmatter}
+
+\begin{fmbox}
+\dochead{Research}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the title of your article here     %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\author[1,2,*]{Sebasti\'an Pinto}
-\author[3]{Federico Albanese}
-\author[1,2]{Claudio O. Dorso}
-\author[1,2]{Pablo Balenzuela}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the authors here                   %%
+%%                                          %%
+%% Specify information, if available,       %%
+%% in the form:                             %%
+%%   <key>={<id1>,<id2>}                    %%
+%%   <key>=                                 %%
+%% Comment or delete the keys which are     %%
+%% not used. Repeat \author command as much %%
+%% as required.                             %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\affil[1]{Departamento de F\'isica, Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires, Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria, 1428, Buenos Aires, Argentina.}
-\affil[2]{Instituto de F\'isica de Buenos Aires (IFIBA), CONICET, Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria, 1428, Buenos Aires, Argentina.}
-\affil[3]{Instituto de Investigaci\'on en Ciencias de la Computaci\'on (ICC), CONICET, Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria, 1428, Buenos Aires, Argentina.}
-\affil[*]{Corresponding author: spinto@df.uba.ar}
+\author[
+   addressref={aff1,aff2},                   % id's of addresses, e.g. {aff1,aff2}
+   email={spinto@df.uba.ar}   % email address
+]{\inits{SP}\fnm{Sebasti\'an} \snm{Pinto}}
+\author[
+   addressref={aff3},                   % id's of addresses, e.g. {aff1,aff2}
+]{\inits{FA}\fnm{Federico} \snm{Albanese}}
+\author[
+   addressref={aff1,aff2},                   % id's of addresses, e.g. {aff1,aff2}
+]{\inits{COD}\fnm{Claudio O} \snm{Dorso}}
+\author[
+   addressref={aff1,aff2},                   % id's of addresses, e.g. {aff1,aff2}
+   email={balen@df.uba.ar}   % email address
+]{\inits{PB}\fnm{Pablo} \snm{Balenzuela}}
 
-\renewcommand\Affilfont{\small}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the authors' addresses here        %%
+%%                                          %%
+%% Repeat \address commands as much as      %%
+%% required.                                %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\date{}
+\address[id=aff1]{%                           % unique id
+  \orgname{Departamento de F\'isica, Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires}, % university, etc
+  \street{Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria},                     %
+  \postcode{1428},                                % post or zip code
+  \city{Buenos Aires},                              % city
+  \cny{AR}                                    % country
+}
+\address[id=aff2]{%                           % unique id
+  \orgname{Instituto de F\'isica de Buenos Aires (IFIBA), CONICET}, % university, etc
+  \street{Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria},                     %
+  \postcode{1428},                                % post or zip code
+  \city{Buenos Aires},                              % city
+  \cny{AR}                                    % country
+}
+\address[id=aff3]{%                           % unique id
+  \orgname{Instituto de Investigaci\'on en Ciencias de la Computaci\'on (ICC), CONICET}, % university, etc
+  \street{Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria},                     %
+  \postcode{1428},                                % post or zip code
+  \city{Buenos Aires},                              % city
+  \cny{AR}                                    % country
+}
 
-\begin{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter short notes here                   %%
+%%                                          %%
+%% Short notes will be after addresses      %%
+%% on first page.                           %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\maketitle
-\begin{abstract}
+\begin{artnotes}
+%\note{Sample of title note}     % note to the article
+\note[id=n1]{Equal contributor} % note, connected to author
+\end{artnotes}
+
+\end{fmbox}% comment this for two column layout
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% The Abstract begins here                 %%
+%%                                          %%
+%% Please refer to the Instructions for     %%
+%% authors on http://www.biomedcentral.com  %%
+%% and include the section headings         %%
+%% accordingly for your article type.       %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{abstractbox}
+
+\begin{abstract} % abstract
 
@@
 
-\section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% The keywords begin here                  %%
+%%                                          %%
+%% Put each keyword in separate \kwd{}.     %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsection{Agenda Setting Theory}
+\begin{keyword}
+\kwd{agenda-setting}
+\kwd{agenda diversity}
+\kwd{coverage bias}
+\kwd{topic modelling}
+\end{keyword}
+
+% MSC classifications codes, if any
+%\begin{keyword}[class=AMS]
+%\kwd[Primary ]{}
+%\kwd{}
+%\kwd[; secondary ]{}
+%\end{keyword}
+
+\end{abstractbox}
+%
+%\end{fmbox}% uncomment this for twcolumn layout
+
+\end{frontmatter}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% The Main Body begins here                %%
+%%                                          %%
+%% Please refer to the instructions for     %%
+%% authors on:                              %%
+%% http://www.biomedcentral.com/info/authors%%
+%% and include the section headings         %%
+%% accordingly for your article type.       %%
+%%                                          %%
+%% See the Results and Discussion section   %%
+%% for details on how to create sub-sections%%
+%%                                          %%
+%% use \cite{...} to cite references        %%
+%%  \cite{koon} and                         %%
+%%  \cite{oreg,khar,zvai,xjon,schn,pond}    %%
+%%  \nocite{smith,marg,hunn,advi,koha,mouse}%%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%% start of article main body
+% <put your article body there>
+
+%%%%%%%%%%%%%%%%
+%% Background %%
+%%
+
+\section*{Introduction}
+
+\subsection*{Agenda Setting Theory}
 
@@
 However, it is based on two assumptions that are not necessarily true: the public spreads its attention in an homogeneous way across the multiple sources, and that the agendas of that sources are different \cite{mccombs2005look}.
-
 \par From the Chapel Hill research, several directions of agenda-setting were established \cite{mccombs2005look}.
@@
 The competition between mass media for the same audience can lead to a homogenization of the agendas \cite{vargo2017networks}, which is in the opposite direction of one of the assumptions that predict the end of agenda-setting, as was mentioned before.
-
 \par Since the irruption of internet in our lives and the access to big data, there were many attempts to analyze from a quantitative point of view the theory of Agenda Setting based on  the original work of McCombs \cite{mccombs1972agenda}.
@@
 Zunino, like \cite{zunino2010cobertura} and \cite{koziner2013cobertura}, studied the coverage given by the main newspapers of particular events which have happened during the former administration of Argentinian president \emph{Cristina Fern\'andez de Kirchner} (from 2007 to 2015), where the government started to confront with news organizations that were critical to its management as they were an opposition party \cite{mitchelstein2017information}.
-
 \par Other line of research have been focused on detecting bias in the media, either by taking into account the number of mentions related  to a preferred political party \cite{lazaridou2016identifying, baumgartner2015all} or by identifying the ideology through the position of the media regards to certain issues or actors \cite{elejalde2018nature, sagarzazu2017hugo}.
 New trends in agenda-setting theory propose to represent ideological aspects or issues emphasized as networks like mind maps, and the basic idea is the comparison between media's knowledge representative network with its counterpart in the audience \cite{guo2012application, vu2014exploring}.
-
 \par Most of the works cited above follow typical methods of social science research.
@@
 The temporal profile of topics is usually embedded in the context of topic tracking \cite{hu2016news, li2017joint}, or in the recognition of emerging topics in real-time \cite{cataldi2010emerging} mostly applied to social media.
-
 \par A typical dynamical analysis of Agenda Setting is focused on a single issue.
@@
 However, a drawback of working with predefined issues is that they usually reflects general themes, such as unemployment or crime, and the issues selection must be made by the researcher. 
-
 \par In this work we propose a novel method in order to study the dynamics of Mass Media Agenda as a set of topic evolving in time and their correspondence with the Public and Social Network Agendas.
@@
 
-\section{Materials and Methods} \label{sec:MatMeth}
+\section*{Materials and Methods}
+ \label{sec:MatMeth}
 
-\subsection{The Media Agenda}
-
-In this work we analyze a three month period of the Argentinian Media's Agenda composed a corpus of news' articles that were published between July 31th and November 5th in the section \emph{Politics} of the electronic editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\'on}, \emph{P\'agina12}, and the news portal \emph{Infobae}.
+\subsection*{The Media Agenda}
+\par In this work we analyze a three month period of the Argentinian Media's Agenda composed a corpus of news' articles that were published between July 31th and November 5th in the section \emph{Politics} of the electronic editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\'on}, \emph{P\'agina12}, and the news portal \emph{Infobae}.
 The first two lead the sale of printed editions in \emph{Buenos Aires} city, but \emph{Clar\'in} reaches roughly two times the readers of \emph{La Naci\'on}, and ten times the readers of \emph{P\'agina 12} \cite{IVC}.
@@
 Except \emph{P\'agina 12}, all articles were taken from the section \emph{Pol\'itica}  (Politics) of the respective news portal, while the articles which belong to \emph{P\'agina 12} were taken from the section \emph{El pa\'is} (The country).
-
 \par In order to perform the analysis of the articles in the corpus, we describe them as numerical vectors through the \textit{term frequency - inverse document frequency (tf-idf)} representation \cite{xu2003document}.
@@
 This was performed \emph{NMF} through the python module \emph{scikit-learn} \cite{scikit-learn}.
-
 \par A time-dependent representation is obtained by defining the temporal profile of the topic $i$, $W_i(day)$, by eq.\ref{eq:topic_weight} where $l(j)$ is the number of words of the document $j$, $h_{ji}$ is the degree of membership of document $j$ on topic $i$ and $\delta$ is the Kronecker delta.
@@
 
-\subsection{The Google and Twitter Agendas}
+\subsection*{The Google and Twitter Agendas}
 
@@
 
-\subsection{Outliers identification}
+\subsection*{Outliers identification}
 \label{sec:outliers_identification}
-
 \par We identify outliers values in a data set of N observations by following the box plot construction.
@@
 
-\begin{equation}
-\begin{split}
-\text{lower inner fence (LIF)} & = Q1 - 1.5  \text{IQ} \\
-\text{upper inner fence (UIF)} & = Q3 + 1.5  \text{IQ} \\
-\text{lower outer fence (LOF)} & = Q1 - 3  \text{IQ} \\
-\text{upper outer fence (UOF)} & = Q3 + 3  \text{IQ}
-\end{split}
-\label{eq:fences}
-\end{equation}
+\begin{eqnarray}\label{eq:fences}
+lower inner fence (LIF) & = Q1 - 1.5 IQ \\
+upper inner fence (UIF) & = Q3 + 1.5  IQ \\
+lower outer fence (LOF) & = Q1 - 3  IQ \\
+upper outer fence (UOF) & = Q3 + 3 IQ
+\end{eqnarray}
 
@@
 
-\subsection{Jensen-Shannon distance}
+\subsection*{Jensen-Shannon distance}
 
@@
 The square root of the Jensen-Shannon divergence (see eq.\ref{eq:jensen_shannon_distance}, where $M = \frac{P + Q}{2}$) is a metric \cite{fuglede2004jensen} often referred as Jensen-Shannon distance ($JSD$).
+\begin{eqnarray}\label{eq:jensen_shannon_distance}
+D_{KL}(P||Q) = -\sum{P(i) log(\frac{Q(i)}{P(i)})} \\
+JSD(P,Q) = \sqrt{JS_{Div}(P,Q)} = \sqrt{\frac{1}{2}[D_{KL}(P||M) + D_{KL}(Q||M)] } 
+\end{eqnarray}
 
-\begin{equation}
-\begin{split}
-D_{KL}(P||Q) = -\sum{P(i) log(\frac{Q(i)}{P(i)})} \\
-JSD(P,Q) = \sqrt{JS_{Div}(P,Q)} = \sqrt{\frac{1}{2}[D_{KL}(P||M) + D_{KL}(Q||M)] } \\
-\end{split}
-\label{eq:jensen_shannon_distance}
-\end{equation}
-
-\subsection{Normalized Shannon's H Information Entropy}
+\subsection*{Normalized Shannon's H Information Entropy}
 
@@
 
-\section{Results}
+\section*{Results}
 
@@
 The meaning of the topics or macro-topics is contextualized in section \ref{sec:Context} of Supplementary Material.
-
 \par After the procedure described in the previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, and all their derivations, as time-dependent distributions.
 
-\subsection{The Public and Media agendas}
+\subsection*{The Public and Media agendas}
 
@@
 In table \ref{table:gt_all_correlation} we show the linear correlation between the topics' temporal profiles from the Public Agenda and their counterparts in the Media Agenda.
-
 \par In figure \ref{fig:all_agenda} we show the time evolution of the topics with a bump chart of the Agendas.
@@
 }
-
-\begin{figure}[H]
-\centering
-\includegraphics[width = \textwidth]{Fig1.pdf}
-\caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic distribution and their corresponding wordclouds.} The Public Agenda is represented either by Google Trends (GT) and Twitter (Tw).
-Topics names are introduced together with the wordclouds containing the most important keywords involved in the definition of each topic.
-In green color we show the keywords used to define the topics in the Google Trends and Twitter queries (see table \ref{table:gt_queries}) and therefore in our construction of the Public Agenda.}
-\label{fig:topics_wordclouds}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width = \textwidth]{Fig2.pdf}
-\caption{\textbf{Bump graph of the Media Agenda (MA) and Public Agenda extracted from Google Trends (GT) and Twitter (Tw)}.
-The curves width and their ordering are related to the topics relative weight.
-Some important events related to the topics are pointed out:
-\textbf{A}: First news about Santiago Maldonado's disappearance;
-\textbf{B}: Primary elections;
-\textbf{C}: March one month after Santiago Maldonado's disappearance;
-\textbf{D}: March two months after Santiago Maldonado's disappearance;
-\textbf{E}: Appearance of Santiago Maldonado's body;
-\textbf{F}: General elections;
-\textbf{G}: Julio De Vido's detention;
-\textbf{H}: Debates on labor reform;
-\textbf{I}: Amado Boudou's detention.
-A more detailed explanation is given in section \ref{sec:Context}.}
-\label{fig:all_agenda}
-\end{figure}
-
-\begin{table}[H]
-\centering
-\resizebox{\textwidth}{!}{\begin{tabular}{lp{10cm}}
-\toprule
-Topic's name & Google Trends query \\ 
-\midrule
-Elections & elecciones + cambiemos + cristina kirchner + massa + randazzo \\
-Missing person & santiago maldonado + juez otranto + patricia bullrich + gendarmería + desaparici\'on forzada \\
-Former Planning minister & de vido + desafuero + ministro de planificaci\'on + minnicelli + baratta \\
-Current President & mauricio macri + cgt + reforma laboral + peña + triaca \\
-Social leader & milagro sala + cidh + tupac amaru + pullen llermanos + morales \\
-Prosecutor's death & nisman + amia + memor\'andum con ir\'an + timerman + juez bonadio \\
-Former Vice-President & amado boudou + ciccone + ariel lijo + vandenbroele + núñez carmona \\
-\bottomrule
-\end{tabular}}
-\caption{Queries used in Google Trends in order to build the Public Agenda.}
-\label{table:gt_queries}
-\end{table}
-
-\begin{table}[H]
-\centering
-\resizebox{\textwidth}{!}{\begin{tabular}{lccc}
-\toprule
-Topic's name & Correlation MA and GT & MA and Twitter & GT and Twitter \\ 
-\midrule
-Elections & \textbf{0.81} & \textbf{0.59} & \textbf{0.75} \\
-Missing person & \textbf{0.68} & \textbf{0.76} & \textbf{0.89} \\
-Former Planning minister & \textbf{0.92} & \textbf{0.82} & \textbf{0.87} \\
-Current President & \textbf{0.77} & \textbf{0.75} & \textbf{0.63} \\
-Social leader & \textbf{0.49} & \textbf{0.25(*)} & \textbf{0.57} \\
-Prosecutor's death & \textbf{0.56} & \textbf{0.59} & \textbf{0.75} \\
-Former Vice-President & \textbf{0.90} & \textbf{0.92} & \textbf{0.97}\\
-\bottomrule
-\end{tabular}}
-\caption{Correlation between the topics' temporal profiles of the Public Agenda and their counterpart in Media Agenda.
-All correlation values are statistical significant ($p < 10^{-9}$), except (*) which is significant with $p < 0.05$.}
-\label{table:gt_all_correlation}
-\end{table}
-
 \par The figures introduced above show not only the topics and their differences between the Agendas, but also the dynamics of the topics.
@@
 We can also observe a great similarity between \textbf{GT} and \textbf{Tw} agendas which both are different faces of the Public Agenda.
-
 \par On the other hand, figure \ref{fig:all_agenda} allow us to appreciate how the main topic change in time and have a glance of the qualitative differences between agendas.
@@
 
-\subsection{A quantitative description of the Agendas}
+\subsection*{A quantitative description of the Agendas}
 
-\subsubsection{Agenda diversity}
+\subsubsection*{Agenda diversity}
 
@@
 Three of them are outliers as defined in section \ref{sec:MatMeth}, two of them from \textbf{GT} and one from \textbf{Tw}.
-
 \par A lower value in the agenda's diversity is due to the fact that the most important topic attracts practically all the attention of the public and the media.
@@
 We emphasize the discussion about this topic because we can appreciate  interesting facts that appear along the analysis.
-
-\begin{figure}[H]
-\centering
-\includegraphics[height=0.7\textheight]{Fig3.pdf}
-\caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda show a less diverse behavior than the Media Agenda as can be seen in the left figure.
-The horizontal lines are the lower inner fences of each signal in order to identify outliers.
-The related radar plots shows that those dates when the agenda has a low diversity, the most important topic catches the most public’s attention.
-\textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
-\label{fig:shannon_entropy_agendas}
-\end{figure}
-
 \par From the measure of $H$ we can also see that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
@@
 
-\subsubsection{Distance between Media and Public Agenda's }
+\subsubsection*{Distance between Media and Public Agenda's }
 
@@
 \par Points \textbf{(c)} and \textbf{(d)} shows that both the Public and the Media highlight this topic, but the Media do not disregard other topics, so the corresponding distance between them can be interpreted  of another way of seeing the diversity effect discussed in the last section.
-
 \par On the other hand,  points \textbf{(a)} (we take this point due to be a local maximum despite not being an outlier) and \textbf{(b)} seem to show an interest of the public in the topic \emph{Missing person} which it is not reflected in the Media.
@@
 It was very important and was initially underestimated by the main Media outlets in Argentina (see section \ref{sec:Context}).
-
 \par It is important to notice that it is our interpretation of the data based on the knowledge of the context, and  we are not measuring causality between Agendas (we will say a few words about it in section \ref{sec:who_sets}), i.e.
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[height = 0.7\textheight]{Fig4.pdf}
-\caption{\textbf{Jensen Shannon distance between the Media Agenda and the Public Agenda as a function of time} (with upper inner fences pointed out).
-The larger distances are due to a greater interest of the audience in the topic \emph{Missing person} which leads to lesser interest in the other topics, which the Media has to cover, maybe except in points (a) and (b) where the Media seems not to anticipate the public interest in the mentioned topic.
-\textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
-\label{fig:jensen_shannon_gt}
-\end{figure}
-
-\subsection{Agenda bias in different Media outlets}
+\subsection*{Agenda bias in different Media outlets}
 
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[width = \textwidth]{Fig5.pdf}
-\caption{\textbf{Bump charts of newspapers' Agenda and radar plot of the average distributions.} The figure shows, in a qualitative way, the bias in the different newspaper's agendas.
-For instance, the greater interest of \emph{P\'agina 12 (P12)} in the \emph{Missing person} topic and its slightly lower coverage in the \emph{Former Planning minister} respect to the other newspapers.}
-\label{fig:news_agenda}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width = \textwidth]{Fig6.pdf}
-\caption{\textbf{Jensen-Shannon distance between the newspapers agenda and the Media Agenda as a function of time}.
-\emph{P\'agina 12} shows the more different behavior, motivated again by its interest in the \emph{Missing person} and \emph{Social leader} topics as can be seen in the radar plots which belongs to points (a) and (c).
-The anomalous behavior of \emph{Infobae} at pint (b) is due to few articles around that date in our database, therefore we ignore its radar plot.
-\textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
-\label{fig:jensen_shannon_news}
-\end{figure}
-
 \par The greater coverage in the topic \emph{Missing person} by \emph{P\'agina 12} is even more clear if we inspect the temporal profile of the topic and compare the coverage given by each newspaper.
@@
 In figure \ref{fig:topics_temporal_profiles} we show the temporal profile of the topic \emph{Missing person} (panel (a)) and the topic \emph{Former Planning minister} in panel (b), as an example where the behavior is the opposite, as can be seen below.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width = \textwidth]{Fig7.pdf}
-\caption{\textbf{Relative weight of the topics (a) \emph{Missing person}, and (b) \emph{Former Planning Minister}, and their corresponding word-clouds of frequent newspapers' keywords}.
-We interpreted the differences shown in given periods as an indicator of coverage bias.
-For instance, in figure (a) \emph{P\'agina 12} pays a greater attention in the first days.
-In the word-clouds, we show which of the defining words are more frequently used by the corresponding newspaper.
-Most of them are less informative, but other seems to represent a first approximation in the study of framing.}
-\label{fig:topics_temporal_profiles}
-\end{figure}
 
@@
 Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represi\'on} (repression) when \emph{P\'agina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (Fern\'andez de Kirchner, former president) which is employed by all newspapers except \emph{P\'agina 12} when they  talk about the topic \emph{Former Planning minister} (see section \ref{sec:Context}).
-
 We think that a more deeply study of topics' keywords could be a first approximation in the study of framing, which will constitute the core of futures works.
 
-\subsection{After all: Who sets the Agenda?}
+\subsection*{After all: Who sets the Agenda?}
 \label{sec:who_sets}
@@
 It is interesting to note that the newspaper responsible to accumulate coverage during the initial stage was the minority one: \emph{P\'agina 12}. 
-
 Our interpretation about the setting agenda dynamics of this particular topic is the following: A small newspaper (\emph{P\'agina 12}) gives great coverage to this topic; it is amplified  by public in the social networks and also expressed  by reiterative Google searches.
@@
 
-\begin{figure}[H]
-\includegraphics[width = \textwidth]{Fig8.pdf}
-\caption{\textbf{Agenda setting direction in Missing person's topic?}
-The temporal profiles of figure (a) show that the Public and Media agenda seem to differentiate around August 15th (vertical grey line (1)) and the Public increase abruptly its interest in the topic around August 24th (grey line (2)).
-It can be seen also in figure (b), where the discrete differences were computed.
-With the computing of the cumulative sum of figure \ref{fig:topics_temporal_profiles} and figure (a), represented as a bump chart in figure (c), we suggest that the topic was first set by \emph{P\'agina 12} and then the Public's interest cause the coverage of the other Media.
-}
-\label{fig:Maldonado_setagenda}
-\end{figure}
-
-\section{Conclusions}
+\section*{Conclusions}
 
@@
 \newpage
-\section{Supplementary Material}
-\subsection{Context}
+\section*{Supplementary Material}
+\subsection*{Context}
 \label{sec:Context}
@@
 
-\subsubsection{\emph{Elections}}
+\subsubsection*{\emph{Elections}}
 \par Two legislative elections were celebrated during the period in great part of the Argentina: Primary elections on August 13th and the general elections on October 22th. 
@@
 
-\subsubsection{Current President}
+\subsubsection*{Current President}
 \par \emph{Mauricio Macri} is the current Argentinian President, since December 2015. 
@@
 
-\subsubsection{\emph{Missing Person}}
+\subsubsection*{\emph{Missing Person}}
 \par \emph{Santiago Maldonado} vanished on August 1st after a minor clash between the Gendarmerie (Border Guards) and a group of Mapuches, which recognize as themselves the original population of an area in the Patagonia.
@@
 
-\subsubsection{\emph{Former Planning minister} and \emph{Former Vice-President}}
+\subsubsection*{\emph{Former Planning minister} and \emph{Former Vice-President}}
 
@@
 
-\subsubsection{\emph{Social leader} and \emph{Prosecutor's death}}
+\subsubsection*{\emph{Social leader} and \emph{Prosecutor's death}}
 
@@
 
-\subsection{Comparison between NMF and LDA}
+\subsection*{Comparison between NMF and LDA}
 
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[scale = 0.4]{FigA2.pdf}
-\includegraphics[scale = 0.4]{FigA1.pdf}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Backmatter begins here                   %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{backmatter}
+
+\section*{Competing interests}
+  The authors declare that they have no competing interests.
+
+\section*{Author's contributions}
+    Text for this section \ldots
+
+\section*{Acknowledgements}
+  Text for this section \ldots
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                  The Bibliography                       %%
+%%                                                         %%
+%%  Bmc_mathpys.bst  will be used to                       %%
+%%  create a .BBL file for submission.                     %%
+%%  After submission of the .TEX file,                     %%
+%%  you will be prompted to submit your .BBL file.         %%
+%%                                                         %%
+%%                                                         %%
+%%  Note that the displayed Bibliography will not          %%
+%%  necessarily be rendered by Latex exactly as specified  %%
+%%  in the online Instructions for Authors.                %%
+%%                                                         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% if your bibliography is in bibtex format, use those commands:
+\bibliographystyle{bmc-mathphys} % Style BST file (bmc-mathphys, vancouver, spbasic).
+\bibliography{bmc_article}      % Bibliography file (usually '*.bib' )
+% for author-year bibliography (bmc-mathphys or spbasic)
+% a) write to bib file (bmc-mathphys only)
+% @settings{label, options="nameyear"}
+% b) uncomment next line
+%\nocite{label}
+
+% or include bibliography directly:
+% \begin{thebibliography}
+% \bibitem{b1}
+% \end{thebibliography}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Figures                       %%
+%%                               %%
+%% NB: this is for captions and  %%
+%% Titles. All graphics must be  %%
+%% submitted separately and NOT  %%
+%% included in the Tex document  %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%
+%% Do not use \listoffigures as most will included as separate files
+
+\section*{Figures}
+
+\begin{figure}[h!]
+%\includegraphics[width = \textwidth]{Fig1.pdf}
+\caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic distribution and their corresponding wordclouds.} The Public Agenda is represented either by Google Trends (GT) and Twitter (Tw).
+Topics names are introduced together with the wordclouds containing the most important keywords involved in the definition of each topic.
+In green color we show the keywords used to define the topics in the Google Trends and Twitter queries (see table \ref{table:gt_queries}) and therefore in our construction of the Public Agenda.}
+\label{fig:topics_wordclouds}
+\end{figure}
+
+\begin{figure}[h!]
+%\includegraphics[width = \textwidth]{Fig2.pdf}
+\caption{\textbf{Bump graph of the Media Agenda (MA) and Public Agenda extracted from Google Trends (GT) and Twitter (Tw)}.
+The curves width and their ordering are related to the topics relative weight.
+Some important events related to the topics are pointed out:
+\textbf{A}: First news about Santiago Maldonado's disappearance;
+\textbf{B}: Primary elections;
+\textbf{C}: March one month after Santiago Maldonado's disappearance;
+\textbf{D}: March two months after Santiago Maldonado's disappearance;
+\textbf{E}: Appearance of Santiago Maldonado's body;
+\textbf{F}: General elections;
+\textbf{G}: Julio De Vido's detention;
+\textbf{H}: Debates on labor reform;
+\textbf{I}: Amado Boudou's detention.
+A more detailed explanation is given in section \ref{sec:Context}.}
+\label{fig:all_agenda}
+\end{figure}
+
+\begin{figure}[h!]
+%\includegraphics[height=0.7\textheight]{Fig3.pdf}
+\caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda show a less diverse behavior than the Media Agenda as can be seen in the left figure.
+The horizontal lines are the lower inner fences of each signal in order to identify outliers.
+The related radar plots shows that those dates when the agenda has a low diversity, the most important topic catches the most public’s attention.
+\textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
+\label{fig:shannon_entropy_agendas}
+\end{figure}
+
+\begin{figure}[h!]
+%\includegraphics[height = 0.7\textheight]{Fig4.pdf}
+\caption{\textbf{Jensen Shannon distance between the Media Agenda and the Public Agenda as a function of time} (with upper inner fences pointed out).
+The larger distances are due to a greater interest of the audience in the topic \emph{Missing person} which leads to lesser interest in the other topics, which the Media has to cover, maybe except in points (a) and (b) where the Media seems not to anticipate the public interest in the mentioned topic.
+\textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
+\label{fig:jensen_shannon_gt}
+\end{figure}
+
+\begin{figure}[h!]
+%\includegraphics[width = \textwidth]{Fig5.pdf}
+\caption{\textbf{Bump charts of newspapers' Agenda and radar plot of the average distributions.} The figure shows, in a qualitative way, the bias in the different newspaper's agendas.
+For instance, the greater interest of \emph{P\'agina 12 (P12)} in the \emph{Missing person} topic and its slightly lower coverage in the \emph{Former Planning minister} respect to the other newspapers.}
+\label{fig:news_agenda}
+\end{figure}
+
+\begin{figure}[h!]
+%\includegraphics[width = \textwidth]{Fig6.pdf}
+\caption{\textbf{Jensen-Shannon distance between the newspapers agenda and the Media Agenda as a function of time}.
+\emph{P\'agina 12} shows the more different behavior, motivated again by its interest in the \emph{Missing person} and \emph{Social leader} topics as can be seen in the radar plots which belongs to points (a) and (c).
+The anomalous behavior of \emph{Infobae} at pint (b) is due to few articles around that date in our database, therefore we ignore its radar plot.
+\textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
+\label{fig:jensen_shannon_news}
+\end{figure}
+
+\begin{figure}[h!]
+%\includegraphics[width = \textwidth]{Fig7.pdf}
+\caption{\textbf{Relative weight of the topics (a) \emph{Missing person}, and (b) \emph{Former Planning Minister}, and their corresponding word-clouds of frequent newspapers' keywords}.
+We interpreted the differences shown in given periods as an indicator of coverage bias.
+For instance, in figure (a) \emph{P\'agina 12} pays a greater attention in the first days.
+In the word-clouds, we show which of the defining words are more frequently used by the corresponding newspaper.
+Most of them are less informative, but other seems to represent a first approximation in the study of framing.}
+\label{fig:topics_temporal_profiles}
+\end{figure}
+
+\begin{figure}[h!]
+%\includegraphics[width = \textwidth]{Fig8.pdf}
+\caption{\textbf{Agenda setting direction in Missing person's topic?}
+The temporal profiles of figure (a) show that the Public and Media agenda seem to differentiate around August 15th (vertical grey line (1)) and the Public increase abruptly its interest in the topic around August 24th (grey line (2)).
+It can be seen also in figure (b), where the discrete differences were computed.
+With the computing of the cumulative sum of figure \ref{fig:topics_temporal_profiles} and figure (a), represented as a bump chart in figure (c), we suggest that the topic was first set by \emph{P\'agina 12} and then the Public's interest cause the coverage of the other Media.
+}
+\label{fig:Maldonado_setagenda}
+\end{figure}
+
+\begin{figure}[h!]
+%\includegraphics[scale = 0.4]{FigA2.pdf}
+%\includegraphics[scale = 0.4]{FigA1.pdf}
 \caption{Temporal profiles of topics \emph{Elections} (left) and \emph{Missing Person} (right) for both LDA and NMF. All the topics found by applying NMF have a highly correlated counterpart in LDA.} 
@@
 
-\begin{table}[H]
-\centering
-\resizebox{\textwidth}{!}{\begin{tabular}{llc}
-\toprule
-& Correlation between NMF and LDA \\
-\midrule
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Tables                        %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Use of \listoftables is discouraged.
+%%
+\section*{Tables}
+
+\begin{table}[h!]
+\caption{Queries used in Google Trends in order to build the Public Agenda.}
+\begin{tabular}{ll}
+Topic's name & Google Trends query \\ \hline
+Elections & elecciones + cambiemos + cristina kirchner + massa + randazzo \\
+Missing person & santiago maldonado + juez otranto + patricia bullrich + gendarmería + desaparici\'on forzada \\
+Former Planning minister & de vido + desafuero + ministro de planificaci\'on + minnicelli + baratta \\
+Current President & mauricio macri + cgt + reforma laboral + peña + triaca \\
+Social leader & milagro sala + cidh + tupac amaru + pullen llermanos + morales \\
+Prosecutor's death & nisman + amia + memor\'andum con ir\'an + timerman + juez bonadio \\
+Former Vice-President & amado boudou + ciccone + ariel lijo + vandenbroele + núñez carmona \\
+\end{tabular}
+\label{table:gt_queries}
+\end{table}
+
+\begin{table}[h!]
+\caption{Correlation between the topics' temporal profiles of the Public Agenda and their counterpart in Media Agenda.
+All correlation values are statistical significant ($p < 10^{-9}$), except (*) which is significant with $p < 0.05$.}
+\begin{tabular}{lccc}
+Topic's name & Correlation MA and GT & MA and Twitter & GT and Twitter \\ \hline
+Elections & \textbf{0.81} & \textbf{0.59} & \textbf{0.75} \\
+Missing person & \textbf{0.68} & \textbf{0.76} & \textbf{0.89} \\
+Former Planning minister & \textbf{0.92} & \textbf{0.82} & \textbf{0.87} \\
+Current President & \textbf{0.77} & \textbf{0.75} & \textbf{0.63} \\
+Social leader & \textbf{0.49} & \textbf{0.25(*)} & \textbf{0.57} \\
+Prosecutor's death & \textbf{0.56} & \textbf{0.59} & \textbf{0.75} \\
+Former Vice-President & \textbf{0.90} & \textbf{0.92} & \textbf{0.97}\\
+\end{tabular}
+\label{table:gt_all_correlation}
+\end{table}
+
+\begin{table}[h!]
+\caption{Correlation between the temporal profiles of the topics found in NMF and associated topics in LDA.}
+\begin{tabular}{llc}
+Topic's name & Correlation between NMF and LDA \\ \hline
 Elections & \textbf{0.98} \\
@@
 Prosecutor's death & \textbf{0.83} \\
-\bottomrule
-\end{tabular}}
-\caption{Correlation between the temporal profiles of the topics found in NMF and associated topics in LDA.}
+\end{tabular}
 \label{table:correlation_nmf_lda}
@@
 
-\newpage
-\bibliography{agenda_diversity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Additional Files              %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+\section*{Additional Files}
+  \subsection*{Additional file 1 --- Sample additional file title}
+    Additional file descriptions text (including details of how to
+    view the file, if it is in a non-standard format or the file extension).  This might
+    refer to a multi-page table or a figure.
+
+  \subsection*{Additional file 2 --- Sample additional file title}
+    Additional file descriptions text.
+
+\end{backmatter}
 \end{document}

### 2018-07-30 plos_latex_template.tex
Primera version pasada a formato plos one

--- 2018-07-13 agenda_diversity.tex
@@
-\documentclass[a4paper, 12pt]{article}
+% Template for PLoS
+% Version 3.5 March 2018
+%
+% % % % % % % % % % % % % % % % % % % % % %
+%
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended 
+% to minimize problems and delays during our production 
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Once your paper is accepted for publication, 
+% PLEASE REMOVE ALL TRACKED CHANGES in this file 
+% and leave only the final text of your manuscript. 
+% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
+% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
+%
+%
+% There are no restrictions on package use within the LaTeX files except that 
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file. 
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig" instead of "Figure".
+% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - spacing/line breaks within cells to alter layout or alignment
+% - do not nest tabular environments (no tabular environments within tabular environments)
+% - no graphics or colored text (cell background color/shading OK)
+% See http://journals.plos.org/plosone/s/tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
+%
+% For inline equations, please be sure to include all portions of an equation in the math environment.
+For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
+%
+% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column. 
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
+%
+% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
+%
+% % % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
 
-%\usepackage[utf8]{inputenc}
-\pdfoutput=1
-\usepackage{graphicx}
-\usepackage[export]{adjustbox}
-\usepackage{amsmath} 
-\usepackage{subfigure}
-\usepackage{lscape}
-\usepackage{authblk}
-\usepackage{float}
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
+\usepackage[utf8x]{inputenc}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
+\usepackage[table]{xcolor}
+
+% array package and thick rules for tables
 \usepackage{array}
-\usepackage{booktabs}
-\usepackage{varwidth}
-\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
 
-\bibliographystyle{ieeetr}
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
 
-\title{Agenda diversity and coverage bias: A quantitative approach to the agenda-setting theory}
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
 
-\author[1,2,*]{Sebasti\'an Pinto}
-\author[3]{Federico Albanese}
-\author[1,2]{Claudio O. Dorso}
-\author[1,2]{Pablo Balenzuela}
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
 
-\affil[1]{Departamento de F\'isica, Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires, Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria, 1428, Buenos Aires, Argentina.}
-\affil[2]{Instituto de F\'isica de Buenos Aires (IFIBA), CONICET, Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria, 1428, Buenos Aires, Argentina.}
-\affil[3]{Instituto de Investigaci\'on en Ciencias de la Computaci\'on (ICC), CONICET, Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria, 1428, Buenos Aires, Argentina.}
-\affil[*]{Corresponding author: spinto@df.uba.ar}
+% Remove comment for double spacing
+%\usepackage{setspace} 
+%\doublespacing
 
-\renewcommand\Affilfont{\small}
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
 
-\date{}
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+%\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+%\setlength{\headheight}{27.023pt}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\today}
+
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
+
+%% END MACROS SECTION
 
 \begin{document}
+\vspace*{0.2in}
 
-\maketitle
-\begin{abstract}
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{Agenda diversity and coverage bias: A quantitative approach to the agenda-setting theory} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Sebasti\'an Pinto\textsuperscript{1,2,*},
+Federico Albanese\textsuperscript{3},
+Claudio O. Dorso\textsuperscript{1,2},
+Pablo Balenzuela\textsuperscript{1,2}
+\\
+\bigskip
+\textbf{1} Departamento de F\'isica, Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires, Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria, 1428, Buenos Aires, Argentina.
+\\
+\textbf{2} Instituto de F\'isica de Buenos Aires (IFIBA), CONICET, Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria, 1428, Buenos Aires, Argentina.
+\\
+\textbf{3} Instituto de Investigaci\'on en Ciencias de la Computaci\'on (ICC), CONICET, Av. Cantilo s/n, Pabell\'on 1, Ciudad Universitaria, 1428, Buenos Aires, Argentina.
+\\
+\bigskip
 
+% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
+% 
+% Remove or comment out the author notes below if they aren't used.
+%
+% Primary Equal Contribution Note
+%\Yinyang These authors contributed equally to this work.
+
+% Additional Equal Contribution Note
+% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
+%\ddag These authors also contributed equally to this work.
+
+% Current address notes
+%\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
+% \textcurrency b Insert second current address 
+% \textcurrency c Insert third current address
+
+% Deceased author note
+%\dag Deceased
+
+% Group/Consortium Author Note
+%\textpilcrow Membership list can be found in the Acknowledgments section.
+
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* spinto@df.uba.ar
+
+\end{flushleft}
+% Please keep the abstract below 300 words
+\section*{Abstract}
 The mass media play a fundamental role in the formation of public opinion, either by defining the topics of discussion or by making a degree of emphasis on certain issues.
@@
 
-\end{abstract}
+% Please keep the Author Summary between 150 and 200 words
+% Use first person. PLOS ONE authors please skip this step. 
+% Author Summary not valid for PLOS ONE submissions.   
+\section*{Author summary}
 
-\section{Introduction}
+\linenumbers
 
-\subsection{Agenda Setting Theory}
-
+% Use "Eq" instead of "Equation" for equation citations.
+\section*{Introduction}
 \par To understand the ecosystem of information flow and opinion formation is one of the goals in these days.
@@
 
-\section{Materials and Methods} \label{sec:MatMeth}
+\section*{Materials and methods}
 
-\subsection{The Media Agenda}
+\subsection*{The Media Agenda}
 
@@
 
-\subsection{Outliers identification}
+\subsection*{Outliers identification}
 \label{sec:outliers_identification}
@@
 
-\subsection{Normalized Shannon's H Information Entropy}
+\subsection*{Normalized Shannon's H Information Entropy}
 
@@
 
-\section{Results}
+% Results and Discussion can be combined.
+\section*{Results}
 
@@
 
-\subsection{The Public and Media agendas}
+\subsection*{The Public and Media agendas}
 
@@
 
-\begin{figure}[H]
+\begin{figure}[!h]
 \centering
-\includegraphics[width = \textwidth]{Fig1.pdf}
+%\includegraphics[width = \textwidth]{Fig1.pdf}
 \caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic distribution and their corresponding wordclouds.} The Public Agenda is represented either by Google Trends (GT) and Twitter (Tw).
@@
 
-\begin{figure}[H]
-\includegraphics[width = \textwidth]{Fig2.pdf}
+\begin{figure}[!h]
+%\includegraphics[width = \textwidth]{Fig2.pdf}
 \caption{\textbf{Bump graph of the Media Agenda (MA) and Public Agenda extracted from Google Trends (GT) and Twitter (Tw)}.
@@
 
-\begin{table}[H]
-\centering
-\resizebox{\textwidth}{!}{\begin{tabular}{lp{10cm}}
-\toprule
-Topic's name & Google Trends query \\ 
-\midrule
+\begin{table}[!h]
+\begin{adjustwidth}{-2.25in}{0in}
+\begin{tabular}{ll}
+Topic's name & Google Trends query \\ \hline
 Elections & elecciones + cambiemos + cristina kirchner + massa + randazzo \\
@@
 Former Vice-President & amado boudou + ciccone + ariel lijo + vandenbroele + núñez carmona \\
-\bottomrule
-\end{tabular}}
+\end{tabular}
 \caption{Queries used in Google Trends in order to build the Public Agenda.}
 \label{table:gt_queries}
+\end{adjustwidth}
 \end{table}
 
-\begin{table}[H]
-\centering
-\resizebox{\textwidth}{!}{\begin{tabular}{lccc}
-\toprule
-Topic's name & Correlation MA and GT & MA and Twitter & GT and Twitter \\ 
-\midrule
+\begin{table}[!h]
+\begin{adjustwidth}{-2.25in}{0in}
+\begin{tabular}{lccc}
+Topic's name & Correlation MA and GT & MA and Twitter & GT and Twitter \\ \hline
 Elections & \textbf{0.81} & \textbf{0.59} & \textbf{0.75} \\
@@
 Former Vice-President & \textbf{0.90} & \textbf{0.92} & \textbf{0.97}\\
-\bottomrule
-\end{tabular}}
+\end{tabular}
 \caption{Correlation between the topics' temporal profiles of the Public Agenda and their counterpart in Media Agenda.
@@
 \label{table:gt_all_correlation}
+\end{adjustwidth}
 \end{table}
@@
 
-\begin{figure}[H]
+\begin{figure}[h!]
 \centering
-\includegraphics[height=0.7\textheight]{Fig3.pdf}
+%\includegraphics[height=0.7\textheight]{Fig3.pdf}
 \caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda show a less diverse behavior than the Media Agenda as can be seen in the left figure.
@@
 
-\begin{figure}[H]
+\begin{figure}[h!]
 \centering
-\includegraphics[height = 0.7\textheight]{Fig4.pdf}
+%\includegraphics[height = 0.7\textheight]{Fig4.pdf}
 \caption{\textbf{Jensen Shannon distance between the Media Agenda and the Public Agenda as a function of time} (with upper inner fences pointed out).
@@
 
-\subsection{Agenda bias in different Media outlets}
+\subsection*{Agenda bias in different Media outlets}
 
@@
 
-\begin{figure}[H]
+\begin{figure}[h!]
 \centering
-\includegraphics[width = \textwidth]{Fig5.pdf}
+%\includegraphics[width = \textwidth]{Fig5.pdf}
 \caption{\textbf{Bump charts of newspapers' Agenda and radar plot of the average distributions.} The figure shows, in a qualitative way, the bias in the different newspaper's agendas.
@@
 
-\begin{figure}[H]
+\begin{figure}[h!]
 \centering
-\includegraphics[width = \textwidth]{Fig6.pdf}
+%\includegraphics[width = \textwidth]{Fig6.pdf}
 \caption{\textbf{Jensen-Shannon distance between the newspapers agenda and the Media Agenda as a function of time}.
@@
 
-\begin{figure}[H]
+\begin{figure}[h!]
 \centering
-\includegraphics[width = \textwidth]{Fig7.pdf}
+%\includegraphics[width = \textwidth]{Fig7.pdf}
 \caption{\textbf{Relative weight of the topics (a) \emph{Missing person}, and (b) \emph{Former Planning Minister}, and their corresponding word-clouds of frequent newspapers' keywords}.
@@
 
-\subsection{After all: Who sets the Agenda?}
+\subsection*{After all: Who sets the Agenda?}
 \label{sec:who_sets}
@@
 
-\begin{figure}[H]
-\includegraphics[width = \textwidth]{Fig8.pdf}
+\begin{figure}[h!]
+%\includegraphics[width = \textwidth]{Fig8.pdf}
 \caption{\textbf{Agenda setting direction in Missing person's topic?}
@@
 
-\section{Conclusions}
+\section*{Conclusions}
 
@@
 
-\newpage
-\section{Supplementary Material}
-\subsection{Context}
+\section*{Supporting information}
+
+\subsection*{Context}
 \label{sec:Context}
@@
 
-\begin{figure}[H]
+\begin{figure}[h!]
 \centering
-\includegraphics[scale = 0.4]{FigA2.pdf}
-\includegraphics[scale = 0.4]{FigA1.pdf}
+%\includegraphics[scale = 0.4]{FigA2.pdf}
+%\includegraphics[scale = 0.4]{FigA1.pdf}
 \caption{Temporal profiles of topics \emph{Elections} (left) and \emph{Missing Person} (right) for both LDA and NMF. All the topics found by applying NMF have a highly correlated counterpart in LDA.} 
@@
 
-\begin{table}[H]
-\centering
-\resizebox{\textwidth}{!}{\begin{tabular}{llc}
-\toprule
-& Correlation between NMF and LDA \\
-\midrule
+\begin{table}[h!]
+\begin{adjustwidth}{-2.25in}{0in}
+{\begin{tabular}{llc}
+& Correlation between NMF and LDA \\ \hline
 Elections & \textbf{0.98} \\
@@
 Prosecutor's death & \textbf{0.83} \\
-\bottomrule
 \end{tabular}}
@@
 \label{table:correlation_nmf_lda}
+\end{adjustwidth}
 \end{table}
 
-\newpage
-\bibliography{agenda_diversity}
+\section*{Acknowledgments}
+Cras egestas velit mauris, eu mollis turpis pellentesque sit amet.
+Interdum et malesuada fames ac ante ipsum primis in faucibus.
+Nam id pretium nisi.
+Sed ac quam id nisi malesuada congue.
+Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.
+
+\nolinenumbers
+
+% Either type in your references using
+% \begin{thebibliography}{}
+% \bibitem{}
+% Text
+% \end{thebibliography}
+%
+% or
+%
+% Compile your BiBTeX database using our plos2015.bst
+% style file and paste the contents of your .bbl file
+% here. See http://journals.plos.org/plosone/s/latex for 
+% step-by-step instructions.
+% 
+\begin{thebibliography}{10}
+
+\end{thebibliography}
 

### 2018-08-21 bmc_article.tex
Formula de topico en funcion del tiempo corregida

@@
 This was performed \emph{NMF} through the python module \emph{scikit-learn} \cite{scikit-learn}.
-\par A time-dependent representation is obtained by defining the temporal profile of the topic $i$, $W_i(day)$, by eq.\ref{eq:topic_weight} where $l(j)$ is the number of words of the document $j$, $h_{ji}$ is the degree of membership of document $j$ on topic $i$ and $\delta$ is the Kronecker delta.
+\par A time-dependent representation is obtained by defining the temporal profile of the topic $i$, $W_i(day)$, by eq.\ref{eq:topic_weight} where $l(j)$ is the number of words of the document $j$, $h_{ji}$ is the degree of membership of document $j$ on topic $i$, $d_j$ is the date of document $j$, and $\delta$ is the Kronecker delta.
 Providing by the fact that each document's vector can have all non-zero components, it is allowed that a document contributes to more than one topics' weight.
@@
 \begin{equation}
-W_i(day) = \sum_j^d l(j) \cdot h_{ji} \cdot \delta_{d,day}
+W_i(day) = \sum_j l(j) \cdot h_{ji} \cdot \delta_{d_j,day}
 \label{eq:topic_weight}

### 2018-08-27 bmc_article.tex
Entropia desarrollada, falta lo que sigue

@@
 
-\def\includegraphic{}
-\def\includegraphics{}
+%\def\includegraphic{}
+%\def\includegraphics{}
+\usepackage{graphicx}
 
@@
 Directly or indirectly, people get informed by consuming news from the media.
-But which is the dynamics of the agenda and how the people become interested in the different topics of the agenda?
+But which is the dynamics of the agenda and how the people become interested in their different topics?
 The Agenda Setting theory provides a conceptual framework in order to understand the role played by the mass media in public opinion formation, but the previous questions can not be answered without proper quantitative measures of agenda's dynamics and public attention.
-In this work we study the agenda of Argentinian newspapers in comparison with public's interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time.
-We measure Agenda's diversity as a function of time using Shannon's entropy and difference between Agendas using Jensen-Shannon's distance.
-We found that the Public Agenda is less diverse than the Media Agenda, and we are also capable to detect periods of time where coverage of certain issues are biased (coverage bias).\\
+In this work we study the agenda of Argentinian newspapers in comparison with public interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time.
+We measure Agenda's diversity as a function of time using Shannon's entropy and differences between Agendas using Jensen-Shannon's distance.
+We found that the Public Agenda is less diverse than the Media Agenda, and we were also capable to detect periods of time where coverage of certain issues are biased (coverage bias).\\
 
@@
 \kwd{agenda-setting}
-\kwd{agenda diversity}
-\kwd{coverage bias}
-\kwd{topic modelling}
+\kwd{opinion formation}
+\kwd{topic detection}
+\kwd{Mass Media influence}
 \end{keyword}
@@
 
-\subsection*{Agenda Setting Theory}
+%\subsection*{Agenda Setting Theory}
 
-\par To understand the ecosystem of information flow and opinion formation is one of the goals in these days.
-In this framework, many ingredients can be part of different mechanism of social influence.
-A major role in this ecosystem is played by the Mass Media outlets, which used to be the source of information of many of us.
-Informed people tends to interact with each other, either via personal interactions or through social networks.
+\par The understanding of  the ecosystem of information flow and opinion formation is one of the challenges in  complex social system research.
+Within this framework, many ingredients can be part of different mechanism of social influence.
+A major role in this ecosystem is played by the Mass Media outlets, which use to be the source of information of many people.
+Then, informed people tends to interact with each other, either via personal interactions or through social networks, giving rise to complex dynamics where opinions are shaping and changing in time.
 In this scenario, becomes essential to understand the role of Mass Media Influence in a given social group.
@@
 In other words, the media agenda is a systematic compilation of the issues or topics presented to the public that identifies the degree of emphasis on these topics''}.
-\par In its basic stage, the theory focus on the comparison between the topics coverage by the media and the public agenda, i.e. the topics that the public consider as priority.
+\par In its first-level stage, the theory focus on the comparison between the topics coverage by the media and the public agenda, i.e. the topics that the public consider as priority.
 It looks for answering the question if the media is able to set the public agenda, which would transform the media as an important actor in the formation of public opinion. 
@@
 However, it is based on two assumptions that are not necessarily true: the public spreads its attention in an homogeneous way across the multiple sources, and that the agendas of that sources are different \cite{mccombs2005look}.
+
 \par From the Chapel Hill research, several directions of agenda-setting were established \cite{mccombs2005look}.
-The ``second level agenda-setting'', sometimes called \textit{attribute agenda-setting}, studies the \textit{objects} (in a social psychology way, where an \textit{attitude object} designate a thing that an individual has an attitude or opinion about) present in the media agenda.
+The ``second level agenda-setting'', sometimes called \textit{attribute agenda-setting}, studies the \textit{objects} (in a social psychology sense, where an \textit{attitude object} designate a thing that an individual has an attitude or opinion about) present in the media agenda.
 When the media talks about an object some attributes are emphasized, and others not.
@@
 The competition between mass media for the same audience can lead to a homogenization of the agendas \cite{vargo2017networks}, which is in the opposite direction of one of the assumptions that predict the end of agenda-setting, as was mentioned before.
+
 \par Since the irruption of internet in our lives and the access to big data, there were many attempts to analyze from a quantitative point of view the theory of Agenda Setting based on  the original work of McCombs \cite{mccombs1972agenda}.
@@
 \subsection*{The Media Agenda}
-\par In this work we analyze a three month period of the Argentinian Media's Agenda composed a corpus of news' articles that were published between July 31th and November 5th in the section \emph{Politics} of the electronic editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\'on}, \emph{P\'agina12}, and the news portal \emph{Infobae}.
+\par In this work we analyze a three month period of the Argentinian Media's Agenda composed by a corpus of news' articles that were published between July 31th and November 5th of 2017 in the section \emph{Politics} of the online editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\'on}, \emph{P\'agina12}, and the news portal \emph{Infobae}.
 The first two lead the sale of printed editions in \emph{Buenos Aires} city, but \emph{Clar\'in} reaches roughly two times the readers of \emph{La Naci\'on}, and ten times the readers of \emph{P\'agina 12} \cite{IVC}.
-On the other hand, \emph{Infobae} has the website with more visitors, above the websites of \emph{Clar\'in} and \emph{La Naci\'on} \cite{AlexaAR}.
-The corpus analyzed is constituted by 2908 politics articles of \emph{Clar\'in}, 3565 of \emph{La Naci\'on}, 3324 of \emph{P\'agina 12}, and 2018 of \emph{Infobae}.
+On the other hand, \emph{Infobae} has the most visited website, much more than \emph{Clar\'in} and \emph{La Naci\'on} \cite{AlexaAR}.
+The corpus analyzed comprise by 2908 politics articles of \emph{Clar\'in}, 3565 of \emph{La Naci\'on}, 3324 of \emph{P\'agina 12}, and 2018 of \emph{Infobae}.
 Except \emph{P\'agina 12}, all articles were taken from the section \emph{Pol\'itica}  (Politics) of the respective news portal, while the articles which belong to \emph{P\'agina 12} were taken from the section \emph{El pa\'is} (The country).
-\par In order to perform the analysis of the articles in the corpus, we describe them as numerical vectors through the \textit{term frequency - inverse document frequency (tf-idf)} representation \cite{xu2003document}.
+
+\par We describe them as numerical vectors through the \textit{term frequency - inverse document frequency (tf-idf)} representation \cite{xu2003document}.
 Given the set of terms contained in the corpus' words after removing non-informative ones, such as prepositions and conjunctions, the \textit{tf-idf} algorithm represents the \textit{i}-document as a vector $v_i = [x_{i1}, x_{i2}, ...
@@
 On the other hand, \emph{W} gives the topics representation in the original term-space.
-The largest components of a row give the group of words which represent more accurately each topic (called keywords) and therefore an insight of what the topic is talking about.
-Since the factorization of eq.\ref{eq:nmf} usually can not be made exactly, it is approximated by minimizing the reconstruction error, i.e.
+The largest components of a row give the most representative words of each topic (called keywords) and therefore an insight of what the topic is talking about.
+Since the factorization of eq.(\ref{eq:nmf}) usually can not be made exactly, it is approximated by minimizing the reconstruction error, i.e.
 the distance between matrix \emph{M} and its approximated form $\tilde{M} = H \cdot W$.
 This was performed \emph{NMF} through the python module \emph{scikit-learn} \cite{scikit-learn}.
-\par A time-dependent representation is obtained by defining the temporal profile of the topic $i$, $W_i(day)$, by eq.\ref{eq:topic_weight} where $l(j)$ is the number of words of the document $j$, $h_{ji}$ is the degree of membership of document $j$ on topic $i$, $d_j$ is the date of document $j$, and $\delta$ is the Kronecker delta.
+
+\par Then  a  time-dependent Media Agenda is represented a a time evolving distribution of topics.
+The daily weight of the topic $i$, $W_i(day)$, is calculated following  eq.(\ref{eq:topic_weight}), where $l(j)$ is the number of words of the document $j$, $h_{ji}$ is the degree of membership of document $j$ on topic $i$, $d_j$ is the date of document $j$, and $\delta$ is the Kronecker delta.
 Providing by the fact that each document's vector can have all non-zero components, it is allowed that a document contributes to more than one topics' weight.
-In order to reduce noise, we apply a linear filter with a sliding window of size 3, and finally we normalize the temporal profiles in order to describe each newspaper agenda as a distribution over the topics' space which evolves over time.
-This last normalization prevent us against the differences in the number of articles that each newspaper publishes.
+In order to reduce noise, we apply a linear filter with a three day wide sliding window, and finally we normalize the temporal profiles in order to describe each newspaper agenda as a distribution over the topics' space which evolves over time.
+%This last normalization prevent us against the differences in the number of articles that each newspaper publishes.
 
@@
 
-\par In order to have a proxy about how the Media Agenda is reaching the public, we look for the same topics in \emph{Google} and \emph{Twitter} in the same period of time.
-We take advantage of topics' keywords on the one hand by making queries to the \emph{Google Trends} tool and getting the relative weight of Google searches that people made about the identified topics, and in the other hand, by making queries to the advance search tool in the social media Twitter in order to get the relative amount of related tweets.
-
-\subsection*{Outliers identification}
-\label{sec:outliers_identification}
-\par We identify outliers values in a data set of N observations by following the box plot construction.
-The quantities (called fences) in \ref{eq:fences} are used, where $Q1$ is the lower quartile (range of the distribution where lies the 25th percent of the data), $Q3$ is the upper quartile (where lies the 75th percent of the data) and $IQ = Q3 - Q1$.
-
-\begin{eqnarray}\label{eq:fences}
-lower inner fence (LIF) & = Q1 - 1.5 IQ \\
-upper inner fence (UIF) & = Q3 + 1.5  IQ \\
-lower outer fence (LOF) & = Q1 - 3  IQ \\
-upper outer fence (UOF) & = Q3 + 3 IQ
-\end{eqnarray}
-
-\par A point above the upper inner fence considered a mild outlier and a point above an outer fence is considered an extreme outlier. The same holds for the lower fences \cite{natrella2010nist}.
-
-\subsection*{Jensen-Shannon distance}
-
-\par In probability theory and statistics, the Jensen-Shannon divergence ($JS_{Div}$) is a method to measure the similarity between two probability distributions.
-It is based on the Kullback-Leibler divergence ($D_{KL}$), but have also useful properties such as it is symmetric and it is always a finite value.
-The square root of the Jensen-Shannon divergence (see eq.\ref{eq:jensen_shannon_distance}, where $M = \frac{P + Q}{2}$) is a metric \cite{fuglede2004jensen} often referred as Jensen-Shannon distance ($JSD$).
-\begin{eqnarray}\label{eq:jensen_shannon_distance}
-D_{KL}(P||Q) = -\sum{P(i) log(\frac{Q(i)}{P(i)})} \\
-JSD(P,Q) = \sqrt{JS_{Div}(P,Q)} = \sqrt{\frac{1}{2}[D_{KL}(P||M) + D_{KL}(Q||M)] } 
-\end{eqnarray}
+\par The other side of time-dependent Media Agenda is to have some measure of the public interest about these topics.
+With this goal, we use  \emph{Google Trends} and \emph{Twitter} as proxy of public interest by  looking for the same topics  in the same period of time.
+We take advantage of topics' keywords to make queries in the \emph{Google Trends}  tool and  into the advance search tool of Twitter  to get the relative weight searches and tweets in both platforms.
 
@@
 
-\par The normalized Shannon's entropy (eq.\ref{eq:shannon_entropy}) is a way to measure how spread is a distribution, taking the maximum value where all outcomes are equally probable in the case of a discrete distribution.
+\par One of the key of our work is the representation of the Agendas as time evolving topic distributions, and the association between the different measures that we can derive from them with the social events observed during the period.
+The first measure we emphasize is the concept of \emph{diversity of the attention}, while the distance between Agendas will be developed in the next section.
+Following \cite{boydstun2014importance} the \emph{diversity} is a very important variable that must be taken into account when dealing with multiple issues as it tells us how the attention is distributed across the different topics of discussion.
+In that work, their also propose the use of the normalized Shannon's entropy as a way to quantify the diversity which we found very suitable for our framework.
+\par The normalized Shannon's entropy $H[p]$ referred in eq.(\ref{eq:shannon_entropy}) give us a measure of how spread is a distribution, taking the maximum value of $1$ where all outcomes are equally probable in the case of a discrete distribution, and $0$ where one of the outcomes is the only possible one.
+This last case will be of particular interest for us because it tells about a topic which absorbs all the attention either from the Media or the Public, while the former shows an absolutely unbiased interest towards any of the topics.
 
@@
 
+\subsection*{Jensen-Shannon distance}
+
+\par While the diversity is a property of each individual distribution, a natural question that arise when comparing different distributions is how far or close are among them.
+Therefore a measure of distances between distributions is necessary. 
+We proposed here the use of the Jensen-Shannon distance ($JSD$) which
+
+DESAROLLAR LA EXPLICACION DE LA DISTANCIA DE JS Y HABLAR SOBRE LAS CONSECUENCIAS DE QUE LAS DISTRIBUCIONES ESTEN CERCA O LEJOS, EN PARTICULAR LA AGENDA PUBLICA DE LA MEDIATICA.
+
+can be seen as a property a In probability theory and statistics, the Jensen-Shannon divergence ($JS_{Div}$) is a method to measure the similarity between two probability distributions.
+It is based on the Kullback-Leibler divergence ($D_{KL}$) with interesting properties such as it is symmetric and it is always a finite value.
+The square root of the Jensen-Shannon divergence (see eq.\ref{eq:jensen_shannon_distance} is a metric \cite{fuglede2004jensen} often referred as Jensen-Shannon distance ($JSD$).
+The measure of the distances between distributions will tell us
+
+\begin{eqnarray}\label{eq:jensen_shannon_distance}
+D_{KL}(P||Q) &= -\sum{P(i) log(\frac{Q(i)}{P(i)})} \nonumber \\
+JSD(P,Q) &= \sqrt{JS_{Div}(P,Q)} = \sqrt{\frac{1}{2}[D_{KL}(P||M) + D_{KL}(Q||M)] } 
+\end{eqnarray}
+
+where $M = \frac{P + Q}{2}$). In Section \ref{results} we will use Jensen-Shannon distance to measure differences between agendas.
+
+\subsection*{Outliers identification}
+
+DADAS LAS MEDIDAS DEFINIDAS ANTERIORMENTE QUEREMOS TENER UN CRITERIO PARA DECIR CUANDO UN PUNTO ES POCO DIVERSO O CUANDO UN PUNTO ESTA ALEJADO.
+MENCIONAR QUE ESTA MEDIDA ES SUGESTIVA POR LO QUE NO NOS BASAMOS ESTRICAMENTE SINO QUE SIMPLEMENTE LOS TOMAMOS COMO UN CRITERIO PARA VER A QUE PUNTOS VAMOS A PRESTARLES MAYOR ATENCION
+
+\label{sec:outliers_identification}
+\par One of the key aspects in our analysis is to identify outliers in distances between agendas. We identify outliers values in a data set of N observations by following the box plot construction.
+Four fences are defined based on a quartile division of the distribution, according to 
+The quantities (called fences) in \ref{eq:fences} are used, where $Q1$ is the lower quartile (range of the distribution where lies the 25th percent of the data), $Q3$ is the upper quartile (where lies the 75th percent of the data) and $IQ = Q3 - Q1$.
+
+\begin{eqnarray}\label{eq:fences}
+LIF & = Q1 - 1.5 IQ \nonumber \\
+UIF & = Q3 + 1.5  IQ \nonumber\\
+LOF & = Q1 - 3  IQ \nonumber \\
+UOF & = Q3 + 3 IQ
+\end{eqnarray}
+
+\par where $LIF$ stands for lower inner fence, $UIF$ for upper inner fence, $LOF$ for lower outer fence and $UOF$ for upper outer fence.
+A point above the upper inner fence considered a mild outlier and a point above an outer fence is considered an extreme outlier.
+The same holds for the lower fences \cite{natrella2010nist}.
+
 \section*{Results}
+\label{results}
 
-\par The starting point of our analysis is the decomposition of the corpus in ten topics.
-This is an arbitrary decision, validated in some manner by our knowledge of the corpus, which could be revised in future works.
-From the initial ten topics, three of them could be interpreted as part of the same macro-topic called \emph{Elections}.
-The same happen with two others which we classified as part of the macro-topic called \emph{Missing person}, leaving the  final description of the agendas as made with seven topics.
+\par We initially focus in the ten most important issues in the three months period corpus of news reported above.
+These ten topics, represented in the word clouds  of Fig.\label{fig:topics_wordclouds}, were reduced to seven (shown in the radar plot of the same figure) given the similarities found in, for instance, three of them that could be interpreted as part of the same macro-topic called \emph{Elections} and two others which were classified as part of a macro-topic called \emph{Missing person}.
 The meaning of the topics or macro-topics is contextualized in section \ref{sec:Context} of Supplementary Material.
-\par After the procedure described in the previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, and all their derivations, as time-dependent distributions.
+\par Following the procedure described in the previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)} (Google and Twitter), and all their derivations, as time-dependent distributions.
 
@@
 \par In figure \ref{fig:topics_wordclouds} we show a ten topic decomposition of the whole corpus using radar plots for the Media \textbf{MA} and Public agendas \textbf{PA} discriminated by \textbf{GT} (Google Trends) and \textbf{Tw} (Twitter).
-A radar plot is an alternative of histograms that allows the visual comparison of distributions easier.
 In this figure we also show the wordclouds of the keywords that define each topic, where the size of the word reflects its importance in the topic's definition.
-In green color, we point out the words involved in the Google Trends and Twitter queries in order to construct the Public Agenda.
-The queries employed are also specified in table \ref{table:gt_queries}.
-In table \ref{table:gt_all_correlation} we show the linear correlation between the topics' temporal profiles from the Public Agenda and their counterparts in the Media Agenda.
-\par In figure \ref{fig:all_agenda} we show the time evolution of the topics with a bump chart of the Agendas.
-The bump chart provides  a very useful visualization tool for displaying the relative weight of the topics at the same time that their ranking.
-In figure \ref{fig:all_agenda} we also highlight some important events related to the dynamics of the topics.
-\footnote{Due to different characteristics in the search tool of Twitter, we adapted the queries employed here but preserving at least at we can the most important keywords.
+In green color, we point out the words involved in the Google Trends and Twitter  \footnote{Due to different characteristics in the search tool of Twitter, we adapted the queries employed here but preserving at least at we can the most important keywords.
 The queries employed by topic were: \\
@@
 Former Vice-President:  boudou + ciccone +  lijo + vandenbroele + carmona
-}
-\par The figures introduced above show not only the topics and their differences between the Agendas, but also the dynamics of the topics.
+} queries in order to construct the Public Agenda.
+The queries employed are also specified in table \ref{table:gt_queries}.
+In table \ref{table:gt_all_correlation} we show the linear correlation between the topics' temporal profiles from the Public Agenda and their counterparts in the Media Agenda.
+
+\par We can observe that both Public Agendas ($GT$ and $Tw$) look similar in this representation, but they show specific differences with the Media Agenda, where a greater interest of the audience in the topic \emph{Missing person} than the Media is observed, or inversely, a lower interest in the topic \emph{Prosecutor's death} takes place.
+However, this static representation is not able to show the complex dynamics of agenda's evolution and the importance of punctual and specific facts which can erase or amplify their differences.
+
+\par This can be observed in figure \ref{fig:all_agenda} where the time evolution of the topics is shown in a bump chart of the Agendas.
+The bump chart provides  a clear visualization of the relative weight of the topics at the same time that their ranking.
+In  this figure  we also highlight some important events related to the dynamics of the topics and  it is  possible to appreciate how the main topic change in time and have a glance of the qualitative differences between agendas.
+In particular, it can be observed some differences between Public Agendas ($GT$ and $Tw$) that were not observed in the previous figure:
+
+IN PARTICULAR.. COMENTAR MAS DE ESTE GRAFICO
+
+\par The linear correlations shown in table \ref{table:gt_all_correlation} are  positive and statistically significant in all the cases, This can be interpreted as a validation of the topics found in the corpus and the keywords that describe it.
+Even though it is expected that the Media's and public's interest should generally follow a similar a pattern due to the external events, we are interested in those periods where they significantly differ.
+A non positive (or a non significant) correlation may imply, besides the obvious conclusion of agenda's disengagement, that we could eventually fail in properly detect the keywords or features that describe a particular topic, so the Google Trends' or Twitter's pattern would not be able to reflect a similar behavior that its counterpart in the Media.
+
+%\par The figures introduced above show not only the topics and their differences between the Agendas, but also the dynamics of the topics.
 For instance, we can see in the radar plot of figure \ref{fig:topics_wordclouds}, a greater interest of the audience in the topic \emph{Missing person} than the Media, or inversely in the topic \emph{Prosecutor's death}, at least in the analyzed time-lapse.
 We can also observe a great similarity between \textbf{GT} and \textbf{Tw} agendas which both are different faces of the Public Agenda.
-\par On the other hand, figure \ref{fig:all_agenda} allow us to appreciate how the main topic change in time and have a glance of the qualitative differences between agendas.
-The linear correlations shown in table \ref{table:gt_all_correlation} are  positive and statistically significant in all the cases, This can be interpreted as a validation of the topics found in the corpus and the keywords that describe it.
-Even though it is expected that the Media's and public's interest should generally follow a similar a pattern due to the external events, we are interested in those periods where they significantly differ.
-A non positive (or a non significant) correlation may imply, besides the obvious conclusion of agenda's disengagement, that we could eventually fail in properly detect the keywords or features that describe a particular topic, so the Google Trends' or Twitter's pattern would not be able to reflect a similar behavior that its counterpart in the Media.
 
@@
 \begin{figure}[h!]
-%\includegraphics[width = \textwidth]{Fig1.pdf}
+\includegraphics[width = \textwidth]{Fig1.pdf}
 \caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic distribution and their corresponding wordclouds.} The Public Agenda is represented either by Google Trends (GT) and Twitter (Tw).
@@
 \begin{figure}[h!]
-%\includegraphics[width = \textwidth]{Fig2.pdf}
+\includegraphics[width = \textwidth]{Fig2.pdf}
 \caption{\textbf{Bump graph of the Media Agenda (MA) and Public Agenda extracted from Google Trends (GT) and Twitter (Tw)}.
@@
 \begin{figure}[h!]
-%\includegraphics[height=0.7\textheight]{Fig3.pdf}
+\includegraphics[height=0.7\textheight]{Fig3.pdf}
 \caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda show a less diverse behavior than the Media Agenda as can be seen in the left figure.
@@
 \begin{figure}[h!]
-%\includegraphics[height = 0.7\textheight]{Fig4.pdf}
+\includegraphics[height = 0.7\textheight]{Fig4.pdf}
 \caption{\textbf{Jensen Shannon distance between the Media Agenda and the Public Agenda as a function of time} (with upper inner fences pointed out).
@@
 \begin{figure}[h!]
-%\includegraphics[width = \textwidth]{Fig5.pdf}
+\includegraphics[width = \textwidth]{Fig5.pdf}
 \caption{\textbf{Bump charts of newspapers' Agenda and radar plot of the average distributions.} The figure shows, in a qualitative way, the bias in the different newspaper's agendas.
@@
 \begin{figure}[h!]
-%\includegraphics[width = \textwidth]{Fig6.pdf}
+\includegraphics[width = \textwidth]{Fig6.pdf}
 \caption{\textbf{Jensen-Shannon distance between the newspapers agenda and the Media Agenda as a function of time}.
@@
 \begin{figure}[h!]
-%\includegraphics[width = \textwidth]{Fig7.pdf}
+\includegraphics[width = \textwidth]{Fig7.pdf}
 \caption{\textbf{Relative weight of the topics (a) \emph{Missing person}, and (b) \emph{Former Planning Minister}, and their corresponding word-clouds of frequent newspapers' keywords}.
@@
 \begin{figure}[h!]
-%\includegraphics[width = \textwidth]{Fig8.pdf}
+\includegraphics[width = \textwidth]{Fig8.pdf}
 \caption{\textbf{Agenda setting direction in Missing person's topic?}
@@
 \begin{figure}[h!]
-%\includegraphics[scale = 0.4]{FigA2.pdf}
-%\includegraphics[scale = 0.4]{FigA1.pdf}
+\includegraphics[scale = 0.3]{FigA2.pdf}
+\includegraphics[scale = 0.3]{FigA1.pdf}
 \caption{Temporal profiles of topics \emph{Elections} (left) and \emph{Missing Person} (right) for both LDA and NMF. All the topics found by applying NMF have a highly correlated counterpart in LDA.} 
@@
 
-\section*{Additional Files}
-  \subsection*{Additional file 1 --- Sample additional file title}
-    Additional file descriptions text (including details of how to
-    view the file, if it is in a non-standard format or the file extension).  This might
-    refer to a multi-page table or a figure.
+%\section*{Additional Files}
+%  \subsection*{Additional file 1 --- Sample additional file title}
+%    Additional file descriptions text (including details of how to
+%    view the file, if it is in a non-standard format or the file extension).  This might
+%    refer to a multi-page table or a figure.
 
-  \subsection*{Additional file 2 --- Sample additional file title}
-    Additional file descriptions text.
+%  \subsection*{Additional file 2 --- Sample additional file title}
+%    Additional file descriptions text.
 

### 2018-08-27 bmc_article.tex
Parte de material and methods reescrita

@@
 %%% Load packages
-%\usepackage{amsthm,amsmath}
+\usepackage{amsthm,amsmath}
 %\RequirePackage{natbib}
@@
 \subsection*{The Media Agenda}
-\par In this work we analyze a three month period of the Argentinian Media's Agenda composed by a corpus of news' articles that were published between July 31th and November 5th of 2017 in the section \emph{Politics} of the online editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\'on}, \emph{P\'agina12}, and the news portal \emph{Infobae}.
+\par In this work we analyze a three month period of the Argentinian Media's Agenda composed by a corpus of news' articles that were published between July 31th and November 5th of 2017. 
+The articles come from the \emph{Politics} section of the online editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\'on}, \emph{P\'agina12}, and the news portal \emph{Infobae}.
 The first two lead the sale of printed editions in \emph{Buenos Aires} city, but \emph{Clar\'in} reaches roughly two times the readers of \emph{La Naci\'on}, and ten times the readers of \emph{P\'agina 12} \cite{IVC}.
@@
 
-\par Then  a  time-dependent Media Agenda is represented a a time evolving distribution of topics.
+\par Then a time-dependent Media Agenda is represented as a time evolving distribution of topics.
 The daily weight of the topic $i$, $W_i(day)$, is calculated following  eq.(\ref{eq:topic_weight}), where $l(j)$ is the number of words of the document $j$, $h_{ji}$ is the degree of membership of document $j$ on topic $i$, $d_j$ is the date of document $j$, and $\delta$ is the Kronecker delta.
@@
 We take advantage of topics' keywords to make queries in the \emph{Google Trends}  tool and  into the advance search tool of Twitter  to get the relative weight searches and tweets in both platforms.
+\par In section \textbf{Results} we give a more detailed description of the keywords involved in the construction of the Google and Twitter Agendas.
 
@@
 \par One of the key of our work is the representation of the Agendas as time evolving topic distributions, and the association between the different measures that we can derive from them with the social events observed during the period.
-The first measure we emphasize is the concept of \emph{diversity of the attention}, while the distance between Agendas will be developed in the next section.
-Following \cite{boydstun2014importance} the \emph{diversity} is a very important variable that must be taken into account when dealing with multiple issues as it tells us how the attention is distributed across the different topics of discussion.
-In that work, their also propose the use of the normalized Shannon's entropy as a way to quantify the diversity which we found very suitable for our framework.
-\par The normalized Shannon's entropy $H[p]$ referred in eq.(\ref{eq:shannon_entropy}) give us a measure of how spread is a distribution, taking the maximum value of $1$ where all outcomes are equally probable in the case of a discrete distribution, and $0$ where one of the outcomes is the only possible one.
-This last case will be of particular interest for us because it tells about a topic which absorbs all the attention either from the Media or the Public, while the former shows an absolutely unbiased interest towards any of the topics.
+In order to do that, the first measure we emphasize is the concept of \emph{diversity of the attention}.
+Following \cite{boydstun2014importance} the \emph{diversity} is a very important variable that must be taken into account when dealing with multiple issues, due to the fact that it tells us how the attention is distributed across the different topics of discussion.
+In that work, their also propose the use of the normalized Shannon's entropy as a way to quantify the diversity, which can be easily calculated and therefore is a very suitable quantity within our framework.
+\par The normalized Shannon's entropy $H[p]$ referred in eq.(\ref{eq:shannon_entropy}) give us a measure of how spread is a -discrete- distribution, taking the maximum value of $1$ when all outcomes are equally probable, and $0$ when there is just one possible outcome.
+This last case -or approximated ones- will be of particular interest for us because it tells about a topic which absorbs all the attention either from the Media or the Public, while the former shows an absolutely unbiased interest towards any of the topics.
 
@@
 
-\par While the diversity is a property of each individual distribution, a natural question that arise when comparing different distributions is how far or close are among them.
-Therefore a measure of distances between distributions is necessary. 
-We proposed here the use of the Jensen-Shannon distance ($JSD$) which
-
-DESAROLLAR LA EXPLICACION DE LA DISTANCIA DE JS Y HABLAR SOBRE LAS CONSECUENCIAS DE QUE LAS DISTRIBUCIONES ESTEN CERCA O LEJOS, EN PARTICULAR LA AGENDA PUBLICA DE LA MEDIATICA.
-
-can be seen as a property a In probability theory and statistics, the Jensen-Shannon divergence ($JS_{Div}$) is a method to measure the similarity between two probability distributions.
-It is based on the Kullback-Leibler divergence ($D_{KL}$) with interesting properties such as it is symmetric and it is always a finite value.
-The square root of the Jensen-Shannon divergence (see eq.\ref{eq:jensen_shannon_distance} is a metric \cite{fuglede2004jensen} often referred as Jensen-Shannon distance ($JSD$).
-The measure of the distances between distributions will tell us
+\par While the diversity is a property of each distribution, a natural question that arise when comparing different distributions is how similar they are.
+We will be for instance particularly interested in measuring the similarity between the Media and Public Agendas, because those dates when the similarity is low tell us about distant interests of the Media and the Public.
+We proposed here to measure the similarity between distributions by the use of the Jensen-Shannon distance ($JSD$). 
+When the similarity of the distributions is low, the distance between them is high.
+\par The Jensen-Shannon distance ($JSD$) is a metric between distributions based on the Jensen-Shannon divergence ($JS_{Div}$) \cite{fuglede2004jensen}, which is in turn a symmetric version of the well-known Kullback-Leibler divergence ($D_{KL}$).
+We recall that the $JSD$ has the advantage of being symmetric and also a well-defined distance, which make it conceptually easy to deal.
+As can be seen in eq.(\ref{eq:jensen_shannon_distance}) the $JSD$ between the distributions $P$ and $Q$ is simply the square root of the Jensen-Shannon divergence.
 
@@
 
-where $M = \frac{P + Q}{2}$). In Section \ref{results} we will use Jensen-Shannon distance to measure differences between agendas.
-
 \subsection*{Outliers identification}
 
-DADAS LAS MEDIDAS DEFINIDAS ANTERIORMENTE QUEREMOS TENER UN CRITERIO PARA DECIR CUANDO UN PUNTO ES POCO DIVERSO O CUANDO UN PUNTO ESTA ALEJADO.
-MENCIONAR QUE ESTA MEDIDA ES SUGESTIVA POR LO QUE NO NOS BASAMOS ESTRICAMENTE SINO QUE SIMPLEMENTE LOS TOMAMOS COMO UN CRITERIO PARA VER A QUE PUNTOS VAMOS A PRESTARLES MAYOR ATENCION
-
-\label{sec:outliers_identification}
-\par One of the key aspects in our analysis is to identify outliers in distances between agendas. We identify outliers values in a data set of N observations by following the box plot construction.
-Four fences are defined based on a quartile division of the distribution, according to 
-The quantities (called fences) in \ref{eq:fences} are used, where $Q1$ is the lower quartile (range of the distribution where lies the 25th percent of the data), $Q3$ is the upper quartile (where lies the 75th percent of the data) and $IQ = Q3 - Q1$.
-
+\par As was mentioned above, once defined the concepts of diversity and distance between distributions, we will be particularly interested in those dates when these concepts take extreme values: When the diversity is low, we know that a topic is absorbing much of the attention of any of the Agendas; on the other hand, when the distance between two distributions is high, we can conclude that they have distant interests.
+However, we still lack the definition of what a low diversity or a high distance are. 
+We face this problem by treating the measures of each observable as random samples from a population with unknown distribution and identifying those extreme values as outliers of the distribution. 
+In order to detect these outliers we follow the popular box-plot construction proposed by Tukey \cite{tukey1977exploratory}, which is a simple data-driven method and make no assumption about the distribution of the data.
+\par The box-plot construction is as follows: First a quartile division of the $N$ observations is made, by naming $Q1$ as the lower quartile, $Q2$ the median of the distribution, and $Q3$ the upper quartile.
+Recall that $Q1$ ($Q3$) are defined to be the division where the 25th (75th) percent of the observations lies below (by definition, the median $Q2$ separates the distribution in two equal parts).
+On the other hand, the inter-quartile range $IQ$ is defined as $IQ = Q3 - Q1$.
+This is the range where the bulk of the data lies inside.
+\par We are not interesting in the visualization of the box-plot in its own but instead in its procedure to identify outliers.
+Therefore from the quartiles, new quantities called \emph{fences} are defined in eq.(\ref{eq:fences}).
+In this equation, $LIF$ stands for \emph{lower inner fence}, $UIF$ for \emph{upper inner fence}, $LOF$ for \emph{lower outer fence} and $UOF$ for \emph{upper outer fence}.
+The fences can be interpreted as the limits of the distribution.
+We then have all the ingredients to label a point as an outlier: A point which lies above the upper inner fence is considered a \emph{mild outlier}, while a point that lies above the upper outer fence is considered an \emph{extreme outlier}.
+The same holds for the lower fences, i.e.
+if a point lies below the lower inner (outer) fences is considered as a mild (extreme) outlier \cite{natrella2010nist}.
 \begin{eqnarray}\label{eq:fences}
@@
 \end{eqnarray}
-
-\par where $LIF$ stands for lower inner fence, $UIF$ for upper inner fence, $LOF$ for lower outer fence and $UOF$ for upper outer fence.
-A point above the upper inner fence considered a mild outlier and a point above an outer fence is considered an extreme outlier.
-The same holds for the lower fences \cite{natrella2010nist}.
+\par We will indicate the proper fences in each figure either when the diversity or the distance is being analyzed.
+We will paid attention not only to those values labeled as outliers, but also to those that are next to any of the fences despite not being strictly defined as that.
 

### 2018-08-28 bmc_article.tex
Version corregida por balen a ver lectura mas o menos definitiva

@@
 %%% Load packages
-\usepackage{amsthm,amsmath}
+%\usepackage{amsthm,amsmath}
 %\RequirePackage{natbib}
@@
 In  this figure  we also highlight some important events related to the dynamics of the topics and  it is  possible to appreciate how the main topic change in time and have a glance of the qualitative differences between agendas.
-In particular, it can be observed some differences between Public Agendas ($GT$ and $Tw$) that were not observed in the previous figure:
+In particular, it can be observed some differences between Public Agendas ($GT$ and $Tw$) that were not observed in the previous figure, as for instance, the persistency of main topics is longer in Twitter than in Google Trends.
+This is more evident at the end of the analyzed period, where topics discussed in Google Trends shows more  responsive to change in Media Agenda than in Twitter, suggesting the existence that the interaction between people is stronger in the analyzed social network.
 
-IN PARTICULAR.. COMENTAR MAS DE ESTE GRAFICO
-
-\par The linear correlations shown in table \ref{table:gt_all_correlation} are  positive and statistically significant in all the cases, This can be interpreted as a validation of the topics found in the corpus and the keywords that describe it.
-Even though it is expected that the Media's and public's interest should generally follow a similar a pattern due to the external events, we are interested in those periods where they significantly differ.
+\par We also calculate linear correlations between same topics of $PA$ and $MA$  and we found that they are  positive and statistically significant in all the cases, as shown in table \ref{table:gt_all_correlation}.
+This can be interpreted as a validation of the topics found in the corpus and the keywords that describe it.
+Even though it is expected that the Media's and public's interest should generally follow a similar a pattern, mainly driven by  external events, we are interested in those periods where they significantly differ.
 A non positive (or a non significant) correlation may imply, besides the obvious conclusion of agenda's disengagement, that we could eventually fail in properly detect the keywords or features that describe a particular topic, so the Google Trends' or Twitter's pattern would not be able to reflect a similar behavior that its counterpart in the Media.
@@
 
-\par In order to quantify the diversity of the Agendas, we start by representing them as distributions in the topic's space. 
+\par How dominant is a main topic?
+Is the degree of dominance of a given topic in the Media Agenda reflected in the Public Agenda?
+In order to answer such kind of questions it is necessary  to quantify the diversity of the Agendas, which are represented as  distributions in the topic's space as was shown above.
 Following \cite{boydstun2014importance}, we calculate the normalized Shannon's entropy ($H$, see eq.\ref{eq:shannon_entropy}) in order to measure the diversity of the \textbf{MA} and \textbf{PA}.
-\par In figure \ref{fig:shannon_entropy_agendas} we can see the value of $H$ as a function of time, where it can be focused in those periods of time where the diversity is lower than usual.
-This effect is notoriously more pronounced in the Public Agenda giving by \textbf{GT}, and in particular in four specific days  where can be detected four local minima of Shannon's entropies.
+\par In figure \ref{fig:shannon_entropy_agendas} we can see the value of $H$ as a function of time for the three agendas.
+It is important to pay attention to those periods of time where the diversity is lower than usual.
+This effect is notoriously more pronounced in the Public Agenda giving by \textbf{GT} and, in particular, in four specific days  where  four local minima of Shannon's entropies can be detected.
 Three of them are outliers as defined in section \ref{sec:MatMeth}, two of them from \textbf{GT} and one from \textbf{Tw}.
-\par A lower value in the agenda's diversity is due to the fact that the most important topic attracts practically all the attention of the public and the media.
-In the radar plots included in figure \ref{fig:shannon_entropy_agendas} we can see that two of these outliers (\textbf{a} and \textbf{d}) belong to the topic \emph{Elections} and are related with the primary and general legislative elections that took place in August 13th and October 22th.
-In all the agendas these points where detected as outliers except point (d) in Twitter Agenda.
+The other one is not an outlier but a pronounced minima and therefore a point of interest in this description.
+
+\par A lower value in the agenda's diversity is due to the fact that the most important topic attracts practically all the attention of the public and the media, collapsing the diversity of the agenda.
+In the radar plots included in figure \ref{fig:shannon_entropy_agendas} we can see how two of these outliers (\textbf{a} and \textbf{d}) belong to the topic \emph{Elections}.
+They are related to the primary and general legislative elections that took place in August 13th and October 22th respectively.
+In all the agendas these points were detected as outliers except point (d) in Twitter Agenda.
 Why is that?
-The radar plot of the Twitter agenda for this day displays an association between the topic \emph{Elections} and the \emph{Current President} which could be decreasing the important of this topic.
+The radar plot of the Twitter agenda for this day displays an association between the topic \emph{Elections} and the \emph{Current President}, decreasing the important of this topic.
 Discussions in Twitter about elections appear also in point (c), when the other agendas seems to be more diverse. 
-On the other hand, we focused in point (b), despite not being detected as a outlier, because it belong to the topic \emph{Missing person} and this date correspond to the rally that took place one month after the disappearance of \emph{Santiago Maldonado} (see section \ref{sec:Context}).
-It is important to notice that the Shannon's Entropy of GT Agenda displays a minimum (collapsing agenda) not shown neither in the Media nor in the Twitter Agendas.
-We emphasize the discussion about this topic because we can appreciate  interesting facts that appear along the analysis.
-\par From the measure of $H$ we can also see that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
+On the other hand, and despite not being classified as outlier, we also focus in point (b) because Shannon's Entropy of $GT$ Agenda displays a minimum (collapsing agenda) which is not corresponded neither in the Media nor in the Twitter Agendas.
+Crawling in the context, we see that it belong to the topic \emph{Missing person} and this date correspond to the rally that took place one month after the disappearance of \emph{Santiago Maldonado} (see section \ref{sec:Context}).
+We  would like to emphasize the discussion about this topic (\emph{Missing person}) because its dynamics show interesting features, as we will show bellow.
+
+\par From the measure of $H$ we have also observed that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
 Specifically $H_{GT} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
 However from figure \ref{fig:shannon_entropy_agendas} we can see that \textbf{GT} shows more abrupt dropouts in the diversity in response to specific events.
-We conclude that its an important fact about audience behavior: given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus more in the most important topic than the Media can do, maybe due to editorial decisions.
+From all this analysis we  can conclude that given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus in the most important topics than Media can do, maybe due to editorial decisions.
 
@@
 
-\par Given our interpretation of the Agendas as time-evolving distributions, we can  compare them by computing the Jensen-Shannon distance.
+\par Given our descriptions of the Agendas as time-evolving distributions, we can  compare them by computing the Jensen-Shannon distance.
 In this context, outliers in selected dates will correspond to divergences between Public and Media Agenda, i.e., specific events where the public interest do not match with media offer.
@@
 We focus in three points that seems to be relevant enough.
-In all cases, the topic distributions at that particular dates displayed by  the radar plots shows that a greater distance is associated with a more interest of public in the topic \emph{Missing person}.
-\par Points \textbf{(c)} and \textbf{(d)} shows that both the Public and the Media highlight this topic, but the Media do not disregard other topics, so the corresponding distance between them can be interpreted  of another way of seeing the diversity effect discussed in the last section.
-\par On the other hand,  points \textbf{(a)} (we take this point due to be a local maximum despite not being an outlier) and \textbf{(b)} seem to show an interest of the public in the topic \emph{Missing person} which it is not reflected in the Media.
+In all cases, the topic distributions at that particular dates displayed by  the radar plots show that the increment in the distance between agendas is due to a greater interest of public opinion in the topic \emph{Missing person}.
+
+\par Points \textbf{(c)} and \textbf{(d)} show that both the Public and the Media highlight this topic, but the Media do not disregard other topics, so the corresponding distance between them can be interpreted as lack of the diversity in Public Agenda as discussed in the last section.
+
+\par On the other hand,  points \textbf{(a)} (we take this point due to be a local maximum despite not being an outlier) and \textbf{(b)}  show a major  interest of the public in the topic \emph{Missing person} which it is not reflected in the Media.
 In figure \ref{fig:all_agenda} we can see that this topic becomes the most important in public's interest (both \textbf{GT} and \textbf{Tw}) days before that  it happen in the Media Agenda.
 It can be associates  with a social networks (like Facebook and Twitter) campaign  in favor  of the appearance of \emph{Santiago Maldonado} (``The missing person") that took place on  August 26th.
-It was very important and was initially underestimated by the main Media outlets in Argentina (see section \ref{sec:Context}).
-\par It is important to notice that it is our interpretation of the data based on the knowledge of the context, and  we are not measuring causality between Agendas (we will say a few words about it in section \ref{sec:who_sets}), i.e.
+This campaign was massive and  initially underestimated by the main Media outlets in Argentina (see section \ref{sec:Context}).
+
+\par % It is important to notice that it is our interpretation of the data based on the knowledge of the context, and  we are not measuring causality between Agendas (we will say a few words about it in section \ref{sec:who_sets}), i.e.
 we can't say, for instance, that in this case the Public Agenda set the Media Agenda.
-However, the Jensen-Shannon distance, in conjunction with the measurement of the agenda diversity given by the Shannon entropy, give an insight of independent behavior of the Public and the Media, and its identification can be a starting point to study the Media reaction to a change in audience's interests.
+Finally, it is important to say that the Jensen-Shannon distance, in conjunction with the measurement of agenda diversity given by the Shannon entropy, give an insight of independent behavior, in certain particular dates,  of the Public and the Media.
+Its identification can be a starting point to study the Media reaction to a change in audience's interests.
 
@@
 
-\par In this section we leave aside the Public Agenda as a whole and we study how the Media agenda of each media outlet. 
-In figure \ref{fig:news_agenda} we show the bump charts corresponding to each newspaper analogously to figure \ref{fig:all_agenda}.
+\par In this section we leave aside the Public Agenda as an unified corpus and we study the composition and evolution of the Media Agenda of each media outlet. 
+In figure \ref{fig:news_agenda} we show the bump charts corresponding to each of the analyzed newspaper analogously to figure \ref{fig:all_agenda}.
 The topics are the same introduced in the wordclouds of figure \ref{fig:topics_wordclouds}, but when computing the topics' weights,  the articles are discriminated by newspaper. 
 We also show the radar plots showing the average distribution, as made in figure \ref{fig:topics_wordclouds}.
-\par In figure \ref{fig:news_agenda} we can see in a qualitative way the slightly differences between the newspapers' agendas.
-For instance, we can see how newspaper called \emph{P\'agina 12} gave more importance to the topics \emph{Missing person} and \emph{Social leader}, while it reduces to minimum the coverage of the topic  \emph{Former Planning minister} as the others did.
 
-\par In other to detect outliers behavior of a given newspaper respect to the others, we again calculate the Jensen-Shannon distance between the newspapers agenda and the Media Agenda.
+\par In figure \ref{fig:news_agenda} we can qualitative have a glance of the  differences between the newspapers' agendas.
+For instance, we can see how the newspaper called \emph{P\'agina 12} gave more importance to the topics \emph{Missing person} and \emph{Social leader}, while it reduces to minimum the coverage of the topic  \emph{Former Planning minister} as the others did.
+
+\par In other to detect significative bias coverage of a given newspaper, we again calculate the Jensen-Shannon distance, but between the individual newspapers agenda and the Media Agenda.
 Note that this is the distance between the distributions of figure \ref{fig:news_agenda} and the top panel of figure \ref{fig:all_agenda}. 
-\par In figure \ref{fig:jensen_shannon_news} we show the Jensen-Shannon distance as a function of time.
-We detect three points as outliers, although we discard the point \textbf{(b)} due to the low information of \emph{Infobae} in that period. 
+ In figure \ref{fig:jensen_shannon_news} we show the Jensen-Shannon distance as a function of time.
+We detect three points as outliers, although we finally disregarded point \textbf{(b)} due to a lack of  information of newspaper \emph{Infobae} in that period. 
 The other two points corresponds to differences between \emph{P\'agina 12} and the other newspapers and correspond to differences in the coverage of the topic \emph{Missing person}.
 
-\par The point \textbf{(a)} corresponds  to the first news of the Santiago Maldonado's disappearance  reported by \emph{P\'agina 12} before the primary elections, and in point \textbf{(c)} to  the two months rally after the disappearance took place (see section \ref{sec:Context}).
-Another difference in point \textbf{(c)} corresponds to a greater coverage of \emph{P\'agina 12} in the topic \emph{Social leader} where the others media outlets seem to be more interested in the topic \emph{Former Vice-President}.
+\par The point \textbf{(a)} corresponds  to the first news of the Santiago Maldonado's disappearance  reported by \emph{P\'agina 12} before the primary elections and the point \textbf{(c)} corresponds to  the two months' rally after the disappearance  (see section \ref{sec:Context}).
+Another singularity of point \textbf{(c)} corresponds to a greater coverage of \emph{P\'agina 12} in the topic \emph{Social leader} where the others media outlets seem to be more interested in the topic \emph{Former Vice-President}.
 
@@
 
-\par From panel (a) of figure \ref{fig:topics_temporal_profiles}, we can see the larger coverage of \emph{P\'agina 12} respect the other newspapers at the beginning of the period.
+\par From panel (a) of figure \ref{fig:topics_temporal_profiles}, we can see the larger coverage of \emph{P\'agina 12} in comparison to other newspapers at the beginning of the period.
 We can, for instance, quantify this difference calculating  the median of the signals.
@@
 
-\par Finally, in figure \ref{fig:topics_temporal_profiles} we also show word-clouds of topic's keywords but separating those who are more frequently mentioned by each newspaper, and filtering the words that are common to all and basically define the factual details of the topic.
+\par Finally, in the same figure \ref{fig:topics_temporal_profiles} we also show wordclouds of topic's keywords highlighting the more frequently mentioned in each newspaper and filtering the common words to all newspapers.
 Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represi\'on} (repression) when \emph{P\'agina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (Fern\'andez de Kirchner, former president) which is employed by all newspapers except \emph{P\'agina 12} when they  talk about the topic \emph{Former Planning minister} (see section \ref{sec:Context}).
@@
 
-\subsection*{After all: Who sets the Agenda?}
+\subsection*{A brief discussion about  Agenda-Setting}
 \label{sec:who_sets}
 
-\par The behavior of the Media Agenda and the Public one, either by looking at Google Trends or Twitter, shows periods when there is a strong similarity among them (mostly in the presence of an unexpected event) and periods when they seem to be unrelated.
-These are mere observation that talk about the correlation between the agendas.
-However the agenda-setting theory is in its nature a theory about causality: Is the audience a passive actor who follows what the Media says, or there are periods where the Media must paid attention at public's interests?
-Paraphrasing the question, who sets the agenda, the Media or the audience?
-In a world where social media exists and the feedback between a Media and its audience is common currency, nowadays the idea that the Media sets the agenda and the audience blindly follows it (as it's seemed to be suggested in the original work of McCombs) is too naive.
-
-\par In spite of the fact that we think that to establish a causation, i.e.
-the direction towards information flows, is a task that must be made with extreme care, we have something to say in this work about causality.
+\par In a world where social media exists and the feedback between a Media and its audience is common currency, nowadays the idea that the Media sets the agenda and the audience blindly follows it (as it's seemed to be suggested in the original work of McCombs) is too naive.
+Based in the data analyzed above, the behavior of the Media  and Public Agendas, either by looking at Google Trends or Twitter, shows periods of strong similarity  (specially in the presence of unexpected event) and periods of disengagement and therefore is not trivial to establish a causal relationship between agendas, specially when they are represented as evolving in time topic distribution as we did in this work.
+However, it is possible to discuss agenda setting if we focus in a single topic.
 We think that the \emph{Missing person} topic is the most adequate topic to be discussed because:
@@
 After all,  the audience get involved about this topic by the Media, so how was the coverage before those events?
-By calculating the cumulative sum we can see  the cumulative coverage during the first events related to the topic. 
+We can answer these questions by calculating the cumulative coverage of this topic since the first events took place.
 This measure can be seen as the numerical integrate of the temporal profiles of figure \ref{fig:topics_temporal_profiles} between the initial date and the current date. 
@@
 
-\par We took the question about causality only in a qualitative way. 
-There are different metrics that would help in this question, such as Granger causality or correlation by sliding windows.
+\par Even tough we face the question about causality only in a qualitative way and just for a specific topic, it was possible to highlight  the complex feedback dynamics that take place between public and media agendas.
+%There are different metrics that would help in this question, such as Granger causality or correlation by sliding windows.
 We think that this analysis must be performed with extreme care since the acquirement of the data.
@@
 
-\par The study of Mass Media, and in particular the agenda setting theory, can be empowered by the used of data mining or machine learning algorithms. 
-In this work, through the implementation of a topic detection algorithm we could describe the Agenda of the Media as a distribution which evolves over time and which is defined in a topic's space which emerges from the analysis of the corpus.
-This gave us an insight of how we can construct and follow the Public's interests, the Public Agenda, in order to compare with the Media Agenda, i.e. Media interests. 
-\par Given the Agendas, we found that the Public one is usually less diverse than the Media, showing that when there is a very attractive topic, the audience focus on this one, when the Media has to cover the other too.
+\par The  Mass media play a fundamental rol in opinion formation and therefore it's of vital importance to have an accurate  quantitative description of the Media  and Public Agenda and their relationship in the framework of Agenda Setting theory.
+In this work, through the implementation of a topic detection algorithm we describe the Agenda of the Media as a distribution which evolves in time and which is defined in a topic's space which emerges from the analysis of the corpus.
+This gave us an insight of how we can construct and follow the Public's interests, the Public Agenda, in order to compare with the Media Agenda, i.e.
+Media interests.
+
+\par Given the Agendas, we found that the Public one is usually less diverse than the Media, showing that when there is a very attractive topic, the audience focus on this one, meanwhile the Media keeps certain degree of diversity.
 On the other hand, the measurement of distances between Agendas can be employed to rapidly detect periods when the Public may have an independent behavior respect to the Media.
@@
 Most articles in political sections are logically devoted to him under different contexts.
-However, it is important to point out that during the period analyzed, and specially after the general elections of October 22th, a controversial labour reform promoted by the government was been discussing.
+However, it is important to point out that during the analyzed period, and specially after the general elections of October $22^{th}$, a controversial labour reform promoted by the government was been discussing.
 
 \subsubsection*{\emph{Missing Person}}
-\par \emph{Santiago Maldonado} vanished on August 1st after a minor clash between the Gendarmerie (Border Guards) and a group of Mapuches, which recognize as themselves the original population of an area in the Patagonia.
+\par \emph{Santiago Maldonado} vanished on August 1st after a minor clash between the Gendarmerie (Border Guards) and a group of Mapuches (Patagonian native population), which recognize as themselves the original population of an area in the Patagonia.
 Since that event, the \emph{Mauricio Macri}'s administration was accused by several people as the responsible of a \textbf{forced disappearance}. 
-\par A very massive campaign in social media took place on August 26th, under the motto ``Where is Santiago Maldonado?", followed by two massive protest marches to the \emph{Plaza de Mayo} that took place on September 1st and October 1st, which the first one had a great repercussion due to several incidents that took place during the march.
-\par The body of \emph{Santiago Maldonado} was found on 17th October in the \emph{Chubut} river, near the place where he was seen the last time, and the autopsy report told that \emph{Santiago Maldonado} had died from ``asphyxia after being submerged", with no injuries on his body.
+\par A very massive campaign in social media took place on August $26^{th}$, under the motto ``Where is Santiago Maldonado?", followed by two massive protest marches to the \emph{Plaza de Mayo} that took place on September 1st and October 1st, which the first one had a great repercussion due to several incidents that took place during the march.
+\par The body of \emph{Santiago Maldonado} was found on $17^{th}$ October in the \emph{Chubut} river, near the place where he was seen the last time, and the autopsy report told that \emph{Santiago Maldonado} had died from ``asphyxia after being submerged", with no injuries on his body.
 However the responsibility of the current administration is still being discussed.
@@
 \par \emph{Julio de Vido} was the Planning minister during the administration of \emph{N\'estor Kirchner} and \emph{Cristina Fern\'andez de Kirchner} (2003-2015).
-In 2015, he was elected to integrate the Chamber of Deputies, which finally voted to strip \emph{De Vido} of his congressional immunity over corruption allegations and was immediatly jailed on October 27th.
+In 2015, he was elected to integrate the Chamber of Deputies, which finally voted to strip \emph{De Vido} of his congressional immunity over corruption allegations and was immediatly jailed on October $27^{th}$.
 
 \par \emph{Amado Boudou} was the Vice-President of the \emph{Cristina Kirchner}'s administration.
-\emph{Boudou} was arrested on November 3th on charges including money-laundering and hiding undeclared assests.
+\emph{Boudou} was arrested on November 3th on charges including money-laundering and hiding undeclared assets.
 
@@
 \par Naturally the topics found with LDA may not coincide with the NMF ones.
-However, one expects that the corpus under studying should be in some manner robust to the election of the topic model.
+However, one expects that the corpus under study displays some degree of  robustness  when considering different topic model.
 On the other hand, as was discussed in \cite{o2015analysis}, NMF can be a more suitable topic modeling method in certain domains, in the way that it produces more coherent topics, while LDA tends to return higher levels of generality and redundancy.
@@
 \includegraphics[width = \textwidth]{Fig1.pdf}
-\caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic distribution and their corresponding wordclouds.} The Public Agenda is represented either by Google Trends (GT) and Twitter (Tw).
+\caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic (then collapsed to seven) distribution and their corresponding wordclouds.} The Public Agenda is represented either by Google Trends (GT) and Twitter (Tw).
 Topics names are introduced together with the wordclouds containing the most important keywords involved in the definition of each topic.
@@
 \includegraphics[width = \textwidth]{Fig2.pdf}
-\caption{\textbf{Bump graph of the Media Agenda (MA) and Public Agenda extracted from Google Trends (GT) and Twitter (Tw)}.
-The curves width and their ordering are related to the topics relative weight.
-Some important events related to the topics are pointed out:
-\textbf{A}: First news about Santiago Maldonado's disappearance;
+\caption{\textbf{Bump graph of the time-dependent Media (MA) and Public Agendas extracted from Google Trends (GT) and Twitter (Tw)}.
+Widths and rankings of the curves encode topic's relative weight.
+Also, some important events related to the topics are pointed out:
+\textbf{A}: First news about Santiago Maldonado's disappearance (Missing person);
 \textbf{B}: Primary elections;
@@
 \textbf{H}: Debates on labor reform;
-\textbf{I}: Amado Boudou's detention.
+\textbf{I}: Amado Boudou's detention (Former vice-president).
 A more detailed explanation is given in section \ref{sec:Context}.}
@@
 \includegraphics[height=0.7\textheight]{Fig3.pdf}
-\caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda show a less diverse behavior than the Media Agenda as can be seen in the left figure.
-The horizontal lines are the lower inner fences of each signal in order to identify outliers.
-The related radar plots shows that those dates when the agenda has a low diversity, the most important topic catches the most public’s attention.
-\textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
+\caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda show a less diverse behavior than the Media Agenda as can be seen in the top figure.
+The horizontal lines correspond to the lower inner fences of each signal in order to identify outliers.
+The related radar plots show  the agenda at the selected days where the time series exhibit dropouts (points a-d), indicating that the most important topic catches the most public's attention.
+\textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.
+}
 \label{fig:shannon_entropy_agendas}
@@
 \includegraphics[height = 0.7\textheight]{Fig4.pdf}
-\caption{\textbf{Jensen Shannon distance between the Media Agenda and the Public Agenda as a function of time} (with upper inner fences pointed out).
-The larger distances are due to a greater interest of the audience in the topic \emph{Missing person} which leads to lesser interest in the other topics, which the Media has to cover, maybe except in points (a) and (b) where the Media seems not to anticipate the public interest in the mentioned topic.
+\caption{\textbf{Jensen Shannon distance between the Media and Public Agendas as a function of time} (with upper inner fences pointed out).
+Larger distances are due to a greater interest of the audience in the topic \emph{Missing person} which  decrease the interest in other topics.
+On the other side the Media Agenda still keeps certain degree of diversity.
 \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}

### 2018-08-29 bmc_article.tex
Algunas correcciones

@@
 On the other hand, \emph{Infobae} has the most visited website, much more than \emph{Clar\'in} and \emph{La Naci\'on} \cite{AlexaAR}.
-The corpus analyzed comprise by 2908 politics articles of \emph{Clar\'in}, 3565 of \emph{La Naci\'on}, 3324 of \emph{P\'agina 12}, and 2018 of \emph{Infobae}.
+The corpus analyzed is made up by 2908 politics articles of \emph{Clar\'in}, 3565 of \emph{La Naci\'on}, 3324 of \emph{P\'agina 12}, and 2018 of \emph{Infobae}.
 Except \emph{P\'agina 12}, all articles were taken from the section \emph{Pol\'itica}  (Politics) of the respective news portal, while the articles which belong to \emph{P\'agina 12} were taken from the section \emph{El pa\'is} (The country).
 
-\par We describe them as numerical vectors through the \textit{term frequency - inverse document frequency (tf-idf)} representation \cite{xu2003document}.
+\par The articles are described as numerical vectors through the \textit{term frequency - inverse document frequency (tf-idf)} representation \cite{xu2003document}. 
 Given the set of terms contained in the corpus' words after removing non-informative ones, such as prepositions and conjunctions, the \textit{tf-idf} algorithm represents the \textit{i}-document as a vector $v_i = [x_{i1}, x_{i2}, ...
-, x_{it}]$, where the component $x_{ij}$ is computed by the equation \ref{ec:tfidf}, where $\textrm{tf}_{ij}$ is the number of times the \textit{j}-term appears in the \textit{i}-document, $d$ is the number of documents in the corpus, and $n_j$ is the number of documents where the \textit{j}-term appears.
-Each document's vector is normalized to unit Euclidean length.
+, x_{it}]$, where the component $x_{ij}$ is computed by the eq.(ref{ec:tfidf}), where $\textrm{tf}_{ij}$ is the number of times the \textit{j}-term appears in the \textit{i}-document, $d$ is the number of documents in the corpus, and $n_j$ is the number of documents where the \textit{j}-term appears.
+Each document's vectors is normalized to unit Euclidean length.
 Once the documents' vector are constructed, we put them together in a document-term matrix (\emph{M}), which has dimensions of number of documents in the corpus ($d$) per number of terms selected ($t$).
@@
 A topic is a group of similar articles which roughly talks about the same subject.
-\emph{NMF} is an algorithm which factorize the matrix \emph{M} into two matrices \emph{W} and \emph{H} (eq.\ref{eq:nmf}), with the property that all three matrices have no negative elements.
-This non-negativity makes the resulting matrices easier to inspect, and very suitable for topic detection \footnote{ Even though there are other techniques in topic detection, as for instance LDA (Latent Dirichlet Allocation), the NMF decomposition suites perfect for the kind of corpus we  have analyzed in this work (A detailed comparison of both, NMF and LDA methods could be found in Supplementary Material)}.
+\emph{NMF} is an algorithm which factorize the matrix \emph{M} into two matrices \emph{W} and \emph{H} (eq.(\ref{eq:nmf})), with the property that all three matrices have no negative elements.
+This non-negativity makes the resulting matrices easier to inspect, and very suitable for topic detection \footnote{ Even though there are other techniques in topic detection, as for instance LDA (Latent Dirichlet Allocation), the NMF decomposition suites perfect for the kind of corpus we  have analyzed in this work (A detailed comparison of both, NMF and LDA methods could be found in Supplementary Material).}.
 \begin{equation}
@@
 Such as the resulting matrix \emph{H} has dimensions of number of documents per $k$ and matrix \emph{W} has dimensions of $k$ per number of terms, the number $k$ is therefore interpreted as the number of topics in the documents and it is a parameter that must be set before the factorization.
+In this work, we arbitrarily set $k=10$. We found this value to be a suitable one based on our knowledge of the corpus.
 \par The matrix \emph{H} is the representation of the documents in the topic-space.
@@
 the distance between matrix \emph{M} and its approximated form $\tilde{M} = H \cdot W$.
-This was performed \emph{NMF} through the python module \emph{scikit-learn} \cite{scikit-learn}.
+The \emph{NMF} factorization through the python module \emph{scikit-learn} \cite{scikit-learn}.
 
-\par Then a time-dependent Media Agenda is represented as a time evolving distribution of topics.
+\par After performing NMF, we represent a time-dependent Media Agenda as a time evolving distribution of topics.
 The daily weight of the topic $i$, $W_i(day)$, is calculated following  eq.(\ref{eq:topic_weight}), where $l(j)$ is the number of words of the document $j$, $h_{ji}$ is the degree of membership of document $j$ on topic $i$, $d_j$ is the date of document $j$, and $\delta$ is the Kronecker delta.
@@
 \par The other side of time-dependent Media Agenda is to have some measure of the public interest about these topics.
-With this goal, we use  \emph{Google Trends} and \emph{Twitter} as proxy of public interest by  looking for the same topics  in the same period of time.
+With this goal, we use  \emph{Google Trends} and \emph{Twitter} as a proxy of public interest by  looking for the same topics  in the same period of time.
 We take advantage of topics' keywords to make queries in the \emph{Google Trends}  tool and  into the advance search tool of Twitter  to get the relative weight searches and tweets in both platforms.
@@
 
-\par One of the key of our work is the representation of the Agendas as time evolving topic distributions, and the association between the different measures that we can derive from them with the social events observed during the period.
+\par In fact, one of the key of our work is the representation of the Agendas as time evolving topic distributions, and the association between the different measures that we can derive from them with the social events observed during the period.
 In order to do that, the first measure we emphasize is the concept of \emph{diversity of the attention}.
-Following \cite{boydstun2014importance} the \emph{diversity} is a very important variable that must be taken into account when dealing with multiple issues, due to the fact that it tells us how the attention is distributed across the different topics of discussion.
-In that work, their also propose the use of the normalized Shannon's entropy as a way to quantify the diversity, which can be easily calculated and therefore is a very suitable quantity within our framework.
+The \emph{diversity} is a very important variable that must be taken into account when dealing with multiple issues \cite{boydstun2014importance}, due to the fact that it tells us how the attention is distributed across the different topics of discussion.
+As was proposed in \cite{boydstun2014importance}, we take the normalized Shannon's entropy as a very suitable way to quantify the diversity within our framework.
 \par The normalized Shannon's entropy $H[p]$ referred in eq.(\ref{eq:shannon_entropy}) give us a measure of how spread is a -discrete- distribution, taking the maximum value of $1$ when all outcomes are equally probable, and $0$ when there is just one possible outcome.
@@
 
-\par While the diversity is a property of each distribution, a natural question that arise when comparing different distributions is how similar they are.
-We will be for instance particularly interested in measuring the similarity between the Media and Public Agendas, because those dates when the similarity is low tell us about distant interests of the Media and the Public.
+\par While the diversity is a property of each distribution, a natural question that arise from comparing different distributions is how similar they are.
+For instance, we will be particularly interested in measuring the similarity between the Media and Public Agendas, because those dates when the similarity is low tell us about distant interests of the Media and the Public.
 We proposed here to measure the similarity between distributions by the use of the Jensen-Shannon distance ($JSD$). 
 When the similarity of the distributions is low, the distance between them is high.
-\par The Jensen-Shannon distance ($JSD$) is a metric between distributions based on the Jensen-Shannon divergence ($JS_{Div}$) \cite{fuglede2004jensen}, which is in turn a symmetric version of the well-known Kullback-Leibler divergence ($D_{KL}$).
+\par The Jensen-Shannon distance ($JSD$) is a metric between distributions based on the Jensen-Shannon divergence ($JS_{Div}$) \cite{fuglede2004jensen}, which is in turn a symmetric version of the well-known Kullback-Leibler divergence ($D_{KL}$, eq.(\ref{eq:kl})).
 We recall that the $JSD$ has the advantage of being symmetric and also a well-defined distance, which make it conceptually easy to deal.
@@
 
-\begin{eqnarray}\label{eq:jensen_shannon_distance}
-D_{KL}(P||Q) &= -\sum{P(i) log(\frac{Q(i)}{P(i)})} \nonumber \\
-JSD(P,Q) &= \sqrt{JS_{Div}(P,Q)} = \sqrt{\frac{1}{2}[D_{KL}(P||M) + D_{KL}(Q||M)] } 
-\end{eqnarray}
+\begin{equation}
+D_{KL}(P||Q) = -\sum{P(i) log(\frac{Q(i)}{P(i)})}
+\label{eq:kl}
+\end{equation}
+
+\begin{equation}
+\label{eq:jensen_shannon_distance}
+JSD(P,Q) = \sqrt{JS_{Div}(P,Q)} = \sqrt{\frac{1}{2}[D_{KL}(P||M) + D_{KL}(Q||M)]} 
+\label{eq:jensen_shannon_distance}
+\end{equation}
 
@@
 
-\par As was mentioned above, once defined the concepts of diversity and distance between distributions, we will be particularly interested in those dates when these concepts take extreme values: When the diversity is low, we know that a topic is absorbing much of the attention of any of the Agendas; on the other hand, when the distance between two distributions is high, we can conclude that they have distant interests.
+\par As was mentioned above, once the concepts of diversity and distance between distributions were defined, we are particularly interested in those dates when these concepts take extreme values: When the diversity is low, we know that a topic is absorbing much of the attention of any of the Agendas; on the other hand, when the distance between two distributions is high, we can conclude that they have distant interests.
 However, we still lack the definition of what a low diversity or a high distance are. 
@@
 \par The box-plot construction is as follows: First a quartile division of the $N$ observations is made, by naming $Q1$ as the lower quartile, $Q2$ the median of the distribution, and $Q3$ the upper quartile.
-Recall that $Q1$ ($Q3$) are defined to be the division where the 25th (75th) percent of the observations lies below (by definition, the median $Q2$ separates the distribution in two equal parts).
+Recall that $Q1$ ($Q3$) is defined to be the division where the 25th (75th) percent of the observations lies below (by definition, the median $Q2$ separates the distribution in two equal parts).
 On the other hand, the inter-quartile range $IQ$ is defined as $IQ = Q3 - Q1$.
@@
 \par We are not interesting in the visualization of the box-plot in its own but instead in its procedure to identify outliers.
-Therefore from the quartiles, new quantities called \emph{fences} are defined in eq.(\ref{eq:fences}).
-In this equation, $LIF$ stands for \emph{lower inner fence}, $UIF$ for \emph{upper inner fence}, $LOF$ for \emph{lower outer fence} and $UOF$ for \emph{upper outer fence}.
+Therefore from the identification of the quartiles, new quantities called \emph{fences} are defined in eq.(\ref{eq:fences}): The \emph{lower inner fence} ($LIF$), the \emph{upper inner fence} ($UIF$), the \emph{lower outer fence} ($LOF$), and the \emph{upper outer fence} ($UOF$).
 The fences can be interpreted as the limits of the distribution.
@@
 \par We initially focus in the ten most important issues in the three months period corpus of news reported above.
-These ten topics, represented in the word clouds  of Fig.\label{fig:topics_wordclouds}, were reduced to seven (shown in the radar plot of the same figure) given the similarities found in, for instance, three of them that could be interpreted as part of the same macro-topic called \emph{Elections} and two others which were classified as part of a macro-topic called \emph{Missing person}.
-The meaning of the topics or macro-topics is contextualized in section \ref{sec:Context} of Supplementary Material.
-\par Following the procedure described in the previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)} (Google and Twitter), and all their derivations, as time-dependent distributions.
+These ten topics, represented in the word clouds of figure \ref{fig:topics_wordclouds}, were reduced to seven (shown in the radar plot of the same figure) given the similarities found in, for instance, three of them that could be interpreted as part of the same macro-topic called \emph{Elections} and two others which were classified as part of a macro-topic called \emph{Missing person}.
+The meaning of the topics or macro-topics is contextualized in the \textbf{Supplementary Material}.
+%\ref{sec:Context} of Supplementary Material. 
+\par Following the procedure described in the previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, in both its Google and Twitter derivations, as time evolving topic distributions.
 
@@
 The queries employed are also specified in table \ref{table:gt_queries}.
-In table \ref{table:gt_all_correlation} we show the linear correlation between the topics' temporal profiles from the Public Agenda and their counterparts in the Media Agenda.
+On the other hand, in table \ref{table:gt_all_correlation} we show the linear correlation between the topics' temporal profiles from the Public Agenda and their counterparts in the Media Agenda.
 
-\par We can observe that both Public Agendas ($GT$ and $Tw$) look similar in this representation, but they show specific differences with the Media Agenda, where a greater interest of the audience in the topic \emph{Missing person} than the Media is observed, or inversely, a lower interest in the topic \emph{Prosecutor's death} takes place.
+\par We can observe that both Public Agendas ($GT$ and $Tw$) look similar in this representation, but they show specific differences with the Media Agenda.
+For instance, a greater interest of the audience in the topic \emph{Missing person} than the Media is observed, or inversely, a lower interest in the topic \emph{Prosecutor's death} takes place.
 However, this static representation is not able to show the complex dynamics of agenda's evolution and the importance of punctual and specific facts which can erase or amplify their differences.
@@
 \par This can be observed in figure \ref{fig:all_agenda} where the time evolution of the topics is shown in a bump chart of the Agendas.
-The bump chart provides  a clear visualization of the relative weight of the topics at the same time that their ranking.
-In  this figure  we also highlight some important events related to the dynamics of the topics and  it is  possible to appreciate how the main topic change in time and have a glance of the qualitative differences between agendas.
-In particular, it can be observed some differences between Public Agendas ($GT$ and $Tw$) that were not observed in the previous figure, as for instance, the persistency of main topics is longer in Twitter than in Google Trends.
+The bump chart provides  a clear visualization of the relative weight of the topics at the same time with their ranking.
+In  this figure  we also highlight some important events related to the dynamics of the topics.
+It is possible to appreciate how the main topic change in time and have a glance of the qualitative differences between agendas.
+In particular, it can be observed some differences between Public Agendas ($GT$ and $Tw$) that were not observed in the previous figure, as for instance, the persistence of main topics is longer in Twitter than in Google Trends.
 This is more evident at the end of the analyzed period, where topics discussed in Google Trends shows more  responsive to change in Media Agenda than in Twitter, suggesting the existence that the interaction between people is stronger in the analyzed social network.
 
-\par We also calculate linear correlations between same topics of $PA$ and $MA$  and we found that they are  positive and statistically significant in all the cases, as shown in table \ref{table:gt_all_correlation}.
+\par The linear correlations between same topics of $PA$ and $MA$ were also calculated.
+In all cases, we found that they are positive and statistically significant, as can be shown in table \ref{table:gt_all_correlation}.
 This can be interpreted as a validation of the topics found in the corpus and the keywords that describe it.
 Even though it is expected that the Media's and public's interest should generally follow a similar a pattern, mainly driven by  external events, we are interested in those periods where they significantly differ.
-A non positive (or a non significant) correlation may imply, besides the obvious conclusion of agenda's disengagement, that we could eventually fail in properly detect the keywords or features that describe a particular topic, so the Google Trends' or Twitter's pattern would not be able to reflect a similar behavior that its counterpart in the Media.
+However, a non positive (or a non significant) correlation may imply, besides the obvious conclusion of agenda's disengagement, that we could eventually fail in properly detect the keywords or features that describe a particular topic, so the Google Trends' or Twitter's pattern would not be able to reflect a similar behavior that its counterpart in the Media.
 
@@
 Is the degree of dominance of a given topic in the Media Agenda reflected in the Public Agenda?
-In order to answer such kind of questions it is necessary  to quantify the diversity of the Agendas, which are represented as  distributions in the topic's space as was shown above.
-Following \cite{boydstun2014importance}, we calculate the normalized Shannon's entropy ($H$, see eq.\ref{eq:shannon_entropy}) in order to measure the diversity of the \textbf{MA} and \textbf{PA}.
+In order to answer such kind of questions we quantify the diversity of the Agendas through the normalized Shannon's entropy $H$, which was introduced in section \textbf{Material and Methods}.
 \par In figure \ref{fig:shannon_entropy_agendas} we can see the value of $H$ as a function of time for the three agendas.
@@
 This effect is notoriously more pronounced in the Public Agenda giving by \textbf{GT} and, in particular, in four specific days  where  four local minima of Shannon's entropies can be detected.
-Three of them are outliers as defined in section \ref{sec:MatMeth}, two of them from \textbf{GT} and one from \textbf{Tw}.
+Three of them are outliers as defined in section \textbf{Material and Methods} \ref{sec:MatMeth}, two of them from \textbf{GT} and one from \textbf{Tw}.
 The other one is not an outlier but a pronounced minima and therefore a point of interest in this description.
 
-\par A lower value in the agenda's diversity is due to the fact that the most important topic attracts practically all the attention of the public and the media, collapsing the diversity of the agenda.
+\par A lower value in the agenda's diversity is due to the fact that the most important topic attracts practically all the attention of the Public and the Media, collapsing the agenda to one of the issues involved.
 In the radar plots included in figure \ref{fig:shannon_entropy_agendas} we can see how two of these outliers (\textbf{a} and \textbf{d}) belong to the topic \emph{Elections}.
@@
 On the other hand, and despite not being classified as outlier, we also focus in point (b) because Shannon's Entropy of $GT$ Agenda displays a minimum (collapsing agenda) which is not corresponded neither in the Media nor in the Twitter Agendas.
-Crawling in the context, we see that it belong to the topic \emph{Missing person} and this date correspond to the rally that took place one month after the disappearance of \emph{Santiago Maldonado} (see section \ref{sec:Context}).
+Crawling in the context, we see that it belongs to the topic \emph{Missing person} and this date correspond to the rally that took place one month after the disappearance of \emph{Santiago Maldonado} (see \textbf{Supplementary Material}).
 We  would like to emphasize the discussion about this topic (\emph{Missing person}) because its dynamics show interesting features, as we will show bellow.
@@
 It can be associates  with a social networks (like Facebook and Twitter) campaign  in favor  of the appearance of \emph{Santiago Maldonado} (``The missing person") that took place on  August 26th.
-This campaign was massive and  initially underestimated by the main Media outlets in Argentina (see section \ref{sec:Context}).
+This campaign was massive and  initially underestimated by the main Media outlets in Argentina (see \textbf{Supplementary Material}).
 
@@
 The topics are the same introduced in the wordclouds of figure \ref{fig:topics_wordclouds}, but when computing the topics' weights,  the articles are discriminated by newspaper. 
-We also show the radar plots showing the average distribution, as made in figure \ref{fig:topics_wordclouds}.
+We also show the radar plots with the average distribution, as made in figure \ref{fig:topics_wordclouds}.
 
@@
 
-\par The point \textbf{(a)} corresponds  to the first news of the Santiago Maldonado's disappearance  reported by \emph{P\'agina 12} before the primary elections and the point \textbf{(c)} corresponds to  the two months' rally after the disappearance  (see section \ref{sec:Context}).
+\par The point \textbf{(a)} corresponds  to the first news of the Santiago Maldonado's disappearance  reported by \emph{P\'agina 12} before the primary elections and the point \textbf{(c)} corresponds to  the two months' rally after the disappearance  (see \textbf{Supplementary Material}).
 Another singularity of point \textbf{(c)} corresponds to a greater coverage of \emph{P\'agina 12} in the topic \emph{Social leader} where the others media outlets seem to be more interested in the topic \emph{Former Vice-President}.
@@
 
-\par Finally, in the same figure \ref{fig:topics_temporal_profiles} we also show wordclouds of topic's keywords highlighting the more frequently mentioned in each newspaper and filtering the common words to all newspapers.
-Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represi\'on} (repression) when \emph{P\'agina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (Fern\'andez de Kirchner, former president) which is employed by all newspapers except \emph{P\'agina 12} when they  talk about the topic \emph{Former Planning minister} (see section \ref{sec:Context}).
+\par Finally, in figure \ref{fig:topics_temporal_profiles} we also show wordclouds of topic's keywords highlighting the more frequently mentioned in each newspaper and filtering the common words to all newspapers.
+Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represi\'on} (repression) when \emph{P\'agina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (Fern\'andez de Kirchner, former president) which is employed by all newspapers except \emph{P\'agina 12} when they  talk about the topic \emph{Former Planning minister} (see \textbf{Supplementary Material}).
 We think that a more deeply study of topics' keywords could be a first approximation in the study of framing, which will constitute the core of futures works.
@@
 \par In a world where social media exists and the feedback between a Media and its audience is common currency, nowadays the idea that the Media sets the agenda and the audience blindly follows it (as it's seemed to be suggested in the original work of McCombs) is too naive.
-Based in the data analyzed above, the behavior of the Media  and Public Agendas, either by looking at Google Trends or Twitter, shows periods of strong similarity  (specially in the presence of unexpected event) and periods of disengagement and therefore is not trivial to establish a causal relationship between agendas, specially when they are represented as evolving in time topic distribution as we did in this work.
+Based in the data analyzed above, the behavior of the Media  and Public Agendas, either by looking at Google Trends or Twitter, shows periods of strong similarity  (specially in the presence of an unexpected event) and periods of disengagement.
+Therefore, it is not trivial to establish a causal relationship between agendas, specially when they are represented as evolving in time topic distribution as we did in this work.
 However, it is possible to discuss agenda setting if we focus in a single topic.
@@
 \item It caused a great impact in either the Media and the audience
-\item  its coverage fully deploys along the time lapse analyzed in this manuscript (see section \ref{sec:Context}).
+\item  its coverage fully deploys along the time lapse analyzed in this manuscript (see \textbf{Supplementary Material}).
 \end{itemize}
@@
 This interpretation try to catch in a qualitative way how the information flow was in this specific topic.
-On the other hand, behind this interpretation there are two important facts that must be mentioned: First, the disappearance of a person is a very sensible theme for the Argentinian society, and second, there are political reasons in why \emph{P\'agina 12} was particularly interested in cover this topic while the other Media did not follow this interest (see section \ref{sec:Context}).
+On the other hand, behind this interpretation there are two important facts that must be mentioned: First, the disappearance of a person is a very sensible theme for the Argentinian society, and second, there are political reasons in why \emph{P\'agina 12} was particularly interested in cover this topic while the other Media did not follow this interest (see \textbf{Supplementary Material}).
 
@@
 
-\par The  Mass media play a fundamental rol in opinion formation and therefore it's of vital importance to have an accurate  quantitative description of the Media  and Public Agenda and their relationship in the framework of Agenda Setting theory.
+\par The  Mass media play a fundamental role in opinion formation and therefore it's of vital importance to have an accurate  quantitative description of the Media  and Public Agenda and their relationship in the framework of Agenda Setting theory.
 In this work, through the implementation of a topic detection algorithm we describe the Agenda of the Media as a distribution which evolves in time and which is defined in a topic's space which emerges from the analysis of the corpus.
@@
 \par We provide here a more detailed explanation of the topics discussed among this work.
-The ideology of the media in Argentina expresses the highly polarized politic climate observe in Argentinian society.
+The ideology of the media in Argentina expresses the highly polarized political climate observe in Argentinian society.
 During the administration of \emph{Cristina Fern\'andez de Kirchner} (2007-2015), the government maintained a conflict with several news organizations.
 It led media such as \emph{Clar\'in}, \emph{La Naci\'on} and the portal news \emph{Infobae} to be very critics of the \emph{Fern\'andez}'s administration, emphasizing the allegations of corruption related to it as can be seen in the importance given to the topics \emph{Former Planning minister} and \emph{Former Vice-President}.
-On the other hand, \emph{P\'agina 12} has a opposite ideological inclination, supporting the former administration of \emph{Cristina Kirchner} and therefore being very critical with the current \emph{Maurico Macri}'s administration, doing special emphasis on issues related to human rights, as can be again observed in the coverage given to the topics \emph{Social leader} and \emph{Missing person}.
+On the other hand, \emph{P\'agina 12} has a opposite ideological inclination, supporting the former administration of \emph{Cristina Kirchner} and therefore being very critical with the current \emph{Mauricio Macri}'s administration, doing special emphasis on issues related to human rights, as can be again observed in the coverage given to the topics \emph{Social leader} and \emph{Missing person}.
 

### 2018-08-30 bmc_article.tex
Nueva intro propuesta

@@
 In this scenario, becomes essential to understand the role of Mass Media Influence in a given social group.
-\par  This question has been raised years ago.
+
+% Agenda Setting Theory
+\par Naturally, how the Media affects public opinion was first explored in the area of social sciences. 
 In the famous study performed in Chapel Hill during the US presidential elections in 1968 \cite{mccombs1972agenda}, Maxwell McCombs and Donald Shaw found that those aspects of public affairs that are prominent in the news become prominent among the public.
-This study is considered the founding of the agenda-setting theory, which focus in the influence of mass media in public opinion.  
-From \cite{mccombs2014agenda}, \textit{``The media agenda is the pattern of news coverage over a period of days, weeks (...) for a set of issues or other topic.
-In other words, the media agenda is a systematic compilation of the issues or topics presented to the public that identifies the degree of emphasis on these topics''}.
-\par In its first-level stage, the theory focus on the comparison between the topics coverage by the media and the public agenda, i.e. the topics that the public consider as priority.
-It looks for answering the question if the media is able to set the public agenda, which would transform the media as an important actor in the formation of public opinion. 
-This stage is sometimes called the ``first level agenda-setting''.
-The very often quoted phrase of Bernard C.
-Cohen \textit{``The press may not be successful much of the time in telling people what to think, but it is stunningly successful in telling its readers what to think about.''} illustrates its object of study.
-With the emergency of the Internet, the end of agenda-setting were predicted due to the audience fragmentation onto multiple sources, which would virtually lead to a highly individualized agenda.
-However, it is based on two assumptions that are not necessarily true: the public spreads its attention in an homogeneous way across the multiple sources, and that the agendas of that sources are different \cite{mccombs2005look}.
+This study is considered the founding of the agenda-setting theory.
+In its basic stage, known as first-level agenda-setting \cite{mccombs2005look}, the theory focuses on the comparison between the topics coverage by the media and the public agenda, i.e.
+the topics that the public consider as priority \cite{brians1996campaign, gerber2009does, coleman2007young}.
+For instance, in Argentina, \cite{mitchelstein2016brecha} examines the difference between public and journalists preferences and several works by E.
+Zunino like \cite{zunino2010cobertura, koziner2013cobertura}, studied the coverage given by the main newspapers of particular events which have happened during the former administration of Argentinian president \emph{Cristina Fern\'andez de Kirchner} (from 2007 to 2015), where the government started to confront with news organizations that were critical to its management \cite{mitchelstein2017information}.
 
-\par From the Chapel Hill research, several directions of agenda-setting were established \cite{mccombs2005look}.
-The ``second level agenda-setting'', sometimes called \textit{attribute agenda-setting}, studies the \textit{objects} (in a social psychology sense, where an \textit{attitude object} designate a thing that an individual has an attitude or opinion about) present in the media agenda.
-When the media talks about an object some attributes are emphasized, and others not.
-This theory is linked with \textit{framing} \cite{guggenheim2015dynamics, tsur2015frame}. 
-To frame is to \textit{select some aspects of a perceived reality and make them more salient in a communicating text, in such a way as to promote a particular problem definition, causal interpretation, moral evaluation and/or treatment recommendation} (Robert Entman) \cite{mccombs2005look}.
-This stage of agenda-setting theory can be summary in the phrase \textit{``the media not only can be successful in telling us what to think about, they also can be successful in telling us how to think about it.''}
-Other interesting stage of agenda-setting concerns with the sources of media agenda, i.e.
-if the media set the public agenda, \textit{who sets the agenda media?} Within this framework, \textit{intermedia agenda-setting} observes the competition between different media and how they influence each other.
-The competition between mass media for the same audience can lead to a homogenization of the agendas \cite{vargo2017networks}, which is in the opposite direction of one of the assumptions that predict the end of agenda-setting, as was mentioned before.
+\par The Chapel Hill investigation also induced other several research directions \cite{mccombs2005look}.
+One of them focused on detecting bias in the media, either by taking into account the number of mentions related  to a preferred political party \cite{lazaridou2016identifying, baumgartner2015all} or by identifying the ideology through the position of the media regards to certain issues or actors \cite{elejalde2018nature, sagarzazu2017hugo}.
+This research line can be linked with the theory of \textit{framing} \cite{guggenheim2015dynamics, tsur2015frame}, which is concerned with how the media emphasizes some attributes of an object, while understating others.
+Other investigations pay attention to the sources of the Media Agenda, theory known as \textit{intermedia agenda-setting} \cite{vargo2017networks, harder2017intermedia, guo2017global}, in which the competition between different media, and the influence exerted between each other, is observed.
 
-\par Since the irruption of internet in our lives and the access to big data, there were many attempts to analyze from a quantitative point of view the theory of Agenda Setting based on  the original work of McCombs \cite{mccombs1972agenda}.
-Many of them follows what we called a ``static approach", i.e.
-by summarizing certain issues present in news media and looking for effects in the audience \cite{brians1996campaign, gerber2009does, coleman2007young}.
-For instance, in Argentina, \cite{mitchelstein2016brecha} examines the difference between public and journalists preferences. 
-Several works by E.
-Zunino, like \cite{zunino2010cobertura} and \cite{koziner2013cobertura}, studied the coverage given by the main newspapers of particular events which have happened during the former administration of Argentinian president \emph{Cristina Fern\'andez de Kirchner} (from 2007 to 2015), where the government started to confront with news organizations that were critical to its management as they were an opposition party \cite{mitchelstein2017information}.
-\par Other line of research have been focused on detecting bias in the media, either by taking into account the number of mentions related  to a preferred political party \cite{lazaridou2016identifying, baumgartner2015all} or by identifying the ideology through the position of the media regards to certain issues or actors \cite{elejalde2018nature, sagarzazu2017hugo}.
-New trends in agenda-setting theory propose to represent ideological aspects or issues emphasized as networks like mind maps, and the basic idea is the comparison between media's knowledge representative network with its counterpart in the audience \cite{guo2012application, vu2014exploring}.
-\par Most of the works cited above follow typical methods of social science research.
-However, a useful tool in the analysis of large corpus of documents, which is not widely used in the agenda setting theory, is unsupervised topic modeling.
-These methods are an alternative to the dictionary-based analysis, which is the most popular automated analysis approach \cite{guo2016big}, and allows to work with a corpus without a prior knowledge, letting the topics emerge from the data.
-Despite the popularity of these methods in other fields, they have been under-employed in the agenda setting framework.
-Many works based on news corpus emphasize the performance of the topic model over a labeled corpus, focusing on the proper detection of the topics \cite{dai2010online, po2016topic, brun2000experiment}.
-The temporal profile of topics is usually embedded in the context of topic tracking \cite{hu2016news, li2017joint}, or in the recognition of emerging topics in real-time \cite{cataldi2010emerging} mostly applied to social media.
-\par A typical dynamical analysis of Agenda Setting is focused on a single issue.
-For instance, in \cite{soroka2017negativity} it is shown that the newspapers and Twitter have an opposite reaction to the changes of the unemployment rates.
-In \cite{guggenheim2015dynamics} the competition of frames about gun control is explored, and in \cite{ali2018measuring} the authors show how fluctuations of  twitter activity in different regions depend on the location of terrorist attacks.
-A remarkable exception is found in  \cite{russell2014dynamics}, where they work with a set of predefined issues.
-In this work the question of \emph{causality} is also faced up.
-Their study shows that sometimes the traditional media set the agenda and sometimes the social media does.
-They show that social media is always more interested in social issues than the traditional one, and despite the existence of correlation, the social media agenda can not be seen as a \emph{slave} of the traditional media.
-However, a drawback of working with predefined issues is that they usually reflects general themes, such as unemployment or crime, and the issues selection must be made by the researcher. 
-\par In this work we propose a novel method in order to study the dynamics of Mass Media Agenda as a set of topic evolving in time and their correspondence with the Public and Social Network Agendas.
+%New trends in agenda-setting theory propose to represent ideological aspects or issues emphasized as networks like mind maps, and the basic idea is the comparison between media's knowledge representative network with its counterpart in the audience \cite{guo2012application, vu2014exploring}.
+
+\par Nonetheless, most of the works cited above follow typical methods of social science research, and fall in what we call a ``static approach": They used to summarize certain issues present in news media and looking for effects in the audience.
+With the irruption of internet in our lives and the access to big data, a richer analysis is allowed, which may take into account the temporal dependence of the Media and Public attention. 
+For instance, in \cite{soroka2017negativity} it is shown that the newspapers and Twitter have an opposite reaction to the changes of the unemployment rates; in \cite{guggenheim2015dynamics}, the competition of frames about gun control is explored; in \cite{ali2018measuring}, the authors show how fluctuations of Twitter activity in different regions depend on the location of terrorist attacks; and in \cite{russell2014dynamics}, the complex interplay between the social media and the traditional one is followed over time on a set of predefined, but general, issues.
+However, one drawback of several works which perform a dynamical analysis of agenda-setting is that the research is usually made on a single issue or on a set of predefined issues.
+Frequently, the last are arbitrarily selected by the own researcher, and normally reflect general themes, such as ``health" or ``gun control".
+
+% Machine Learning
+\par The question about what issues should be selected can be solved by an useful tool employed in the analysis of large corpus of documents, but understated in the agenda-setting framework and its derivatives: Unsupervised topic modeling.
+It is an alternative to the dictionary-based analysis, which is the most popular automated analysis approach \cite{guo2016big}, and allows to work with a corpus without a prior knowledge, letting the topics emerge from the data.
+Although many works employ unsupervised topic modeling on news corpus, much of them emphasize the performance of the topic model over a labeled corpus, focusing on the proper detection of the topics \cite{dai2010online, po2016topic, brun2000experiment}.
+In general, issues about the temporal profile of topics are embedded in the context of topic tracking \cite{hu2016news, li2017joint}, or in the recognition of emerging topics in real-time \cite{cataldi2010emerging}, mostly applied to social media.
+
+\par In this work we propose a novel method in order to study the dynamics of Mass Media Agenda, which consist in performing an unsupervised topic model on newspapers articles, and studying how the emerging topics evolve in time.
+We look also at their correspondence with the Public and Social Network Agendas.Rather than focus on a single issue or a set of independent topics, we work with the agendas (the Media and the Public) as an object in their own.
 Our work intends to contribute another quantitative approach which complements the agenda-setting theory describe above.
 It mainly stands within the framework of first-level agenda setting, but issues about the comparison between media agendas and framing are also discussed.
-Rather than focus on a single issue or a set of independent topics, we work with the agendas (the media and the public) as an object in their own, studying their evolution over time. 
-On the other hand, we aim to take an insight about Media dynamics and Public response in order to create useful tools at the time of constructing mathematical models about the interaction between Media and Public, investigation that we started in \cite{pinto2016setting}.
+\par On the other hand, in recent years new approaches to study social dynamics through several tools taken from statistical physics have proposed mathematical models to explore the interplay between Mass Media and society \cite{crokidakis2012effects,gonzalez2012model, moussaid2013opinion, rodriguez2010effects, pinto2016setting}.
+Much of them lack in being contrasted with real data.
+With our work we aim to gain a closer insight on the complex interaction between Media and Public, and provide a quantitative research that would be useful at the time of constructing better and more data-driven models.
 

### 2018-08-30 bmc_article.tex
Algunas correciones

@@
 \caption{Queries used in Google Trends in order to build the Public Agenda.}
-\begin{tabular}{ll}
+\begin{tabular}{l|p{7.5cm}}
 Topic's name & Google Trends query \\ \hline
@@
 \caption{Correlation between the temporal profiles of the topics found in NMF and associated topics in LDA.}
-\begin{tabular}{llc}
+\begin{tabular}{lc}
 Topic's name & Correlation between NMF and LDA \\ \hline

### 2018-08-31 bmc_article_final.tex
Algunas correcciones, faltan algunos detalles

--- 2018-08-30 bmc_article.tex
@@
 
-\title{Agenda diversity and coverage bias: A quantitative approach to the agenda-setting theory}
+%\title{Agenda diversity and coverage bias: A quantitative approach to the agenda-setting theory}
+%\title{Agenda setting by comparison of time-evolving topic distribution}
+\title{A quantitative analysis of Media Agenda and Public Opinion using time-evolving topic distribution}
 
@@
 But which is the dynamics of the agenda and how the people become interested in their different topics?
-The Agenda Setting theory provides a conceptual framework in order to understand the role played by the mass media in public opinion formation, but the previous questions can not be answered without proper quantitative measures of agenda's dynamics and public attention.
+The agenda-setting theory provides a conceptual framework in order to understand the role played by the mass media in public opinion formation, but the previous questions can not be answered without proper quantitative measures of agenda's dynamics and public attention.
 In this work we study the agenda of Argentinian newspapers in comparison with public interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time.
-We measure Agenda's diversity as a function of time using Shannon's entropy and differences between Agendas using Jensen-Shannon's distance.
+We measure agenda's diversity as a function of time using Shannon's entropy and differences between agendas using Jensen-Shannon's distance.
 We found that the Public Agenda is less diverse than the Media Agenda, and we were also capable to detect periods of time where coverage of certain issues are biased (coverage bias).\\
@@
 \kwd{topic detection}
-\kwd{Mass Media influence}
+\kwd{mass media influence}
 \end{keyword}
@@
 Within this framework, many ingredients can be part of different mechanism of social influence.
-A major role in this ecosystem is played by the Mass Media outlets, which use to be the source of information of many people.
+A major role in this ecosystem is played by the mass media outlets, which use to be the source of information of many people.
 Then, informed people tends to interact with each other, either via personal interactions or through social networks, giving rise to complex dynamics where opinions are shaping and changing in time.
-In this scenario, becomes essential to understand the role of Mass Media Influence in a given social group.
+In this scenario, becomes essential to understand the role of mass media influence in a given social group.
 
 % Agenda Setting Theory
-\par Naturally, how the Media affects public opinion was first explored in the area of social sciences. 
+\par Naturally, how the media affect public opinion was first explored in the area of social sciences. 
 In the famous study performed in Chapel Hill during the US presidential elections in 1968 \cite{mccombs1972agenda}, Maxwell McCombs and Donald Shaw found that those aspects of public affairs that are prominent in the news become prominent among the public.
 This study is considered the founding of the agenda-setting theory.
-In its basic stage, known as first-level agenda-setting \cite{mccombs2005look}, the theory focuses on the comparison between the topics coverage by the media and the public agenda, i.e.
-the topics that the public consider as priority \cite{brians1996campaign, gerber2009does, coleman2007young}.
-For instance, in Argentina, \cite{mitchelstein2016brecha} examines the difference between public and journalists preferences and several works by E.
+In its basic stage, known as first-level agenda-setting \cite{mccombs2005look}, the theory focuses on the comparison between the topics covered by the media and those that the public consider as priority \cite{brians1996campaign, gerber2009does, coleman2007young}.
+For instance, in Argentina, \cite{mitchelstein2016brecha} examines the difference between public and journalists preferences, and several works by E.
 Zunino like \cite{zunino2010cobertura, koziner2013cobertura}, studied the coverage given by the main newspapers of particular events which have happened during the former administration of Argentinian president \emph{Cristina Fern\'andez de Kirchner} (from 2007 to 2015), where the government started to confront with news organizations that were critical to its management \cite{mitchelstein2017information}.
@@
 \par The Chapel Hill investigation also induced other several research directions \cite{mccombs2005look}.
-One of them focused on detecting bias in the media, either by taking into account the number of mentions related  to a preferred political party \cite{lazaridou2016identifying, baumgartner2015all} or by identifying the ideology through the position of the media regards to certain issues or actors \cite{elejalde2018nature, sagarzazu2017hugo}.
+One of them is focused on detecting bias in the media, either by taking into account the number of mentions related  to a preferred political party \cite{lazaridou2016identifying, baumgartner2015all} or by identifying the ideology through the position of the media respect to certain issues or actors \cite{elejalde2018nature, sagarzazu2017hugo}.
 This research line can be linked with the theory of \textit{framing} \cite{guggenheim2015dynamics, tsur2015frame}, which is concerned with how the media emphasizes some attributes of an object, while understating others.
-Other investigations pay attention to the sources of the Media Agenda, theory known as \textit{intermedia agenda-setting} \cite{vargo2017networks, harder2017intermedia, guo2017global}, in which the competition between different media, and the influence exerted between each other, is observed.
+Other investigations pay attention to the sources of the Media Agenda, theory known as \textit{intermedia agenda-setting} \cite{vargo2017networks, harder2017intermedia, guo2017global}, in which the competition between different media and the influence exerted between each other, is observed.
 
@@
 \par Nonetheless, most of the works cited above follow typical methods of social science research, and fall in what we call a ``static approach": They used to summarize certain issues present in news media and looking for effects in the audience.
-With the irruption of internet in our lives and the access to big data, a richer analysis is allowed, which may take into account the temporal dependence of the Media and Public attention. 
-For instance, in \cite{soroka2017negativity} it is shown that the newspapers and Twitter have an opposite reaction to the changes of the unemployment rates; in \cite{guggenheim2015dynamics}, the competition of frames about gun control is explored; in \cite{ali2018measuring}, the authors show how fluctuations of Twitter activity in different regions depend on the location of terrorist attacks; and in \cite{russell2014dynamics}, the complex interplay between the social media and the traditional one is followed over time on a set of predefined, but general, issues.
-However, one drawback of several works which perform a dynamical analysis of agenda-setting is that the research is usually made on a single issue or on a set of predefined issues.
+With the irruption of internet in our lives and the access to big data, a richer analysis is allowed, which may take into account the temporal dependence of the media and public attention. 
+For instance, in \cite{soroka2017negativity} it is shown that the newspapers and Twitter have an opposite reaction to the changes of the unemployment rates; in \cite{guggenheim2015dynamics}, the competition of frames about gun control is explored; in \cite{ali2018measuring}, the authors show how fluctuations of Twitter activity in different regions depend on the location of terrorist attacks; and in \cite{russell2014dynamics}, the complex interplay between the social media and the traditional one is followed over time on a set of general issues.
+However, a drawback of several works which perform a dynamical analysis of agenda-setting is that the research is usually made on just a single issue or on a set of predefined ones.
 Frequently, the last are arbitrarily selected by the own researcher, and normally reflect general themes, such as ``health" or ``gun control".
@@
 It is an alternative to the dictionary-based analysis, which is the most popular automated analysis approach \cite{guo2016big}, and allows to work with a corpus without a prior knowledge, letting the topics emerge from the data.
-Although many works employ unsupervised topic modeling on news corpus, much of them emphasize the performance of the topic model over a labeled corpus, focusing on the proper detection of the topics \cite{dai2010online, po2016topic, brun2000experiment}.
+Although many works employ unsupervised topic modeling on news corpus, much of them emphasize the performance of the topic model over a labeled corpus, by focusing on the proper detection of the topics \cite{dai2010online, po2016topic, brun2000experiment}.
 In general, issues about the temporal profile of topics are embedded in the context of topic tracking \cite{hu2016news, li2017joint}, or in the recognition of emerging topics in real-time \cite{cataldi2010emerging}, mostly applied to social media.
 
-\par In this work we propose a novel method in order to study the dynamics of Mass Media Agenda, which consist in performing an unsupervised topic model on newspapers articles, and studying how the emerging topics evolve in time.
-We look also at their correspondence with the Public and Social Network Agendas.Rather than focus on a single issue or a set of independent topics, we work with the agendas (the Media and the Public) as an object in their own.
+\par In this work we propose a novel method in order to study the dynamics of the Media Agenda, which consist in performing an unsupervised topic model on newspapers articles, and studying how the emerging topics evolve in time.
+We look also at their correspondence with the Public Agenda, by looking at the behaviour of the audience both in Google and Twitter.
+Rather than focus on a single issue or treat the topics as were independent, we work with the Agendas as an object in their own.
 Our work intends to contribute another quantitative approach which complements the agenda-setting theory describe above.
-It mainly stands within the framework of first-level agenda setting, but issues about the comparison between media agendas and framing are also discussed.
-\par On the other hand, in recent years new approaches to study social dynamics through several tools taken from statistical physics have proposed mathematical models to explore the interplay between Mass Media and society \cite{crokidakis2012effects,gonzalez2012model, moussaid2013opinion, rodriguez2010effects, pinto2016setting}.
+It mainly stands within the framework of first-level agenda-setting, but issues about the comparison between media agendas and framing are also discussed.
+\par On the other hand, in recent years new approaches to study social dynamics, through several tools taken from statistical physics, have proposed the use of mathematical models to explore the interplay between mass media and society \cite{crokidakis2012effects,gonzalez2012model, moussaid2013opinion, rodriguez2010effects, pinto2016setting}.
 Much of them lack in being contrasted with real data.
-With our work we aim to gain a closer insight on the complex interaction between Media and Public, and provide a quantitative research that would be useful at the time of constructing better and more data-driven models.
+With our work, we aim to gain a closer insight on the complex interaction between media and its audience, and therefore provide a quantitative research that would be useful at the time of constructing better and more data-driven models.
 
@@
 \subsection*{The Media Agenda}
-\par In this work we analyze a three month period of the Argentinian Media's Agenda composed by a corpus of news' articles that were published between July 31th and November 5th of 2017. 
-The articles come from the \emph{Politics} section of the online editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\'on}, \emph{P\'agina12}, and the news portal \emph{Infobae}.
+\par In this work we analyze a three month period of the Argentinian Media Agenda composed by a corpus of news' articles that were published between July 31th and November 5th of 2017. 
+The articles come from the politics section of the online editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\'on}, \emph{P\'agina12}, and the news portal, \emph{Infobae}.
 The first two lead the sale of printed editions in \emph{Buenos Aires} city, but \emph{Clar\'in} reaches roughly two times the readers of \emph{La Naci\'on}, and ten times the readers of \emph{P\'agina 12} \cite{IVC}.
@@
 \par The articles are described as numerical vectors through the \textit{term frequency - inverse document frequency (tf-idf)} representation \cite{xu2003document}. 
-Given the set of terms contained in the corpus' words after removing non-informative ones, such as prepositions and conjunctions, the \textit{tf-idf} algorithm represents the \textit{i}-document as a vector $v_i = [x_{i1}, x_{i2}, ...
-, x_{it}]$, where the component $x_{ij}$ is computed by the eq.(ref{ec:tfidf}), where $\textrm{tf}_{ij}$ is the number of times the \textit{j}-term appears in the \textit{i}-document, $d$ is the number of documents in the corpus, and $n_j$ is the number of documents where the \textit{j}-term appears.
-Each document's vectors is normalized to unit Euclidean length.
-Once the documents' vector are constructed, we put them together in a document-term matrix (\emph{M}), which has dimensions of number of documents in the corpus ($d$) per number of terms selected ($t$).
+Given the set of terms contained in the corpus' words, after removing non-informative ones such as prepositions and conjunctions, the \textit{tf-idf} algorithm represents the \textit{i}-document as a vector $v_i = [x_{i1}, x_{i2}, ...
+, x_{it}]$, where the component $x_{ij}$ is computed by the eq.(\ref{ec:tfidf}), where $\textrm{tf}_{ij}$ is the number of times the \textit{j}-term appears in the \textit{i}-document; $d$ is the number of documents in the corpus; and $n_j$ is the number of documents where the \textit{j}-term appears.
+Each vector is then normalized to unit Euclidean length. 
+Once the documents' vector are constructed, we put them together in a document-term matrix (\emph{M}), which has dimensions of number of documents in the corpus ($d$) per number of terms ($t$).
 
@@
 
-\par We perform \emph{non-negative matrix factorization (NMF)} \cite{xu2003document, lee1999learning} on the document-term matrix (\emph{M}) in order to detect the main topics in the corpus.
-A topic is a group of similar articles which roughly talks about the same subject.
-\emph{NMF} is an algorithm which factorize the matrix \emph{M} into two matrices \emph{W} and \emph{H} (eq.(\ref{eq:nmf})), with the property that all three matrices have no negative elements.
-This non-negativity makes the resulting matrices easier to inspect, and very suitable for topic detection \footnote{ Even though there are other techniques in topic detection, as for instance LDA (Latent Dirichlet Allocation), the NMF decomposition suites perfect for the kind of corpus we  have analyzed in this work (A detailed comparison of both, NMF and LDA methods could be found in Supplementary Material).}.
+\par In order to detect the main topics in the corpus, we perform \emph{non-negative matrix factorization (NMF)} \cite{xu2003document, lee1999learning} on the document-term matrix (\emph{M}).
+A topic is defined to be a group of similar articles which roughly talks about the same subject.
+\emph{NMF} is an unsupervided topic model which factorize the matrix \emph{M} into two matrices \emph{W} and \emph{H} with the property that all three matrices have no negative elements (see eq.(\ref{eq:nmf})).
+This non-negativity makes the resulting matrices easier to inspect, and very suitable for topic detection \footnote{ Even though there are other techniques in topic detection, as for instance LDA (Latent Dirichlet Allocation), the NMF decomposition suites perfect for the kind of corpus we  have analyzed in this work (A detailed comparison of both, NMF and LDA methods could be found in \textbf{Supplementary Material}).}.
 \begin{equation}
@@
 In this work, we arbitrarily set $k=10$. We found this value to be a suitable one based on our knowledge of the corpus.
+Since the factorization of eq.(\ref{eq:nmf}) usually can not be made exactly, it is approximated by minimizing the reconstruction error, i.e.
+the distance between matrix \emph{M} and its approximated form $\tilde{M} = H \cdot W$.
+The \emph{NMF} factorization was made through the python module \emph{scikit-learn} \cite{scikit-learn}.
+
 \par The matrix \emph{H} is the representation of the documents in the topic-space.
-Each row is normalized to unit $l_1$-norm so that their components can be viewed as a degree of membership of a given document in the set of topics.
+We normalized its rows to unit $l_1$-norm in order to view their components as a degree of membership of a given document in the set of topics.
 In particular, the index of the largest component tells us which is the most representative topic of the document.
 On the other hand, \emph{W} gives the topics representation in the original term-space.
-The largest components of a row give the most representative words of each topic (called keywords) and therefore an insight of what the topic is talking about.
-Since the factorization of eq.(\ref{eq:nmf}) usually can not be made exactly, it is approximated by minimizing the reconstruction error, i.e.
-the distance between matrix \emph{M} and its approximated form $\tilde{M} = H \cdot W$.
-The \emph{NMF} factorization through the python module \emph{scikit-learn} \cite{scikit-learn}.
+The largest components of a row give the most representative words of each topic, which we call \emph{keywords}, and therefore an insight of what the topic is talking about.
 
-\par After performing NMF, we represent a time-dependent Media Agenda as a time evolving distribution of topics.
-The daily weight of the topic $i$, $W_i(day)$, is calculated following  eq.(\ref{eq:topic_weight}), where $l(j)$ is the number of words of the document $j$, $h_{ji}$ is the degree of membership of document $j$ on topic $i$, $d_j$ is the date of document $j$, and $\delta$ is the Kronecker delta.
+\par After performing NMF, we represent the time-dependent Media Agenda as a time evolving distribution of topics.
+We define $W_i(day)$ to be the daily weight of the topic $i$, which is calculated following the eq.(\ref{eq:topic_weight}), where $l(j)$ is the number of words of the document $j$; $h_{ji}$ is the degree of membership of document $j$ on topic $i$; $d_j$ is the date of document $j$; and $\delta$ is the Kronecker delta.
 Providing by the fact that each document's vector can have all non-zero components, it is allowed that a document contributes to more than one topics' weight.
-In order to reduce noise, we apply a linear filter with a three day wide sliding window, and finally we normalize the temporal profiles in order to describe each newspaper agenda as a distribution over the topics' space which evolves over time.
+In order to reduce noise, we apply a linear filter with a three day wide sliding window, and finally we normalize the temporal profiles in order to describe each newspaper agenda as a distribution over the topics' space, which evolves over time.
 %This last normalization prevent us against the differences in the number of articles that each newspaper publishes.
@@
 
-\par The other side of time-dependent Media Agenda is to have some measure of the public interest about these topics.
-With this goal, we use  \emph{Google Trends} and \emph{Twitter} as a proxy of public interest by  looking for the same topics  in the same period of time.
-We take advantage of topics' keywords to make queries in the \emph{Google Trends}  tool and  into the advance search tool of Twitter  to get the relative weight searches and tweets in both platforms.
-\par In section \textbf{Results} we give a more detailed description of the keywords involved in the construction of the Google and Twitter Agendas.
+\par The other side of the Media Agenda is to have some measure of the public interests about its topics, by finally making up what we call the Public Agenda. 
+To achieve this goal, we take Google and Twitter as proxies of the public interests by looking for the same topics in the same period of time.
+We take advantage of topics' keywords in order to make queries into the \emph{Google Trends} tool and into the advance search tool of Twitter, and therefore to get the relative weight of searches and tweets in each respective platform.
+Therefore we describe the Public Agenda by describing, in an independent way, both the Google and Twitter Agendas. 
+In section \textbf{Results} we will give a more detailed description of the keywords involved in their construction.
 
@@
 \par The normalized Shannon's entropy $H[p]$ referred in eq.(\ref{eq:shannon_entropy}) give us a measure of how spread is a -discrete- distribution, taking the maximum value of $1$ when all outcomes are equally probable, and $0$ when there is just one possible outcome.
-This last case -or approximated ones- will be of particular interest for us because it tells about a topic which absorbs all the attention either from the Media or the Public, while the former shows an absolutely unbiased interest towards any of the topics.
+This last case, or approximated ones, will be of particular interest for us because it tells about a topic which absorbs all the attention either from the Media or the Public, while the former shows an absolutely unbiased interest towards any of the topics.
 
@@
 
-\par While the diversity is a property of each distribution, a natural question that arise from comparing different distributions is how similar they are.
-For instance, we will be particularly interested in measuring the similarity between the Media and Public Agendas, because those dates when the similarity is low tell us about distant interests of the Media and the Public.
+\par While the diversity is a property of each distribution, a natural question that arises from comparing different distributions is how similar they are.
+For instance, we will be particularly interested in measuring the similarity between the Media and Public Agendas, because those dates when the similarity is low tell us about distant interests of the media and its audience.
 We proposed here to measure the similarity between distributions by the use of the Jensen-Shannon distance ($JSD$). 
 When the similarity of the distributions is low, the distance between them is high.
-\par The Jensen-Shannon distance ($JSD$) is a metric between distributions based on the Jensen-Shannon divergence ($JS_{Div}$) \cite{fuglede2004jensen}, which is in turn a symmetric version of the well-known Kullback-Leibler divergence ($D_{KL}$, eq.(\ref{eq:kl})).
-We recall that the $JSD$ has the advantage of being symmetric and also a well-defined distance, which make it conceptually easy to deal.
-As can be seen in eq.(\ref{eq:jensen_shannon_distance}) the $JSD$ between the distributions $P$ and $Q$ is simply the square root of the Jensen-Shannon divergence.
+\par The Jensen-Shannon distance ($JSD$) is a metric between distributions based on the Jensen-Shannon divergence ($JS_{Div}$) \cite{fuglede2004jensen}, which is in turn a symmetric version of the well-known Kullback-Leibler divergence $D_{KL}$ (eq.(\ref{eq:kl})).
+We recall that the $JSD$ has the advantage of being symmetric and also a well-defined distance, which make it conceptually easier to deal.
+As can be seen in eq.(\ref{eq:jensen_shannon_distance}), the $JSD$ between the distributions $P$ and $Q$ is simply the square root of the Jensen-Shannon divergence, where $M = \frac{P + Q}{2}$.
 
@@
 However, we still lack the definition of what a low diversity or a high distance are. 
-We face this problem by treating the measures of each observable as random samples from a population with unknown distribution and identifying those extreme values as outliers of the distribution. 
-In order to detect these outliers we follow the popular box-plot construction proposed by Tukey \cite{tukey1977exploratory}, which is a simple data-driven method and make no assumption about the distribution of the data.
-\par The box-plot construction is as follows: First a quartile division of the $N$ observations is made, by naming $Q1$ as the lower quartile, $Q2$ the median of the distribution, and $Q3$ the upper quartile.
+We face this problem by treating the measures of each observable as random samples from a population with unknown distribution, and identifying those extreme values as outliers of the distribution. 
+In order to detect these outliers we follow the popular box-plot construction proposed by Tukey \cite{tukey1977exploratory}, which is a simple data-driven method and has the advantage of making no prior assumption about the distribution of the data.
+\par In the box-plot construction a quartile division of the $N$ observations is proposed.
+We name $Q1$ as the lower quartile, $Q2$ the median of the distribution, and $Q3$ the upper quartile.
 Recall that $Q1$ ($Q3$) is defined to be the division where the 25th (75th) percent of the observations lies below (by definition, the median $Q2$ separates the distribution in two equal parts).
-On the other hand, the inter-quartile range $IQ$ is defined as $IQ = Q3 - Q1$.
+On the other hand, the inter-quartile range $IQ$ is defined to be $IQ = Q3 - Q1$.
 This is the range where the bulk of the data lies inside.
-\par We are not interesting in the visualization of the box-plot in its own but instead in its procedure to identify outliers.
+We are not interesting in the visualization of the box-plot in its own but instead in its procedure to identify outliers.
 Therefore from the identification of the quartiles, new quantities called \emph{fences} are defined in eq.(\ref{eq:fences}): The \emph{lower inner fence} ($LIF$), the \emph{upper inner fence} ($UIF$), the \emph{lower outer fence} ($LOF$), and the \emph{upper outer fence} ($UOF$).
 The fences can be interpreted as the limits of the distribution.
-We then have all the ingredients to label a point as an outlier: A point which lies above the upper inner fence is considered a \emph{mild outlier}, while a point that lies above the upper outer fence is considered an \emph{extreme outlier}.
-The same holds for the lower fences, i.e.
-if a point lies below the lower inner (outer) fences is considered as a mild (extreme) outlier \cite{natrella2010nist}.
 \begin{eqnarray}\label{eq:fences}
@@
 \end{eqnarray}
-\par We will indicate the proper fences in each figure either when the diversity or the distance is being analyzed.
+\par We then have all the ingredients to label a point as an outlier: A point which lies above the upper inner fence is considered a \emph{mild outlier}, while a point that lies above the upper outer fence is considered an \emph{extreme outlier}.
+The same holds for the lower fences, i.e.
+if a point lies below the lower inner (outer) fences is considered as a mild (extreme) outlier \cite{natrella2010nist}.
+We will indicate the proper fences in each figure either when the diversity or the distance is being analyzed.
 We will paid attention not only to those values labeled as outliers, but also to those that are next to any of the fences despite not being strictly defined as that.
@@
 
-\par We initially focus in the ten most important issues in the three months period corpus of news reported above.
-These ten topics, represented in the word clouds of figure \ref{fig:topics_wordclouds}, were reduced to seven (shown in the radar plot of the same figure) given the similarities found in, for instance, three of them that could be interpreted as part of the same macro-topic called \emph{Elections} and two others which were classified as part of a macro-topic called \emph{Missing person}.
+\par We initially focus in the ten most important issues from the three months period corpus of news reported above.
+These ten topics are represented in the word clouds of figure \ref{fig:topics_wordclouds}.
+Given our interpretation of the keywords found in three of them, we joined these topics as being part of the same macro-topic which we called \emph{Elections}.
+On the other hand the same holds for other two topics, which were classified as part of a macro-topic called \emph{Missing person}. 
+Therefore, the ten original topics were reduced to seven, which are pointed out in the radar plot of figure \ref{fig:topics_wordclouds}.
 The meaning of the topics or macro-topics is contextualized in the \textbf{Supplementary Material}.
-%\ref{sec:Context} of Supplementary Material. 
-\par Following the procedure described in the previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, in both its Google and Twitter derivations, as time evolving topic distributions.
+\par Finally by following the procedure described in the previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, in both its Google and Twitter derivations, as time evolving distributions in a space of seven topics.
 
-\subsection*{The Public and Media agendas}
+\subsection*{The Media and Public Agendas}
 
-\par In figure \ref{fig:topics_wordclouds} we show a ten topic decomposition of the whole corpus using radar plots for the Media \textbf{MA} and Public agendas \textbf{PA} discriminated by \textbf{GT} (Google Trends) and \textbf{Tw} (Twitter).
-In this figure we also show the wordclouds of the keywords that define each topic, where the size of the word reflects its importance in the topic's definition.
-In green color, we point out the words involved in the Google Trends and Twitter  \footnote{Due to different characteristics in the search tool of Twitter, we adapted the queries employed here but preserving at least at we can the most important keywords.
-The queries employed by topic were: \\
-Elections: elecciones + cambiemos + kirchner + massa + randazzo \\
-Missing person: maldonado + otranto + gendarmer\'ia + desaparici\'on \\
-Former Planning minister: vido + desafuero + minnicelli + baratta \\
-Current President: macri + cgt + laboral +  triaca \\
-Social leader:  sala + cidh + tupac + amaru + pullen + llermanos + morales \\
-Prosecutor’s death: nisman + amia + memorandum + timerman +  bonadio \\
-Former Vice-President:  boudou + ciccone +  lijo + vandenbroele + carmona
-} queries in order to construct the Public Agenda.
-The queries employed are also specified in table \ref{table:gt_queries}.
+\par In figure \ref{fig:topics_wordclouds} we show a seven topic decomposition of the whole corpus using radar plots for the Media \textbf{MA} and Public agendas \textbf{PA} discriminated by \textbf{GT} (Google Trends) and \textbf{Tw} (Twitter).
+In this figure we also show the wordclouds of the keywords that define each the ten original topics, where the size of the word reflects its importance in the topic's definition.
+In green color, we point out the words involved in the Google Trends and Twitter queries in order to construct the Public Agenda.
+The queries employed are also specified in tables \ref{table:gt_queries} and \ref{table:tw_queries}.
 On the other hand, in table \ref{table:gt_all_correlation} we show the linear correlation between the topics' temporal profiles from the Public Agenda and their counterparts in the Media Agenda.
-
-\par We can observe that both Public Agendas ($GT$ and $Tw$) look similar in this representation, but they show specific differences with the Media Agenda.
-For instance, a greater interest of the audience in the topic \emph{Missing person} than the Media is observed, or inversely, a lower interest in the topic \emph{Prosecutor's death} takes place.
+\par We can observe that both GT and Tw look similar in this representation, but they show specific differences with the Media Agenda.
+For instance, a greater interest of the audience in the topic \emph{Missing person} than the media is observed, or inversely, a lower interest in the topic \emph{Prosecutor's death} takes place.
 However, this static representation is not able to show the complex dynamics of agenda's evolution and the importance of punctual and specific facts which can erase or amplify their differences.
@@
 It is possible to appreciate how the main topic change in time and have a glance of the qualitative differences between agendas.
-In particular, it can be observed some differences between Public Agendas ($GT$ and $Tw$) that were not observed in the previous figure, as for instance, the persistence of main topics is longer in Twitter than in Google Trends.
-This is more evident at the end of the analyzed period, where topics discussed in Google Trends shows more  responsive to change in Media Agenda than in Twitter, suggesting the existence that the interaction between people is stronger in the analyzed social network.
-
-\par The linear correlations between same topics of $PA$ and $MA$ were also calculated.
-In all cases, we found that they are positive and statistically significant, as can be shown in table \ref{table:gt_all_correlation}.
-This can be interpreted as a validation of the topics found in the corpus and the keywords that describe it.
-Even though it is expected that the Media's and public's interest should generally follow a similar a pattern, mainly driven by  external events, we are interested in those periods where they significantly differ.
-However, a non positive (or a non significant) correlation may imply, besides the obvious conclusion of agenda's disengagement, that we could eventually fail in properly detect the keywords or features that describe a particular topic, so the Google Trends' or Twitter's pattern would not be able to reflect a similar behavior that its counterpart in the Media.
+In particular, it can be observed some differences between the Public Agendas that were not observed in the previous figure, as for instance, the persistence of main topics is longer in Twitter than in Google Trends.
+This is more evident at the end of the analyzed period, where topics discussed in Google Trends shows more  responsive to change in Media Agenda than in Twitter, maybe due to the existence of a different pattern of interaction in the social network, to which a deeper analysis could be devoted in future works.
+\par The linear correlations between the same topics of MA and PA were also calculated.
+In all cases, we found that the correlations are positive and statistically significant, as it is shown in table \ref{table:gt_all_correlation}.
+We interpret this as a validation of the topics found in the corpus and the keywords that describe it.
+Even though we are particularly interested in those periods where the Agendas differ, it is expected that the media and public interest should generally follow a similar a pattern, mainly driven by external events
+A non positive (or a non significant) correlation may imply, besides the obvious conclusion of agenda's disengagement, that we can be eventually failing in properly detect the keywords or features that describe a particular topic, and therefore the comparison of the Google Trends' or Twitter's patterns with their counterpart in the Media Agenda would be wrong.
 
@@
 Is the degree of dominance of a given topic in the Media Agenda reflected in the Public Agenda?
-In order to answer such kind of questions we quantify the diversity of the Agendas through the normalized Shannon's entropy $H$, which was introduced in section \textbf{Material and Methods}.
+In order to answer such kind of questions we quantify the diversity of the agendas through the normalized Shannon's entropy $H$, which was introduced in section \textbf{Material and Methods}.
 \par In figure \ref{fig:shannon_entropy_agendas} we can see the value of $H$ as a function of time for the three agendas.
-It is important to pay attention to those periods of time where the diversity is lower than usual.
-This effect is notoriously more pronounced in the Public Agenda giving by \textbf{GT} and, in particular, in four specific days  where  four local minima of Shannon's entropies can be detected.
-Three of them are outliers as defined in section \textbf{Material and Methods} \ref{sec:MatMeth}, two of them from \textbf{GT} and one from \textbf{Tw}.
-The other one is not an outlier but a pronounced minima and therefore a point of interest in this description.
+It is important to pay attention to those periods of time when the diversity is lower than usual.
+This effect is notoriously more pronounced in the Public Agenda giving by GT and, in particular in four specific days, where four local minima of the Shannon's entropy can be detected.
+Three of them are outliers as defined in section \textbf{Material and Methods}, two of them from GT and one from Tw.
+The other one has been not identified as an outlier but it is a pronounced minima and therefore a point of interest in our description.
 
-\par A lower value in the agenda's diversity is due to the fact that the most important topic attracts practically all the attention of the Public and the Media, collapsing the agenda to one of the issues involved.
+\par A lower value in the agenda's diversity is due to the fact that the most important topic attracts practically all the attention of the public and the media, collapsing the agenda to one of the issues involved.
 In the radar plots included in figure \ref{fig:shannon_entropy_agendas} we can see how two of these outliers (\textbf{a} and \textbf{d}) belong to the topic \emph{Elections}.
@@
 Discussions in Twitter about elections appear also in point (c), when the other agendas seems to be more diverse. 
-On the other hand, and despite not being classified as outlier, we also focus in point (b) because Shannon's Entropy of $GT$ Agenda displays a minimum (collapsing agenda) which is not corresponded neither in the Media nor in the Twitter Agendas.
-Crawling in the context, we see that it belongs to the topic \emph{Missing person} and this date correspond to the rally that took place one month after the disappearance of \emph{Santiago Maldonado} (see \textbf{Supplementary Material}).
+On the other hand, and despite not being classified as outlier, we also focus in point (b) because the Shannon's Entropy in the Google Agenda displays a minimum (collapsing agenda) which is not corresponded neither in the Media nor in the Twitter Agendas.
+Crawling in the context, we see that it belongs to the topic \emph{Missing person} and this date corresponds to the rally that took place one month after the disappearance of \emph{Santiago Maldonado} (see \textbf{Supplementary Material}).
 We  would like to emphasize the discussion about this topic (\emph{Missing person}) because its dynamics show interesting features, as we will show bellow.
@@
 Specifically $H_{GT} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
-However from figure \ref{fig:shannon_entropy_agendas} we can see that \textbf{GT} shows more abrupt dropouts in the diversity in response to specific events.
+However from figure \ref{fig:shannon_entropy_agendas} we can see that GT shows more abrupt dropouts in the diversity in response to specific events.
 From all this analysis we  can conclude that given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus in the most important topics than Media can do, maybe due to editorial decisions.
@@
 
-\par Given our descriptions of the Agendas as time-evolving distributions, we can  compare them by computing the Jensen-Shannon distance.
+\par Given our descriptions of the agendas as time-evolving distributions, we can  compare them by computing the Jensen-Shannon distance.
 In this context, outliers in selected dates will correspond to divergences between Public and Media Agenda, i.e., specific events where the public interest do not match with media offer.
-In figure \ref{fig:jensen_shannon_gt} we show the Jensen-Shannon distance between Media and Publics Agendas as a function of time.
+In figure \ref{fig:jensen_shannon_gt} we show the Jensen-Shannon distance between Media and Public Agendas as a function of time.
 We focus in three points that seems to be relevant enough.
@@
 
-\par Points \textbf{(c)} and \textbf{(d)} show that both the Public and the Media highlight this topic, but the Media do not disregard other topics, so the corresponding distance between them can be interpreted as lack of the diversity in Public Agenda as discussed in the last section.
+\par Points \textbf{(c)} and \textbf{(d)} show that both the public and the media highlight this topic, but the media do not disregard other topics, so the corresponding distance between them can be interpreted as lack of the diversity in Public Agenda as discussed in the last section.
 
 \par On the other hand,  points \textbf{(a)} (we take this point due to be a local maximum despite not being an outlier) and \textbf{(b)}  show a major  interest of the public in the topic \emph{Missing person} which it is not reflected in the Media.
-In figure \ref{fig:all_agenda} we can see that this topic becomes the most important in public's interest (both \textbf{GT} and \textbf{Tw}) days before that  it happen in the Media Agenda.
+In figure \ref{fig:all_agenda} we can see that this topic becomes the most important in public's interest (both in GT and Tw) days before that  it happen in the Media Agenda.
 It can be associates  with a social networks (like Facebook and Twitter) campaign  in favor  of the appearance of \emph{Santiago Maldonado} (``The missing person") that took place on  August 26th.
@@
 we can't say, for instance, that in this case the Public Agenda set the Media Agenda.
-Finally, it is important to say that the Jensen-Shannon distance, in conjunction with the measurement of agenda diversity given by the Shannon entropy, give an insight of independent behavior, in certain particular dates,  of the Public and the Media.
-Its identification can be a starting point to study the Media reaction to a change in audience's interests.
+Finally, it is important to say that the Jensen-Shannon distance, in conjunction with the measurement of agenda diversity given by the Shannon entropy, give an insight of independent behavior, in certain particular dates,  of the public and the media.
+Its identification can be a starting point to study the media reaction to a change in audience's interests.
 
@@
 This interpretation try to catch in a qualitative way how the information flow was in this specific topic.
-On the other hand, behind this interpretation there are two important facts that must be mentioned: First, the disappearance of a person is a very sensible theme for the Argentinian society, and second, there are political reasons in why \emph{P\'agina 12} was particularly interested in cover this topic while the other Media did not follow this interest (see \textbf{Supplementary Material}).
+On the other hand, behind this interpretation there are two important facts that must be mentioned: First, the disappearance of a person is a very sensible theme for the Argentinian society, and second, there are political reasons in why \emph{P\'agina 12} was particularly interested in cover this topic while the other media did not follow this interest (see \textbf{Supplementary Material}).
 
@@
 
-\par The  Mass media play a fundamental role in opinion formation and therefore it's of vital importance to have an accurate  quantitative description of the Media  and Public Agenda and their relationship in the framework of Agenda Setting theory.
-In this work, through the implementation of a topic detection algorithm we describe the Agenda of the Media as a distribution which evolves in time and which is defined in a topic's space which emerges from the analysis of the corpus.
-This gave us an insight of how we can construct and follow the Public's interests, the Public Agenda, in order to compare with the Media Agenda, i.e.
-Media interests.
+\par The mass media play a fundamental role in opinion formation and therefore it's of vital importance to have an accurate  quantitative description of the Media  and Public Agenda and their relationship in the framework of agenda-setting theory.
+In this work, through the implementation of a topic detection algorithm we describe the Media Agenda as a distribution which evolves in time and which is defined in a topic's space which emerges from the analysis of the corpus.
+This gave us an insight of how we can construct and follow the public's interests, i.e the Public Agenda, in order to compare with the media interests.
 
 \par Given the Agendas, we found that the Public one is usually less diverse than the Media, showing that when there is a very attractive topic, the audience focus on this one, meanwhile the Media keeps certain degree of diversity.
-On the other hand, the measurement of distances between Agendas can be employed to rapidly detect periods when the Public may have an independent behavior respect to the Media.
+On the other hand, the measurement of distances between agendas can be employed to rapidly detect those periods when the public may have an independent behavior respect to the media.
 The methodology implemented here also allow us to detect coverage bias in newspapers and gave us a first approximation in the theory of framing.
-\par We hope that some of the elements studied here will give us insights at the time of proposing a mathematical model about Mass Media and Public interaction.
-Future works may include a more systematic study and its extension to international Media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitative analysis about causality.
+\par We hope that some of the elements studied here will give us insights at the time of proposing a mathematical model about mass media and public interaction.
+Future works may include a more systematic study and its extension to international media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitative analysis about causality.
 
@@
 \begin{table}[h!]
+\caption{Queries used in Twitter: Due to different characteristics in the search tool of Twitter, we adapted the queries employed in Google Trends but preserving at least at we can the most important keywords.}
+\begin{tabular}{l|p{7.5cm}}
+Topic's name & Twitter query \\ \hline
+Elections & elecciones + cambiemos + kirchner + massa + randazzo \\
+Missing person & maldonado + otranto + gendarmer\'ia + desaparici\'on \\
+Former Planning minister & vido + desafuero + minnicelli + baratta \\
+Current President & macri + cgt + laboral +  triaca \\
+Social leader &  sala + cidh + tupac + amaru + pullen + llermanos + morales \\
+Prosecutor’s death & nisman + amia + memorandum + timerman +  bonadio \\
+Former Vice-President & boudou + ciccone +  lijo + vandenbroele + carmona \\ 
+\end{tabular}
+\label{table:tw_queries}
+\end{table}
+
+\begin{table}[h!]
 \caption{Correlation between the topics' temporal profiles of the Public Agenda and their counterpart in Media Agenda.

### 2018-09-03 bmc_article.tex
A tomar esto como ultima version

--- 2018-08-30 bmc_article.tex
@@
 But which is the dynamics of the agenda and how the people become interested in their different topics?
-The Agenda Setting theory provides a conceptual framework in order to understand the role played by the mass media in public opinion formation, but the previous questions can not be answered without proper quantitative measures of agenda's dynamics and public attention.
+The agenda-setting theory provides a conceptual framework in order to understand the role played by the mass media in public opinion formation, but the previous questions can not be answered without proper quantitative measures of agenda dynamics and public attention.
 In this work we study the agenda of Argentinian newspapers in comparison with public interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time.
-We measure Agenda's diversity as a function of time using Shannon's entropy and differences between Agendas using Jensen-Shannon's distance.
+We measure agenda diversity as a function of time using the Shannon entropy and differences between agendas using the Jensen-Shannon distance.
 We found that the Public Agenda is less diverse than the Media Agenda, and we were also capable to detect periods of time where coverage of certain issues are biased (coverage bias).\\
@@
 
-\par The understanding of the ecosystem of information flow and opinion formation is one of the challenges in  complex social system research.
-Within this framework, many ingredients can be part of different mechanism of social influence.
-A major role in this ecosystem is played by the Mass Media outlets, which use to be the source of information of many people.
-Then, informed people tends to interact with each other, either via personal interactions or through social networks, giving rise to complex dynamics where opinions are shaping and changing in time.
-In this scenario, becomes essential to understand the role of Mass Media Influence in a given social group.
+\par One of the challenges in  complex social system research is to understand of the ecosystem of information flow and opinion formation.
+Within this framework, many ingredients can be parts of different mechanisms of social influence.
+A major role in this ecosystem is played by the Mass Media outlets, which is used to be the source of information for many people.
+Then, informed people tend to interact with each other  via personal interactions or through social networks, giving rise to complex dynamics where opinions are shaping and changing in time.
+In this scenario to understand the role of Mass Media Influence in a given social group  becomes essential.
 
@@
 \par Naturally, how the Media affects public opinion was first explored in the area of social sciences. 
-In the famous study performed in Chapel Hill during the US presidential elections in 1968 \cite{mccombs1972agenda}, Maxwell McCombs and Donald Shaw found that those aspects of public affairs that are prominent in the news become prominent among the public.
-This study is considered the founding of the agenda-setting theory.
+In the seminal study performed in Chapel Hill during the US presidential elections in 1968 \cite{mccombs1972agenda}, Maxwell McCombs and Donald Shaw found that the aspects of public affairs that are prominent in the news become prominent in the public.
+This work is considered the founding of the agenda-setting theory.
 In its basic stage, known as first-level agenda-setting \cite{mccombs2005look}, the theory focuses on the comparison between the topics coverage by the media and the public agenda, i.e.
 the topics that the public consider as priority \cite{brians1996campaign, gerber2009does, coleman2007young}.
-For instance, in Argentina, \cite{mitchelstein2016brecha} examines the difference between public and journalists preferences and several works by E.
-Zunino like \cite{zunino2010cobertura, koziner2013cobertura}, studied the coverage given by the main newspapers of particular events which have happened during the former administration of Argentinian president \emph{Cristina Fern\'andez de Kirchner} (from 2007 to 2015), where the government started to confront with news organizations that were critical to its management \cite{mitchelstein2017information}.
+For instance, in Argentina, \cite{mitchelstein2016brecha} examines the differences between public and journalists preferences and other works, like \cite{zunino2010cobertura, koziner2013cobertura}, studied the coverage of the main newspapers on particular events related to a confrontation scenario between government and press \cite{mitchelstein2017information}.
+
+%during the former administration of Argentinian president \emph{Cristina Fern\'andez de Kirchner} (from 2007 to 2015), where the government started to confront with news organizations that were critical to its management \cite{mitchelstein2017information}.
 
 \par The Chapel Hill investigation also induced other several research directions \cite{mccombs2005look}.
-One of them focused on detecting bias in the media, either by taking into account the number of mentions related  to a preferred political party \cite{lazaridou2016identifying, baumgartner2015all} or by identifying the ideology through the position of the media regards to certain issues or actors \cite{elejalde2018nature, sagarzazu2017hugo}.
-This research line can be linked with the theory of \textit{framing} \cite{guggenheim2015dynamics, tsur2015frame}, which is concerned with how the media emphasizes some attributes of an object, while understating others.
-Other investigations pay attention to the sources of the Media Agenda, theory known as \textit{intermedia agenda-setting} \cite{vargo2017networks, harder2017intermedia, guo2017global}, in which the competition between different media, and the influence exerted between each other, is observed.
+One of them focus on detecting bias in the media, either by taking into account the number of mentions related  to a preferred political party \cite{lazaridou2016identifying, baumgartner2015all} or by identifying the ideology through the position of the media regards to certain issues or actors \cite{elejalde2018nature, sagarzazu2017hugo}.
+This research line can be linked with the theory of \textit{framing} \cite{guggenheim2015dynamics, tsur2015frame}, which focus on the way media emphasizes some attributes of an object, while understating others.
+Other investigations pay attention to the sources of the Media Agenda, theory known as \textit{intermedia agenda-setting} \cite{vargo2017networks, harder2017intermedia, guo2017global}, where the competition and the mutual influence between different media is observed.
 
@@
 
-\par Nonetheless, most of the works cited above follow typical methods of social science research, and fall in what we call a ``static approach": They used to summarize certain issues present in news media and looking for effects in the audience.
-With the irruption of internet in our lives and the access to big data, a richer analysis is allowed, which may take into account the temporal dependence of the Media and Public attention. 
-For instance, in \cite{soroka2017negativity} it is shown that the newspapers and Twitter have an opposite reaction to the changes of the unemployment rates; in \cite{guggenheim2015dynamics}, the competition of frames about gun control is explored; in \cite{ali2018measuring}, the authors show how fluctuations of Twitter activity in different regions depend on the location of terrorist attacks; and in \cite{russell2014dynamics}, the complex interplay between the social media and the traditional one is followed over time on a set of predefined, but general, issues.
-However, one drawback of several works which perform a dynamical analysis of agenda-setting is that the research is usually made on a single issue or on a set of predefined issues.
-Frequently, the last are arbitrarily selected by the own researcher, and normally reflect general themes, such as ``health" or ``gun control".
+%\par Nonetheless, most of the works cited above follow typical methods of social science research, and fall in what we call a ``static approach": They used to summarize certain issues present in news media and looking for effects in the audience.
+\par From the irruption of internet, quantitative analysis based on  the access to big data were possible and, for instance, take into account the temporal dependence of the Media and Public attention.
+In \cite{soroka2017negativity} it is shown that the newspapers and Twitter have an opposite reaction to the changes of the unemployment rates; in \cite{guggenheim2015dynamics}, the competition of frames about gun control is explored; in \cite{ali2018measuring}, the authors show how fluctuations of Twitter activity in different regions depend on the location of terrorist attacks; and in \cite{russell2014dynamics}, the complex interplay between the social media and the traditional one is followed over time on a set of predefined, but general, issues.
+However the works cited above have performed a dynamical analysis of agenda-setting based on a single issue or on a set of predefined issues.
+These are usually  selected by the researcher and use to reflect general subjects, such as ``health" or ``gun control".
 
 % Machine Learning
-\par The question about what issues should be selected can be solved by an useful tool employed in the analysis of large corpus of documents, but understated in the agenda-setting framework and its derivatives: Unsupervised topic modeling.
+\par The question about what issues should be selected can be solved by an useful tool employed in the analysis of large documents corpus, but understated in the agenda-setting framework and its derivatives: Unsupervised topic modeling.
 It is an alternative to the dictionary-based analysis, which is the most popular automated analysis approach \cite{guo2016big}, and allows to work with a corpus without a prior knowledge, letting the topics emerge from the data.
@@
 \par In this work we propose a novel method in order to study the dynamics of Mass Media Agenda, which consist in performing an unsupervised topic model on newspapers articles, and studying how the emerging topics evolve in time.
-We look also at their correspondence with the Public and Social Network Agendas.Rather than focus on a single issue or a set of independent topics, we work with the agendas (the Media and the Public) as an object in their own.
-Our work intends to contribute another quantitative approach which complements the agenda-setting theory describe above.
-It mainly stands within the framework of first-level agenda setting, but issues about the comparison between media agendas and framing are also discussed.
+We look also at their correspondence with the Public and Social Network Agendas.
+Rather than focus on a single issue or a set of independent topics, this method allow us to define  the agendas (the Media and the Public) as an object which evolved in time.
+Our work focus on a quantitative approach which complements the agenda-setting theory describe above, which mainly stands within the framework of first-level agenda setting, but also allows to face  agenda bias and framing.
+
 \par On the other hand, in recent years new approaches to study social dynamics through several tools taken from statistical physics have proposed mathematical models to explore the interplay between Mass Media and society \cite{crokidakis2012effects,gonzalez2012model, moussaid2013opinion, rodriguez2010effects, pinto2016setting}.
@@
 \subsection*{The Media Agenda}
-\par In this work we analyze a three month period of the Argentinian Media's Agenda composed by a corpus of news' articles that were published between July 31th and November 5th of 2017. 
-The articles come from the \emph{Politics} section of the online editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\'on}, \emph{P\'agina12}, and the news portal \emph{Infobae}.
+\par In this work we analyze a three-month period of the Argentinian Media Agenda composed by a corpus of news articles that were published between July 31st, 2017 and November 5th, 2017. 
+The articles come from the politics section of the online editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\'on}, \emph{P\'agina12}, and the news portal, \emph{Infobae}.
 The first two lead the sale of printed editions in \emph{Buenos Aires} city, but \emph{Clar\'in} reaches roughly two times the readers of \emph{La Naci\'on}, and ten times the readers of \emph{P\'agina 12} \cite{IVC}.
@@
 The corpus analyzed is made up by 2908 politics articles of \emph{Clar\'in}, 3565 of \emph{La Naci\'on}, 3324 of \emph{P\'agina 12}, and 2018 of \emph{Infobae}.
-Except \emph{P\'agina 12}, all articles were taken from the section \emph{Pol\'itica}  (Politics) of the respective news portal, while the articles which belong to \emph{P\'agina 12} were taken from the section \emph{El pa\'is} (The country).
+Except \emph{P\'agina 12}, all articles were taken from the section \emph{Pol\'itica}  (Politics) of the respective news portals, while the articles which belong to \emph{P\'agina 12} were taken from the section \emph{El pa\'is} (The country).
 
 \par The articles are described as numerical vectors through the \textit{term frequency - inverse document frequency (tf-idf)} representation \cite{xu2003document}. 
-Given the set of terms contained in the corpus' words after removing non-informative ones, such as prepositions and conjunctions, the \textit{tf-idf} algorithm represents the \textit{i}-document as a vector $v_i = [x_{i1}, x_{i2}, ...
-, x_{it}]$, where the component $x_{ij}$ is computed by the eq.(ref{ec:tfidf}), where $\textrm{tf}_{ij}$ is the number of times the \textit{j}-term appears in the \textit{i}-document, $d$ is the number of documents in the corpus, and $n_j$ is the number of documents where the \textit{j}-term appears.
-Each document's vectors is normalized to unit Euclidean length.
-Once the documents' vector are constructed, we put them together in a document-term matrix (\emph{M}), which has dimensions of number of documents in the corpus ($d$) per number of terms selected ($t$).
+Given the set of terms contained in the corpus words, after removing non-informative ones such as prepositions and conjunctions, the \textit{tf-idf} algorithm represents the \textit{i}-document as a vector $v_i = [x_{i1}, x_{i2}, ...
+, x_{it}]$, where the component $x_{ij}$ is computed by the eq.(\ref{ec:tfidf}), where $\textrm{tf}_{ij}$ is the number of times the \textit{j}-term appears in the \textit{i}-document; $d$ is the number of documents in the corpus; and $n_j$ is the number of documents where the \textit{j}-term appears.
+Each vector is then normalized to unit Euclidean length. 
+Once the document vectors are constructed, we put them together in a document-term matrix (\emph{M}), which has dimensions of number of documents in the corpus ($d$) by number of terms ($t$).
 
@@
 
-\par We perform \emph{non-negative matrix factorization (NMF)} \cite{xu2003document, lee1999learning} on the document-term matrix (\emph{M}) in order to detect the main topics in the corpus.
-A topic is a group of similar articles which roughly talks about the same subject.
-\emph{NMF} is an algorithm which factorize the matrix \emph{M} into two matrices \emph{W} and \emph{H} (eq.(\ref{eq:nmf})), with the property that all three matrices have no negative elements.
-This non-negativity makes the resulting matrices easier to inspect, and very suitable for topic detection \footnote{ Even though there are other techniques in topic detection, as for instance LDA (Latent Dirichlet Allocation), the NMF decomposition suites perfect for the kind of corpus we  have analyzed in this work (A detailed comparison of both, NMF and LDA methods could be found in Supplementary Material).}.
+\par In order to detect the main topics in the corpus, we perform \emph{non-negative matrix factorization (NMF)} \cite{xu2003document, lee1999learning} on the document-term matrix (\emph{M}).
+A topic is defined to be a group of similar articles which roughly talks about the same subject.
+\emph{NMF} is an unsupervised topic model which factorizes the matrix \emph{M} into two matrices \emph{W} and \emph{H} with the property that all three matrices have no negative elements (see eq.(\ref{eq:nmf})).
+This non-negativity makes the resulting matrices easier to inspect, and very suitable for topic detection \footnote{ Even though there are other techniques in topic detection, as for instance LDA (Latent Dirichlet Allocation), the NMF decomposition suites perfect for the kind of corpus we  have analyzed in this work (A detailed comparison of both, NMF and LDA methods could be found in \textbf{Supplementary Material}).}.
 \begin{equation}
@@
 \end{equation}
-Such as the resulting matrix \emph{H} has dimensions of number of documents per $k$ and matrix \emph{W} has dimensions of $k$ per number of terms, the number $k$ is therefore interpreted as the number of topics in the documents and it is a parameter that must be set before the factorization.
+Such as the resulting matrix \emph{H} has dimensions of number of documents by $k$ and matrix \emph{W} has dimensions of $k$ per number of terms, the number $k$ is therefore interpreted as the number of topics in the documents and it is a parameter that must be set before the factorization.
 In this work, we arbitrarily set $k=10$. We found this value to be a suitable one based on our knowledge of the corpus.
-\par The matrix \emph{H} is the representation of the documents in the topic-space.
-Each row is normalized to unit $l_1$-norm so that their components can be viewed as a degree of membership of a given document in the set of topics.
-In particular, the index of the largest component tells us which is the most representative topic of the document.
-On the other hand, \emph{W} gives the topics representation in the original term-space.
-The largest components of a row give the most representative words of each topic (called keywords) and therefore an insight of what the topic is talking about.
 Since the factorization of eq.(\ref{eq:nmf}) usually can not be made exactly, it is approximated by minimizing the reconstruction error, i.e.
 the distance between matrix \emph{M} and its approximated form $\tilde{M} = H \cdot W$.
-The \emph{NMF} factorization through the python module \emph{scikit-learn} \cite{scikit-learn}.
+The \emph{NMF} factorization was made through the python module \emph{scikit-learn} \cite{scikit-learn}.
 
-\par After performing NMF, we represent a time-dependent Media Agenda as a time evolving distribution of topics.
-The daily weight of the topic $i$, $W_i(day)$, is calculated following  eq.(\ref{eq:topic_weight}), where $l(j)$ is the number of words of the document $j$, $h_{ji}$ is the degree of membership of document $j$ on topic $i$, $d_j$ is the date of document $j$, and $\delta$ is the Kronecker delta.
-Providing by the fact that each document's vector can have all non-zero components, it is allowed that a document contributes to more than one topics' weight.
-In order to reduce noise, we apply a linear filter with a three day wide sliding window, and finally we normalize the temporal profiles in order to describe each newspaper agenda as a distribution over the topics' space which evolves over time.
+\par The matrix \emph{H} is the representation of the documents in the topic space.
+We normalized its rows to unit $l_1$-norm in order to view their components as a degree of membership of a given document in the set of topics.
+In particular, the index of the largest component tells us which is the most representative topic of the document.
+On the other hand, \emph{W} gives the topics representation in the original term space.
+The largest components of a row give the most representative words of each topic, which we call \emph{keywords}, and therefore an insight of what the topic is talking about.
+
+\par After performing NMF, we represent the time-dependent Media Agenda as a time evolving distribution of topics.
+We define $W_i(day)$ to be the daily weight of the topic $i$, which is calculated following the eq.(\ref{eq:topic_weight}), where $l(j)$ is the number of words of the document $j$; $h_{ji}$ is the degree of membership of document $j$ on topic $i$; $d_j$ is the date of document $j$; and $\delta$ is the Kronecker delta.
+Providing by the fact that each document vector can have all non-zero components, it is allowed that a document contributes to more than one topic weights.
+In order to reduce noise, we apply a linear filter with a three day wide sliding window, and finally we normalize the temporal profiles in order to describe each newspaper agenda as a distribution over the topics' space, which evolves over time.
 %This last normalization prevent us against the differences in the number of articles that each newspaper publishes.
@@
 
-\par The other side of time-dependent Media Agenda is to have some measure of the public interest about these topics.
-With this goal, we use  \emph{Google Trends} and \emph{Twitter} as a proxy of public interest by  looking for the same topics  in the same period of time.
-We take advantage of topics' keywords to make queries in the \emph{Google Trends}  tool and  into the advance search tool of Twitter  to get the relative weight searches and tweets in both platforms.
-\par In section \textbf{Results} we give a more detailed description of the keywords involved in the construction of the Google and Twitter Agendas.
+\par The other side of the Media Agenda is to have some measure of the public interests about its topics, by finally making up what we call the Public Agenda. 
+To achieve this goal, we take Google and Twitter as proxies of the public interests by looking for the same topics in the same period of time.
+We take advantage of the topic keywords in order to make queries into the \emph{Google Trends} tool and into the advance search tool of Twitter, and therefore to get the relative weight of searches and tweets in each respective platform.
+Therefore we describe the Public Agenda by describing, in an independent way, both the Google and Twitter Agendas. 
+In section \textbf{Results} we will give a more detailed description of the keywords involved in their construction.
 
-\subsection*{Normalized Shannon's H Information Entropy}
+\subsection*{Normalized Shannon Entropy ($H$)}
 
@@
 In order to do that, the first measure we emphasize is the concept of \emph{diversity of the attention}.
-The \emph{diversity} is a very important variable that must be taken into account when dealing with multiple issues \cite{boydstun2014importance}, due to the fact that it tells us how the attention is distributed across the different topics of discussion.
-As was proposed in \cite{boydstun2014importance}, we take the normalized Shannon's entropy as a very suitable way to quantify the diversity within our framework.
-\par The normalized Shannon's entropy $H[p]$ referred in eq.(\ref{eq:shannon_entropy}) give us a measure of how spread is a -discrete- distribution, taking the maximum value of $1$ when all outcomes are equally probable, and $0$ when there is just one possible outcome.
-This last case -or approximated ones- will be of particular interest for us because it tells about a topic which absorbs all the attention either from the Media or the Public, while the former shows an absolutely unbiased interest towards any of the topics.
+\emph{Diversity} is a very important variable that must be taken into account when dealing with multiple issues \cite{boydstun2014importance}, due to the fact that it tells us how the attention is distributed across the different topics of discussion.
+As was proposed in \cite{boydstun2014importance}, we take the normalized Shannon entropy as a very suitable way to quantify the diversity within our framework.
+\par The normalized Shannon entropy $H[p]$ referred in eq.(\ref{eq:shannon_entropy}) gives us a measure of how spread is a -discrete- distribution, taking the maximum value of $1$ when all outcomes are equally probable, and $0$ when there is just one possible outcome.
+This last case, or an approximated one, will be of particular interest for us because it tells about a topic which absorbs all the attention either from the Media or the Public, while the former shows an absolutely unbiased interest towards any of the topics.
 
@@
 
-\par While the diversity is a property of each distribution, a natural question that arise from comparing different distributions is how similar they are.
-For instance, we will be particularly interested in measuring the similarity between the Media and Public Agendas, because those dates when the similarity is low tell us about distant interests of the Media and the Public.
+\par While the diversity is a property of each distribution, a natural question that arises from comparing different distributions is how similar they are.
+For instance, we will be particularly interested in measuring the similarity between the Media and Public Agendas, because those dates when the similarity is low tell us about distant interests of the media and its audience.
 We proposed here to measure the similarity between distributions by the use of the Jensen-Shannon distance ($JSD$). 
 When the similarity of the distributions is low, the distance between them is high.
-\par The Jensen-Shannon distance ($JSD$) is a metric between distributions based on the Jensen-Shannon divergence ($JS_{Div}$) \cite{fuglede2004jensen}, which is in turn a symmetric version of the well-known Kullback-Leibler divergence ($D_{KL}$, eq.(\ref{eq:kl})).
-We recall that the $JSD$ has the advantage of being symmetric and also a well-defined distance, which make it conceptually easy to deal.
-As can be seen in eq.(\ref{eq:jensen_shannon_distance}) the $JSD$ between the distributions $P$ and $Q$ is simply the square root of the Jensen-Shannon divergence.
+\par The Jensen-Shannon distance ($JSD$) is a metric between distributions based on the Jensen-Shannon divergence ($JS_{Div}$) \cite{fuglede2004jensen}, which is in turn a symmetric version of the well-known Kullback-Leibler divergence $D_{KL}$ (eq.(\ref{eq:kl})).
+We recall that the $JSD$ has the advantage of being symmetric and also a well-defined distance, which makes it conceptually easier to deal with.
+As can be seen in eq.(\ref{eq:jensen_shannon_distance}), the $JSD$ between the distributions $P$ and $Q$ is simply the square root of the Jensen-Shannon divergence, where $M = \frac{P + Q}{2}$.
 
@@
 However, we still lack the definition of what a low diversity or a high distance are. 
-We face this problem by treating the measures of each observable as random samples from a population with unknown distribution and identifying those extreme values as outliers of the distribution. 
-In order to detect these outliers we follow the popular box-plot construction proposed by Tukey \cite{tukey1977exploratory}, which is a simple data-driven method and make no assumption about the distribution of the data.
-\par The box-plot construction is as follows: First a quartile division of the $N$ observations is made, by naming $Q1$ as the lower quartile, $Q2$ the median of the distribution, and $Q3$ the upper quartile.
+We face this problem by treating the measures of each observable as random samples from a population with unknown distribution, and identifying those extreme values as outliers of the distribution. 
+In order to detect these outliers we follow the popular box-plot construction proposed by Tukey \cite{tukey1977exploratory}, which is a simple data-driven method and has the advantage of making no prior assumption about the distribution of the data.
+However, it is important to remark that the constants involved in the outliers definition (see eq.(\ref{eq:fences})) is taken from applying this method on a normal distribution.
+\par In the box-plot construction a quartile division of the $N$ observations is proposed.
+We name $Q1$ as the lower quartile, $Q2$ the median of the distribution, and $Q3$ the upper quartile.
 Recall that $Q1$ ($Q3$) is defined to be the division where the 25th (75th) percent of the observations lies below (by definition, the median $Q2$ separates the distribution in two equal parts).
-On the other hand, the inter-quartile range $IQ$ is defined as $IQ = Q3 - Q1$.
+On the other hand, the inter-quartile range $IQ$ is defined to be $IQ = Q3 - Q1$.
 This is the range where the bulk of the data lies inside.
-\par We are not interesting in the visualization of the box-plot in its own but instead in its procedure to identify outliers.
-Therefore from the identification of the quartiles, new quantities called \emph{fences} are defined in eq.(\ref{eq:fences}): The \emph{lower inner fence} ($LIF$), the \emph{upper inner fence} ($UIF$), the \emph{lower outer fence} ($LOF$), and the \emph{upper outer fence} ($UOF$).
+We are not interesting in the visualization of the box-plot in its own but instead in its procedure to identify outliers.
+Therefore, from the identification of the quartiles, new quantities called \emph{fences} are defined in eq.(\ref{eq:fences}): The \emph{lower inner fence} ($LIF$), the \emph{upper inner fence} ($UIF$), the \emph{lower outer fence} ($LOF$), and the \emph{upper outer fence} ($UOF$).
 The fences can be interpreted as the limits of the distribution.
-We then have all the ingredients to label a point as an outlier: A point which lies above the upper inner fence is considered a \emph{mild outlier}, while a point that lies above the upper outer fence is considered an \emph{extreme outlier}.
-The same holds for the lower fences, i.e.
-if a point lies below the lower inner (outer) fences is considered as a mild (extreme) outlier \cite{natrella2010nist}.
 \begin{eqnarray}\label{eq:fences}
@@
 \end{eqnarray}
-\par We will indicate the proper fences in each figure either when the diversity or the distance is being analyzed.
-We will paid attention not only to those values labeled as outliers, but also to those that are next to any of the fences despite not being strictly defined as that.
+\par We then have all the ingredients to label a point as an outlier: A point which lies above the upper inner fence is considered a \emph{mild outlier}, while a point that lies above the upper outer fence is considered an \emph{extreme outlier}.
+The same holds for the lower fences, i.e.
+if a point lies below the lower inner (outer) fences is considered as a mild (extreme) outlier \cite{natrella2010nist}.
+We will indicate the proper fences in each figure either when the diversity or the distance is being analyzed.
+We will pay attention not only to those values labeled as outliers, but also to those that are next to any of the fences despite not being strictly defined as that.
 
@@
 
-\par We initially focus in the ten most important issues in the three months period corpus of news reported above.
-These ten topics, represented in the word clouds of figure \ref{fig:topics_wordclouds}, were reduced to seven (shown in the radar plot of the same figure) given the similarities found in, for instance, three of them that could be interpreted as part of the same macro-topic called \emph{Elections} and two others which were classified as part of a macro-topic called \emph{Missing person}.
+\par We initially focus on the ten most important issues from the three-month period corpus of news reported above.
+These ten topics are represented in the wordclouds of figure \ref{fig:topics_wordclouds}.
+Given our interpretation of the keywords found in three of them, we joined these topics as being part of the same macro-topic which we called \emph{Elections}.
+On the other hand, the same holds for other two topics which were classified as part of a macro-topic called \emph{Missing person}. 
+Therefore, the ten original topics were reduced to seven, which are pointed out in the radar plot of figure \ref{fig:topics_wordclouds}.
 The meaning of the topics or macro-topics is contextualized in the \textbf{Supplementary Material}.
-%\ref{sec:Context} of Supplementary Material. 
-\par Following the procedure described in the previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, in both its Google and Twitter derivations, as time evolving topic distributions.
+\par Finally, by following the procedure described in the previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, in both its Google and Twitter derivations, as time evolving distributions in a space of seven topics.
 
-\subsection*{The Public and Media agendas}
+\subsection*{The Media and Public Agendas}
 
-\par In figure \ref{fig:topics_wordclouds} we show a ten topic decomposition of the whole corpus using radar plots for the Media \textbf{MA} and Public agendas \textbf{PA} discriminated by \textbf{GT} (Google Trends) and \textbf{Tw} (Twitter).
-In this figure we also show the wordclouds of the keywords that define each topic, where the size of the word reflects its importance in the topic's definition.
-In green color, we point out the words involved in the Google Trends and Twitter  \footnote{Due to different characteristics in the search tool of Twitter, we adapted the queries employed here but preserving at least at we can the most important keywords.
-The queries employed by topic were: \\
-Elections: elecciones + cambiemos + kirchner + massa + randazzo \\
-Missing person: maldonado + otranto + gendarmer\'ia + desaparici\'on \\
-Former Planning minister: vido + desafuero + minnicelli + baratta \\
-Current President: macri + cgt + laboral +  triaca \\
-Social leader:  sala + cidh + tupac + amaru + pullen + llermanos + morales \\
-Prosecutor’s death: nisman + amia + memorandum + timerman +  bonadio \\
-Former Vice-President:  boudou + ciccone +  lijo + vandenbroele + carmona
-} queries in order to construct the Public Agenda.
-The queries employed are also specified in table \ref{table:gt_queries}.
-On the other hand, in table \ref{table:gt_all_correlation} we show the linear correlation between the topics' temporal profiles from the Public Agenda and their counterparts in the Media Agenda.
-
-\par We can observe that both Public Agendas ($GT$ and $Tw$) look similar in this representation, but they show specific differences with the Media Agenda.
-For instance, a greater interest of the audience in the topic \emph{Missing person} than the Media is observed, or inversely, a lower interest in the topic \emph{Prosecutor's death} takes place.
-However, this static representation is not able to show the complex dynamics of agenda's evolution and the importance of punctual and specific facts which can erase or amplify their differences.
+\par In figure \ref{fig:topics_wordclouds} we show a seven topic decomposition of the whole corpus using radar plots for the Media \textbf{MA} and Public agendas \textbf{PA} discriminated by \textbf{GT} (Google Trends) and \textbf{Tw} (Twitter).
+In this figure we also show the wordclouds of the keywords that define each of the ten original topics, where the size of the word reflects its importance in the topic definition.
+In green color, we point out the words involved in the Google Trends and Twitter queries in order to construct the Public Agenda.
+The queries employed are also specified in tables \ref{table:gt_queries} and \ref{table:tw_queries}.
+On the other hand, in table \ref{table:gt_all_correlation} we show the linear correlation between the topic temporal profiles from the Public Agenda and their counterparts in the Media Agenda.
+\par We can observe that both GT and Tw look similar in this representation, but they show specific differences with the Media Agenda.
+For instance, a greater interest of the audience in the topic \emph{Missing person} than the media is observed, or inversely, a lower interest in the topic \emph{Prosecutor's death} takes place.
+However, this static representation is not able to show the complex dynamics of the agendas evolution and the importance of punctual and specific facts which can erase or amplify their differences.
 
@@
 In  this figure  we also highlight some important events related to the dynamics of the topics.
-It is possible to appreciate how the main topic change in time and have a glance of the qualitative differences between agendas.
-In particular, it can be observed some differences between Public Agendas ($GT$ and $Tw$) that were not observed in the previous figure, as for instance, the persistence of main topics is longer in Twitter than in Google Trends.
-This is more evident at the end of the analyzed period, where topics discussed in Google Trends shows more  responsive to change in Media Agenda than in Twitter, suggesting the existence that the interaction between people is stronger in the analyzed social network.
-
-\par The linear correlations between same topics of $PA$ and $MA$ were also calculated.
-In all cases, we found that they are positive and statistically significant, as can be shown in table \ref{table:gt_all_correlation}.
-This can be interpreted as a validation of the topics found in the corpus and the keywords that describe it.
-Even though it is expected that the Media's and public's interest should generally follow a similar a pattern, mainly driven by  external events, we are interested in those periods where they significantly differ.
-However, a non positive (or a non significant) correlation may imply, besides the obvious conclusion of agenda's disengagement, that we could eventually fail in properly detect the keywords or features that describe a particular topic, so the Google Trends' or Twitter's pattern would not be able to reflect a similar behavior that its counterpart in the Media.
+It is possible to appreciate how the main topic changes in time and has a glance of the qualitative differences between the agendas.
+In particular, it can be observed some differences between the Public Agendas that were not observed in the previous figure, as for instance, the persistence of main topics is longer in Twitter than in Google Trends.
+This is more evident at the end of the analyzed period, where the topics discussed in Google Trends show more response to change in Media Agenda than in Twitter, maybe due to the existence of a different pattern of interaction in the social network, to which a deeper analysis could be devoted in future works.
+\par The linear correlations between the same topics of MA and PA were also calculated.
+In all cases, we found that the correlations are positive and statistically significantly, as it is shown in table \ref{table:gt_all_correlation}.
+We interpret this as a validation of the topics found in the corpus and the keywords that describe it.
+Even though we are particularly interested in those periods where the Agendas differ, it is expected that the media and public interests should generally follow a similar a pattern, mainly driven by external events
+A non positively (or a non significantly) correlation may imply, besides the obvious conclusion of agendas disengagement, that we can be eventually failing to properly detect the keywords or features that describe a particular topic, and therefore the comparison of the Google Trends or Twitter patterns with their counterpart in the Media Agenda would be wrong.
 
@@
 Is the degree of dominance of a given topic in the Media Agenda reflected in the Public Agenda?
-In order to answer such kind of questions we quantify the diversity of the Agendas through the normalized Shannon's entropy $H$, which was introduced in section \textbf{Material and Methods}.
+In order to answer such kind of questions we quantify the diversity of the agendas through the normalized Shannonentropy $H$, which was introduced in section \textbf{Material and Methods}.
 \par In figure \ref{fig:shannon_entropy_agendas} we can see the value of $H$ as a function of time for the three agendas.
-It is important to pay attention to those periods of time where the diversity is lower than usual.
-This effect is notoriously more pronounced in the Public Agenda giving by \textbf{GT} and, in particular, in four specific days  where  four local minima of Shannon's entropies can be detected.
-Three of them are outliers as defined in section \textbf{Material and Methods} \ref{sec:MatMeth}, two of them from \textbf{GT} and one from \textbf{Tw}.
-The other one is not an outlier but a pronounced minima and therefore a point of interest in this description.
+It is important to pay attention to those periods of time when the diversity is lower than usual.
+This effect is notoriously more pronounced in the Public Agenda giving by GT, and in particular in four specific days when four local minimums of the Shannon entropy can be detected.
+Three of them are outliers as defined in section \textbf{Material and Methods}, two of them from GT and one from Tw.
+The other one has been not identified as an outlier but it is a pronounced minimum and therefore a point of interest in our description.
 
-\par A lower value in the agenda's diversity is due to the fact that the most important topic attracts practically all the attention of the Public and the Media, collapsing the agenda to one of the issues involved.
+\par A lower value in the agenda diversity is due to the fact that the most important topic attracts practically all the attention of the public and the media, collapsing the agenda to one of the issues involved.
 In the radar plots included in figure \ref{fig:shannon_entropy_agendas} we can see how two of these outliers (\textbf{a} and \textbf{d}) belong to the topic \emph{Elections}.
-They are related to the primary and general legislative elections that took place in August 13th and October 22th respectively.
+They are related to the primary and general legislative elections that took place in August 13th and October 22nd respectively.
 In all the agendas these points were detected as outliers except point (d) in Twitter Agenda.
 Why is that?
-The radar plot of the Twitter agenda for this day displays an association between the topic \emph{Elections} and the \emph{Current President}, decreasing the important of this topic.
-Discussions in Twitter about elections appear also in point (c), when the other agendas seems to be more diverse. 
-On the other hand, and despite not being classified as outlier, we also focus in point (b) because Shannon's Entropy of $GT$ Agenda displays a minimum (collapsing agenda) which is not corresponded neither in the Media nor in the Twitter Agendas.
-Crawling in the context, we see that it belongs to the topic \emph{Missing person} and this date correspond to the rally that took place one month after the disappearance of \emph{Santiago Maldonado} (see \textbf{Supplementary Material}).
-We  would like to emphasize the discussion about this topic (\emph{Missing person}) because its dynamics show interesting features, as we will show bellow.
+The radar plot of the Twitter agenda for this day displays an association between the topic \emph{Elections} and the \emph{Current President}, decreasing the importance of this topic.
+Discussions in Twitter about elections appear also in point (c), when the other agendas seem to be more diverse. 
+On the other hand, and despite not being classified as outlier, we also focus in point (b) because the Shannon Entropy in the Google Agenda displays a minimum (collapsing agenda) which is not corresponded neither in the Media nor in the Twitter Agendas.
+Crawling in the context, we see that it belongs to the topic \emph{Missing person} and this date corresponds to the rally that took place one month after the disappearance of \emph{Santiago Maldonado} (see \textbf{Supplementary Material}).
+We  would like to emphasize the discussion about this topic (\emph{Missing person}) because its dynamics show interesting features, as we will show below.
 
-\par From the measure of $H$ we have also observed that the median of the Public Agenda diversity is statistical significant lower than the Media Agenda's one.
-Specifically $H_{GT} = 0.73$ and $H_{Tw} = 0.74$ are statistical significant lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
-However from figure \ref{fig:shannon_entropy_agendas} we can see that \textbf{GT} shows more abrupt dropouts in the diversity in response to specific events.
-From all this analysis we  can conclude that given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus in the most important topics than Media can do, maybe due to editorial decisions.
+\par From the measure of $H$ we have also observed that the median of the Public Agenda diversity is statistical significant lower than the observed in the Media Agenda.
+Specifically $H_{GT} = 0.73$ and $H_{Tw} = 0.74$ are statistically significantly lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
+However, from figure \ref{fig:shannon_entropy_agendas} we can see that GT shows more abrupt dropouts in the diversity in response to specific events.
+From all this analysis we  can conclude that given a finite set of topics, \textbf{the Public Agenda is less diverse than the Media Agenda}, because the public seems to focus on the most important topics than the media can do, maybe due to editorial decisions.
 
-\subsubsection*{Distance between Media and Public Agenda's }
+\subsubsection*{Distance between Media and Public Agendas}
 
-\par Given our descriptions of the Agendas as time-evolving distributions, we can  compare them by computing the Jensen-Shannon distance.
-In this context, outliers in selected dates will correspond to divergences between Public and Media Agenda, i.e., specific events where the public interest do not match with media offer.
-In figure \ref{fig:jensen_shannon_gt} we show the Jensen-Shannon distance between Media and Publics Agendas as a function of time.
-We focus in three points that seems to be relevant enough.
-In all cases, the topic distributions at that particular dates displayed by  the radar plots show that the increment in the distance between agendas is due to a greater interest of public opinion in the topic \emph{Missing person}.
+\par Given our descriptions of the agendas as time-evolving distributions, we can  compare them by computing the Jensen-Shannon distance.
+In this context, outliers in selected dates will correspond to divergences between the Media and Public Agenda: Specific events when the public interests do not match with media offer.
+In figure \ref{fig:jensen_shannon_gt} we show the Jensen-Shannon distance between Media and Public Agendas as a function of time.
+We focus in three points that seem to be relevant enough.
+In all cases, the topic distributions at that particular dates displayed by  the radar plots show that the increment in the distance between agendas is due to a greater interest of public opinion in the \emph{Missing person} topic.
 
-\par Points \textbf{(c)} and \textbf{(d)} show that both the Public and the Media highlight this topic, but the Media do not disregard other topics, so the corresponding distance between them can be interpreted as lack of the diversity in Public Agenda as discussed in the last section.
+\par Points \textbf{(c)} and \textbf{(d)} show that both the public and the media highlight this topic, but the media do not disregard other topics, so the corresponding distance between them can be interpreted as lack of diversity in Public Agenda as discussed in the last section.
 
 \par On the other hand,  points \textbf{(a)} (we take this point due to be a local maximum despite not being an outlier) and \textbf{(b)}  show a major  interest of the public in the topic \emph{Missing person} which it is not reflected in the Media.
-In figure \ref{fig:all_agenda} we can see that this topic becomes the most important in public's interest (both \textbf{GT} and \textbf{Tw}) days before that  it happen in the Media Agenda.
-It can be associates  with a social networks (like Facebook and Twitter) campaign  in favor  of the appearance of \emph{Santiago Maldonado} (``The missing person") that took place on  August 26th.
-This campaign was massive and  initially underestimated by the main Media outlets in Argentina (see \textbf{Supplementary Material}).
+In figure \ref{fig:all_agenda} we can see that this topic becomes the most important in public interests (both in GT and Tw) days before that it happens in the Media Agenda.
+This fact can be associated  with a social networks (like Facebook and Twitter) campaign  in favor  of the appearance of \emph{Santiago Maldonado} (``The missing person") that took place on  August 26th.
+This campaign was massive and  initially underestimated by the main media outlets in Argentina (see \textbf{Supplementary Material}).
 
@@
 we can't say, for instance, that in this case the Public Agenda set the Media Agenda.
-Finally, it is important to say that the Jensen-Shannon distance, in conjunction with the measurement of agenda diversity given by the Shannon entropy, give an insight of independent behavior, in certain particular dates,  of the Public and the Media.
-Its identification can be a starting point to study the Media reaction to a change in audience's interests.
+Finally, it is important to say that the Jensen-Shannon distance, in conjunction with the measurement of agenda diversity given by the Shannon entropy, give an insight of independent behavior, in certain particular dates,  of the public and the media.
+Its identification can be a starting point to study the media reaction to a change in audience interests.
 
-\subsection*{Agenda bias in different Media outlets}
+\subsection*{Agenda bias in different media outlets}
 
 \par In this section we leave aside the Public Agenda as an unified corpus and we study the composition and evolution of the Media Agenda of each media outlet. 
-In figure \ref{fig:news_agenda} we show the bump charts corresponding to each of the analyzed newspaper analogously to figure \ref{fig:all_agenda}.
-The topics are the same introduced in the wordclouds of figure \ref{fig:topics_wordclouds}, but when computing the topics' weights,  the articles are discriminated by newspaper. 
+In figure \ref{fig:news_agenda} we show the bump charts corresponding to each of the analyzed newspapers analogously to figure \ref{fig:all_agenda}.
+The topics are the same introduced in the wordclouds of figure \ref{fig:topics_wordclouds}, but when computing the topic weights, the articles are discriminated by newspaper. 
 We also show the radar plots with the average distribution, as made in figure \ref{fig:topics_wordclouds}.
 
-\par In figure \ref{fig:news_agenda} we can qualitative have a glance of the  differences between the newspapers' agendas.
+\par In figure \ref{fig:news_agenda} we can qualitative have a glance of the differences between the newspaper agendas.
 For instance, we can see how the newspaper called \emph{P\'agina 12} gave more importance to the topics \emph{Missing person} and \emph{Social leader}, while it reduces to minimum the coverage of the topic  \emph{Former Planning minister} as the others did.
 
-\par In other to detect significative bias coverage of a given newspaper, we again calculate the Jensen-Shannon distance, but between the individual newspapers agenda and the Media Agenda.
+\par In other to detect significant bias coverage of a given newspaper, we again calculate the Jensen-Shannon distance, but between the individual newspapers agenda and the Media Agenda.
 Note that this is the distance between the distributions of figure \ref{fig:news_agenda} and the top panel of figure \ref{fig:all_agenda}. 
@@
 
-\par The point \textbf{(a)} corresponds  to the first news of the Santiago Maldonado's disappearance  reported by \emph{P\'agina 12} before the primary elections and the point \textbf{(c)} corresponds to  the two months' rally after the disappearance  (see \textbf{Supplementary Material}).
-Another singularity of point \textbf{(c)} corresponds to a greater coverage of \emph{P\'agina 12} in the topic \emph{Social leader} where the others media outlets seem to be more interested in the topic \emph{Former Vice-President}.
+\par Point \textbf{(a)} corresponds  to the first news the disappearance of Santiago Maldonado, reported by \emph{P\'agina 12} before the primary elections, and point \textbf{(c)} corresponds to  the two months' rally after the disappearance  (see \textbf{Supplementary Material}).
+Another singularity of point \textbf{(c)} corresponds to a greater coverage of \emph{P\'agina 12} in the topic \emph{Social leader} while the other media outlets seem to be more interested in the topic \emph{Former Vice-President}.
 
@@
 \par From panel (a) of figure \ref{fig:topics_temporal_profiles}, we can see the larger coverage of \emph{P\'agina 12} in comparison to other newspapers at the beginning of the period.
-We can, for instance, quantify this difference calculating  the median of the signals.
-If we focus in the period between July 31th and August 27th, the median of the topic's relative weight for \emph{P\'agina 12} is roughly 0.14 and this is statistically significant larger ($p < 10^{-7}$) than other medians, which are lower than 0.05.
-Analyzing the same period, but in panel (b), we again can show that the median in \emph{P\'agina 12}, which is roughly 0.01, is lower than the others, which oscillate around 0.05 ($p<10^{-3}$)
+For example, we can quantify this difference calculating  the median of the signals.
+If we focus in the period between July 31st and August 27th, the median of the topic relative weight in \emph{P\'agina 12} is roughly 0.14 and this is statistically significantly larger ($p < 10^{-7}$) than other medians, which are lower than 0.05.
+Analyzing the same period, but in panel (b), we again can show that the median in \emph{P\'agina 12}, which is roughly 0.01, is lower than the others, which oscillate around 0.05 ($p<10^{-3}$).
 This quantification is proposed as method of studying coverage bias in the context of the methodology implemented in our work.
 
-\par Finally, in figure \ref{fig:topics_temporal_profiles} we also show wordclouds of topic's keywords highlighting the more frequently mentioned in each newspaper and filtering the common words to all newspapers.
-Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represi\'on} (repression) when \emph{P\'agina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (Fern\'andez de Kirchner, former president) which is employed by all newspapers except \emph{P\'agina 12} when they  talk about the topic \emph{Former Planning minister} (see \textbf{Supplementary Material}).
-We think that a more deeply study of topics' keywords could be a first approximation in the study of framing, which will constitute the core of futures works.
+\par Finally, in figure \ref{fig:topics_temporal_profiles} we also show the topic keywords wordclouds, highlighting the most frequently mentioned in each newspaper and filtering the common words to all newspapers.
+Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represi\'on} (repression) when \emph{P\'agina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (\emph{Fern\'andez de Kirchner}, former president) which is employed by all newspapers except \emph{P\'agina 12} when they  talk about the topic \emph{Former Planning minister} (see \textbf{Supplementary Material}).
+We think that a deeper study of the topic keywords could be a first approximation in the study of framing, which will constitute the core of futures works.
 
-\subsection*{A brief discussion about  Agenda-Setting}
+\subsection*{A brief discussion about agenda-setting}
 \label{sec:who_sets}
 
-\par In a world where social media exists and the feedback between a Media and its audience is common currency, nowadays the idea that the Media sets the agenda and the audience blindly follows it (as it's seemed to be suggested in the original work of McCombs) is too naive.
-Based in the data analyzed above, the behavior of the Media  and Public Agendas, either by looking at Google Trends or Twitter, shows periods of strong similarity  (specially in the presence of an unexpected event) and periods of disengagement.
+\par In a world where social media exist and the feedback between the media and audience is common currency, nowadays the idea that the Media set the agenda and the audience blindly follows it (as it's seemed to be suggested in the original work of McCombs) is too naive.
+Based on the data analyzed above, the behavior of the Media and Public Agendas, either by looking at Google Trends or Twitter, shows periods of strong similarity  (specially in the presence of an unexpected event) and periods of disengagement.
 Therefore, it is not trivial to establish a causal relationship between agendas, specially when they are represented as evolving in time topic distribution as we did in this work.
@@
 \begin{itemize} 
-\item It caused a great impact in either the Media and the audience
+\item It caused a great impact in both the media and the audience
 \item  its coverage fully deploys along the time lapse analyzed in this manuscript (see \textbf{Supplementary Material}).
@@
 
-\par In figure \ref{fig:Maldonado_setagenda} we show the topic's relative weight from the Public and Media Agendas.
-After the initial coverage, the agendas seem to differentiate around August 15th, when topic started to became more important in the Public Agenda than in the Media one.
-Around August 24th, the topic abruptly increase in public's interest while the reaction in the Media is slower, showing a significant peak in the plot of the discrete difference (panel (b)).
+\par In figure \ref{fig:Maldonado_setagenda} we show the topic relative weight from the Public and Media Agendas.
+After the initial coverage, the agendas seem to differentiate around August 15th, when topic started to become more important in the Public Agenda than in the Media one.
+Around August 24th, the topic abruptly increases in the audience interests while the reaction in the media is slower, showing a significant peak in the plot of the discrete difference (panel (b)).
 This date is very close to August 26th, when a campaign in social media took place.
@@
 
-\par Is this a case of reverse agenda-setting, i.e, when the audience set the Media Agenda? 
-After all,  the audience get involved about this topic by the Media, so how was the coverage before those events?
+\par Is this a case of reverse agenda-setting \cite{russell2014dynamics}, i.e, when the audience set the Media Agenda? 
+After all, the audience gets involved about this topic by the media, so how was the coverage before those events?
 We can answer these questions by calculating the cumulative coverage of this topic since the first events took place.
-This measure can be seen as the numerical integrate of the temporal profiles of figure \ref{fig:topics_temporal_profiles} between the initial date and the current date. 
-It is interesting to note that the newspaper responsible to accumulate coverage during the initial stage was the minority one: \emph{P\'agina 12}. 
-Our interpretation about the setting agenda dynamics of this particular topic is the following: A small newspaper (\emph{P\'agina 12}) gives great coverage to this topic; it is amplified  by public in the social networks and also expressed  by reiterative Google searches.
-Then the rest of the Media  pay attention to this subject and it becomes an important topic in the Media Agenda.
-This interpretation try to catch in a qualitative way how the information flow was in this specific topic.
-On the other hand, behind this interpretation there are two important facts that must be mentioned: First, the disappearance of a person is a very sensible theme for the Argentinian society, and second, there are political reasons in why \emph{P\'agina 12} was particularly interested in cover this topic while the other Media did not follow this interest (see \textbf{Supplementary Material}).
+This measure can be seen as the numerical integration of the temporal profiles of figure \ref{fig:topics_temporal_profiles} between the initial date and the current date. 
+It is interesting to note that the newspaper responsible for accumulating coverage during the initial stage was the minority one: \emph{P\'agina 12}. 
+Our interpretation about the setting agenda dynamics of this particular topic is the following: A small newspaper (\emph{P\'agina 12}) gives great coverage to this topic; the topic is then amplified by public in the social networks and it is also expressed  by reiterative Google searches.
+Then, the rest of the Media pays attention to this subject and it becomes an important topic in the Media Agenda.
+This interpretation tries to catch in a qualitative way how the information flow was in this specific topic.
+On the other hand, behind this interpretation there are two important facts that must be mentioned: First, the disappearance of a person is a very sensitive theme for the Argentinian society, and second, there are political reasons why \emph{P\'agina 12} was particularly interested in cover this topic while the other media did not follow this interest (see \textbf{Supplementary Material}).
 
@@
 
-\par The  Mass media play a fundamental role in opinion formation and therefore it's of vital importance to have an accurate  quantitative description of the Media  and Public Agenda and their relationship in the framework of Agenda Setting theory.
-In this work, through the implementation of a topic detection algorithm we describe the Agenda of the Media as a distribution which evolves in time and which is defined in a topic's space which emerges from the analysis of the corpus.
-This gave us an insight of how we can construct and follow the Public's interests, the Public Agenda, in order to compare with the Media Agenda, i.e.
-Media interests.
+\par The mass media play a fundamental role in opinion formation and therefore, it's of vital importance to have an accurate  quantitative description of the Media  and Public Agenda and their relationship in the framework of agenda-setting theory.
+In this work, through the implementation of a topic detection algorithm we describe the Media Agenda as a distribution which evolves in time and which is defined in a topic space which emerges from the analysis of the corpus.
+This gave us an insight of how we can construct and follow the audience interests, i.e the Public Agenda, in order to compare with the media interests.
 
-\par Given the Agendas, we found that the Public one is usually less diverse than the Media, showing that when there is a very attractive topic, the audience focus on this one, meanwhile the Media keeps certain degree of diversity.
-On the other hand, the measurement of distances between Agendas can be employed to rapidly detect periods when the Public may have an independent behavior respect to the Media.
-The methodology implemented here also allow us to detect coverage bias in newspapers and gave us a first approximation in the theory of framing.
-\par We hope that some of the elements studied here will give us insights at the time of proposing a mathematical model about Mass Media and Public interaction.
-Future works may include a more systematic study and its extension to international Media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitative analysis about causality.
+\par Given the Agendas, we found that the Public one is usually less diverse than the Media, showing that when there is a very attractive topic, the audience focuses on this one, meanwhile the media keep certain degree of diversity.
+On the other hand, the measurement of distances between agendas can be employed to rapidly detect those periods when the public may have an independent behavior respect to the media.
+The methodology implemented here also allowed us to detect coverage bias in newspapers and gave us a first approximation in the theory of framing.
+\par We hope that some of the elements studied here will give us insights at the time of proposing a mathematical model about the interaction between mass media and audience.
+Future works may include a more systematic study and its extension to international media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitative analysis about causality.
 
@@
 
-\par We provide here a more detailed explanation of the topics discussed among this work.
-The ideology of the media in Argentina expresses the highly polarized political climate observe in Argentinian society.
+\par We provide here a more detailed explanation of the topics discussed within this work. The topics belong to the period between July 31th and November 5th, 2017.
+The ideology of the media in Argentina expresses the highly polarized political climate observed in Argentinian society.
 During the administration of \emph{Cristina Fern\'andez de Kirchner} (2007-2015), the government maintained a conflict with several news organizations.
-It led media such as \emph{Clar\'in}, \emph{La Naci\'on} and the portal news \emph{Infobae} to be very critics of the \emph{Fern\'andez}'s administration, emphasizing the allegations of corruption related to it as can be seen in the importance given to the topics \emph{Former Planning minister} and \emph{Former Vice-President}.
-On the other hand, \emph{P\'agina 12} has a opposite ideological inclination, supporting the former administration of \emph{Cristina Kirchner} and therefore being very critical with the current \emph{Mauricio Macri}'s administration, doing special emphasis on issues related to human rights, as can be again observed in the coverage given to the topics \emph{Social leader} and \emph{Missing person}.
+It led the media such as \emph{Clar\'in}, \emph{La Naci\'on} and the news portal \emph{Infobae} to be very critics of the \emph{Fern\'andez}'s administration, emphasizing the allegations of corruption related to it, as can be seen in the importance given to the topics \emph{Former Planning minister} and \emph{Former Vice-President}.
+On the other hand, \emph{P\'agina 12} has an opposite ideological inclination, supporting the former administration of \emph{Cristina Kirchner} and therefore being very critical with the current \emph{Mauricio Macri}'s administration, doing special emphasis on issues related to human rights, as can be again observed in the coverage given to the topics \emph{Social leader} and \emph{Missing person}.
 
 \subsubsection*{\emph{Elections}}
-\par Two legislative elections were celebrated during the period in great part of the Argentina: Primary elections on August 13th and the general elections on October 22th. 
+\par Two legislative elections were celebrated during the period in great part of Argentina: Primary elections on August 13th and the general elections on October 22nd, 2017. 
 A special focus was put on the elections in the Buenos Aires province, where the former President \emph{Cristina Fern\'andez de Kirchner} participated as a senator candidate representing the alliance \emph{Unidad Ciudadana}, confronting \emph{Cambiemos}, which is the alliance of the current President \emph{Mauricio Macri} and the current governor of Buenos Aires province \emph{Maria Eugenia Vidal}.
@@
 \subsubsection*{Current President}
-\par \emph{Mauricio Macri} is the current Argentinian President, since December 2015. 
-Most articles in political sections are logically devoted to him under different contexts.
-However, it is important to point out that during the analyzed period, and specially after the general elections of October $22^{th}$, a controversial labour reform promoted by the government was been discussing.
+\par \emph{Mauricio Macri} is the current Argentinian President since December 2015. 
+Most of the articles in political sections are logically devoted to him under different contexts.
+However, it is important to point out that during the analyzed period, and specially after the general elections of October 22nd, 2017, a controversial labour reform promoted by the government was being discussed.
 
 \subsubsection*{\emph{Missing Person}}
-\par \emph{Santiago Maldonado} vanished on August 1st after a minor clash between the Gendarmerie (Border Guards) and a group of Mapuches (Patagonian native population), which recognize as themselves the original population of an area in the Patagonia.
-Since that event, the \emph{Mauricio Macri}'s administration was accused by several people as the responsible of a \textbf{forced disappearance}. 
-\par A very massive campaign in social media took place on August $26^{th}$, under the motto ``Where is Santiago Maldonado?", followed by two massive protest marches to the \emph{Plaza de Mayo} that took place on September 1st and October 1st, which the first one had a great repercussion due to several incidents that took place during the march.
-\par The body of \emph{Santiago Maldonado} was found on $17^{th}$ October in the \emph{Chubut} river, near the place where he was seen the last time, and the autopsy report told that \emph{Santiago Maldonado} had died from ``asphyxia after being submerged", with no injuries on his body.
-However the responsibility of the current administration is still being discussed.
+\par \emph{Santiago Maldonado} vanished on August 1st, 2017 after a minor clash between the Gendarmerie (Border Guards) and a group of Mapuches (Patagonian native population), which recognize themselves as the original population of an area in the Patagonia.
+Since that event, the \emph{Mauricio Macri}'s administration was accused by several people as the responsible for a \textbf{forced disappearance}. 
+\par A very massive campaign in social media took place on August 26th, 2017 under the motto ``Where is Santiago Maldonado?", followed by two massive protest marches to the \emph{Plaza de Mayo} that took place on September 1st and October 1st, of which the first one had a great repercussion due to several incidents that took place during the march.
+\par The body of \emph{Santiago Maldonado} was found dead on October 17th, 2017 in the \emph{Chubut} river, near the place where he was seen the last time, and the autopsy report told that \emph{Santiago Maldonado} had died from ``asphyxia after being submerged", with no injuries on his body.
+However, the responsibility of the current administration is still being discussed.
 
@@
 \par \emph{Julio de Vido} was the Planning minister during the administration of \emph{N\'estor Kirchner} and \emph{Cristina Fern\'andez de Kirchner} (2003-2015).
-In 2015, he was elected to integrate the Chamber of Deputies, which finally voted to strip \emph{De Vido} of his congressional immunity over corruption allegations and was immediatly jailed on October $27^{th}$.
+In 2015, he was elected to integrate the Chamber of Deputies, which finally voted to strip \emph{De Vido} of his congressional immunity over corruption allegations and was immediatly jailed on October 27th, 2017.
 
 \par \emph{Amado Boudou} was the Vice-President of the \emph{Cristina Kirchner}'s administration.
-\emph{Boudou} was arrested on November 3th on charges including money-laundering and hiding undeclared assets.
+\emph{Boudou} was arrested on November 3rd, 2017 on charges including money-laundering and hiding undeclared assets.
 
@@
 She faces allegations of embezzlement related to government funding for housing projects managed by T\'upac Amaru, her social organization.
-Sala accused the government of ``violating her human rights", and several people think that she is a political prisoner of the \emph{Mauricio Macri} administration.
+Sala accused the government of ``violating her human rights", and several people think that she is a political prisoner of the \emph{Mauricio Macri}'s administration.
 
-\par \emph{Alberto Nisman} was a special prosecutor who were investigating the 1994 terror attack on the Argentine Israeli Mutual Association (AMIA), until his suspicious death on January 2015.
+\par \emph{Alberto Nisman} was a special prosecutor who were investigating the 1994 terror attack on the Argentine Israeli Mutual Association (AMIA), until his suspicious death in January 2015.
 During the period analyzed in this work, a team of experts led by the Gendarmerie (Border Guard) concluded that late prosecutor's death may have been a case of murder, not suicide.
@@
 \par Naturally the topics found with LDA may not coincide with the NMF ones.
-However, one expects that the corpus under study displays some degree of  robustness  when considering different topic model.
+However, one expects that the corpus under study displays some degree of  robustness  when considering different topic models.
 On the other hand, as was discussed in \cite{o2015analysis}, NMF can be a more suitable topic modeling method in certain domains, in the way that it produces more coherent topics, while LDA tends to return higher levels of generality and redundancy.
@@
 It's important to note that if two terms have no co-occurrences, the contribution to the summation is zero, and if these ones appear only together the contribution is one.
-A topic with higher coherence is a topic where the terms that define it co-occurrence frequently.
+A topic with higher coherence is a topic where the terms that define it co-occur frequently.
 
@@
 
-\par We perform a decomposition into 10 topics using LDA with the python module \emph{gensim} \cite{rehurek_lrec}, which allow us to modify the number of times the corpus is read, improving the coherence of the topics.
+\par We perform a decomposition into 10 topics using LDA with the python module \emph{gensim} \cite{rehurek_lrec}, which allows us to modify the number of times the corpus is read, improving the coherence of the topics.
 Unlike to what we see with NMF, the LDA's performance depends strongly on the initial condition of the algorithm.
@@
 The association between topic models was simply made by looking at the topics which share common keywords.
-As can be seen from the figure and the table \ref{table:correlation_nmf_lda}, those LDA topics which can be linked to NMF ones or to a combination of these, show a temporal profile highly correlated.
+As can be seen from figure \ref{fig:temporal_profiles_nmf_lda} and table \ref{table:correlation_nmf_lda}, those LDA topics which can be linked to NMF ones or to a combination of these, show a temporal profile highly correlated.
 
@@
 \includegraphics[width = \textwidth]{Fig1.pdf}
-\caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic (then collapsed to seven) distribution and their corresponding wordclouds.} The Public Agenda is represented either by Google Trends (GT) and Twitter (Tw).
-Topics names are introduced together with the wordclouds containing the most important keywords involved in the definition of each topic.
-In green color we show the keywords used to define the topics in the Google Trends and Twitter queries (see table \ref{table:gt_queries}) and therefore in our construction of the Public Agenda.}
+\caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic (then collapsed to seven) distribution and their corresponding wordclouds.} The Public Agenda is represented both by Google Trends (GT) and Twitter (Tw).
+Topic names are introduced together with the wordclouds containing the most important keywords involved in the definition of each topic.
+In green color we show the keywords used to define the topics in the Google Trends and Twitter queries (see tables \ref{table:gt_queries} and \ref{table:tw_queries}) and therefore in our construction of the Public Agenda.}
 \label{fig:topics_wordclouds}
@@
 \textbf{I}: Amado Boudou's detention (Former vice-president).
-A more detailed explanation is given in section \ref{sec:Context}.}
+A more detailed explanation is given in section \textbf{Supplementary Material}.}
 \label{fig:all_agenda}
@@
 \includegraphics[height=0.7\textheight]{Fig3.pdf}
-\caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda show a less diverse behavior than the Media Agenda as can be seen in the top figure.
+\caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda shows a less diverse behavior than the Media Agenda as can be seen in the top figure.
 The horizontal lines correspond to the lower inner fences of each signal in order to identify outliers.
-The related radar plots show  the agenda at the selected days where the time series exhibit dropouts (points a-d), indicating that the most important topic catches the most public's attention.
+The related radar plots show  the agenda at the selected days where the time series exhibit dropouts (points a-d), indicating that the most important topic catches most of the public's attention.
 \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.
@@
 \includegraphics[height = 0.7\textheight]{Fig4.pdf}
-\caption{\textbf{Jensen Shannon distance between the Media and Public Agendas as a function of time} (with upper inner fences pointed out).
-Larger distances are due to a greater interest of the audience in the topic \emph{Missing person} which  decrease the interest in other topics.
-On the other side the Media Agenda still keeps certain degree of diversity.
+\caption{\textbf{Jensen-Shannon distance between the Media and Public Agendas as a function of time} (with upper inner fences pointed out).
+Larger distances are due to a greater interest of the audience in the topic \emph{Missing person} which  decreases the interest in other topics.
+On the other side, the Media Agenda still keeps certain degree of diversity.
 \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
@@
 \includegraphics[width = \textwidth]{Fig5.pdf}
-\caption{\textbf{Bump charts of newspapers' Agenda and radar plot of the average distributions.} The figure shows, in a qualitative way, the bias in the different newspaper's agendas.
+\caption{\textbf{Bump charts of newspaper agendas and radar plot of the average distributions.} The figure shows, in a qualitative way, the bias in the different newspaper agendas.
 For instance, the greater interest of \emph{P\'agina 12 (P12)} in the \emph{Missing person} topic and its slightly lower coverage in the \emph{Former Planning minister} respect to the other newspapers.}
@@
 \includegraphics[width = \textwidth]{Fig6.pdf}
-\caption{\textbf{Jensen-Shannon distance between the newspapers agenda and the Media Agenda as a function of time}.
-\emph{P\'agina 12} shows the more different behavior, motivated again by its interest in the \emph{Missing person} and \emph{Social leader} topics as can be seen in the radar plots which belongs to points (a) and (c).
-The anomalous behavior of \emph{Infobae} at pint (b) is due to few articles around that date in our database, therefore we ignore its radar plot.
+\caption{\textbf{Jensen-Shannon distance between the newspaper agendas and the Media Agenda as a function of time}.
+\emph{P\'agina 12} shows the most different behavior, motivated again by its interest in the \emph{Missing person} and \emph{Social leader} topics, as can be seen in the radar plots which belong to points (a) and (c).
+The anomalous behavior of \emph{Infobae} at point (b) is due to few articles around that date in our database, therefore we ignore its radar plot.
 \textbf{E}: Elections; \textbf{FPm}: Former Planning minister; \textbf{FVP}: Former Vice-President; \textbf{Sl}: Social leader; \textbf{Pd}: Prosecutor's death; \textbf{Mp}: Missing person; \textbf{CP}: Current President.}
@@
 \includegraphics[width = \textwidth]{Fig7.pdf}
-\caption{\textbf{Relative weight of the topics (a) \emph{Missing person}, and (b) \emph{Former Planning Minister}, and their corresponding word-clouds of frequent newspapers' keywords}.
+\caption{\textbf{Relative weight of the topics (a) \textit{Missing person}, and (b) \textit{Former Planning Minister}, and their corresponding wordclouds of frequent newspaper keywords}.
 We interpreted the differences shown in given periods as an indicator of coverage bias.
@@
 In the word-clouds, we show which of the defining words are more frequently used by the corresponding newspaper.
-Most of them are less informative, but other seems to represent a first approximation in the study of framing.}
+Most of them are less informative, but others seem to represent a first approximation in the study of framing.}
 \label{fig:topics_temporal_profiles}
@@
 \includegraphics[width = \textwidth]{Fig8.pdf}
-\caption{\textbf{Agenda setting direction in Missing person's topic?}
-The temporal profiles of figure (a) show that the Public and Media agenda seem to differentiate around August 15th (vertical grey line (1)) and the Public increase abruptly its interest in the topic around August 24th (grey line (2)).
+\caption{\textbf{Can we guess the agenda-setting direction in the Missing person topic?}
+The temporal profiles of figure (a) show that the Public and Media agenda seem to differentiate around August 15th (vertical grey line (1)) and the Public increases abruptly its interest in the topic around August 24th (grey line (2)).
 It can be seen also in figure (b), where the discrete differences were computed.
-With the computing of the cumulative sum of figure \ref{fig:topics_temporal_profiles} and figure (a), represented as a bump chart in figure (c), we suggest that the topic was first set by \emph{P\'agina 12} and then the Public's interest cause the coverage of the other Media.
+With the computing of the cumulative coverage of figure \ref{fig:topics_temporal_profiles} and figure (a), represented as a bump chart in figure (c), we suggest that the topic was first set by \emph{P\'agina 12} and then the audience's interest cause the coverage of the other media.
 }
@@
 \caption{Queries used in Google Trends in order to build the Public Agenda.}
-\begin{tabular}{ll}
-Topic's name & Google Trends query \\ \hline
+\begin{tabular}{l|p{7.5cm}}
+Topic name & Google Trends query \\ \hline
 Elections & elecciones + cambiemos + cristina kirchner + massa + randazzo \\
@@
 \begin{table}[h!]
-\caption{Correlation between the topics' temporal profiles of the Public Agenda and their counterpart in Media Agenda.
-All correlation values are statistical significant ($p < 10^{-9}$), except (*) which is significant with $p < 0.05$.}
+\caption{Queries used in Twitter: Due to different characteristics in the search tool of Twitter, we adapted the queries employed in Google Trends, but preserving, at least we can, the most important keywords.}
+\begin{tabular}{l|p{7.5cm}}
+Topic name & Twitter query \\ \hline
+Elections & elecciones + cambiemos + kirchner + massa + randazzo \\
+Missing person & maldonado + otranto + gendarmer\'ia + desaparici\'on \\
+Former Planning minister & vido + desafuero + minnicelli + baratta \\
+Current President & macri + cgt + laboral +  triaca \\
+Social leader &  sala + cidh + tupac + amaru + pullen + llermanos + morales \\
+Prosecutor’s death & nisman + amia + memorandum + timerman +  bonadio \\
+Former Vice-President & boudou + ciccone +  lijo + vandenbroele + carmona \\ 
+\end{tabular}
+\label{table:tw_queries}
+\end{table}
+
+\begin{table}[h!]
+\caption{Correlation between the topic temporal profiles of the Public Agenda and their counterpart in Media Agenda.
+All correlation values are statistically significant ($p < 10^{-9}$), except (*) which is significant with $p < 0.05$.}
 \begin{tabular}{lccc}
-Topic's name & Correlation MA and GT & MA and Twitter & GT and Twitter \\ \hline
+Topic name & Correlation MA and GT & MA and Tw & GT and Tw \\ \hline
 Elections & \textbf{0.81} & \textbf{0.59} & \textbf{0.75} \\
@@
 \caption{Correlation between the temporal profiles of the topics found in NMF and associated topics in LDA.}
-\begin{tabular}{llc}
-Topic's name & Correlation between NMF and LDA \\ \hline
+\begin{tabular}{lc}
+Topic name & Correlation between NMF and LDA \\ \hline
 Elections & \textbf{0.98} \\

### 2018-09-04 bmc_article.tex
Desarrollo de la primera parte

@@
 This work is considered the founding of the agenda-setting theory.
-In its basic stage, known as first-level agenda-setting \cite{mccombs2005look}, the theory focuses on the comparison between the topics coverage by the media and the public agenda, i.e.
-the topics that the public consider as priority \cite{brians1996campaign, gerber2009does, coleman2007young}.
-For instance, in Argentina, \cite{mitchelstein2016brecha} examines the differences between public and journalists preferences and other works, like \cite{zunino2010cobertura, koziner2013cobertura}, studied the coverage of the main newspapers on particular events related to a confrontation scenario between government and press \cite{mitchelstein2017information}.
+In its basic stage, known as first-level agenda-setting \cite{mccombs2005look}, the theory focuses on the comparison between the topics coverage by the media and the public agenda: The topics that the public consider as priority.
+For instance, it explores how media content correlate with audiences of different ages \cite{coleman2007young} and how people agendas differ based on the way they consume news \cite{althaus2002agenda}.
+On the other hand, the theory hypothesizes how the media affect the audience opinion, for instance, how political coverage and political advertisement shape candidate knowledge among the audience \cite{brians1996campaign, gerber2009does}, or how the coverage given by the media to a particular nation affects people perception about its importance to local political interests \cite{wanta2004agenda}.
+Related to our work, in Argentina, \cite{mitchelstein2016brecha} examines the differences between public and journalists preferences and other works, like \cite{zunino2010cobertura, koziner2013cobertura}, studied the coverage of the main newspapers on particular events related to a confrontation scenario between government and press \cite{mitchelstein2017information}.
 

### 2018-09-04 bmc_article.tex
Correcciones a la intro

@@
 
-\par One of the challenges in  complex social system research is to understand of the ecosystem of information flow and opinion formation.
+\par One of the challenges in  complex social system research is to understand the ecosystem of information flow and opinion formation.
 Within this framework, many ingredients can be parts of different mechanisms of social influence.
-A major role in this ecosystem is played by the Mass Media outlets, which is used to be the source of information for many people.
-Then, informed people tend to interact with each other  via personal interactions or through social networks, giving rise to complex dynamics where opinions are shaping and changing in time.
-In this scenario to understand the role of Mass Media Influence in a given social group  becomes essential.
+A major role in this ecosystem is played by the mass media outlets, which is used to be the source of information for many people.
+Then, informed people tend to interact with each other  via personal interactions or through social networks, giving rise to a complex dynamics where opinions are shaping and changing in time.
+In this scenario to understand the role of the mass media influence in a given social group  becomes essential.
 
 % Agenda Setting Theory
-\par Naturally, how the Media affects public opinion was first explored in the area of social sciences. 
+\par Naturally, how the media affects public opinion was first explored in the area of social sciences. 
 In the seminal study performed in Chapel Hill during the US presidential elections in 1968 \cite{mccombs1972agenda}, Maxwell McCombs and Donald Shaw found that the aspects of public affairs that are prominent in the news become prominent in the public.
@@
 In its basic stage, known as first-level agenda-setting \cite{mccombs2005look}, the theory focuses on the comparison between the topics coverage by the media and the public agenda: The topics that the public consider as priority.
-For instance, it explores how media content correlate with audiences of different ages \cite{coleman2007young} and how people agendas differ based on the way they consume news \cite{althaus2002agenda}.
+For instance, within the agenda-setting framework, it was explored how media content correlate with audiences of different ages \cite{coleman2007young} and how people agendas differ based on the way they consume news \cite{althaus2002agenda}.
 On the other hand, the theory hypothesizes how the media affect the audience opinion, for instance, how political coverage and political advertisement shape candidate knowledge among the audience \cite{brians1996campaign, gerber2009does}, or how the coverage given by the media to a particular nation affects people perception about its importance to local political interests \cite{wanta2004agenda}.
-Related to our work, in Argentina, \cite{mitchelstein2016brecha} examines the differences between public and journalists preferences and other works, like \cite{zunino2010cobertura, koziner2013cobertura}, studied the coverage of the main newspapers on particular events related to a confrontation scenario between government and press \cite{mitchelstein2017information}.
+Related to our work, in Argentina, \cite{mitchelstein2016brecha} examines the differences between public and journalists preferences, and other works like \cite{zunino2010cobertura, koziner2013cobertura}, studied the coverage of the main newspapers on particular events related to a confrontation scenario between government and press \cite{mitchelstein2017information}.
 
@@
 One of them focus on detecting bias in the media, either by taking into account the number of mentions related  to a preferred political party \cite{lazaridou2016identifying, baumgartner2015all} or by identifying the ideology through the position of the media regards to certain issues or actors \cite{elejalde2018nature, sagarzazu2017hugo}.
-This research line can be linked with the theory of \textit{framing} \cite{guggenheim2015dynamics, tsur2015frame}, which focus on the way media emphasizes some attributes of an object, while understating others.
-Other investigations pay attention to the sources of the Media Agenda, theory known as \textit{intermedia agenda-setting} \cite{vargo2017networks, harder2017intermedia, guo2017global}, where the competition and the mutual influence between different media is observed.
+This research line can be linked with the theory of \textit{framing} \cite{guggenheim2015dynamics, tsur2015frame}, which focus on the way the media emphasizes some attributes of an object, while understating others.
+Other investigations pay attention to the sources of the media agenda, theory known as \textit{intermedia agenda-setting} \cite{vargo2017networks, harder2017intermedia, guo2017global}, where the competition and the mutual influence between different media is observed.
 
@@
 %\par Nonetheless, most of the works cited above follow typical methods of social science research, and fall in what we call a ``static approach": They used to summarize certain issues present in news media and looking for effects in the audience.
-\par From the irruption of internet, quantitative analysis based on  the access to big data were possible and, for instance, take into account the temporal dependence of the Media and Public attention.
+\par From the irruption of internet, quantitative analysis based on  the access to big data were possible and, for instance, take into account the temporal dependence of the media and public attention.
 In \cite{soroka2017negativity} it is shown that the newspapers and Twitter have an opposite reaction to the changes of the unemployment rates; in \cite{guggenheim2015dynamics}, the competition of frames about gun control is explored; in \cite{ali2018measuring}, the authors show how fluctuations of Twitter activity in different regions depend on the location of terrorist attacks; and in \cite{russell2014dynamics}, the complex interplay between the social media and the traditional one is followed over time on a set of predefined, but general, issues.
@@
 
-\par In this work we propose a novel method in order to study the dynamics of Mass Media Agenda, which consist in performing an unsupervised topic model on newspapers articles, and studying how the emerging topics evolve in time.
-We look also at their correspondence with the Public and Social Network Agendas.
-Rather than focus on a single issue or a set of independent topics, this method allow us to define  the agendas (the Media and the Public) as an object which evolved in time.
-Our work focus on a quantitative approach which complements the agenda-setting theory describe above, which mainly stands within the framework of first-level agenda setting, but also allows to face  agenda bias and framing.
+\par In this work we propose a novel method in order to study the dynamics of the mass media agenda, which consist of performing an unsupervised topic model on newspapers articles, and studying how the emerging topics evolve in time.
+We look also at their correspondence with the audience agenda, by looking at the Google searches and Twitter in the studied period. 
+Rather than focus on a single issue or on a set of independent topics, this method allows us to define  the agendas (both the media and the public) as an object which evolves in time.
+Our work focus on a quantitative approach which complements the agenda-setting theory describe above, which mainly stands within the framework of first-level agenda setting, but also allows us to face agenda bias and framing.
 
-\par On the other hand, in recent years new approaches to study social dynamics through several tools taken from statistical physics have proposed mathematical models to explore the interplay between Mass Media and society \cite{crokidakis2012effects,gonzalez2012model, moussaid2013opinion, rodriguez2010effects, pinto2016setting}.
+\par On the other hand, in recent years new approaches to study social dynamics through several tools taken from statistical physics have proposed mathematical models to explore the interplay between the mass media and society \cite{crokidakis2012effects,gonzalez2012model, moussaid2013opinion, rodriguez2010effects, pinto2016setting}.
 Much of them lack in being contrasted with real data.
-With our work we aim to gain a closer insight on the complex interaction between Media and Public, and provide a quantitative research that would be useful at the time of constructing better and more data-driven models.
+With our work we aim to gain a closer insight on the complex interaction between the media and the public, and provide a quantitative research that would be useful at the time of constructing better and more data-driven models.
 
@@
 \subsection*{The Media Agenda}
-\par In this work we analyze a three-month period of the Argentinian Media Agenda composed by a corpus of news articles that were published between July 31st, 2017 and November 5th, 2017. 
+\par In this work we analyze a three-month period of the Argentinian media agenda composed by a corpus of news articles that were published between July 31st, 2017 and November 5th, 2017. 
 The articles come from the politics section of the online editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\'on}, \emph{P\'agina12}, and the news portal, \emph{Infobae}.

### 2018-09-06 bmc_article.tex
Algunas correcciones de Fede

@@
 
-The mass media play a fundamental role in the formation of public opinion, either by defining the topics of discussion or by making a degree of emphasis on certain issues.
+The mass media plays a fundamental role in the formation of public opinion, either by defining the topics of discussion or by making an emphasis on certain issues.
 Directly or indirectly, people get informed by consuming news from the media.
@@
 We measure agenda diversity as a function of time using the Shannon entropy and differences between agendas using the Jensen-Shannon distance.
-We found that the Public Agenda is less diverse than the Media Agenda, and we were also capable to detect periods of time where coverage of certain issues are biased (coverage bias).\\
+We found that the Public Agenda is less diverse than the Media Agenda, and we were also capable of detecting periods of time where coverage of certain issues are biased (coverage bias).\\
 
@@
 This research line can be linked with the theory of \textit{framing} \cite{guggenheim2015dynamics, tsur2015frame}, which focus on the way the media emphasizes some attributes of an object, while understating others.
-Other investigations pay attention to the sources of the media agenda, theory known as \textit{intermedia agenda-setting} \cite{vargo2017networks, harder2017intermedia, guo2017global}, where the competition and the mutual influence between different media is observed.
+On the other hand, several investigations pay attention to the sources of the media agenda, theory known as \textit{intermedia agenda-setting} \cite{vargo2017networks, harder2017intermedia, guo2017global}, where the competition and the mutual influence between different media is observed.
 
@@
 %\par Nonetheless, most of the works cited above follow typical methods of social science research, and fall in what we call a ``static approach": They used to summarize certain issues present in news media and looking for effects in the audience.
-\par From the irruption of internet, quantitative analysis based on  the access to big data were possible and, for instance, take into account the temporal dependence of the media and public attention.
+\par Since the irruption of internet, a quantitative analysis based on  the access to big data has been possible.
+For instance, this analysis can take into account the temporal dependence of the media and public attention.
 In \cite{soroka2017negativity} it is shown that the newspapers and Twitter have an opposite reaction to the changes of the unemployment rates; in \cite{guggenheim2015dynamics}, the competition of frames about gun control is explored; in \cite{ali2018measuring}, the authors show how fluctuations of Twitter activity in different regions depend on the location of terrorist attacks; and in \cite{russell2014dynamics}, the complex interplay between the social media and the traditional one is followed over time on a set of predefined, but general, issues.
@@
 
-\par In this work we propose a novel method in order to study the dynamics of the mass media agenda, which consist of performing an unsupervised topic model on newspapers articles, and studying how the emerging topics evolve in time.
-We look also at their correspondence with the audience agenda, by looking at the Google searches and Twitter in the studied period. 
-Rather than focus on a single issue or on a set of independent topics, this method allows us to define  the agendas (both the media and the public) as an object which evolves in time.
-Our work focus on a quantitative approach which complements the agenda-setting theory describe above, which mainly stands within the framework of first-level agenda setting, but also allows us to face agenda bias and framing.
+\par In this work we propose a novel method in order to study the dynamics of the mass media agenda, which consist of performing an unsupervised topic model on newspapers articles, and studying how the emerging topics evolve with time.
+We look also at their correspondence with the audience agenda, by looking both the Google searches and Twitter activity in the studied period. 
+Rather than focus on a single issue or on a set of independent topics, this method allows us to define  the agendas (both the media and the public) as an object which evolves with time.
+Our work focuses on a quantitative approach which complements the agenda-setting theory describe above, which mainly stands within the framework of first-level agenda setting, but also allows us to face agenda bias and framing.
+We apply this method to study the dynamics of the Argentinian media agenda due to our familiarity with the political background, but as can be seen throughout the work, the methodology implemented is far general and can be easily extended to other context.
 

### 2018-09-06 bmc_article.tex
Correcciones mias, seccion agenda setting final reescrita, incorporado cosas de Fede y de Marcos

@@
 %\note{Sample of title note}     % note to the article
-\note[id=n1]{Equal contributor} % note, connected to author
+%\note[id=n1]{Equal contributor} % note, connected to author
 \end{artnotes}
@@
 The agenda-setting theory provides a conceptual framework in order to understand the role played by the mass media in public opinion formation, but the previous questions can not be answered without proper quantitative measures of agenda dynamics and public attention.
-In this work we study the agenda of Argentinian newspapers in comparison with public interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time.
+In this work we study the media agenda in comparison with public interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time.
 We measure agenda diversity as a function of time using the Shannon entropy and differences between agendas using the Jensen-Shannon distance.
@@
 \par One of the challenges in  complex social system research is to understand the ecosystem of information flow and opinion formation. 
-Within this framework, many ingredients can be parts of different mechanisms of social influence.
-A major role in this ecosystem is played by the mass media outlets, which is used to be the source of information for many people.
-Then, informed people tend to interact with each other  via personal interactions or through social networks, giving rise to a complex dynamics where opinions are shaping and changing in time.
-In this scenario to understand the role of the mass media influence in a given social group  becomes essential.
+%Within this framework, many ingredients can be parts of different mechanisms of social influence. 
+A major role within this ecosystem is played by the mass media outlets, which are massively used as sources of information.
+People get informed by the media and then interact with each other  via personal interactions or through social networks, giving rise to a complex dynamics where opinions are shaping and changing with time.
+In this scenario, it becomes essential to understand the influence of mass media in a given social group.
 
 % Agenda Setting Theory
-\par Naturally, how the media affects public opinion was first explored in the area of social sciences. 
+\par The influence of the media on public opinion was first explored by the social sciences. 
 In the seminal study performed in Chapel Hill during the US presidential elections in 1968 \cite{mccombs1972agenda}, Maxwell McCombs and Donald Shaw found that the aspects of public affairs that are prominent in the news become prominent in the public.
@@
 On the other hand, the theory hypothesizes how the media affect the audience opinion, for instance, how political coverage and political advertisement shape candidate knowledge among the audience \cite{brians1996campaign, gerber2009does}, or how the coverage given by the media to a particular nation affects people perception about its importance to local political interests \cite{wanta2004agenda}.
-Related to our work, in Argentina, \cite{mitchelstein2016brecha} examines the differences between public and journalists preferences, and other works like \cite{zunino2010cobertura, koziner2013cobertura}, studied the coverage of the main newspapers on particular events related to a confrontation scenario between government and press \cite{mitchelstein2017information}.
+Other works examine the differences between public and journalists preferences \cite{mitchelstein2016brecha}, or studied the coverage of the main newspapers on particular events related to a confrontation scenario between government and press \cite{zunino2010cobertura, koziner2013cobertura}.
 
@@
 Our work focuses on a quantitative approach which complements the agenda-setting theory describe above, which mainly stands within the framework of first-level agenda setting, but also allows us to face agenda bias and framing.
-We apply this method to study the dynamics of the Argentinian media agenda due to our familiarity with the political background, but as can be seen throughout the work, the methodology implemented is far general and can be easily extended to other context.
+We apply this method to study the dynamics of the Argentinian media agenda due to our familiarity with the political background, but as can be seen throughout the work, the methodology implemented is far general and can be easily extended to other data-sets.
 
@@
 
-\par As was mentioned above, once the concepts of diversity and distance between distributions were defined, we are particularly interested in those dates when these concepts take extreme values: When the diversity is low, we know that a topic is absorbing much of the attention of any of the Agendas; on the other hand, when the distance between two distributions is high, we can conclude that they have distant interests.
+\par As was mentioned before, once the concepts of diversity and distance between distributions were defined, we are particularly interested in those dates when these concepts take extreme values: When the diversity is low, we know that a topic is absorbing much of the attention of any of the Agendas; on the other hand, when the distance between two distributions is high, we can conclude that they have distant interests.
 However, we still lack the definition of what a low diversity or a high distance are. 
@@
 \par We initially focus on the ten most important issues from the three-month period corpus of news reported above. 
-These ten topics are represented in the wordclouds of figure \ref{fig:topics_wordclouds}.
+The election of factorizing the corpus in ten topics was based on having a low dimensional representation of the corpus and a clear interpretation of the topics due to our prior knowledge of the political background.
+We found that this factorization allowed us to draw useful conclusions.
+However, more sophisticated methodologies to estimate the number of topics in a corpus can be taken into account in future researches.
+The ten topics are represented in the word clouds of figure \ref{fig:topics_wordclouds}.
 Given our interpretation of the keywords found in three of them, we joined these topics as being part of the same macro-topic which we called \emph{Elections}.
@@
 \par In figure \ref{fig:topics_wordclouds} we show a seven topic decomposition of the whole corpus using radar plots for the Media \textbf{MA} and Public agendas \textbf{PA} discriminated by \textbf{GT} (Google Trends) and \textbf{Tw} (Twitter).
-In this figure we also show the wordclouds of the keywords that define each of the ten original topics, where the size of the word reflects its importance in the topic definition.
+In this figure we also show the word clouds of the keywords that define each of the ten original topics, where the size of the word reflects its importance in the topic definition.
 In green color, we point out the words involved in the Google Trends and Twitter queries in order to construct the Public Agenda.
@@
 On the other hand, in table \ref{table:gt_all_correlation} we show the linear correlation between the topic temporal profiles from the Public Agenda and their counterparts in the Media Agenda.
-\par We can observe that both GT and Tw look similar in this representation, but they show specific differences with the Media Agenda.
+\par We can see that both GT and Tw look similar in this representation, but they show specific differences with the Media Agenda.
 For instance, a greater interest of the audience in the topic \emph{Missing person} than the media is observed, or inversely, a lower interest in the topic \emph{Prosecutor's death} takes place.
@@
 
-\par This can be observed in figure \ref{fig:all_agenda} where the time evolution of the topics is shown in a bump chart of the Agendas.
+\par The time evolution of the topics is shown in a bump chart of the Agendas by figure \ref{fig:all_agenda}.
 The bump chart provides  a clear visualization of the relative weight of the topics at the same time with their ranking.
-In  this figure  we also highlight some important events related to the dynamics of the topics.
-It is possible to appreciate how the main topic changes in time and has a glance of the qualitative differences between the agendas.
-In particular, it can be observed some differences between the Public Agendas that were not observed in the previous figure, as for instance, the persistence of main topics is longer in Twitter than in Google Trends.
+In figure \ref{fig:all_agenda}, we also highlight some important events related to the dynamics of the topics.
+It is possible to appreciate how the main topic changes with time and have a glance of the qualitative differences between the agendas.
+In particular, it can be seen some differences between the Public Agendas that were not observed in figure \ref{fig:topics_wordclouds}, as for instance, the persistence of main topics is longer in Twitter than in Google Trends.
 This is more evident at the end of the analyzed period, where the topics discussed in Google Trends show more response to change in Media Agenda than in Twitter, maybe due to the existence of a different pattern of interaction in the social network, to which a deeper analysis could be devoted in future works.
@@
 Discussions in Twitter about elections appear also in point (c), when the other agendas seem to be more diverse. 
-On the other hand, and despite not being classified as outlier, we also focus in point (b) because the Shannon Entropy in the Google Agenda displays a minimum (collapsing agenda) which is not corresponded neither in the Media nor in the Twitter Agendas.
+On the other hand, and despite not being classified as outlier, we also focus on point (b) because the Shannon Entropy in the Google Agenda displays a minimum (collapsing agenda) which is not corresponded neither in the Media nor in the Twitter Agendas.
 Crawling in the context, we see that it belongs to the topic \emph{Missing person} and this date corresponds to the rally that took place one month after the disappearance of \emph{Santiago Maldonado} (see \textbf{Supplementary Material}).
@@
 
-\par From the measure of $H$ we have also observed that the median of the Public Agenda diversity is statistical significant lower than the observed in the Media Agenda.
+\par From the measure of $H$ we have also observed that the median of the Public Agenda diversity is statistical significant lower than the median of the Media Agenda.
 Specifically $H_{GT} = 0.73$ and $H_{Tw} = 0.74$ are statistically significantly lower than $H_{MA} = 0.85$ with $p < 10^{-18}$, while there is no significant difference between the first two. 
@@
 In figure \ref{fig:jensen_shannon_gt} we show the Jensen-Shannon distance between Media and Public Agendas as a function of time.
-We focus in three points that seem to be relevant enough.
+We focus on three points that seem to be relevant enough.
 In all cases, the topic distributions at that particular dates displayed by  the radar plots show that the increment in the distance between agendas is due to a greater interest of public opinion in the \emph{Missing person} topic.
@@
 
-\par In this section we leave aside the Public Agenda as an unified corpus and we study the composition and evolution of the Media Agenda of each media outlet. 
+\par In this section we leave aside the Public Agenda as an unified corpus and we study the composition and evolution of the Media Agenda on each media outlet. 
 In figure \ref{fig:news_agenda} we show the bump charts corresponding to each of the analyzed newspapers analogously to figure \ref{fig:all_agenda}.
-The topics are the same introduced in the wordclouds of figure \ref{fig:topics_wordclouds}, but when computing the topic weights, the articles are discriminated by newspaper. 
+The topics are the same which were introduced in the word clouds of figure \ref{fig:topics_wordclouds}, but when computing the topic weights, the articles are discriminated by newspaper. 
 We also show the radar plots with the average distribution, as made in figure \ref{fig:topics_wordclouds}.
 
-\par In figure \ref{fig:news_agenda} we can qualitative have a glance of the differences between the newspaper agendas.
+\par In figure \ref{fig:news_agenda} we can qualitative look at the differences between the newspaper agendas.
 For instance, we can see how the newspaper called \emph{P\'agina 12} gave more importance to the topics \emph{Missing person} and \emph{Social leader}, while it reduces to minimum the coverage of the topic  \emph{Former Planning minister} as the others did.
@@
 For example, we can quantify this difference calculating  the median of the signals.
-If we focus in the period between July 31st and August 27th, the median of the topic relative weight in \emph{P\'agina 12} is roughly 0.14 and this is statistically significantly larger ($p < 10^{-7}$) than other medians, which are lower than 0.05.
+If we focus on the period between July 31st and August 27th, the median of the topic relative weight in \emph{P\'agina 12} is roughly 0.14 and this is statistically significantly larger ($p < 10^{-7}$) than other medians, which are lower than 0.05.
 Analyzing the same period, but in panel (b), we again can show that the median in \emph{P\'agina 12}, which is roughly 0.01, is lower than the others, which oscillate around 0.05 ($p<10^{-3}$).
@@
 
-\par Finally, in figure \ref{fig:topics_temporal_profiles} we also show the topic keywords wordclouds, highlighting the most frequently mentioned in each newspaper and filtering the common words to all newspapers.
-Although most of the words are not relevant enough, some of them are quite interesting, as for instance the word \emph{represi\'on} (repression) when \emph{P\'agina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (\emph{Fern\'andez de Kirchner}, former president) which is employed by all newspapers except \emph{P\'agina 12} when they  talk about the topic \emph{Former Planning minister} (see \textbf{Supplementary Material}).
+\par Finally, in figure \ref{fig:topics_temporal_profiles} we also show the topic keywords word clouds, highlighting the most frequently mentioned in each newspaper and filtering the common words to all newspapers.
+Although most of the words are not relevant enough, some of them are quite interesting, for instance the word \emph{represi\'on} (repression) when \emph{P\'agina 12} talks about the topic \emph{Missing Person} and the word \emph{Cristina} (\emph{Fern\'andez de Kirchner}, former president) which is employed by all newspapers except \emph{P\'agina 12} when they  talk about the topic \emph{Former Planning minister} (see \textbf{Supplementary Material}).
 We think that a deeper study of the topic keywords could be a first approximation in the study of framing, which will constitute the core of futures works.
@@
 
-\par In a world where social media exist and the feedback between the media and audience is common currency, nowadays the idea that the Media set the agenda and the audience blindly follows it (as it's seemed to be suggested in the original work of McCombs) is too naive.
-Based on the data analyzed above, the behavior of the Media and Public Agendas, either by looking at Google Trends or Twitter, shows periods of strong similarity  (specially in the presence of an unexpected event) and periods of disengagement.
-Therefore, it is not trivial to establish a causal relationship between agendas, specially when they are represented as evolving in time topic distribution as we did in this work.
-However, it is possible to discuss agenda setting if we focus in a single topic.
+\par In a world where social media exists and the feedback between the media and audience is common currency, nowadays the idea that the media sets the agenda and the audience blindly follows it (as it's seemed to be suggested in the original work of McCombs) is too naive.
+Based on the data analyzed above, the behavior of the Media and Public Agendas, either by looking at Google Trends or Twitter, shows periods of strong similarity, for instance in the presence of an unexpected event, and periods of disengagement.
+Therefore, it is not trivial to establish a causal relationship between the agendas, specially when they are represented as evolving in time topic distributions as we did in this work. 
+However, it is possible to discuss agenda-setting if we focus on a single topic.
  We think that the \emph{Missing person} topic is the most adequate topic to be discussed because:
@@
 
-\par In figure \ref{fig:Maldonado_setagenda} we show the topic relative weight from the Public and Media Agendas.
-After the initial coverage, the agendas seem to differentiate around August 15th, when topic started to become more important in the Public Agenda than in the Media one.
-Around August 24th, the topic abruptly increases in the audience interests while the reaction in the media is slower, showing a significant peak in the plot of the discrete difference (panel (b)).
+\par In figure \ref{fig:Maldonado_setagenda} panel (a), we show the \emph{Missing Person} relative weight from both the Media and Public Agendas. 
+After the initial coverage, the agendas seem to differentiate around August 15th, when the topic starts to become more important in the Public Agendas than in the Media one. 
+Around August 24th, the topic abruptly increases in the audience interests while the reaction in the media is slower, showing a significant peak in the plot of the discrete difference of the temporal profiles (panel (b)).
 This date is very close to August 26th, when a campaign in social media took place.
-After that, the Media increase its coverage about the topic.
-
-\par Is this a case of reverse agenda-setting \cite{russell2014dynamics}, i.e, when the audience set the Media Agenda? 
-After all, the audience gets involved about this topic by the media, so how was the coverage before those events?
-We can answer these questions by calculating the cumulative coverage of this topic since the first events took place.
-This measure can be seen as the numerical integration of the temporal profiles of figure \ref{fig:topics_temporal_profiles} between the initial date and the current date. 
-It is interesting to note that the newspaper responsible for accumulating coverage during the initial stage was the minority one: \emph{P\'agina 12}. 
-Our interpretation about the setting agenda dynamics of this particular topic is the following: A small newspaper (\emph{P\'agina 12}) gives great coverage to this topic; the topic is then amplified by public in the social networks and it is also expressed  by reiterative Google searches.
-Then, the rest of the Media pays attention to this subject and it becomes an important topic in the Media Agenda.
-This interpretation tries to catch in a qualitative way how the information flow was in this specific topic.
-On the other hand, behind this interpretation there are two important facts that must be mentioned: First, the disappearance of a person is a very sensitive theme for the Argentinian society, and second, there are political reasons why \emph{P\'agina 12} was particularly interested in cover this topic while the other media did not follow this interest (see \textbf{Supplementary Material}).
-
-\par Even tough we face the question about causality only in a qualitative way and just for a specific topic, it was possible to highlight  the complex feedback dynamics that take place between public and media agendas.
+After that event, the media increases its coverage about the topic.
+Is this a case of reverse agenda-setting \cite{russell2014dynamics}, when a discussion in a given social network triggers the interest of the media? 
+In order to understand this behaviour, we calculate the cumulative coverage of the \emph{Missing Person} topic, which is displayed in figure \ref{fig:Maldonado_setagenda} panel (c).
+The cumulative coverage of the \emph{Missing Person} topic is defined to be the numerical integration between the initial date and the current date, of the topic temporal profile in each media outlets (figure \ref{fig:topics_temporal_profiles}) and in the Google and Twitter Agendas (which can be seen in figure \ref{fig:Maldonado_setagenda} panel (a)).
+This quantity shows us how the media and public attention have been accumulated since the first events.
+\par The figure \ref{fig:Maldonado_setagenda} panel (c) shows that it is not as simple as to say that the Public Agenda sets the Media one: 
+Before the \emph{Missing Person} topic becomes prominent to the public, \emph{P\'agina 12} was leading the coverage of this topic with respect to the rest of the media.
+It is important to recall that \emph{P\'agina 12} is the newspaper with fewer readers among the analyzed ones.
+This fact leads to a complex agenda-setting dynamics within the \emph{Missing Person} topic: The media outlet with less contribution in the Media Agenda construction, can still put in public debate a topic of its interest.
+As the audience becomes more concerned about this topic, it is amplified by both reiterative Google searches and discussions in social networks.
+Due to this increasing public interest, the rest of the media ought to pay attention to this subject and finally, the topic becomes also prominent to the Media Agenda.
+\par Beside the analysis performed above, there are two important facts that must be mentioned about the \emph{Missing Person} topic: First, the disappearance of a person is a very sensitive theme for the Argentinian society, which can explain why this particular topic triggered the audience interest; and second, there were political reasons why \emph{P\'agina 12} was particularly interested in covering this topic since the beginning, while the rest of the media did not until the topic was prominent to the Public Agenda (see \textbf{Supplementary Material}).
+\par The analysis of the cummulative coverage allows us to face the question about causality at least in a qualitative way.
+However, it was possible to highlight the complex feedback dynamics that take place between public and media agendas.
 %There are different metrics that would help in this question, such as Granger causality or correlation by sliding windows.
@@
 \par A very massive campaign in social media took place on August 26th, 2017 under the motto ``Where is Santiago Maldonado?", followed by two massive protest marches to the \emph{Plaza de Mayo} that took place on September 1st and October 1st, of which the first one had a great repercussion due to several incidents that took place during the march.
-\par The body of \emph{Santiago Maldonado} was found dead on October 17th, 2017 in the \emph{Chubut} river, near the place where he was seen the last time, and the autopsy report told that \emph{Santiago Maldonado} had died from ``asphyxia after being submerged", with no injuries on his body.
-However, the responsibility of the current administration is still being discussed.
+\par The body of \emph{Santiago Maldonado} was found dead on October 17th, 2017 in the \emph{Chubut} river, near the place where he was seen for the last time, and the autopsy report told that \emph{Santiago Maldonado} had died from ``asphyxia after being submerged", with no injuries on his body.
+However, the responsibility of the current administration is still being discussed by different sectors of the Argentinian society.
 
@@
 
-\par In this section we apply other topic model, Latent Dirichlet Allocation \cite{blei2003latent} (LDA), to our corpus and compare its results to the shown in this paper.
+\par In this section we apply other topic model, Latent Dirichlet Allocation \cite{blei2003latent} (LDA), to our corpus and compare its results with the shown in this paper.
 Due to the increasingly use of LDA, we think that a few words about the performance of LDA in our work is necessary.
@@
 \includegraphics[width = \textwidth]{Fig1.pdf}
-\caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic (then collapsed to seven) distribution and their corresponding wordclouds.} The Public Agenda is represented both by Google Trends (GT) and Twitter (Tw).
-Topic names are introduced together with the wordclouds containing the most important keywords involved in the definition of each topic.
+\caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic (then collapsed to seven) distribution and their corresponding word clouds.} The Public Agenda is represented both by Google Trends (GT) and Twitter (Tw).
+Topic names are introduced together with the word clouds containing the most important keywords involved in the definition of each topic.
 In green color we show the keywords used to define the topics in the Google Trends and Twitter queries (see tables \ref{table:gt_queries} and \ref{table:tw_queries}) and therefore in our construction of the Public Agenda.}
@@
 \includegraphics[width = \textwidth]{Fig7.pdf}
-\caption{\textbf{Relative weight of the topics (a) \textit{Missing person}, and (b) \textit{Former Planning Minister}, and their corresponding wordclouds of frequent newspaper keywords}.
+\caption{\textbf{Relative weight of the topics (a) \textit{Missing person}, and (b) \textit{Former Planning Minister}, and their corresponding word clouds of frequent newspaper keywords}.
 We interpreted the differences shown in given periods as an indicator of coverage bias.
@@
 \includegraphics[width = \textwidth]{Fig8.pdf}
-\caption{\textbf{Can we guess the agenda-setting direction in the Missing person topic?}
+\caption{\textbf{Non-trivial agenda interplay in the Missing person topic.}
 The temporal profiles of figure (a) show that the Public and Media agenda seem to differentiate around August 15th (vertical grey line (1)) and the Public increases abruptly its interest in the topic around August 24th (grey line (2)).

### 2018-09-07 bmc_article.tex
Version con agradecimientos y contribuciones

@@
 A special focus was put on the elections in the Buenos Aires province, where the former President \emph{Cristina Fern\'andez de Kirchner} participated as a senator candidate representing the alliance \emph{Unidad Ciudadana}, confronting \emph{Cambiemos}, which is the alliance of the current President \emph{Mauricio Macri} and the current governor of Buenos Aires province \emph{Maria Eugenia Vidal}.
+On the other hand, two other candidates that also participated in the election were \emph{Sergio Massa} and \emph{Florencio Randazzo}.
 
@@
 \par The body of \emph{Santiago Maldonado} was found dead on October 17th, 2017 in the \emph{Chubut} river, near the place where he was seen for the last time, and the autopsy report told that \emph{Santiago Maldonado} had died from ``asphyxia after being submerged", with no injuries on his body.
-However, the responsibility of the current administration is still being discussed by different sectors of the Argentinian society.
+However, due to the fact that this topic is a very sensitive one for the Argentinian society, the causes of the \emph{Maldonado}'s death are still being investigated.
 
@@
 \section*{Author's contributions}
-    Text for this section \ldots
+P.B.
+conceived the study.
+S.P.
+collected and analysed most of the data.
+F.A.
+collected Twitter data; F.A., P.B, and S.P.
+interpreted the data and prepared the manuscript.
+P.B.
+and C.O.D  give the final approval of the version to be published.
 
 \section*{Acknowledgements}
-  Text for this section \ldots
+  We thank Dr. A. Chernomoretz, Dr. M. Otero, Dra. V. Semeshenko, and Dr. M. Trevis\'an for bringing us a critical revision of the article.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-11 bmc_article.tex
Algunas correcciones menores sobre version vista por Pablo

@@
 The mass media plays a fundamental role in the formation of public opinion, either by defining the topics of discussion or by making an emphasis on certain issues.
-Directly or indirectly, people get informed by consuming news from the media.
-But which is the dynamics of the agenda and how the people become interested in their different topics?
-The agenda-setting theory provides a conceptual framework in order to understand the role played by the mass media in public opinion formation, but the previous questions can not be answered without proper quantitative measures of agenda dynamics and public attention.
-In this work we study the media agenda in comparison with public interests through a quantitative approach by performing topic detection over the news, identifying the main topics covered and their evolution over time.
+Directly or indirectly, people get informed by
+consuming news from the media. But what are the dynamics of the agenda and how the people become interested in their different topics? 
+This  question cannot be answered without proper quantitative measures of agenda dynamics and public attention. 
+In this work we study the agenda of newspapers in comparison with public interests  by performing topic detection over the news and identifying the main topics covered and their evolution over time. 
 We measure agenda diversity as a function of time using the Shannon entropy and differences between agendas using the Jensen-Shannon distance.
-We found that the Public Agenda is less diverse than the Media Agenda, and we were also capable of detecting periods of time where coverage of certain issues are biased (coverage bias).\\
+We found that the Public Agenda is less diverse than the Media Agenda, especially when there is a very attractive topic and the audience naturally focuses only on this one.
+Using the same methodology we  detect coverage bias in newspapers and have a first approximation to the theory of framing.
+Finally it was possible to identify a complex agenda-setting dynamics within a given topic where the least sold newspaper  triggered a public debate  via a positive feedback mechanism with social networks discussions which install the issue in the Media Agenda.\\
 
 \end{abstract}
+
+%hen there is a very attractive topic, the audience naturally focuses only on this one
 
@@
 A major role within this ecosystem is played by the mass media outlets, which are massively used as sources of information.
-People get informed by the media and then interact with each other  via personal interactions or through social networks, giving rise to a complex dynamics where opinions are shaping and changing with time.
+People get informed by the media and then interact among them via personal discussions or through social networks, giving rise to a complex dynamics where opinions are shaping and changing with time. 
 In this scenario, it becomes essential to understand the influence of mass media in a given social group.
@@
 This work is considered the founding of the agenda-setting theory.
-In its basic stage, known as first-level agenda-setting \cite{mccombs2005look}, the theory focuses on the comparison between the topics coverage by the media and the public agenda: The topics that the public consider as priority.
+In its basic stage, known as first-level agenda-setting \cite{mccombs2005look}, the theory focuses on the comparison between the topics coverage by the media and the public agenda, i.e., the topics that the public consider as priority.
 For instance, within the agenda-setting framework, it was explored how media content correlate with audiences of different ages \cite{coleman2007young} and how people agendas differ based on the way they consume news \cite{althaus2002agenda}.
-On the other hand, the theory hypothesizes how the media affect the audience opinion, for instance, how political coverage and political advertisement shape candidate knowledge among the audience \cite{brians1996campaign, gerber2009does}, or how the coverage given by the media to a particular nation affects people perception about its importance to local political interests \cite{wanta2004agenda}.
-Other works examine the differences between public and journalists preferences \cite{mitchelstein2016brecha}, or studied the coverage of the main newspapers on particular events related to a confrontation scenario between government and press \cite{zunino2010cobertura, koziner2013cobertura}.
+On the other hand, the theory hypothesizes how the media affects the audience opinion, in particular, how political coverage and political advertisement shape candidate knowledge among the audience \cite{brians1996campaign, gerber2009does}, or how the coverage given by the media to a particular nation affects people perception about its importance to local political interests \cite{wanta2004agenda}.
+Other works examine the differences between public and journalists preferences \cite{mitchelstein2016brecha}, or study the coverage of the main newspapers on particular events related to a confrontation scenario between government and press \cite{zunino2010cobertura, koziner2013cobertura}.
 
@@
 \par The Chapel Hill investigation also induced other several research directions \cite{mccombs2005look}.
-One of them focus on detecting bias in the media, either by taking into account the number of mentions related  to a preferred political party \cite{lazaridou2016identifying, baumgartner2015all} or by identifying the ideology through the position of the media regards to certain issues or actors \cite{elejalde2018nature, sagarzazu2017hugo}.
+One of them focus on detecting media bias, either by taking into account the number of mentions related  to a preferred political party \cite{lazaridou2016identifying, baumgartner2015all} or by identifying the ideology through the position of the media regards to certain issues or actors \cite{elejalde2018nature, sagarzazu2017hugo}.
 This research line can be linked with the theory of \textit{framing} \cite{guggenheim2015dynamics, tsur2015frame}, which focus on the way the media emphasizes some attributes of an object, while understating others.
-On the other hand, several investigations pay attention to the sources of the media agenda, theory known as \textit{intermedia agenda-setting} \cite{vargo2017networks, harder2017intermedia, guo2017global}, where the competition and the mutual influence between different media is observed.
+On the other hand, several investigations pay attention to the sources of the media agenda, theory known as \textit{intermedia agenda-setting} \cite{vargo2017networks, harder2017intermedia, guo2017global}, where the competition and the mutual influence between different media are observed.
 
@@
 %\par Nonetheless, most of the works cited above follow typical methods of social science research, and fall in what we call a ``static approach": They used to summarize certain issues present in news media and looking for effects in the audience.
-\par Since the irruption of internet, a quantitative analysis based on  the access to big data has been possible.
-For instance, this analysis can take into account the temporal dependence of the media and public attention.
+\par Since the irruption of internet, a quantitative analysis based on  the access to big data became available, as for instance, those who takes into account  temporal dependence of the media and public attention.
 In \cite{soroka2017negativity} it is shown that the newspapers and Twitter have an opposite reaction to the changes of the unemployment rates; in \cite{guggenheim2015dynamics}, the competition of frames about gun control is explored; in \cite{ali2018measuring}, the authors show how fluctuations of Twitter activity in different regions depend on the location of terrorist attacks; and in \cite{russell2014dynamics}, the complex interplay between the social media and the traditional one is followed over time on a set of predefined, but general, issues.
@@
 % Machine Learning
-\par The question about what issues should be selected can be solved by an useful tool employed in the analysis of large documents corpus, but understated in the agenda-setting framework and its derivatives: Unsupervised topic modeling.
+%by an useful tool employed in the analysis of large documents corpus, but understated in the agenda-setting framework and its derivatives:
+
+\par However, a data driven selection of issues can be performed using a tool frequently employed in the analysis of large document corpus: Unsupervised topic modeling. 
 It is an alternative to the dictionary-based analysis, which is the most popular automated analysis approach \cite{guo2016big}, and allows to work with a corpus without a prior knowledge, letting the topics emerge from the data.
@@
 
-\par In this work we propose a novel method in order to study the dynamics of the mass media agenda, which consist of performing an unsupervised topic model on newspapers articles, and studying how the emerging topics evolve with time.
+\par In this work we propose a novel method in order to study the dynamics of the mass media agenda, which consists of performing an unsupervised topic model on newspapers articles, and studying how the emerging topics evolve with time.
 We look also at their correspondence with the audience agenda, by looking both the Google searches and Twitter activity in the studied period. 
@@
 Our work focuses on a quantitative approach which complements the agenda-setting theory describe above, which mainly stands within the framework of first-level agenda setting, but also allows us to face agenda bias and framing.
-We apply this method to study the dynamics of the Argentinian media agenda due to our familiarity with the political background, but as can be seen throughout the work, the methodology implemented is far general and can be easily extended to other data-sets.
+We apply this method to study the dynamics of the Argentinian media agenda due to our familiarity with the political background, but as can be seen throughout the work, the methodology implemented is far general and can be easily extended to other datasets.
 
-\par On the other hand, in recent years new approaches to study social dynamics through several tools taken from statistical physics have proposed mathematical models to explore the interplay between the mass media and society \cite{crokidakis2012effects,gonzalez2012model, moussaid2013opinion, rodriguez2010effects, pinto2016setting}.
-Much of them lack in being contrasted with real data.
-With our work we aim to gain a closer insight on the complex interaction between the media and the public, and provide a quantitative research that would be useful at the time of constructing better and more data-driven models.
+\par On the other hand,  new approaches to study social dynamics coming from statistical physics have proposed mathematical models to explore the interplay between the mass media and society \cite{crokidakis2012effects,gonzalez2012model, moussaid2013opinion, rodriguez2010effects, pinto2016setting}.
+However, much of them lack in being contrasted with real data.
+In this work we are intended to get a closer insight on the complex interaction between the media and the public, and provide a quantitative research in order to construct better and more data-driven models.
 
@@
 \subsection*{The Media Agenda}
-\par In this work we analyze a three-month period of the Argentinian media agenda composed by a corpus of news articles that were published between July 31st, 2017 and November 5th, 2017. 
-The articles come from the politics section of the online editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\'on}, \emph{P\'agina12}, and the news portal, \emph{Infobae}.
-The first two lead the sale of printed editions in \emph{Buenos Aires} city, but \emph{Clar\'in} reaches roughly two times the readers of \emph{La Naci\'on}, and ten times the readers of \emph{P\'agina 12} \cite{IVC}.
+\par We analyze a three-month period of the Argentinian media agenda composed by a corpus of news articles that were published between July 31st, 2017 and November 5th, 2017. 
+The articles come from the political section of the online editions of the Argentinian newspapers \emph{Clar\'in}, \emph{La Naci\'on}, \emph{P\'agina12}, and the news portal, \emph{Infobae}.
+The first two lead the sale of printed editions in \emph{Buenos Aires} city, but \emph{Clar\'in} reaches roughly two times the readers of \emph{La Naci\'on}, and ten times the readers of \emph{P\'agina 12} \cite{IVC}, who was chosen because of its left political orientation.
 On the other hand, \emph{Infobae} has the most visited website, much more than \emph{Clar\'in} and \emph{La Naci\'on} \cite{AlexaAR}.
@@
 \par In order to detect the main topics in the corpus, we perform \emph{non-negative matrix factorization (NMF)} \cite{xu2003document, lee1999learning} on the document-term matrix (\emph{M}).
-A topic is defined to be a group of similar articles which roughly talks about the same subject.
+A topic is defined as a  group of similar articles which roughly talks about the same subject.
 \emph{NMF} is an unsupervised topic model which factorizes the matrix \emph{M} into two matrices \emph{W} and \emph{H} with the property that all three matrices have no negative elements (see eq.(\ref{eq:nmf})).
@@
 Such as the resulting matrix \emph{H} has dimensions of number of documents by $k$ and matrix \emph{W} has dimensions of $k$ per number of terms, the number $k$ is therefore interpreted as the number of topics in the documents and it is a parameter that must be set before the factorization.
-In this work, we arbitrarily set $k=10$. We found this value to be a suitable one based on our knowledge of the corpus.
+In this work, we arbitrarily set $k=10$, based on our knowledge of the corpus.
 Since the factorization of eq.(\ref{eq:nmf}) usually can not be made exactly, it is approximated by minimizing the reconstruction error, i.e.
@@
 
-\par After performing NMF, we represent the time-dependent Media Agenda as a time evolving distribution of topics.
+\par After performing NMF, we represent the time-dependent Media Agenda as a time-evolving distribution of topics.
 We define $W_i(day)$ to be the daily weight of the topic $i$, which is calculated following the eq.(\ref{eq:topic_weight}), where $l(j)$ is the number of words of the document $j$; $h_{ji}$ is the degree of membership of document $j$ on topic $i$; $d_j$ is the date of document $j$; and $\delta$ is the Kronecker delta.
 Providing by the fact that each document vector can have all non-zero components, it is allowed that a document contributes to more than one topic weights.
-In order to reduce noise, we apply a linear filter with a three day wide sliding window, and finally we normalize the temporal profiles in order to describe each newspaper agenda as a distribution over the topics' space, which evolves over time.
+In order to reduce noise, we apply a linear filter with a three day wide sliding window, and finally we normalize the temporal profiles in order to describe each newspaper agenda as a distribution over the topic space, which evolves over time.
 %This last normalization prevent us against the differences in the number of articles that each newspaper publishes.
@@
 
-\par The other side of the Media Agenda is to have some measure of the public interests about its topics, by finally making up what we call the Public Agenda. 
+\par Besides the construction of the Media Agenda it is important to have some measure of the public interests and construct what we call the Public Agenda. 
 To achieve this goal, we take Google and Twitter as proxies of the public interests by looking for the same topics in the same period of time.
-We take advantage of the topic keywords in order to make queries into the \emph{Google Trends} tool and into the advance search tool of Twitter, and therefore to get the relative weight of searches and tweets in each respective platform.
-Therefore we describe the Public Agenda by describing, in an independent way, both the Google and Twitter Agendas. 
+We take advantage of the topic keywords in order to make queries into the \emph{Google Trends} tool and into the advance search tool of Twitter, and therefore we get the relative weight of searches and tweets in each respective platform.
+In this way, the Public Agenda is described, in an independent way, by the Google and Twitter Agendas. 
 In section \textbf{Results} we will give a more detailed description of the keywords involved in their construction.
@@
 \par In fact, one of the key of our work is the representation of the Agendas as time evolving topic distributions, and the association between the different measures that we can derive from them with the social events observed during the period.
-In order to do that, the first measure we emphasize is the concept of \emph{diversity of the attention}.
+In order to do that, we focus in the concept of \emph{diversity of the attention}.
 \emph{Diversity} is a very important variable that must be taken into account when dealing with multiple issues \cite{boydstun2014importance}, due to the fact that it tells us how the attention is distributed across the different topics of discussion.
-As was proposed in \cite{boydstun2014importance}, we take the normalized Shannon entropy as a very suitable way to quantify the diversity within our framework.
-\par The normalized Shannon entropy $H[p]$ referred in eq.(\ref{eq:shannon_entropy}) gives us a measure of how spread is a -discrete- distribution, taking the maximum value of $1$ when all outcomes are equally probable, and $0$ when there is just one possible outcome.
-This last case, or an approximated one, will be of particular interest for us because it tells about a topic which absorbs all the attention either from the Media or the Public, while the former shows an absolutely unbiased interest towards any of the topics.
+As was proposed in \cite{boydstun2014importance}, we use the normalized Shannon entropy to quantify the diversity within our framework.
+\par The normalized Shannon entropy $H[p]$ referred in eq.(\ref{eq:shannon_entropy}) gives us a measure of how spread is a -discrete- distribution, taking the maximum value of $1$ when all outcomes are equally probable (as in the case of having a diverse agenda), and $0$ when there is just one possible outcome (when one topic of discussion dominates the agenda).
+%This last case, or an approximated one, will be of particular interest for us because it tells about a topic which absorbs all the attention either from the Media or the Public, while the former shows an absolutely unbiased interest towards any of the topics.
 
@@
 
-\par While the diversity is a property of each distribution, a natural question that arises from comparing different distributions is how similar they are.
-For instance, we will be particularly interested in measuring the similarity between the Media and Public Agendas, because those dates when the similarity is low tell us about distant interests of the media and its audience.
-We proposed here to measure the similarity between distributions by the use of the Jensen-Shannon distance ($JSD$). 
+\par While the diversity is a property of each distribution, a natural question that arises when comparing different distributions is how similar they are.
+For instance, we will be particularly interested in measuring the similarity between the Media and Public Agendas, because lower values would indicate distant interests between the media and its audience.
+We measure the similarity between distributions via the Jensen-Shannon distance ($JSD$). 
 When the similarity of the distributions is low, the distance between them is high.
@@
 
-\par As was mentioned before, once the concepts of diversity and distance between distributions were defined, we are particularly interested in those dates when these concepts take extreme values: When the diversity is low, we know that a topic is absorbing much of the attention of any of the Agendas; on the other hand, when the distance between two distributions is high, we can conclude that they have distant interests.
+\par As was mentioned before, once the concepts of diversity and distance between distributions were defined, we are particularly interested in those dates when these measures take extreme values: Lower values of diversity indicate a topic which is absorbing much of the attention of any of the Agendas; on the other hand, when the distance between two distributions is high, we can conclude that they have distant interests.
 However, we still lack the definition of what a low diversity or a high distance are. 
@@
 The meaning of the topics or macro-topics is contextualized in the \textbf{Supplementary Material}.
-\par Finally, by following the procedure described in the previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, in both its Google and Twitter derivations, as time evolving distributions in a space of seven topics.
+\par Finally, by following the procedure described in the previous section, we construct the \textbf{Media Agenda (MA)} and the \textbf{Public Agenda (PA)}, in both its Google and Twitter derivations, as time-evolving distributions in the space of seven topics.
 
@@
 Is the degree of dominance of a given topic in the Media Agenda reflected in the Public Agenda?
-In order to answer such kind of questions we quantify the diversity of the agendas through the normalized Shannonentropy $H$, which was introduced in section \textbf{Material and Methods}.
+In order to answer such kind of questions we quantify the diversity of the agendas through the normalized Shannon entropy $H$, which was introduced in section \textbf{Material and Methods}.
 \par In figure \ref{fig:shannon_entropy_agendas} we can see the value of $H$ as a function of time for the three agendas.
@@
 We focus on three points that seem to be relevant enough.
-In all cases, the topic distributions at that particular dates displayed by  the radar plots show that the increment in the distance between agendas is due to a greater interest of public opinion in the \emph{Missing person} topic.
+In all cases, the topic distributions at these days displayed show that the increment in the distance between agendas is due to a greater interest of public opinion in the \emph{Missing person} topic.
 
@@
 we can't say, for instance, that in this case the Public Agenda set the Media Agenda.
-Finally, it is important to say that the Jensen-Shannon distance, in conjunction with the measurement of agenda diversity given by the Shannon entropy, give an insight of independent behavior, in certain particular dates,  of the public and the media.
+Finally, it is important to say that the Jensen-Shannon distance, together with the measurement of agenda diversity given by the Shannon entropy, give an insight of independent behavior, in certain particular dates,  of the public and the media.
 Its identification can be a starting point to study the media reaction to a change in audience interests.
@@
 
-\par In other to detect significant bias coverage of a given newspaper, we again calculate the Jensen-Shannon distance, but between the individual newspapers agenda and the Media Agenda.
+\par In order to detect significant bias coverage of a given newspaper, we again calculate the Jensen-Shannon distance, but between the individual newspapers agenda and the Media Agenda.
 Note that this is the distance between the distributions of figure \ref{fig:news_agenda} and the top panel of figure \ref{fig:all_agenda}. 
@@
 We detect three points as outliers, although we finally disregarded point \textbf{(b)} due to a lack of  information of newspaper \emph{Infobae} in that period. 
-The other two points corresponds to differences between \emph{P\'agina 12} and the other newspapers and correspond to differences in the coverage of the topic \emph{Missing person}.
+The other two points correspond to differences between \emph{P\'agina 12} and the other newspapers and correspond to differences in the coverage of the topic \emph{Missing person}.
 
-\par Point \textbf{(a)} corresponds  to the first news the disappearance of Santiago Maldonado, reported by \emph{P\'agina 12} before the primary elections, and point \textbf{(c)} corresponds to  the two months' rally after the disappearance  (see \textbf{Supplementary Material}).
+\par Point \textbf{(a)} corresponds  to the first news of the disappearance of Santiago Maldonado, reported by \emph{P\'agina 12} before the primary elections, and point \textbf{(c)} corresponds to  the two months rally after the disappearance  (see \textbf{Supplementary Material}).
 Another singularity of point \textbf{(c)} corresponds to a greater coverage of \emph{P\'agina 12} in the topic \emph{Social leader} while the other media outlets seem to be more interested in the topic \emph{Former Vice-President}.
@@
 \par The greater coverage in the topic \emph{Missing person} by \emph{P\'agina 12} is even more clear if we inspect the temporal profile of the topic and compare the coverage given by each newspaper.
-A difference in the coverage is what it is called \emph{coverage bias} \cite{dallmann2015media}.
+Differences in the coverage are due to  \emph{coverage bias} \cite{dallmann2015media}.
 In figure \ref{fig:topics_temporal_profiles} we show the temporal profile of the topic \emph{Missing person} (panel (a)) and the topic \emph{Former Planning minister} in panel (b), as an example where the behavior is the opposite, as can be seen below.
@@
 For example, we can quantify this difference calculating  the median of the signals.
-If we focus on the period between July 31st and August 27th, the median of the topic relative weight in \emph{P\'agina 12} is roughly 0.14 and this is statistically significantly larger ($p < 10^{-7}$) than other medians, which are lower than 0.05.
-Analyzing the same period, but in panel (b), we again can show that the median in \emph{P\'agina 12}, which is roughly 0.01, is lower than the others, which oscillate around 0.05 ($p<10^{-3}$).
-This quantification is proposed as method of studying coverage bias in the context of the methodology implemented in our work.
+If we focus on the period between July 31st and August 27th, the median of the topic relative weight in \emph{P\'agina 12} agenda is roughly 0.14 and this is statistically significantly larger ($p < 10^{-7}$) than other medians, which are lower than 0.05.
+Analyzing the same period, but in panel (b), we  can show again that the median in \emph{P\'agina 12} agenda, which is roughly 0.01, is lower than the others, which oscillate around 0.05 ($p<10^{-3}$).
+This quantification is proposed as a method of studying coverage bias in the context of the methodology implemented in our work.
 
@@
 Based on the data analyzed above, the behavior of the Media and Public Agendas, either by looking at Google Trends or Twitter, shows periods of strong similarity, for instance in the presence of an unexpected event, and periods of disengagement.
-Therefore, it is not trivial to establish a causal relationship between the agendas, specially when they are represented as evolving in time topic distributions as we did in this work. 
+Therefore, it is not trivial to establish a causal relationship between the agendas, specially when they are represented as time.evolving topic distributions as we did in this work. 
 However, it is possible to discuss agenda-setting if we focus on a single topic.
@@
 \begin{itemize} 
-\item It caused a great impact in both the media and the audience
+\item It caused a great impact in both the media and the audience;
 \item  its coverage fully deploys along the time lapse analyzed in this manuscript (see \textbf{Supplementary Material}).
@@
 After that event, the media increases its coverage about the topic.
-Is this a case of reverse agenda-setting \cite{russell2014dynamics}, when a discussion in a given social network triggers the interest of the media? 
-In order to understand this behaviour, we calculate the cumulative coverage of the \emph{Missing Person} topic, which is displayed in figure \ref{fig:Maldonado_setagenda} panel (c).
+
+In order to understand this behaviour we calculate the cumulative coverage of the \emph{Missing Person} topic, which is displayed in figure \ref{fig:Maldonado_setagenda} panel (c).
 The cumulative coverage of the \emph{Missing Person} topic is defined to be the numerical integration between the initial date and the current date, of the topic temporal profile in each media outlets (figure \ref{fig:topics_temporal_profiles}) and in the Google and Twitter Agendas (which can be seen in figure \ref{fig:Maldonado_setagenda} panel (a)).
 This quantity shows us how the media and public attention have been accumulated since the first events.
-\par The figure \ref{fig:Maldonado_setagenda} panel (c) shows that it is not as simple as to say that the Public Agenda sets the Media one: 
-Before the \emph{Missing Person} topic becomes prominent to the public, \emph{P\'agina 12} was leading the coverage of this topic with respect to the rest of the media.
+
+\par The figure \ref{fig:Maldonado_setagenda} panel (c) shows a complex agenda-setting dynamics within the \emph{Missing Person} topic: The least sold newspaper (\emph{P\'agina 12}) triggered a public debate  via a positive feedback mechanism reinforced by reiterative Google searches and discussions in social networks.
+Due to this increasing public interest, the rest of the media were forced to pay attention to this subject and finally, the topic becomes also prominent to the Media Agenda.
+
+%\par The figure \ref{fig:Maldonado_setagenda} panel (c) shows that it is not as simple as to say that the Public Agenda sets the Media one: Before the \emph{Missing Person} topic becomes prominent to the public, \emph{P\'agina 12} was leading the coverage of this topic with respect to the rest of the media.
 It is important to recall that \emph{P\'agina 12} is the newspaper with fewer readers among the analyzed ones.
@@
 Due to this increasing public interest, the rest of the media ought to pay attention to this subject and finally, the topic becomes also prominent to the Media Agenda.
-\par Beside the analysis performed above, there are two important facts that must be mentioned about the \emph{Missing Person} topic: First, the disappearance of a person is a very sensitive theme for the Argentinian society, which can explain why this particular topic triggered the audience interest; and second, there were political reasons why \emph{P\'agina 12} was particularly interested in covering this topic since the beginning, while the rest of the media did not until the topic was prominent to the Public Agenda (see \textbf{Supplementary Material}).
-\par The analysis of the cummulative coverage allows us to face the question about causality at least in a qualitative way.
+
+\par Beside the analysis performed above, there are two important facts that must be mentioned about the \emph{Missing Person} topic: First, the disappearance of a person is a very sensitive issue in the Argentinian society, which can explain why this particular topic triggered the audience interest; and second, there were political reasons why \emph{P\'agina 12} was particularly interested in covering this topic since the beginning, while the rest of the media did not until the topic was prominent to the Public Agenda (see \textbf{Supplementary Material}).
+\par The analysis of the cumulative coverage allows us to face the question about causality at least in a qualitative way.
 However, it was possible to highlight the complex feedback dynamics that take place between public and media agendas.
@@
 
-\par The mass media play a fundamental role in opinion formation and therefore, it's of vital importance to have an accurate  quantitative description of the Media  and Public Agenda and their relationship in the framework of agenda-setting theory.
-In this work, through the implementation of a topic detection algorithm we describe the Media Agenda as a distribution which evolves in time and which is defined in a topic space which emerges from the analysis of the corpus.
+\par The mass media plays a fundamental role in opinion formation and therefore, it’s of vital importance to have an accurate quantitative description of the Media and Public Agenda and their relationship in the framework of agenda-setting theory.
+In this work, through the implementation of a topic detection algorithm we describe the Media Agenda as a distribution which evolves with time and which is defined in a topic space which emerges intrinsically from the corpus.
 This gave us an insight of how we can construct and follow the audience interests, i.e the Public Agenda, in order to compare with the media interests.
 
-\par Given the Agendas, we found that the Public one is usually less diverse than the Media, showing that when there is a very attractive topic, the audience focuses on this one, meanwhile the media keep certain degree of diversity.
-On the other hand, the measurement of distances between agendas can be employed to rapidly detect those periods when the public may have an independent behavior respect to the media.
-The methodology implemented here also allowed us to detect coverage bias in newspapers and gave us a first approximation in the theory of framing.
+\par This approach with newspaper, Twitter and Google trends data, lets us understand that the Public Agenda is usually less diverse than the Media Agenda.
+Specifically, it is shown that when there is a very attractive topic, the audience naturally focuses only on this one.
+On the other hand, the media keeps a certain degree of diversity and a wider range of topics.
+
+\par Interestingly, we show how the measurement of distances between agendas can be employed to rapidly detect those periods when the public may have an independent behaviour respect to the media and also when it does not.
+The ``Missing person" topic analysis, presented in figure  \ref{fig:Maldonado_setagenda}, shows concrete evidence of a complex dynamics agenda-setting case.
+Therefore, this work depicts a methodology which can be used in order to understand who sets the agenda: If it is a media outlet or the society.
+[SEBAS ....
+agregar alguna linea de texto de porque esto es muy bueno]
+
+\par Moreover, the methodology implemented here also allowed us to detect coverage bias in newspapers and gave us a first approximation in the theory of framing.
+The implementation of the word clouds and topic detection algorithms, which were described in this work, allow us to clearly observe the huge differences between any pair of newspapers.
+In particular, it is shown in figures \ref{fig:news_agenda} and \ref{fig:topics_temporal_profiles}  how \emph{Clarín}, \emph{La Nación} and \emph{Infobae}, that share a similar political view with the current government, focused on the former president \emph{Cristina Fern\'andez de Kirchner}, whereas \emph{P\'agina 12}, the newspaper that  criticizes and condemns the government, focused on the denounced repression that \emph{Santiago Maldonado} suffered from the police.
+
 \par We hope that some of the elements studied here will give us insights at the time of proposing a mathematical model about the interaction between mass media and audience.
-Future works may include a more systematic study and its extension to international media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitative analysis about causality.
+Future works may include a more systematic study and its extension to international media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitative analysis about causality .
 
@@
   We thank Dr. A. Chernomoretz, Dr. M. Otero, Dra. V. Semeshenko, and Dr. M. Trevis\'an for bringing us a critical revision of the article.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-11 bmc_article.tex
Cambios finales

@@
 
-\par The mass media plays a fundamental role in opinion formation and therefore, it’s of vital importance to have an accurate quantitative description of the Media and Public Agenda and their relationship in the framework of agenda-setting theory.
+\par The mass media plays a fundamental role in opinion formation and therefore, it is of vital importance to have an accurate quantitative description of the Media and Public Agenda and their relationship in the framework of agenda-setting theory.
 In this work, through the implementation of a topic detection algorithm we describe the Media Agenda as a distribution which evolves with time and which is defined in a topic space which emerges intrinsically from the corpus.
@@
 
-\par This approach with newspaper, Twitter and Google trends data, lets us understand that the Public Agenda is usually less diverse than the Media Agenda.
+\par This approach with newspaper, Twitter and Google trends data, let us understand that the Public Agenda is usually less diverse than the Media Agenda.
 Specifically, it is shown that when there is a very attractive topic, the audience naturally focuses only on this one.
@@
 The ``Missing person" topic analysis, presented in figure  \ref{fig:Maldonado_setagenda}, shows concrete evidence of a complex dynamics agenda-setting case.
-Therefore, this work depicts a methodology which can be used in order to understand who sets the agenda: If it is a media outlet or the society.
-[SEBAS ....
-agregar alguna linea de texto de porque esto es muy bueno]
+Therefore, this work depicts a very general methodology which can be used in order to understand who sets the agenda: If it is the media or the society. 
+The generality of our method allows to easily face up the agenda-setting issue in other datasets.
 

### 2018-09-11 bmc_article.tex
Cambios en el formato de Author Contribution

@@
 \section*{Author's contributions}
-P.B.
-conceived the study.
-S.P.
-collected and analysed most of the data.
-F.A.
-collected Twitter data; F.A., P.B, and S.P.
-interpreted the data and prepared the manuscript.
-P.B.
-and C.O.D  give the final approval of the version to be published.
+PB conceived the study.
+SP collected and analysed most of the data.
+FA collected Twitter data.
+FA, PB, and SP interpreted the data and prepared the manuscript.
+PB and COD  give the final approval of the version to be published.
 

### 2018-09-11 bmc_article.tex
Algo en una de las caption

@@
 It can be seen also in figure (b), where the discrete differences were computed.
-With the computing of the cumulative coverage of figure \ref{fig:topics_temporal_profiles} and figure (a), represented as a bump chart in figure (c), we suggest that the topic was first set by \emph{P\'agina 12} and then the audience's interest cause the coverage of the other media.
+With the computing of the cumulative coverage of figure \ref{fig:topics_temporal_profiles} and figure (a), represented as a bump chart in figure (c), we suggest that the topic was first set by \emph{P\'agina 12} and then the audience interest causes the coverage of the rest of the media.
 }

### 2018-09-11 bmc_article.tex
Version para subir sin comentar las figuras

@@
 \usepackage{graphicx}
+\usepackage{endnotes}
 
@@
 \endlocaldefs
+
+\let\footnote=\endnote
 
@@
 We found that the Public Agenda is less diverse than the Media Agenda, especially when there is a very attractive topic and the audience naturally focuses only on this one.
-Using the same methodology we  detect coverage bias in newspapers and have a first approximation to the theory of framing.
+Using the same methodology we  detect coverage bias in newspapers and framing.
 Finally it was possible to identify a complex agenda-setting dynamics within a given topic where the least sold newspaper  triggered a public debate  via a positive feedback mechanism with social networks discussions which install the issue in the Media Agenda.\\
@@
 \begin{keyword}
-\kwd{agenda-setting}
+\kwd{mass media influence}
 \kwd{opinion formation}
 \kwd{topic detection}
-\kwd{mass media influence}
+\kwd{agenda-setting}
 \end{keyword}
@@
 
-\par We provide here a more detailed explanation of the topics discussed within this work. The topics belong to the period between July 31th and November 5th, 2017.
-The ideology of the media in Argentina expresses the highly polarized political climate observed in Argentinian society.
-During the administration of \emph{Cristina Fern\'andez de Kirchner} (2007-2015), the government maintained a conflict with several news organizations.
-It led the media such as \emph{Clar\'in}, \emph{La Naci\'on} and the news portal \emph{Infobae} to be very critics of the \emph{Fern\'andez}'s administration, emphasizing the allegations of corruption related to it, as can be seen in the importance given to the topics \emph{Former Planning minister} and \emph{Former Vice-President}.
-On the other hand, \emph{P\'agina 12} has an opposite ideological inclination, supporting the former administration of \emph{Cristina Kirchner} and therefore being very critical with the current \emph{Mauricio Macri}'s administration, doing special emphasis on issues related to human rights, as can be again observed in the coverage given to the topics \emph{Social leader} and \emph{Missing person}.
+\par Here we provide the context of the the discussed topics  within this work. The news belong to the period between July 31th and November 5th, 2017.
+The bias of the different media outlets reflect the highly polarized political climate observed in Argentinian society.
+During the administration of \emph{Cristina Fern\'andez de Kirchner} (2007-2015), the government confront with several news organizations.
+It led to media outlets such as \emph{Clar\'in}, \emph{La Naci\'on} and the news portal \emph{Infobae} to be very critical of the \emph{Fern\'andez}'s administration, emphasizing the allegations of corruption related to it, as can be seen in the importance given to the topics \emph{Former Planning minister} and \emph{Former Vice-President}.
+On the other hand, \emph{P\'agina 12} has an opposite ideological bias, supporting the former administration of \emph{Cristina Kirchner} and therefore being very critical with the current \emph{Mauricio Macri}'s administration, doing special emphasis on issues related to human rights, as can be again observed in the coverage given to the topics \emph{Social leader} and \emph{Missing person}.
 
@@
 \subsubsection*{Current President}
-\par \emph{Mauricio Macri} is the current Argentinian President since December 2015. 
-Most of the articles in political sections are logically devoted to him under different contexts.
-However, it is important to point out that during the analyzed period, and specially after the general elections of October 22nd, 2017, a controversial labour reform promoted by the government was being discussed.
+\par \emph{Mauricio Macri} is the current Argentinian President since December 2015 and this topic is mainly composed of articles related to his administration, specially after the general elections of October 22nd, 2017, when a labour reform promoted by the government was being discussed.
 
 \subsubsection*{\emph{Missing Person}}
-\par \emph{Santiago Maldonado} vanished on August 1st, 2017 after a minor clash between the Gendarmerie (Border Guards) and a group of Mapuches (Patagonian native population), which recognize themselves as the original population of an area in the Patagonia.
+\par \emph{Santiago Maldonado} dissapear on August 1st, 2017 after a minor clash between the Gendarmerie (Border Guards) and a group of Mapuches (Patagonian native population), which recognize themselves as the original population of an area in the Patagonia.
 Since that event, the \emph{Mauricio Macri}'s administration was accused by several people as the responsible for a \textbf{forced disappearance}. 
@@
 
-\subsubsection*{\emph{Former Planning minister} and \emph{Former Vice-President}}
+\subsubsection*{\emph{Former Planning minister} and \emph{Former Vice-President} (Corruption of former administration)}
 
@@
 
-\subsubsection*{\emph{Social leader} and \emph{Prosecutor's death}}
+\subsubsection*{\emph{Social leader}}
 
@@
 She faces allegations of embezzlement related to government funding for housing projects managed by T\'upac Amaru, her social organization.
-Sala accused the government of ``violating her human rights", and several people think that she is a political prisoner of the \emph{Mauricio Macri}'s administration.
+Sala accused the government of ``violating her human rights", and several people think that she is a political prisoner.
+
+\subsubsection*{\emph{Prosecutor's death}}
 
@@
 
-\par In this section we apply other topic model, Latent Dirichlet Allocation \cite{blei2003latent} (LDA), to our corpus and compare its results with the shown in this paper.
-Due to the increasingly use of LDA, we think that a few words about the performance of LDA in our work is necessary.
+\par In this section we compare the results of applying a different topic model to our corpus.
+The reference is Latent Dirichlet Allocation \cite{blei2003latent} (LDA) which is one of the more used topic models in last years.
 
-\par Naturally the topics found with LDA may not coincide with the NMF ones.
-However, one expects that the corpus under study displays some degree of  robustness  when considering different topic models.
+\par Even though the topics found with LDA may not coincide with the NMF ones, it is expected that the corpus under study displays some degree of  robustness  when considering different topic models.
 On the other hand, as was discussed in \cite{o2015analysis}, NMF can be a more suitable topic modeling method in certain domains, in the way that it produces more coherent topics, while LDA tends to return higher levels of generality and redundancy.
-Topic coherence is defined as the semantic interpretability of the terms used to describe a particular topic, although the coherence of a topic may depend on the end user's expectations.
+Topic coherence is defined as the semantic interpretability of the terms used to describe a particular topic, although the coherence of a topic may depend on the user's expectations.
 
-\par We define a simple coherence measure defined in equation \ref{eq:topic_coherence}, where $d_{ij}$ is the number of documents where the term $i$ and term $j$ appear simultaneously, and $d_{x}$ is the number of documents where appears the term $x$.
+\par We define a simple coherence measure defined in eq.
+(\ref{eq:topic_coherence}), where $d_{ij}$ is the number of documents where the term $i$ and term $j$ appear simultaneously, and $d_{x}$ is the number of documents where appears the term $x$.
 The summation is over the $N$ top terms of the topic.
@@
 
-\par Nevertheless, LDA returns other topics which can not be directly associated, some of them composed of very general words. 
-By keeping only those topics which can be associated with NMF and re-defining the Media Agenda over this topic space with reduced dimension, we observed similar results by both methods.  
-The same procedure is proposed in absence of an alternative topic model to which make the comparison: Keep only those topics easily interpretable and define the Agendas over this reduced space.
+\par The seven main topics obtained with LDA are practically the same as those found with NMF.
+Only minor differences, related to other topics composed of very general words were found.
+This comparison shows us that the Agendas obtained following both methods are similar.
 
@@
 
+\section*{Abbreviations}
+Media Agenda (MA).
+Public Agenda (PA).
+Google Trends (GT).
+Twitter (Tw).
+Clar\'in (Cl).
+La Naci\'on (LN).
+P\'agina 12 (P12).
+Infobae (Inf).
+Non-negative matrix factorization (NMF).
+Latent Dirichlet Allocation (LDA).
+
+\section*{Availability of data and material}
+The data that support the findings of this study are available from Clar\'in at https://www.clarin.com/, La Naci\'on at https://www.lanacion.com.ar/, P\'agina 12 at https://www.pagina12.com.ar/, and Infobae at https://www.infobae.com/, but restrictions apply to the availability of these data and so are not publicly available.
+Google Trends and Twitter data are respectively openly available at https://trends.google.com/ and https://twitter.com/.
+
 \section*{Competing interests}
@@
 
+ \section*{Funding}
+P. Balenzuela was supported by grants PICT 201-0215 from Agencia Nacional de Promoción Científica y Tecnológica and UBACyT 20020170100356BA from University of Buenos Aires.
+F. Albanese and S. Pinto were supported by Conicet fellowships.
+
 \section*{Author's contributions}
 PB conceived the study.
-SP collected and analysed most of the data.
+SP collected and analyzed most of the data.
 FA collected Twitter data.
@@
 
+\theendnotes
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-11 bmc_article.tex
Algunas minimas correciones

@@
 The implementation of the word clouds and topic detection algorithms, which were described in this work, allow us to clearly observe the huge differences between any pair of newspapers.
-In particular, it is shown in figures \ref{fig:news_agenda} and \ref{fig:topics_temporal_profiles}  how \emph{Clarín}, \emph{La Nación} and \emph{Infobae}, that share a similar political view with the current government, focused on the former president \emph{Cristina Fern\'andez de Kirchner}, whereas \emph{P\'agina 12}, the newspaper that  criticizes and condemns the government, focused on the denounced repression that \emph{Santiago Maldonado} suffered from the police.
+In particular, it is shown in figures \ref{fig:news_agenda} and \ref{fig:topics_temporal_profiles}  how \emph{Clar\'in}, \emph{La Naci\'on} and \emph{Infobae}, that share a similar political view with the current government, focused on the former president \emph{Cristina Fern\'andez de Kirchner}, whereas \emph{P\'agina 12}, the newspaper that criticizes and condemns the government, focused on the denounced repression that \emph{Santiago Maldonado} suffered from the police.
 
 \par We hope that some of the elements studied here will give us insights at the time of proposing a mathematical model about the interaction between mass media and audience.
-Future works may include a more systematic study and its extension to international media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitative analysis about causality .
+Future works may include a more systematic study and its extension to international media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitative analysis about causality.
 
@@
   We thank Dr. A. Chernomoretz, Dr. M. Otero, Dra. V. Semeshenko, and Dr. M. Trevis\'an for bringing us a critical revision of the article.
+
+\theendnotes
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\theendnotes
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-11 bmc_article.tex
Para subir de a poco

@@
 
-%\def\includegraphic{}
-%\def\includegraphics{}
-\usepackage{graphicx}
+\def\includegraphic{}
+\def\includegraphics{}
+%\usepackage{graphicx}
+
 \usepackage{endnotes}
+\let\footnote=\endnote
 
@@
 \endlocaldefs
-
-\let\footnote=\endnote
 
@@
 
-%hen there is a very attractive topic, the audience naturally focuses only on this one
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%\subsection*{Agenda Setting Theory}
-
 \par One of the challenges in  complex social system research is to understand the ecosystem of information flow and opinion formation. 
-%Within this framework, many ingredients can be parts of different mechanisms of social influence. 
 A major role within this ecosystem is played by the mass media outlets, which are massively used as sources of information.
@@
 In this scenario, it becomes essential to understand the influence of mass media in a given social group.
-
-% Agenda Setting Theory
 \par The influence of the media on public opinion was first explored by the social sciences. 
@@
 
-%during the former administration of Argentinian president \emph{Cristina Fern\'andez de Kirchner} (from 2007 to 2015), where the government started to confront with news organizations that were critical to its management \cite{mitchelstein2017information}.
-
 \par The Chapel Hill investigation also induced other several research directions \cite{mccombs2005look}.
@@
 On the other hand, several investigations pay attention to the sources of the media agenda, theory known as \textit{intermedia agenda-setting} \cite{vargo2017networks, harder2017intermedia, guo2017global}, where the competition and the mutual influence between different media are observed.
-
-%New trends in agenda-setting theory propose to represent ideological aspects or issues emphasized as networks like mind maps, and the basic idea is the comparison between media's knowledge representative network with its counterpart in the audience \cite{guo2012application, vu2014exploring}.
-
-%\par Nonetheless, most of the works cited above follow typical methods of social science research, and fall in what we call a ``static approach": They used to summarize certain issues present in news media and looking for effects in the audience.
 \par Since the irruption of internet, a quantitative analysis based on  the access to big data became available, as for instance, those who takes into account  temporal dependence of the media and public attention.
@@
 These are usually  selected by the researcher and use to reflect general subjects, such as ``health" or ``gun control".
-
-% Machine Learning
-%by an useful tool employed in the analysis of large documents corpus, but understated in the agenda-setting framework and its derivatives:
-
 \par However, a data driven selection of issues can be performed using a tool frequently employed in the analysis of large document corpus: Unsupervised topic modeling. 
@@
 In order to reduce noise, we apply a linear filter with a three day wide sliding window, and finally we normalize the temporal profiles in order to describe each newspaper agenda as a distribution over the topic space, which evolves over time.
-%This last normalization prevent us against the differences in the number of articles that each newspaper publishes.
 
@@
 \par The normalized Shannon entropy $H[p]$ referred in eq.(\ref{eq:shannon_entropy}) gives us a measure of how spread is a -discrete- distribution, taking the maximum value of $1$ when all outcomes are equally probable (as in the case of having a diverse agenda), and $0$ when there is just one possible outcome (when one topic of discussion dominates the agenda).
-%This last case, or an approximated one, will be of particular interest for us because it tells about a topic which absorbs all the attention either from the Media or the Public, while the former shows an absolutely unbiased interest towards any of the topics.
 
@@
 
-%\par The figures introduced above show not only the topics and their differences between the Agendas, but also the dynamics of the topics.
-For instance, we can see in the radar plot of figure \ref{fig:topics_wordclouds}, a greater interest of the audience in the topic \emph{Missing person} than the Media, or inversely in the topic \emph{Prosecutor's death}, at least in the analyzed time-lapse.
-We can also observe a great similarity between \textbf{GT} and \textbf{Tw} agendas which both are different faces of the Public Agenda.
-
 \subsection*{A quantitative description of the Agendas}
@@
 
-\par % It is important to notice that it is our interpretation of the data based on the knowledge of the context, and  we are not measuring causality between Agendas (we will say a few words about it in section \ref{sec:who_sets}), i.e.
-we can't say, for instance, that in this case the Public Agenda set the Media Agenda.
-Finally, it is important to say that the Jensen-Shannon distance, together with the measurement of agenda diversity given by the Shannon entropy, give an insight of independent behavior, in certain particular dates,  of the public and the media.
+\par Finally, it is important to say that the Jensen-Shannon distance, together with the measurement of agenda diversity given by the Shannon entropy, give an insight of independent behavior, in certain particular dates,  of the public and the media.
 Its identification can be a starting point to study the media reaction to a change in audience interests.
@@
 
-%\par The figure \ref{fig:Maldonado_setagenda} panel (c) shows that it is not as simple as to say that the Public Agenda sets the Media one: Before the \emph{Missing Person} topic becomes prominent to the public, \emph{P\'agina 12} was leading the coverage of this topic with respect to the rest of the media.
-It is important to recall that \emph{P\'agina 12} is the newspaper with fewer readers among the analyzed ones.
-This fact leads to a complex agenda-setting dynamics within the \emph{Missing Person} topic: The media outlet with less contribution in the Media Agenda construction, can still put in public debate a topic of its interest.
-As the audience becomes more concerned about this topic, it is amplified by both reiterative Google searches and discussions in social networks.
-Due to this increasing public interest, the rest of the media ought to pay attention to this subject and finally, the topic becomes also prominent to the Media Agenda.
-
 \par Beside the analysis performed above, there are two important facts that must be mentioned about the \emph{Missing Person} topic: First, the disappearance of a person is a very sensitive issue in the Argentinian society, which can explain why this particular topic triggered the audience interest; and second, there were political reasons why \emph{P\'agina 12} was particularly interested in covering this topic since the beginning, while the rest of the media did not until the topic was prominent to the Public Agenda (see \textbf{Supplementary Material}).
@@
 However, it was possible to highlight the complex feedback dynamics that take place between public and media agendas.
-%There are different metrics that would help in this question, such as Granger causality or correlation by sliding windows.
-We think that this analysis must be performed with extreme care since the acquirement of the data.
-With this work we aimed to provide a quantitative characterization of the behavior of the Media and the Public but not to establish direction of causation, which we hope this to be the core of future ones.
 
@@
 \begin{figure}[h!]
-\includegraphics[width = \textwidth]{Fig1.pdf}
+%\includegraphics[width = \textwidth]{Fig1.pdf}
 \caption{\textbf{Radar plots of the Media and Public Agendas represented by the ten topic (then collapsed to seven) distribution and their corresponding word clouds.} The Public Agenda is represented both by Google Trends (GT) and Twitter (Tw).
@@
 \begin{figure}[h!]
-\includegraphics[width = \textwidth]{Fig2.pdf}
+%\includegraphics[width = \textwidth]{Fig2.pdf}
 \caption{\textbf{Bump graph of the time-dependent Media (MA) and Public Agendas extracted from Google Trends (GT) and Twitter (Tw)}.
@@
 \begin{figure}[h!]
-\includegraphics[height=0.7\textheight]{Fig3.pdf}
+%\includegraphics[height=0.7\textheight]{Fig3.pdf}
 \caption{\textbf{Shannon entropy (H) as a measure of agenda diversity.} The Public Agenda shows a less diverse behavior than the Media Agenda as can be seen in the top figure.
@@
 \begin{figure}[h!]
-\includegraphics[height = 0.7\textheight]{Fig4.pdf}
+%\includegraphics[height = 0.7\textheight]{Fig4.pdf}
 \caption{\textbf{Jensen-Shannon distance between the Media and Public Agendas as a function of time} (with upper inner fences pointed out).
@@
 \begin{figure}[h!]
-\includegraphics[width = \textwidth]{Fig5.pdf}
+%\includegraphics[width = \textwidth]{Fig5.pdf}
 \caption{\textbf{Bump charts of newspaper agendas and radar plot of the average distributions.} The figure shows, in a qualitative way, the bias in the different newspaper agendas.
@@
 \begin{figure}[h!]
-\includegraphics[width = \textwidth]{Fig6.pdf}
+%\includegraphics[width = \textwidth]{Fig6.pdf}
 \caption{\textbf{Jensen-Shannon distance between the newspaper agendas and the Media Agenda as a function of time}.
@@
 \begin{figure}[h!]
-\includegraphics[width = \textwidth]{Fig7.pdf}
+%\includegraphics[width = \textwidth]{Fig7.pdf}
 \caption{\textbf{Relative weight of the topics (a) \textit{Missing person}, and (b) \textit{Former Planning Minister}, and their corresponding word clouds of frequent newspaper keywords}.
@@
 \begin{figure}[h!]
-\includegraphics[width = \textwidth]{Fig8.pdf}
+%\includegraphics[width = \textwidth]{Fig8.pdf}
 \caption{\textbf{Non-trivial agenda interplay in the Missing person topic.}
@@
 \begin{figure}[h!]
-\includegraphics[scale = 0.3]{FigA2.pdf}
-\includegraphics[scale = 0.3]{FigA1.pdf}
+%\includegraphics[width = \textwidth]{Fig9.pdf}
 \caption{Temporal profiles of topics \emph{Elections} (left) and \emph{Missing Person} (right) for both LDA and NMF. All the topics found by applying NMF have a highly correlated counterpart in LDA.} 
